### 2013-08-12 natphys/hedpc_natphys.tex
thomas version

%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
%\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}  % for review and submission
%\documentclass[aps,prl,preprint]{revtex4-1}  % for double-spaced preprint
\documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}

%% Packages
\usepackage{graphicx}  %figures
\usepackage{subfigure} %subfigures
\usepackage{amssymb}   %math
\usepackage{upgreek}   %non-italic greek letters
\usepackage[utf8]{inputenc} %Umlaute

%% hyphenation settings
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

%% New commands
\newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}}
\newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}

%% ----------------------------------------------------------------------------------------------------------------
\begin{document}

\title{X-ray phase-contrast imaging at 100~keV}

\author{T.~Thüring}
  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
  \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
\author{M.~Abis}
  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
  \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
\author{Z.~Wang}
  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
\author{C.~David}
  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
\author{M.~Stampanoni}
  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
  \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}

\date{\today}

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
Phase contrast imaging with X-rays is an exciting field that reveals new insights into material properties by providing access to a complementary physical contrast mechanism. Phase sensitive imaging in the high energy range of hard X-rays, i.e. between $80$ and $150 \unit{keV}$ is still largely unexplored, as the current methods typically entail severe technical challenges. With a novel approach, we demonstrate phase contrast as well as dark-field contrast imaging on laboratory systems with low-brilliance X-ray sources in the entire diagnostic energy range. A phase-contrast technique at such high energies is of particularly high scientific and industrial interest as it would vastly expand the range of applications, for instance, by the examination of materials of high density or thickness. The approach includes a new technique for the grating manufacturing in Talbot-Lau interferometry. Firstly, the approach breaks the current limits of achievable grating aspect ratios, which has been a key issue for a long time in the past. Secondly, it solves the intrinsic reduction of the field of view which occurs for gratings with such high aspect ratios. Using an imaging arrangement based on a conventional X-ray tube, phase and dark-field-contrast imaging at $100 \unit{keV}$ is demonstrated for the first time. This achievement paves the road for the transfer of phase-contrast imaging into fields where high energies are required, such as medical CT, chip failure analysis or homeland security.
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Body of manuscript
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

X-ray radiography and computed tomography (CT) are nowadays standard imaging techniques in materials and life science for the non-destructive examination of samples or the diagnosis of diseases in patients. The underlying contrast mechanism relies on the different X-ray attenuation properties of two materials or tissue types. The dominant physical effects contributing to attenuation are the photo-electric effect and incoherent (Compton) scattering. The sum of their contributions determine the attenuation coefficient, which is a wavelenght dependent material parameter. Apart from attenuation, the wave nature of X-rays reveals another contrast mechanism, which is the phase shift. The physical interaction effect attributed to phase shifts is coherent (Rayleigh) scattering \cite{Als-Nielsen2011}.

Using the material parameter $n=1-\delta(\mathbf{r},\lambda) + i \beta(\mathbf{r},\lambda)$, known from X-ray wave optics as the complex index of refraction, the wavelenght dependent attenuation and phase shift properties of an object at the spatial coordinate $\mathbf{r}$ are fully described. The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the attenuation per unit length (attenuation coefficient) by $\mu = 4 \pi \beta(\mathbf{r},\lambda) / \lambda$ and the total attenuation by an object of thickness $d$ can be described by the line integral $L_\mu = \int_0^d \mu(\mathbf{r},\lambda) \d l$. Similarly, the real part $\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by $\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi = \int_0^d \phi(\mathbf{r}) \d l$.

While the attenuation line integral $L_\mu$ can be directly measured with an X-ray detector by measuring the reduction of the beam intensity $I$ ($L_\mu \propto \log(I)$), the measurement of the phase shift integral $L_\phi$ is more challenging as there is no such simple relation. However, phase sensitive imaging is a desirable modality, as it can provide an enhanced contrast-to-noise ratio (CNR) in images compared to attenuation for certain materials or in different tissue \cite{Pfeiffer2007a,McDonald2009}. Furthermore, the refractive index decrement $\delta$ provides direct access to the electron density \cite{Als-Nielsen2011} and in combination with attenuation, it further enables the determination of the effective atomic number of a material \cite{Qi2010}.

In the past, a lot of effort has been invested into the development of techniques which are sensitive to the phase shift. Since most of the available phase contrast techniques rely on interference and thus typically on optical hardware (e.g. crystals, gratings), they vary a lot in terms of sensitivity, practical applicability or achievable resolution. The vast majority of the methods, including crystal analyzer based \cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996} methods rely on X-ray beams of high spatial and temporal coherence, which is available only at synchrotron sources. Techniques which are compatible with an X-ray beam of low temporal coherence (broad bandwidth) are the in-line phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}. Phase-contrast imaging using X-ray beams of low temporal \textit{and} spatial coherence (i.e. from low-brilliance X-ray sources) have been demonstrated with Talbot-Lau interferometry \cite{Pfeiffer2006} and coded apertures \cite{Munro2012}.

Phase-contrast imaging has so far been used in the lower diagnostic energy range, i.e. from $15$ up to $85 \unit{keV}$. Talbot interferometry has been demonstrated using a synchrotron source at $82 \unit{keV}$ \cite{Willner2013}. Also using a synchrotron source, phase-contrast imaging at $85 \unit{keV}$ has been reported. Using a low-brilliance X-ray tube, Talbot-Lau interferometry was applied at $60 \unit{keV}$ mean energy \cite{Donath2009}. Imaging applications which may benefit from phase contrast at higher energies are for instance medical imaging tasks; chest or abdominal radiography or CT require energies between $100$ and $150 \unit{keV}$. Other potential applications are homeland security or chip failure analysis, which require high energies for the visualization of materials of high density.

Here, we introduce a new method for phase-contrast imaging which is compatible with the entire diagnostic energy range of X-rays. Moreover, the method is fully compatible with compact imaging arrangements based on conventional X-ray tubes. The method is based on Talbot-Lau interferometry \cite{Pfeiffer2006} and employs a novel approach for the grating design and arrangement. Up to now, Talbot-Lau interferometry has been applied with a maximum design energy of $60 \unit{keV}$ \cite{Donath2009}. The challenge which limited the progress towards higher energies was mainly related to the manufacturing of gratings with high aspect ratios. The aspect ratio, given by
\begin{equation}
 \textnormal{AR} = \frac{2h}{p},
\end{equation}
where $p$ is the grating period and $h$ the grating structure height, is normally limited by the lithographic process, as grating structures tend to collapse or to deform (e.g. through capillary forces) if the aspect ratio is too high. For a given setup distance and for $p \propto 1/\sqrt{E}$ and $h \propto E^3$, it can be shown that $\textnormal{AR} \propto E^{7/2}$, where $E$ is the design energy of the system \cite{Momose2003a}. If at $E=25 \unit{keV}$ an aspect ratio for the absorption grating of around $\textnormal{AR}=30$ is necessary for a reasonable length of the experimental arrangement, it would have to be at least $128$ for $E=100 \unit{keV}$. Moreover, when using a polychromatic spectrum, photons above the design energy should also be efficiently attenuated by the gratings to guarantee their contribution to the signal, which requires even higher aspect ratios. Maximum achievable aspect ratios of current grating fabrication techniques \cite{David2007,Kenntner2010} are approximately around 60, whereas such high values are often even beyond the limit and come at the expense of a poor grating quality and performance.

Our approach is based on a new grating design which introduces the edge-on illumination of circularly aligned structures. Edge-on illumination, as opposed to face-on illumination, exploits the dimension along the grating lines to form a high aspect ratio of the structures in beam direction. The effective structure height of the grating is then determined by the grating dimension along the grating lines, which essentially allows arbitrarily high aspect ratios. FIG.~\ref{Fig:schematic} illustrates the edge-on illumination approach.
\begin{figure} [ht]
  \includegraphics[width = \linewidth]{figures/figure1.eps}
  \caption{Schematic of a grating interferometer for high X-ray energies in edge-on illumination mode. The aspect ratio is defined by the ratio of the travelling distance along the grating lines and the period and can be arbitrarily long. In order to avoid a reduction of the field of view, the grating structures are aligned on an arc.}
  \label{Fig:schematic}
\end{figure}

Increasing the effective aspect ratio of the gratings typically leads to a reduction of the field of view due to the change of the grating transmission function at high incident angles, which has also been identified by using a glancing angle of the gratings between zero and $90$ degrees \cite{Stutman2012a}. In order to overcome this problem with edge-on illuminated gratings, the grating lines are circularly aligned (i.e. on an arc) with a radius equal to the distance to the source.

The combination of edge-on illumination and circularly aligned structures enables phase-contrast imaging at arbitrary design energies and with a maximum field of view in horizontal direction ($x$ direction). These advantages come at the expense of a limited field of view in the vertical direction ($y$ direction), which is, depending on the X-ray detector, typically a few pixels. However, radiographic 2D imaging is possible in scanning mode, without increasing dose. Similarly, for tomographic images, the approach allows single slice CT or full 3D imaging in scanning mode.

Grating design and fabrication is non-standard and involves a complex mask design, as shown in FIG.~\ref{Fig:grating_mask}. Each grating resides on a silicon chip and has its specific structure length and curvature. For the present experiments, a symmetric interferometer with a grating period of $p = 2.8 \unit{\upmu m}$ for all gratings has been used. The design energy is $100 \unit{keV}$ and the beam splitter grating periodically shifts the phase by zero and $\pi$ at this energy \cite{David2002}. Using gold as the phase shifting material, this requires a structure length of $h_1 = 19.8 \unit{\upmu m}$. The analyzer grating is an absorption mask for sensing slight changes of the interference pattern generated by the beam splitter \cite{Momose2003a}. With a structure length of $h_2 = 800 \unit{\upmu m}$, this grating has an aspect ratio of $2h/p \approx 570$ and thus sufficiently attenuates X-rays up to energies of around $160 \unit{keV}$. Beam splitter- and analyzer grating are separated at the first fractional Talbot order \cite{Weitkamp2005}, resulting in an inter-grating distance of $158 \unit{mm}$. The source grating splits the relatively large focal spot ($\sim 1 \unit{mm}$) into an array of individually coherent, but mutually incoherent sources \cite{Pfeiffer2006}. It is also made of gold structures with a structure length of $h_0 = h_2 = 800 \unit{\upmu m}$.
\begin{figure} [ht]
  \includegraphics[width = \linewidth]{figures/grating_mask.eps}
  \caption{Grating design mask for the edge-on illumination approach. (a) Top part of the 4 inch wafer, showing five grating chips; one source grating, two beam splitter gratings and two analyzer gratings (from top to bottom). The gratings have different curvatures which are specific to the grating interferometer geometry. (b) Zoom into the grating structures, contain interrupting bridges used for stabilizing the grating structures in the lithographic process \cite{Kenntner2010}.}
  \label{Fig:grating_mask}
\end{figure}

Due to the high spectral acceptance \cite{Weitkamp2005,Thuering2013c} of the interferometer ($50 \unit{keV}$ to $>160 \unit{keV}$) and the high attenuation efficiencies of the source- and analyzer gratings ($>90\%$ up to $160 \unit{keV}$), the voltage of the X-ray source was set to the maximum of $160 \unit{kV}$. With a grating structure height of approx. $100 \unit{\upmu m}$, the field of view in the vertical direction is limited to one detector pixel row. In the horizontal direction, the field of view is limited by the grating size and the geometric magnification of the sample, yielding a maximum field of view of $30 \unit{mm}$. In addition to the standard components (source, camera, interferometer), two optical slits, one in front of the source grating, the other in front of the camera, were required for the collimation of the beam in the vertical direction. X-rays which are not travelling through all of the gratings do not contribute to the signal and are attenuated by the slits.

%Fig. 3 shows a radiographic image of a metal screw in all three contrast modes, acquired with the $100 \unit{keV}$ setup. The images were acquired in scanning mode, using a step size of $100 \unit{\upmu m}$. The number of phase steps was 24 and the exposure time was 15 seconds per step. Grating interferometry at such a high diagnostic energy allows to examine more dense materials such as metals in phase contrast mode. At lower energies, the phase shifts of such materials would be too large and wrap over multiple periods of the analyzer grating.

Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip. Several resistors and an integrated circuit are located on different layers on the chip. The images were acquired in scanning mode, using a step size of $100 \unit{\upmu m}$ in $y$-direction. For a better comparison of the magnified phase and attenuation images, the attenuation image has been replaced with the differential attenuation image, which was obtained by digital differentiation. In the attenuation image, the soldering points of the integrated circuit are hardly visible underneath the resistors, while in the phase image, they can clearly be identified. This clearly implies the benefit of the differential nature of the phase-contrast image, which may be useful to identify flaws in multi-layered structures such as electronic chips.
\begin{figure} [ht]
  \includegraphics[width = \linewidth]{figures/img_chip_dabs.pdf}
  \caption{}
  \label{Fig:img_chip}
\end{figure}

Edge-on illuminated grating interferometry breaks the current limitations of phase-contrast imaging to the lower diagnostic energy range. Compact geometries  using conventional X-ray sources for design energies well above $100 \unit{keV}$ could be realized with the approach. This enables the examination of materials of higher density or thickness which would be intransparent at lower energies. Finally, the approach is not limited to X-ray imaging, but could easily be applied to other grating-based imaging modalities (e.g., with neutrons \cite{Grunzweig2008}) where high aspect ratios are required.

\section*{Methods}
Edge-on illuminated gratings were manufactured by Micro Works GmbH, Germany, using a LIGA process \cite{Kenntner2010}. Each grating resides on a $5 \times 60 \unit{mm^2}$ silicon chip and several grating chips are fabricated on a single 4 inch silicon wafer. The experimental arrangement for a design energy at 100 keV is a symmetric Talbot-Lau interferometer with a grating period of $p = 2.8 \unit{\upmu m}$ for all gratings. The distance from the source grating to the analyzer grating is $32 \unit{cm}$ and the source grating is positioned $23 \unit{cm}$ away from the source. The number of phase steps for one projection was 24 \cite{Weitkamp2005} and the exposure time for the images was 15 seconds per phase steps.

The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output voltage of $160 \unit{kV}$. In the experiment, it was set to the maximum voltage. The focal spot size is approximately $1 \unit{mm}$. The detector is a CCD camera from Finger Lakes Instruments. A cesium iodide (CsI:Ti) scintillator of $600 \unit{\upmu m}$ thickness converts the X-rays to visible light and is coupled with an optical lens projecting the image onto the CCD. The effective pixel size is $80 \unit{\upmu m}$. The widths of the collimating slits are $25 \unit{\upmu m}$ and $100 \unit{\upmu m}$, respectively.

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps \cite{Weitkamp2005} and an exposure time of 15 seconds per step.

\section*{Acknowledgements}
We thank Gordan Mikuljan from Paul Scherrer Institute, Switzerland, for his work on the mechanical design, Joachim Schulz and Marco Walter from Micro Works GmbH, Germany, for the competent support on grating design issues, Christian Kottler and Vincent Revol from Centre Suisse d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful discussions on the design of the system.

\bibliographystyle{apsrev4-1}
\bibliography{library}

\end{document}

### 2013-08-12 prl/hedpc_prl.tex
thomas version

--- 2013-08-12 natphys/hedpc_natphys.tex
@@
 \begin{abstract}
-Phase contrast imaging with X-rays is an exciting field that reveals new insights into material properties by providing access to a complementary physical contrast mechanism.
+Phase contrast imaging with X-rays is an exciting modality that reveals new insights into material properties by providing access to a complementary physical contrast mechanism.
 Phase sensitive imaging in the high energy range of hard X-rays, i.e.
-between $80$ and $150 \unit{keV}$ is still largely unexplored, as the current methods typically entail severe technical challenges.
-With a novel approach, we demonstrate phase contrast as well as dark-field contrast imaging on laboratory systems with low-brilliance X-ray sources in the entire diagnostic energy range.
-A phase-contrast technique at such high energies is of particularly high scientific and industrial interest as it would vastly expand the range of applications, for instance, by the examination of materials of high density or thickness.
+between 60 and $150 \unit{keV}$ is still largely unexplored, as the current methods typically involve severe technical challenges.
+A novel approach is demonstrated, which enables phase contrast as well as dark field contrast imaging on laboratory systems with low brilliance X-ray sources in the entire diagnostic energy range.
+A phase contrast technique at such high energies is of particularly high scientific and industrial interest as it would vastly expand the range of applications, for instance, by the examination of materials of high density or thickness.
 The approach includes a new technique for the grating manufacturing in Talbot-Lau interferometry.
-Firstly, the approach breaks the current limits of achievable grating aspect ratios, which has been a key issue for a long time in the past.
+Firstly, the approach breaks the current limits of achievable grating aspect ratios, which has been a key issue
+in the past.
 Secondly, it solves the intrinsic reduction of the field of view which occurs for gratings with such high aspect ratios.
-Using an imaging arrangement based on a conventional X-ray tube, phase and dark-field-contrast imaging at $100 \unit{keV}$ is demonstrated for the first time.
-This achievement paves the road for the transfer of phase-contrast imaging into fields where high energies are required, such as medical CT, chip failure analysis or homeland security.
+Using an imaging arrangement based on a conventional X-ray tube, phase- and dark-field-contrast imaging at $100 \unit{keV}$ is demonstrated for the first time.
+This achievement paves the road for the transfer of phase contrast imaging into fields where high energies are required, such as medical CT, chip failure analysis or homeland security.
+%The examination in phase contrast of dense materials, such as metals, has not been feasible so far due to the high absorption and scattering cross sections in the lower energy range.
+%requires  is the electron density  provides direct access to electron densityovercomes the limitation in the achievable contrast in objects with low absorbing materials and  
 \end{abstract}
@@
 The physical interaction effect attributed to phase shifts is coherent (Rayleigh) scattering \cite{Als-Nielsen2011}.
-
-Using the material parameter $n=1-\delta(\mathbf{r},\lambda) + i \beta(\mathbf{r},\lambda)$, known from X-ray wave optics as the complex index of refraction, the wavelenght dependent attenuation and phase shift properties of an object at the spatial coordinate $\mathbf{r}$ are fully described.
+The material parameter $n=1-\delta(\mathbf{r},\lambda) + i \beta(\mathbf{r},\lambda)$, known from X-ray wave optics as the complex index of refraction, describes the wavelenght dependent attenuation and phase shift properties of an object at the spatial coordinate $\mathbf{r}$.
 The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the attenuation per unit length (attenuation coefficient) by $\mu = 4 \pi \beta(\mathbf{r},\lambda) / \lambda$ and the total attenuation by an object of thickness $d$ can be described by the line integral $L_\mu = \int_0^d \mu(\mathbf{r},\lambda) \d l$.
-Similarly, the real part $\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by $\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi = \int_0^d \phi(\mathbf{r}) \d l$.
+The real part $\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by $\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi = \int_0^d \phi(\mathbf{r}) \d l$.
 
 While the attenuation line integral $L_\mu$ can be directly measured with an X-ray detector by measuring the reduction of the beam intensity $I$ ($L_\mu \propto \log(I)$), the measurement of the phase shift integral $L_\phi$ is more challenging as there is no such simple relation.
-However, phase sensitive imaging is a desirable modality, as it can provide an enhanced contrast-to-noise ratio (CNR) in images compared to attenuation for certain materials or in different tissue \cite{Pfeiffer2007a,McDonald2009}.
+However, phase sensitive imaging is a desirable modality, as it can provide an enhanced image contrast-to-noise ratio (CNR) compared to attenuation for certain materials or in different tissue.
 Furthermore, the refractive index decrement $\delta$ provides direct access to the electron density \cite{Als-Nielsen2011} and in combination with attenuation, it further enables the determination of the effective atomic number of a material \cite{Qi2010}.
+%Furthermore, depending on the sensitivity of the phase sensitive technique, an enhanced contrast-to-noise ratio (CNR) in phase images compared to absorption images may apply for a variety of materials or in different tissues.
+
+% Similar to attenuation, an energy dependent parameter can be derived, describing the phase shift properties of a material.
+% 
+% In a material, the X-ray phase can be shifted with respect to the undisturbed wave, which is, compared to attenuation, a fundamentally different interaction mechanism and can mainly be attributed to the coherent (Rayleigh) scattering of X-rays in a material.
+% 
+% 
+% Regarding the wave properties, a transition from one medium into another causes a change in the wave's phase velocity and thus in a net change of the output phase (a phase shift) behind the object.
+Since no detection device is able to measure a phase shift directly, advanced techniques are required to determine the phase shift in a material.
+% 
+% Referring to the particle properties of X-rays, photons can be randomly scattered in the material. Compton scattering 
+% 
+% Depending on the imaging system (geometry and energy), wide angle and small angle scattering can be sources of noise in conventional X-ray images.
+For the special type of scattering which occurs exclusively in forward direction and under ultra small angles (order of nano radiants), the particles usually remain within the area of a detector pixel.
+This effect is not recorded by absorption images and cannot directly be detected with standard techniques.
+% 
+% The main interest in the detectability of those additional interaction mechanisms is the fact that attenuation, phase shift and scattering are physically complementary interaction mechanisms, in the sense that their occurrence is mutually independent.
+This gives rise to hypothesize that the complementary interaction mechanisms may eventually yield complementary image contrasts.
 
@@
 Techniques which are compatible with an X-ray beam of low temporal coherence (broad bandwidth) are the in-line phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
-Phase-contrast imaging using X-ray beams of low temporal \textit{and} spatial coherence (i.e.
-from low-brilliance X-ray sources) have been demonstrated with Talbot-Lau interferometry \cite{Pfeiffer2006} and coded apertures \cite{Munro2012}.
+Phase-contrast techniques with X-ray beams of low temporal \textit{and} spatial coherence (i.e.
+from low-brilliance X-ray sources) are Talbot-Lau interferometry \cite{Pfeiffer2006} and coded apertures \cite{Munro2012}.
 
@@
 Also using a synchrotron source, phase-contrast imaging at $85 \unit{keV}$ has been reported.
-Using a low-brilliance X-ray tube, Talbot-Lau interferometry was applied at $60 \unit{keV}$ mean energy \cite{Donath2009}.
+Using a low-brilliance X-ray tube, Talbot-Lau interferometry was applied at $60 \unit{keV}$ \cite{Donath2009}.
+
 Imaging applications which may benefit from phase contrast at higher energies are for instance medical imaging tasks; chest or abdominal radiography or CT require energies between $100$ and $150 \unit{keV}$.
@@
 
-Here, we introduce a new method for phase-contrast imaging which is compatible with the entire diagnostic energy range of X-rays.
-Moreover, the method is fully compatible with compact imaging arrangements based on conventional X-ray tubes.
-The method is based on Talbot-Lau interferometry \cite{Pfeiffer2006} and employs a novel approach for the grating design and arrangement.
+Here, we introduce a new method for phase-contrast imaging which is compatible with the entire diagnostic energy range of X-rays and with a compact geometry based on conventional X-ray tubes.
+The method is based on Talbot-Lau interferometry \cite{Pfeiffer2006} and employs a novel approach for the grating arrangement.
 Up to now, Talbot-Lau interferometry has been applied with a maximum design energy of $60 \unit{keV}$ \cite{Donath2009}.
@@
 Moreover, when using a polychromatic spectrum, photons above the design energy should also be efficiently attenuated by the gratings to guarantee their contribution to the signal, which requires even higher aspect ratios.
-Maximum achievable aspect ratios of current grating fabrication techniques \cite{David2007,Kenntner2010} are approximately around 60, whereas such high values are often even beyond the limit and come at the expense of a poor grating quality and performance.
+The maximum achievable aspect ratios of current grating fabrication techniques \cite{David2007,Kenntner2010} are $\textnormal{AR} \approx 60$, whereas such high values are often even beyond the limit and come at the expense of a poor grating quality and performance.
 
-Our approach is based on a new grating design which introduces the edge-on illumination of circularly aligned structures.
+Our approach is based on a new grating design which introduces the edge-on illumination of circularly shaped gratings.
 Edge-on illumination, as opposed to face-on illumination, exploits the dimension along the grating lines to form a high aspect ratio of the structures in beam direction.
@@
 
-The combination of edge-on illumination and circularly aligned structures enables phase-contrast imaging at arbitrary design energies and with a maximum field of view in horizontal direction ($x$ direction).
+The combination of edge-on illumination and the circularly curved structures enables phase-contrast imaging at arbitrary design energies and with a maximum field of view in horizontal direction ($x$ direction).
 These advantages come at the expense of a limited field of view in the vertical direction ($y$ direction), which is, depending on the X-ray detector, typically a few pixels.
@@
 Beam splitter- and analyzer grating are separated at the first fractional Talbot order \cite{Weitkamp2005}, resulting in an inter-grating distance of $158 \unit{mm}$.
-The source grating splits the relatively large focal spot ($\sim 1 \unit{mm}$) into an array of individually coherent, but mutually incoherent sources \cite{Pfeiffer2006}.
+The source grating splits the relatively large focal spot ($\sim 1 \unit{mm}$ into an array of individually coherent, but mutually incoherent sources \cite{Pfeiffer2006}.
 It is also made of gold structures with a structure length of $h_0 = h_2 = 800 \unit{\upmu m}$.
@@
 $100 \unit{\upmu m}$, the field of view in the vertical direction is limited to one detector pixel row.
-In the horizontal direction, the field of view is limited by the grating size and the geometric magnification of the sample, yielding a maximum field of view of $30 \unit{mm}$.
+In the horizontal direction, the field of view is limited by the grating size and the geometric magnification of the sample, yielding a maximum of $30 \unit{mm}$.
 In addition to the standard components (source, camera, interferometer), two optical slits, one in front of the source grating, the other in front of the camera, were required for the collimation of the beam in the vertical direction.
@@
 
-Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
+Fig.~\ref{Fig:img_chip} shows an example of a radiographic scan of an electronic chip.
 Several resistors and an integrated circuit are located on different layers on the chip.
 The images were acquired in scanning mode, using a step size of $100 \unit{\upmu m}$ in $y$-direction.
-For a better comparison of the magnified phase and attenuation images, the attenuation image has been replaced with the differential attenuation image, which was obtained by digital differentiation.
+The number of phase steps \cite{Weitkamp2005} was 24 and the exposure time was 15 seconds per step.
+For the comparison of phase and absorption image, the figure further shows the differential absorption image, which has been obtained by digital differentiation.
 In the attenuation image, the soldering points of the integrated circuit are hardly visible underneath the resistors, while in the phase image, they can clearly be identified.
-This clearly implies the benefit of the differential nature of the phase-contrast image, which may be useful to identify flaws in multi-layered structures such as electronic chips.
+This suggests that the differential nature of the phase contrast image may be useful to identify flaws in multi-layered electronic chips.
 \begin{figure} [ht]
-  \includegraphics[width = \linewidth]{figures/img_chip_dabs.pdf}
+  \includegraphics[width = \linewidth]{figures/img_chip.eps}
   \caption{}
@@
 
-Edge-on illuminated grating interferometry breaks the current limitations of phase-contrast imaging to the lower diagnostic energy range.
+Edge-on illuminated grating interferometry breaks the current limitations to the lower diagnostic energy range for X-ray phase contrast imagin.
 Compact geometries  using conventional X-ray sources for design energies well above $100 \unit{keV}$ could be realized with the approach.
 This enables the examination of materials of higher density or thickness which would be intransparent at lower energies.
-Finally, the approach is not limited to X-ray imaging, but could easily be applied to other grating-based imaging modalities (e.g., with neutrons \cite{Grunzweig2008}) where high aspect ratios are required.
+Finally, the approach is not limited to X-ray imaging, but could easily be applied to other grating-based imaging modalities (e.g., with neutrons \cite{Grunzweig2008}) where high aspect ratios are necessary.
 
@@
 
-In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps \cite{Weitkamp2005} and an exposure time of 15 seconds per step.
-
 \section*{Acknowledgements}
@@
 
+\bibliography{library.bib}
 \bibliographystyle{apsrev4-1}
-\bibliography{library}
 

### 2013-08-12 prl/hedpc_prl_v3.tex
thomas version

%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}  % for review and submission
%\documentclass[aps,prl,preprint]{revtex4-1}  % for double-spaced preprint
\usepackage{graphicx}  % needed for figures
\usepackage{subfigure} % for subfigures
%\usepackage{dcolumn}   % needed for some tables
%\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage{upgreek}	% for non-italic greek letters

% avoids incorrect hyphenation, added Nov/08 by SSR
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

%% New commands
\newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}}
\newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}

\begin{document}

\title{Compact X-ray grating interferometry at 100~keV}

\author{T.~Thuering}
  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
  \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
\author{M.~Abis}
  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
  \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
\author{Z.~Wang}
  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
\author{C.~David}
  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
\author{M.~Stampanoni}
  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
  \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}

\date{\today}

\begin{abstract}
Todays X-ray phase contrast imaging techniques are not only limited by spatial and temporal coherence properties of the beam, but also in the applicable energy range due to technical limitations. Imaging at higher energies is of particularly high interest as it would clearly expand the range of applications, e.g., towards the examination of materials with a higher density or thickness. Grating interferometry, albeit proven to be one of the most promising methods for the industrial applicability, is limited to energies up to about $50 \unit{keV}$ by the fabrication of gratings with sufficiently high aspect ratios. Here, we propose an alternative approach, which enables the access to the entire diagnostic energy range of X-rays for phase and dark field contrast imaging on compact systems with low brilliance X-ray tubes. Based on Talbot-Lau interferometry, the novel approach involves the edge-on illumination of specially designed gratings, which solves two fundamental problems. First, the effective aspect ratio is not determined or limited by the structure height limitation of the manufacturing technology and thus, arbitrary aspect ratios are feasible. Secondly, the intrinsic reduction of the field of view for higher aspec ratios is solved by a circular alignment of the grating structures. Based on this, a compact Talbot-Lau interferometer has been set up with a design energy at $100 \unit{keV}$, providing 2D and 3D phase contrast images of dense materials. The approach is not only applicable to X-rays, but is also compatible to other grating based imaging modalities such as neutrons.
\end{abstract}

%\pacs{}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Body of paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Introduction
X-ray radiography and computed tomography (CT) are nowadays standard imaging techniques for non-destructive testing of materials or for medical diagnosis in daily routine. The physical contrast mechanism relies on the attenuation of X-rays in an object through the photo-electric effect or Compton scattering, whereas two materials can be distinguished due to their different attenuation properties. The wave and particle nature of X-rays reveal two further physical interaction mechanisms that occur if an object is exposed to X-rays.

Regarding the wave properties, an interface of two different materials in an object causes a change in the wave's phase velocity and thus in a net change of the output phase (a phase shift) downstream of the object. Since no detection device is able to measure a phase shift directly, advanced techniques are necessary to obtain access to this signal.

Regarding the particle properties of X-rays, photons are randomly scattered on small structures in the material. Depending on the imaging system (geometry and energy), wide angle and small angle scattering represent typical sources of noise in absorption imaging. For the type of scattering which occurs exclusively in forward direction and under ultra small angles (order of nano radiants), the particles usually remain within the area of a detector pixel and thus this effect cannot directly be detected.

The main interest in the detectability of those additional interaction mechanisms is the fact that attenuation, phase shift and scattering are phyiscally complementary interaction mechanisms, in the sense that their occurence is mutually independent. In the context of information content of images, this gives rise to hypothesize that the complementary interaction mechanisms may eventually yield complementary image information, manifested with different image contrasts.

Since currently available phase contrast techniques rely on secondary physical effects, such as interference, and thus typically on optical hardware (e.g. crystals, gratings), they vary a lot in terms of sensitivity, practical applicability or achievable resolution. The vast majority of the methods, including crystal analyzer based \cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996} methods rely on X-ray beams of high spatial and temporal coherence, available only at synchrotons. Techniques with a high degree of spectral acceptance are inline phase contrast \cite{Snigirev1995,Wilkins1996,Cloetens1996} and Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}. Regarding the acceptance of X-ray beams with low temporal and spatial coherence, Talbot-Lau interferometry \cite{Pfeiffer2006} and coded apertures \cite{Munro2012} are currently the only feasible techniques.

While current phase contrast methods are today broadly available on synchrotrons and constantly improving for conventional X-ray tubes, the applicable energy range is still limited to the low energy range. All of the reported methods have been designed for X-ray energies between 5 and 40 keV. None of the current methods is compatible to industrial or medical applications, where higher X-ray energies ($>50 \unit{keV}$) are required. For instance, the portability of Talbot-Lau interferometry towards medical imaging such as chest or abdominal radiography or CT, which require energies up to $150 \unit{keV}$, has still been impossible due to the technical limitations in grating fabrication for X-ray energies higher than approx. $50 \unit{keV}$. Grating manufacturing methods are well established for energies up to about $E=40 \unit{keV}$, which partly explains the reported successes of the technique in mammography \cite{Stampanoni2011} or hand imaging \cite{Thuering2013a}. The limiting factor for currently available grating fabrication techniques is the aspect ratio $\textnormal{AR} = 2h/p$, where $p$ is the grating period and $h$ the structure height. For a given setup distance, $p \propto 1/\sqrt{E}$ and $h \propto E^3$, and for the aspect ratio, it can be shown that $\textnormal{AR} \propto E^{7/2}$. While for $25 \unit{keV}$, an aspect ratio for the absorption grating of around $\textnormal{AR}=30$ is necessary for a reasonable setup length, it would have to be at least 128 for $100 \unit{keV}$. This is only approximate and ignores absorption edges of the materials (e.g., at around $80 \unit{keV}$ for gold in an absorption grating). Furthermore, when using a polychromatic spectrum, photons above the design energy should also be efficiently attenuated by the gratings to guarantee their contribution to the signal, requiring even higher aspect ratios. The current technical limitation is at $\textnormal{AR} \approx 50$, whereas such high values are pushing the limits and usually come at the expense of a poor grating quality and performance.

% Grating interferometry is currently the most promising technique to become a widespread method for multimodal imaging using phase and scattering contrast.
% 
% Grating interferometry exploits the Talbot effect of a periodic phase grating (beam splitter) to generate an interference pattern, which can then be sensed for any changes in intensity (absorption signal), lateral shift \cite{David2002} (refraction signal) and amplitude \cite{Pfeiffer2008} (scattering signal) by using an analyzer grating (absorption grating) \cite{Momose2003a}. The compatibility to standard low-brilliance X-ray sources, being the most valuable property in terms of practical applicability, is on one hand achieved with a third grating in front of the source (source grating) \cite{Pfeiffer2006}. On the other hand, the comparably high degree of achromaticity of a grating interferometer enables the operation with the polychromatic spectrum.
% 
% In the past few years, the potential impact of grating interferometry on conventional X-ray tubes has been studied for a variety of applications in medical imaging or materials science, whereas the most prominent contributions in the medical field are probably from mammography \cite{Stampanoni2011} or from human hand imaging \cite{Donath2010a,Thuering2013}. *** anyhting from the pfeiffer group? *** 
% 
% The portability of this technique towards medical applications such as chest or abdominal radiography or CT has so far been difficult due to the requirement of higher X-ray energies (up to $150 \unit{keV}$). Gratings with reliable quality can be fabricated for energies up to about $E=40 \unit{keV}$, which partly explains the success of the technique in mammography or hand imaging. The limiting factor of currently available grating fabrication techniques is the aspect ratio, given by $\textnormal{AR} = 2h/p$, where $p$ is the grating period and $h$ the structure height. For a given setup distance, $p \propto 1/\sqrt{E}$ and $h \propto E^3$, such that for the aspect ratio, we obtain $\textnormal{AR} \propto E^{7/2}$. While for $25 \unit{keV}$, an aspect ratio for the absorption grating of around $\textnormal{AR}=30$ is necessary for a reasonable setup length, it would have to be $\textnormal{AR} \approx 128$ for $100 \unit{keV}$. This rough calculation is only approximate and ignores absorption edges of the materials (e.g., at around $80 \unit{keV}$ for gold in an absorption grating). Furthermore, when using a polychromatic spectrum, photons above the design energy should also be efficiently attenuated by the gratings to guarantee their contribution to the signal, requiring even higher aspect ratios.

We herein propose an alternative design method of X-ray Talbot-Lau grating interferometers, which allows phase contrast and dark field imaging with low brilliance X-ray tubes at arbitrarily high energies. The approach is based on the edge-on illumination of gratings. Edge-on illumination, as opposed to the standard face-on illumination, exploits the arbitrary length of the grating lines to form high aspect ratios of the structures along the beam direction. Since the effective structure height of the grating is in then determined by the grating dimension, the aspect ratio can be arbitrarily high. FIG.~\ref{Fig:schematic} illustrates the edge-on illumination approach.

%We herein propose an alternative design method of X-ray grating interferometry, which allows phase and dark field imaging at arbitrarily high energies. The approach is based on the edge-on illumination of gratings. Edge-on illumination, as opposed to the standard face-on illumination, has the advantage that the dimension along the grating lines, which originally has been the vertical dimension in the image plane, is now the dimension defining the effective structure height $h_\msub{eff}$ of the grating in beam direction. Since this dimension is only limited by the achievable grating size, the effective aspect ratio $\textnormal{AR}_\msub{eff}$ can virtually be of any size. 
\begin{figure} [ht]
  \includegraphics[width = \linewidth]{figures/figure1.eps}
  \caption{Schematic of a grating interferometer for high X-ray energies in edge-on illumination mode. The gratings are curved to maintain a large field of view.}
  \label{Fig:schematic}
\end{figure}

Increasing the effective aspect ratio of the gratings typically leads to a reduction of the field of view due to the change of the transmission function at high incident angles, which has also been demonstrated by using a glancing angle of the gratings between zero and $90$ degrees \cite{Stutman2012}. In order to overcome this problem in edge-on illuminated grating interferometry, the grating lines are alined on an arc with a radius equal to the distance from the source to the grating.

The combination of edge-on illumination and the circularly curved structure alignment allows to design a grating interferometer at any design energy in the diagnostic energy range of X-rays. The arbitrary aspect ratio only comes at the expense of a limited field of view in the vertical dimension of the image plane, which is, depending on the detector, typically a few pixels. However, radiographic 2D images can still be acquired in scanning mode without increasing dose. Similary, in tomographic mode, the approach allows single slice CT or full 3D imaging in scanning mode.

%A similar approach to increase the effective aspect ratios has successfully been demonstrated by using a glancing angle of the gratings between zero and $90$ degrees \cite{Stutman2012}. With this approach, conventional gratings mounted on a rotation stage can be used, keeping the grating design simple and standard. However, a major limitation of this method is the severe reduction of the field of view at higher glancing angles, due to the non-curved alignment of the grating structures.

Gratings were manufactured by Micro Works GmbH, Germany, using a LIGA process \cite{Kenntner2010}. The grating design and fabrication is non-standard and involves a complex mask design, as shown in FIG. 2. Each grating is on a $5 \times 60 \unit{mm^2}$ silicon chip and has its specific structure length and curvature. Several grating chips can be fabricated on a single 4 inch silicon wafer. For the present experiments, a symmetric interferometer with a grating period of $p = 2.8 \unit{\upmu m}$ has been used. The design energy is $100 \unit{keV}$ and the beam splitter grating periodically shifts the phase by zero and $\pi$ at this energy. Using gold as the phase shifting material, this requires a structure length of $b = 19.8 \unit{\upmu m}$. The analyzer grating is an absorption mask for sensing the changes of the interference pattern generated by the beam splitter. The structure length of this grating is $b = 800 \unit{\upmu m}$, providing sufficient attenuation of the X-rays up to $160 \unit{keV}$. Beam splitter- and analyzer grating are separated at the first fractional Talbot order and the distance from the source grating to the analyzer grating is $32 \unit{cm}$.

The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output voltage of $160 \unit{kV}$. Since the absorption gratings perform efficiently up to $160 \unit{keV}$ and the spectral acceptance at the first fractional Talbot order is high (50 to $>160 \unit{keV}$), the tube voltage was set to the maximum of $160 \unit{kV}$ and operated at a current of $10 \unit{mA}$. The focal spot size is approx. $1 \unit{mm}$. The detector is a CCD camera from Finger Lakes Instruments. A cesium idodide (CsI) scintillator of $600 \unit{\upmu m}$ thickness converts the X-rays to visible light and is coupled with an optical lens projecting the image onto the CCD. The effective pixel size is $80 \unit{\upmu m}$. With a grating structure height of approx. $100 \unit{\upmu m}$, the field of view in the vertical direction is limited to one pixel row. In addition to the standard components (source, camera, interferometer), two optical slit, one in front of the source grating, the other in front of the camera, have been installed for the collimation of the beam in vertical direction. X-rays which are not travelling through all of the gratings do not contribute to the signal and must be attenuated by the slits. The slit widths are $25 \unit{\upmu m}$ and $100 \unit{\upmu m}$, respectively.

FIG. 3 shows a radiographic image of a metal screw in all three contrast modes, acquired with the $100 \unit{keV}$ grating interferometer setup. Grating interferometry at such a high diagnostic energy allows to examine more dense materials such as heavy metals in phase contrast mode. At lower energies, the phase shifts would be too large and wrap over multiple periods of the analyzer grating.

We thank Gordan Mikuljan from Paul Scherrer Institute, Switzerland, for his work on the mechanical design, Joachim Schulz and Marco Walter from Micro Works GmbH, Germany, for the competent support on grating design issues, Christian Kottler and Vincent Revol from Centre Suisse d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful discussions on grating interferometer design.

%If the spatial coherence of the beam is too low to form interference, another absorption grating, splitting the beam into an array of smaller sources, can be added.Adding another absorption grating in front of a

%In wave optics, the two interaction mechanisms of X-ray with matter are described by the complex index of refraction, $n=1-\dleta  + i\beta$, where $\beta$ takes into account the absorption and $\delta$ the phase shift properties of the material.

- Grating interferometry can yield additional information. bla bla

- Signal decay of the attenuation coefficient $\mu$ is proportional to $1/E^3$, for phase it is only $1/E$. -> Higher benefit of PC at higher energies. optimum energy (according to raupach paper) of PC compared to ABS is .... (figure out from raupach paper or so).

- high energies are important for thick samples and medical CT applications

- grating interferometry is the most promising technique for PC on conventional X-ray tubes. It further allows to retrieve a dark field image. So far, grating interferometry was limited in field of view and energy. High aspect ratios are essential for grating interferometry at high energies. Glancing angle has been reported and increased the aspect ratio and thus visibility \cite{Stutman2012}. However, the problem of a reduced field of view (reported as vignetting in Stutman) becomes severe for low glancing angles. So, higher aspect ratios always reduce the field of view.

- Here, a new method by using curved gratings in edge illumination mode, is presented. Description of edge illumination principle: tilting the grating in 90 degrees, the limiting dimension is now the vertical axis, radiography is possible only in scanning mode, single slice tomography is possible. High field of view by curved gratings, curved gratings represent an elegant solution to the limited FOV, which has already been demonstrated for compact grating interferometery \cite{Thuering2011}.

%Methods
- Setup basic hardware: The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output voltage of $160 \unit{kV}$. The detector consists of a cesium idodide (CsI) scintillator of $600 \unit{\mu m}$ thickness, an optical lens and a CCD camera from Finger Lakes Instruments. The effective pixel size is $80 \unit{\mu m}$.

- Grating manufacturing:

- setup design: Due to the large focal spot size of the source of approx. $1 \unit{mm}$, the grating interferometer is a Talbot-Lau type interferometer with a source grating \cite{Pfeiffer2006}. Symmetric design, $p_0 = p_1 = p_2 = 2.8 \unit{\mu m}$. Design energy at ... keV, Talbot order .... Gold was used for the absorption grating. The effective thickness of the gold structure in beam direction is $800 \unit{\mu m}$, resulting in an aspect ratio of $2h/p \approx 570$. For the phase shifting grating, Nickel/Gold with a thickness of $... \unit{\mu m}$, generating a phase shift of $\pi$ at the design energy. The vertical FOV is limited by the height of the grating structures of G2, which is $100 \unit{\mu m}$. With a pixel size of $80 \unit{\mu m}$, only a single detector line must be read out. To avoid blurring of the interference pattern in perpendicular direction of this line, an efficient beam collimation has been implemented. Two collimator slits have been used, one with a slit height of $25 \unit{\mu m}$ placed after the source and another one with a slit width of $100 \unit{\mu m}$ placed between G2 and the detector.

%Results
- It would be nice to show an image from the slit, where also the fringes are visible. Specify visibility \\
- Phantom tomography \\
- Real data tomography \\
- Effect of scattering (Silvia) \\

\bibliography{library.bib}
\bibliographystyle{apsrev4-1}

\end{document}

### 2013-08-12 prl/hedpc_prl_v6.tex
thomas version

--- 2013-08-12 prl/hedpc_prl.tex
@@
 \newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
-\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
 
@@
 Phase sensitive imaging in the high energy range of hard X-rays, i.e.
-between 60 and $150 \unit{keV}$ is still largely unexplored, as the current methods typically involve severe technical challenges.
-A novel approach is demonstrated, which enables phase contrast as well as dark field contrast imaging on laboratory systems with low brilliance X-ray sources in the entire diagnostic energy range.
+above 60 keV is still largely unexplored, as the currently availabe methods are technically limited.
+We demonstrate a novel approach, which enables the access to the entire diagnostic energy range of X-rays for phase contast as well as dark field contrast imaging on laboratory systems with low brilliance X-ray sources.
 A phase contrast technique at such high energies is of particularly high scientific and industrial interest as it would vastly expand the range of applications, for instance, by the examination of materials of high density or thickness.
-The approach includes a new technique for the grating manufacturing in Talbot-Lau interferometry.
-Firstly, the approach breaks the current limits of achievable grating aspect ratios, which has been a key issue
-in the past.
-Secondly, it solves the intrinsic reduction of the field of view which occurs for gratings with such high aspect ratios.
-Using an imaging arrangement based on a conventional X-ray tube, phase- and dark-field-contrast imaging at $100 \unit{keV}$ is demonstrated for the first time.
-This achievement paves the road for the transfer of phase contrast imaging into fields where high energies are required, such as medical CT, chip failure analysis or homeland security.
+The approach exploits the principles of differential phase contrast imaging and employs a new technique for diffraction grating manufacturing, which is compatible to any X-ray energy in the diagnostic range.
+Firstly, the approach breaks the current limits of achievable grating aspect ratios, which has been the key issue in the past.
+Secondly, it solves the intrinsic reduction of the field of view, which occurs for such high grating aspect ratios.
+An imaging arrangement has been set up, which allows to acquire phase- and dark-field-contrast images at $100 \unit{keV}$ for the first time.
+This successful step forward to access the high diagnositc energy range will pave the road for the transfer of phase contrast imaging into fields where high energies are required, such as medical CT, chip failure analysis or homeland security.
 %The examination in phase contrast of dense materials, such as metals, has not been feasible so far due to the high absorption and scattering cross sections in the lower energy range.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+X-ray radiography and computed tomography (CT) are nowadays standard imaging techniques in materials and life science for the non-destructive examination of samples.
+The physical contrast mechanism relies on the attenuation of X-rays in an object through the photo-electric effect or Compton scattering, whereas two materials can be distinguished due to their different attenuation properties.
+Apart from attenuation, the wave and particle nature of X-rays reveal two further physical interaction mechanisms that occur if an object is exposed to X-rays.
 
-X-ray radiography and computed tomography (CT) are nowadays standard imaging techniques in materials and life science for the non-destructive examination of samples or the diagnosis of diseases in patients.
-The underlying contrast mechanism relies on the different X-ray attenuation properties of two materials or tissue types.
-The dominant physical effects contributing to attenuation are the photo-electric effect and incoherent (Compton) scattering.
-The sum of their contributions determine the attenuation coefficient, which is a wavelenght dependent material parameter.
-Apart from attenuation, the wave nature of X-rays reveals another contrast mechanism, which is the phase shift.
-The physical interaction effect attributed to phase shifts is coherent (Rayleigh) scattering \cite{Als-Nielsen2011}.
-The material parameter $n=1-\delta(\mathbf{r},\lambda) + i \beta(\mathbf{r},\lambda)$, known from X-ray wave optics as the complex index of refraction, describes the wavelenght dependent attenuation and phase shift properties of an object at the spatial coordinate $\mathbf{r}$.
-The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the attenuation per unit length (attenuation coefficient) by $\mu = 4 \pi \beta(\mathbf{r},\lambda) / \lambda$ and the total attenuation by an object of thickness $d$ can be described by the line integral $L_\mu = \int_0^d \mu(\mathbf{r},\lambda) \d l$.
-The real part $\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by $\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi = \int_0^d \phi(\mathbf{r}) \d l$.
+Regarding the wave properties, a transition from one medium into another causes a change in the wave's phase velocity and thus in a net change of the output phase (a phase shift) downstream of the object.
+Since no detection device is able to measure a phase shift directly, advanced techniques are necessary to obtain access to this signal.
 
-While the attenuation line integral $L_\mu$ can be directly measured with an X-ray detector by measuring the reduction of the beam intensity $I$ ($L_\mu \propto \log(I)$), the measurement of the phase shift integral $L_\phi$ is more challenging as there is no such simple relation.
-However, phase sensitive imaging is a desirable modality, as it can provide an enhanced image contrast-to-noise ratio (CNR) compared to attenuation for certain materials or in different tissue.
-Furthermore, the refractive index decrement $\delta$ provides direct access to the electron density \cite{Als-Nielsen2011} and in combination with attenuation, it further enables the determination of the effective atomic number of a material \cite{Qi2010}.
-%Furthermore, depending on the sensitivity of the phase sensitive technique, an enhanced contrast-to-noise ratio (CNR) in phase images compared to absorption images may apply for a variety of materials or in different tissues.
-
-% Similar to attenuation, an energy dependent parameter can be derived, describing the phase shift properties of a material.
-% 
-% In a material, the X-ray phase can be shifted with respect to the undisturbed wave, which is, compared to attenuation, a fundamentally different interaction mechanism and can mainly be attributed to the coherent (Rayleigh) scattering of X-rays in a material.
-% 
-% 
-% Regarding the wave properties, a transition from one medium into another causes a change in the wave's phase velocity and thus in a net change of the output phase (a phase shift) behind the object.
-Since no detection device is able to measure a phase shift directly, advanced techniques are required to determine the phase shift in a material.
-% 
-% Referring to the particle properties of X-rays, photons can be randomly scattered in the material. Compton scattering 
-% 
-% Depending on the imaging system (geometry and energy), wide angle and small angle scattering can be sources of noise in conventional X-ray images.
+Regarding the particle properties of X-rays, photons are randomly scattered on fine structures in the material.
+Depending on the imaging system (geometry and energy), wide angle and small angle scattering are considered as typical sources of noise in conventional X-ray images.
 For the special type of scattering which occurs exclusively in forward direction and under ultra small angles (order of nano radiants), the particles usually remain within the area of a detector pixel.
 This effect is not recorded by absorption images and cannot directly be detected with standard techniques.
-% 
-% The main interest in the detectability of those additional interaction mechanisms is the fact that attenuation, phase shift and scattering are physically complementary interaction mechanisms, in the sense that their occurrence is mutually independent.
+
+The main interest in the detectability of those additional interaction mechanisms is the fact that attenuation, phase shift and scattering are physically complementary interaction mechanisms, in the sense that their occurrence is mutually independent.
 This gives rise to hypothesize that the complementary interaction mechanisms may eventually yield complementary image contrasts.
 
-In the past, a lot of effort has been invested into the development of techniques which are sensitive to the phase shift.
-Since most of the available phase contrast techniques rely on interference and thus typically on optical hardware (e.g.
+A huge effort has been invested in the past into the discovery of techniques which are sensitive to phase shift or scattering events.
+Since currently available phase contrast techniques rely on secondary physical effects, such as interference, and thus typically on optical hardware (e.g.
 crystals, gratings), they vary a lot in terms of sensitivity, practical applicability or achievable resolution.
-The vast majority of the methods, including crystal analyzer based \cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996} methods rely on X-ray beams of high spatial and temporal coherence, which is available only at synchrotron sources.
-Techniques which are compatible with an X-ray beam of low temporal coherence (broad bandwidth) are the in-line phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
-Phase-contrast techniques with X-ray beams of low temporal \textit{and} spatial coherence (i.e.
-from low-brilliance X-ray sources) are Talbot-Lau interferometry \cite{Pfeiffer2006} and coded apertures \cite{Munro2012}.
+The vast majority of the methods, including crystal analyzer based \cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996} methods rely on X-ray beams of high spatial and temporal coherence, available only at synchrotrons.
+Techniques with a high degree of spectral acceptance are the in-line phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
+Regarding the acceptance of X-ray beams with low temporal and spatial coherence (i.e.
+beams of low-brilliance X-ray source), Talbot-Lau interferometry \cite{Pfeiffer2006} and coded apertures \cite{Munro2012} are currently the only compatible techniques.
 
-Phase-contrast imaging has so far been used in the lower diagnostic energy range, i.e.
-from $15$ up to $85 \unit{keV}$.
-Talbot interferometry has been demonstrated using a synchrotron source at $82 \unit{keV}$ \cite{Willner2013}.
-Also using a synchrotron source, phase-contrast imaging at $85 \unit{keV}$ has been reported.
-Using a low-brilliance X-ray tube, Talbot-Lau interferometry was applied at $60 \unit{keV}$ \cite{Donath2009}.
-
-Imaging applications which may benefit from phase contrast at higher energies are for instance medical imaging tasks; chest or abdominal radiography or CT require energies between $100$ and $150 \unit{keV}$.
-Other potential applications are homeland security or chip failure analysis, which require high energies for the visualization of materials of high density.
-
-Here, we introduce a new method for phase-contrast imaging which is compatible with the entire diagnostic energy range of X-rays and with a compact geometry based on conventional X-ray tubes.
-The method is based on Talbot-Lau interferometry \cite{Pfeiffer2006} and employs a novel approach for the grating arrangement.
-Up to now, Talbot-Lau interferometry has been applied with a maximum design energy of $60 \unit{keV}$ \cite{Donath2009}.
-The challenge which limited the progress towards higher energies was mainly related to the manufacturing of gratings with high aspect ratios.
+Phase contrast techniques are nowadays widely available on synchrotrons, whereas only a few are applicable on compact imaging arrangements with conventional X-ray tubes.
+Up to now, none of the methods is compatible to the higher energy range of hard X-rays ($>50 \unit{keV}$).
+Therefore, imaging tasks requiring phase contrast at such high energies have so far been infeasible.
+Prominent examples are for instance medical imaging tasks such as chest or abdominal radiography or CT, which require energies up to $150 \unit{keV}$.
+Due to the low spatial coherence of typical X-ray sources in this energy range, in-line phase contrast methods are not promising.
+For the most promising technique, which is Talbot-Lau interferometry, grating fabrication is limited to X-ray energies up to approx.
+$50 \unit{keV}$ where the grating aspect ratio is the technical limiting factor.
 The aspect ratio, given by
@@
 \end{equation}
-where $p$ is the grating period and $h$ the grating structure height, is normally limited by the lithographic process, as grating structures tend to collapse or to deform (e.g.
-through capillary forces) if the aspect ratio is too high.
-For a given setup distance and for $p \propto 1/\sqrt{E}$ and $h \propto E^3$, it can be shown that $\textnormal{AR} \propto E^{7/2}$, where $E$ is the design energy of the system \cite{Momose2003a}.
-If at $E=25 \unit{keV}$ an aspect ratio for the absorption grating of around $\textnormal{AR}=30$ is necessary for a reasonable length of the experimental arrangement, it would have to be at least $128$ for $E=100 \unit{keV}$.
+where $p$ is the grating period and $h$ the grating structure height, cannot be aribtrarily high, as grating structures tend to collapse or to deform due to capillary forces.
+For a given setup distance and for $p \propto 1/\sqrt{E}$ and $h \propto E^3$, it can be shown that $\textnormal{AR} \propto E^{7/2}$.
+While for $25 \unit{keV}$, an aspect ratio for the absorption grating of around $\textnormal{AR}=30$ is necessary for a reasonable length of the experimental arrangement, it would have to be at least 128 for $100 \unit{keV}$.
 Moreover, when using a polychromatic spectrum, photons above the design energy should also be efficiently attenuated by the gratings to guarantee their contribution to the signal, which requires even higher aspect ratios.
-The maximum achievable aspect ratios of current grating fabrication techniques \cite{David2007,Kenntner2010} are $\textnormal{AR} \approx 60$, whereas such high values are often even beyond the limit and come at the expense of a poor grating quality and performance.
+The maximum aspect ratio, which has not significantly improved in the past few years, is $\textnormal{AR} \approx 60$, whereas such high values are often even beyond the limit and come at the expense of a poor grating quality and performance.
 
-Our approach is based on a new grating design which introduces the edge-on illumination of circularly shaped gratings.
+Here, we introduce a novel approach, which is based on Talbot-Lau interferometry and allows phase contrast and dark field imaging with low brilliance X-ray tubes at arbitrarily high energies.
+The approach is based on a new grating design, aiming at the edge-on illumination of gratings.
 Edge-on illumination, as opposed to face-on illumination, exploits the dimension along the grating lines to form a high aspect ratio of the structures in beam direction.
@@
 Increasing the effective aspect ratio of the gratings typically leads to a reduction of the field of view due to the change of the grating transmission function at high incident angles, which has also been identified by using a glancing angle of the gratings between zero and $90$ degrees \cite{Stutman2012a}.
-In order to overcome this problem with edge-on illuminated gratings, the grating lines are circularly aligned (i.e.
-on an arc) with a radius equal to the distance to the source.
+In order to overcome this problem with edge-on illuminated gratings, the grating lines are aligned on an arc with a radius equal to the distance to the source.
 
-The combination of edge-on illumination and the circularly curved structures enables phase-contrast imaging at arbitrary design energies and with a maximum field of view in horizontal direction ($x$ direction).
-These advantages come at the expense of a limited field of view in the vertical direction ($y$ direction), which is, depending on the X-ray detector, typically a few pixels.
-However, radiographic 2D imaging is possible in scanning mode, without increasing dose.
+The combination of edge-on illumination and the circularly curved structures allows design energies in the entire diagnostic energy range of X-rays.
+The arbitrary aspect ratio only comes at the expense of a limited field of view in the vertical dimension of the image plane, which is, depending on the detector, typically a few pixels.
+However, radiographic 2D images can still be acquired in sample scanning mode without increasing dose.
 Similarly, for tomographic images, the approach allows single slice CT or full 3D imaging in scanning mode.
@@
 For the present experiments, a symmetric interferometer with a grating period of $p = 2.8 \unit{\upmu m}$ for all gratings has been used.
-The design energy is $100 \unit{keV}$ and the beam splitter grating periodically shifts the phase by zero and $\pi$ at this energy \cite{David2002}.
+The design energy is $100 \unit{keV}$ and the beam splitter grating periodically shifts the phase by zero and $\pi$ at this energy.
 Using gold as the phase shifting material, this requires a structure length of $h_1 = 19.8 \unit{\upmu m}$.
-The analyzer grating is an absorption mask for sensing slight changes of the interference pattern generated by the beam splitter \cite{Momose2003a}.
+The analyzer grating is an absorption mask for sensing slight changes of the interference pattern generated by the beam splitter.
 With a structure length of $h_2 = 800 \unit{\upmu m}$, this grating has an aspect ratio of $2h/p \approx 570$ and thus sufficiently attenuates X-rays up to energies of around $160 \unit{keV}$.
@@
 The gratings have different curvatures which are specific to the grating interferometer geometry.
-(b) Zoom into the grating structures, contain interrupting bridges used for stabilizing the grating structures in the lithographic process \cite{Kenntner2010}.}
+(b) Zoom into the grating structures, contain interrupting bridges used for stabilizing the grating structures in the LIGA process.}
   \label{Fig:grating_mask}
@@
 
-Due to the high spectral acceptance \cite{Weitkamp2005,Thuering2013c} of the interferometer ($50 \unit{keV}$ to $>160 \unit{keV}$) and the high attenuation efficiencies of the source- and analyzer gratings ($>90\%$ up to $160 \unit{keV}$), the voltage of the X-ray source was set to the maximum of $160 \unit{kV}$.
+Due to the high spectral acceptance \cite{Weitkamp2005,Thuering2013c} of the interferometer ($50 \unit{keV}$ to $>160 \unit{keV}$) and the high attenuation efficiencies of the source- and analyzer gratings (<10\% up to $160 \unit{keV}$), the voltage of the X-ray source was set to the maximum of $160 \unit{kV}$.
 With a grating structure height of approx.
@@
 
-%Fig.
+Fig.
 3 shows a radiographic image of a metal screw in all three contrast modes, acquired with the $100 \unit{keV}$ setup.
@@
 
-Fig.~\ref{Fig:img_chip} shows an example of a radiographic scan of an electronic chip.
-Several resistors and an integrated circuit are located on different layers on the chip.
-The images were acquired in scanning mode, using a step size of $100 \unit{\upmu m}$ in $y$-direction.
-The number of phase steps \cite{Weitkamp2005} was 24 and the exposure time was 15 seconds per step.
-For the comparison of phase and absorption image, the figure further shows the differential absorption image, which has been obtained by digital differentiation.
-In the attenuation image, the soldering points of the integrated circuit are hardly visible underneath the resistors, while in the phase image, they can clearly be identified.
-This suggests that the differential nature of the phase contrast image may be useful to identify flaws in multi-layered electronic chips.
-\begin{figure} [ht]
-  \includegraphics[width = \linewidth]{figures/img_chip.eps}
-  \caption{}
-  \label{Fig:img_chip}
-\end{figure}
+Fig.
+4 shows another example of a radiographic scan of an electronic chip.
+The scan parameters were the same as for the previous example.
+Several resistors and an integrated circuit are located on a different layer on the chip.
+In the attenuation based projection image, the soldering points of the integrated circuit are hardly visibible underneath the resistors.
+In the phase image, they can clearly be identified.
+Furthermore, the phase image reveals variations in the shape of these soldering points.
+This illustrates how the differential nature of the phase contrast signal could potentially be used to identify flaws in multi-layered electronic chips, which might remain undetected on the absorption image.
 
-Edge-on illuminated grating interferometry breaks the current limitations to the lower diagnostic energy range for X-ray phase contrast imagin.
-Compact geometries  using conventional X-ray sources for design energies well above $100 \unit{keV}$ could be realized with the approach.
-This enables the examination of materials of higher density or thickness which would be intransparent at lower energies.
-Finally, the approach is not limited to X-ray imaging, but could easily be applied to other grating-based imaging modalities (e.g., with neutrons \cite{Grunzweig2008}) where high aspect ratios are necessary.
+Edge-on illuminated grating interferometry breaks the current limitation to the low diagnostic energy range for X-ray phase contrast imaging with conventional X-ray sources.
+Compact geometries for design energies well above 100 keV can be realized for the examination of dense materials which would be intransparent at lower energies of currently used phase contrast techniques.
+The approach is not limited to X-ray imaging, it can also be applied to other grating based imaging modalities (e.g., with neutrons \cite{Grunzweig2008}) where high aspect ratios are necessary.
 
@@
 \section*{Acknowledgements}
-We thank Gordan Mikuljan from Paul Scherrer Institute, Switzerland, for his work on the mechanical design, Joachim Schulz and Marco Walter from Micro Works GmbH, Germany, for the competent support on grating design issues, Christian Kottler and Vincent Revol from Centre Suisse d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful discussions on the design of the system.
+We thank Gordan Mikuljan from Paul Scherrer Institute, Switzerland, for his work on the mechanical design, Joachim Schulz and Marco Walter from Micro Works GmbH, Germany, for the competent support on grating design issues, Christian Kottler and Vincent Revol from Centre Suisse d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful discussions on grating interferometer design.
 

### 2013-08-20 natphys/hedpc_natphys.tex
Matteo's first review of the paper
- removed "new", "novel" and general hype
- general rephrasing, avoid repetitions and such
- included siunitx, acronym packages

@@
-%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for review and submission
-%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
-%\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}  % for review and submission
-%\documentclass[aps,prl,preprint]{revtex4-1}  % for double-spaced preprint
+%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
+%% for review and submission
+%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}
+% for double-spaced preprint
+%\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}
+% for review and submission
+%\documentclass[aps,prl,preprint]{revtex4-1} 
+% for double-spaced preprint
 \documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}
@@
 \usepackage{amssymb}   %math
-\usepackage{upgreek}   %non-italic greek letters
+\usepackage[detect-all]{siunitx}
 \usepackage[utf8]{inputenc} %Umlaute
+\usepackage{acronym}
 
@@
 %% New commands
-\newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}}
 \newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
@@
 
+%acronyms
+\acrodef{CT}{computed tomography}
+\acrodef{SNR}{signal-to-noise ratio}
+\acrodef{CNR}{contrast-to-noise ratio}
 %% ----------------------------------------------------------------------------------------------------------------
@@
 
-\title{X-ray phase-contrast imaging at 100~keV}
+\title{X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt}}
 
-\author{T.~Thüring}
+\author{T.~Thüring} \affiliation{Paul Scherrer Institut, Villigen PSI,
+Switzerland} \affiliation{Institute for Biomedical Engineering, Swiss
+Federal Institute of Technology, Zurich, Switzerland} \author{M.~Abis}
 \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
-  \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
-\author{M.~Abis}
+\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute
+of Technology, Zurich, Switzerland} \author{Z.~Wang} \affiliation{Paul
+Scherrer Institut, Villigen PSI, Switzerland} \author{C.~David}
 \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
-  \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
-\author{Z.~Wang}
-  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
-\author{C.~David}
-  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
-\author{M.~Stampanoni}
-  \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
-  \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
+\author{M.~Stampanoni} \affiliation{Paul Scherrer Institut, Villigen PSI,
+Switzerland} \affiliation{Institute for Biomedical Engineering, Swiss
+Federal Institute of Technology, Zurich, Switzerland}
 
@@
 %% ----------------------------------------------------------------------------------------------------------------
-\begin{abstract}
-Phase contrast imaging with X-rays is an exciting field that reveals new insights into material properties by providing access to a complementary physical contrast mechanism.
-Phase sensitive imaging in the high energy range of hard X-rays, i.e.
-between $80$ and $150 \unit{keV}$ is still largely unexplored, as the current methods typically entail severe technical challenges.
-With a novel approach, we demonstrate phase contrast as well as dark-field contrast imaging on laboratory systems with low-brilliance X-ray sources in the entire diagnostic energy range.
-A phase-contrast technique at such high energies is of particularly high scientific and industrial interest as it would vastly expand the range of applications, for instance, by the examination of materials of high density or thickness.
-The approach includes a new technique for the grating manufacturing in Talbot-Lau interferometry.
-Firstly, the approach breaks the current limits of achievable grating aspect ratios, which has been a key issue for a long time in the past.
-Secondly, it solves the intrinsic reduction of the field of view which occurs for gratings with such high aspect ratios.
-Using an imaging arrangement based on a conventional X-ray tube, phase and dark-field-contrast imaging at $100 \unit{keV}$ is demonstrated for the first time.
-This achievement paves the road for the transfer of phase-contrast imaging into fields where high energies are required, such as medical CT, chip failure analysis or homeland security.
-\end{abstract}
+\begin{abstract} Phase contrast imaging with X-rays provides access to
+    complementary physical contrast mechanisms. Phase sensitive imaging in
+    the diagnostic energy range between $80$ and
+    $\SI{150}{\kilo\electronvolt}$ is still largely unexplored, as the
+    current methods typically entail severe technical challenges. A
+    phase-contrast technique at such high energies is of scientific and
+    industrial interest as it vastly expands the range of applications, for
+    instance, by the examination of materials of high density or thickness.
+    The approach includes a new design for the grating manufacturing in
+    Talbot-Lau interferometry, with an edge-on illumination and curved
+    structures to match the beam divergence. The edge-on approach breaks the
+    current limits of achievable grating aspect ratios, which has been a key
+    issue for a long time. The curvature of the gratings solves the
+    intrinsic reduction of the field of view which occurs for gratings with
+    such high aspect ratios. Using an imaging arrangement based on a
+    conventional X-ray tube, phase and dark-field contrast imaging at
+    $\SI{100}{\kilo\electronvolt}$ is demonstrated. This achievement paves
+    the road for the transfer of phase-contrast imaging into fields where
+    high energies are required, such as medical computed tomography, chip
+    failure analysis or homeland security. \end{abstract}
 
@@
 
-X-ray radiography and computed tomography (CT) are nowadays standard imaging techniques in materials and life science for the non-destructive examination of samples or the diagnosis of diseases in patients.
-The underlying contrast mechanism relies on the different X-ray attenuation properties of two materials or tissue types.
-The dominant physical effects contributing to attenuation are the photo-electric effect and incoherent (Compton) scattering.
-The sum of their contributions determine the attenuation coefficient, which is a wavelenght dependent material parameter.
-Apart from attenuation, the wave nature of X-rays reveals another contrast mechanism, which is the phase shift.
-The physical interaction effect attributed to phase shifts is coherent (Rayleigh) scattering \cite{Als-Nielsen2011}.
+X-ray radiography and \ac{CT} are nowadays standard imaging techniques in
+materials and life sciences for the nondestructive examination of samples or
+the diagnosis of diseases in patients. The underlying contrast mechanism
+relies on the different X-ray attenuation properties of different materials
+or tissue types. The dominant physical effects contributing to attenuation
+are the photoelectric effect and incoherent (Compton) scattering. The sum of
+their contributions determines the attenuation coefficient, which is a
+wavelength dependent material parameter. Besides attenuation, the wave
+nature of X-rays reveals another contrast mechanism, which is the phase
+shift. The interaction contributing to phase shifts is coherent (Rayleigh)
+scattering \cite{Als-Nielsen2011}.
 
-Using the material parameter $n=1-\delta(\mathbf{r},\lambda) + i \beta(\mathbf{r},\lambda)$, known from X-ray wave optics as the complex index of refraction, the wavelenght dependent attenuation and phase shift properties of an object at the spatial coordinate $\mathbf{r}$ are fully described.
-The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the attenuation per unit length (attenuation coefficient) by $\mu = 4 \pi \beta(\mathbf{r},\lambda) / \lambda$ and the total attenuation by an object of thickness $d$ can be described by the line integral $L_\mu = \int_0^d \mu(\mathbf{r},\lambda) \d l$.
-Similarly, the real part $\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by $\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi = \int_0^d \phi(\mathbf{r}) \d l$.
+Using the material parameter $n=1-\delta(\mathbf{r},\lambda) + i
+\beta(\mathbf{r},\lambda)$, known from X-ray wave optics as the complex
+index of refraction, the wavelength dependent attenuation and phase shift
+properties of an object at the spatial coordinate $\mathbf{r}$ are fully
+described. The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the
+attenuation per unit length (attenuation coefficient) by $\mu = 4 \pi
+\beta(\mathbf{r},\lambda) / \lambda$ and the total attenuation by an object
+of thickness $d$ can be described by the line integral $L_\mu = \int_0^d
+\mu(\mathbf{r},\lambda) \d l$. Similarly, the real part
+$\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by
+$\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi =
+\int_0^d \phi(\mathbf{r}) \d l$.
 
-While the attenuation line integral $L_\mu$ can be directly measured with an X-ray detector by measuring the reduction of the beam intensity $I$ ($L_\mu \propto \log(I)$), the measurement of the phase shift integral $L_\phi$ is more challenging as there is no such simple relation.
-However, phase sensitive imaging is a desirable modality, as it can provide an enhanced contrast-to-noise ratio (CNR) in images compared to attenuation for certain materials or in different tissue \cite{Pfeiffer2007a,McDonald2009}.
-Furthermore, the refractive index decrement $\delta$ provides direct access to the electron density \cite{Als-Nielsen2011} and in combination with attenuation, it further enables the determination of the effective atomic number of a material \cite{Qi2010}.
+While the attenuation line integral $L_\mu$ can be directly measured with an
+X-ray detector by measuring the reduction of the beam intensity $I$ ($L_\mu
+\propto \log(I)$), the measurement of the phase shift integral $L_\phi$ is
+more challenging as there is no such simple relation. However, phase
+sensitive imaging is a desirable modality, as it can provide an enhanced
+\ac{CNR} in images compared to attenuation for certain
+materials or in different tissues \cite{Pfeiffer2007a,McDonald2009}.
+Furthermore, the refractive index decrement $\delta$ provides direct access
+to the electron density \cite{Als-Nielsen2011} and in combination with
+attenuation, it further enables the determination of the effective atomic
+number of a material \cite{Qi2010}.
 
-In the past, a lot of effort has been invested into the development of techniques which are sensitive to the phase shift.
-Since most of the available phase contrast techniques rely on interference and thus typically on optical hardware (e.g.
-crystals, gratings), they vary a lot in terms of sensitivity, practical applicability or achievable resolution.
-The vast majority of the methods, including crystal analyzer based \cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996} methods rely on X-ray beams of high spatial and temporal coherence, which is available only at synchrotron sources.
-Techniques which are compatible with an X-ray beam of low temporal coherence (broad bandwidth) are the in-line phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
-Phase-contrast imaging using X-ray beams of low temporal \textit{and} spatial coherence (i.e.
-from low-brilliance X-ray sources) have been demonstrated with Talbot-Lau interferometry \cite{Pfeiffer2006} and coded apertures \cite{Munro2012}.
+In the past, a lot of effort has been invested into the development of
+techniques which are sensitive to the phase shift. Since most of the
+available phase contrast techniques rely on interference and thus typically
+on optical hardware (e.g. crystals, gratings), they vary a lot in terms of
+sensitivity, practical applicability or achievable resolution. The vast
+majority of the methods, including crystal analyzer based
+\cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996}
+methods rely on X-ray beams of high spatial and temporal coherence, which is
+available only at synchrotron sources. Techniques which are compatible with
+an X-ray beam of low temporal coherence (broad bandwidth) are the in-line
+phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
+Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
+Phase-contrast imaging using X-ray beams of low temporal \emph{and}
+spatial coherence such as conventional low-brilliance X-ray tubes have been
+demonstrated with Talbot-Lau interferometry \cite{Pfeiffer2006} and coded
+apertures \cite{Munro2012}.
 
-Phase-contrast imaging has so far been used in the lower diagnostic energy range, i.e.
-from $15$ up to $85 \unit{keV}$.
-Talbot interferometry has been demonstrated using a synchrotron source at $82 \unit{keV}$ \cite{Willner2013}.
-Also using a synchrotron source, phase-contrast imaging at $85 \unit{keV}$ has been reported.
-Using a low-brilliance X-ray tube, Talbot-Lau interferometry was applied at $60 \unit{keV}$ mean energy \cite{Donath2009}.
-Imaging applications which may benefit from phase contrast at higher energies are for instance medical imaging tasks; chest or abdominal radiography or CT require energies between $100$ and $150 \unit{keV}$.
-Other potential applications are homeland security or chip failure analysis, which require high energies for the visualization of materials of high density.
+Phase-contrast imaging has so far been used in the energy
+range from $15$ up to $\SI{85}{\kilo\electronvolt}$. Talbot
+interferometry has been demonstrated using a synchrotron source at
+$\SI{82}{\kilo\electronvolt}$ \cite{Willner2013}. Also using a synchrotron
+source, phase-contrast imaging at $\SI{85}{\kilo\electronvolt}$ has been
+reported. Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
+applied at $\SI{60}{\kilo\electronvolt}$ mean energy \cite{Donath2009}.
+Medical imaging applications may benefit from phase contrast at higher
+energies: chest or abdominal
+radiography or \ac{CT} require energies between $100$ and
+$\SI{150}{\kilo\electronvolt}$. Other potential applications are homeland
+security or chip failure analysis, which require high energies for the
+visualization of materials of high density and atomic number.
 
-Here, we introduce a new method for phase-contrast imaging which is compatible with the entire diagnostic energy range of X-rays.
-Moreover, the method is fully compatible with compact imaging arrangements based on conventional X-ray tubes.
-The method is based on Talbot-Lau interferometry \cite{Pfeiffer2006} and employs a novel approach for the grating design and arrangement.
-Up to now, Talbot-Lau interferometry has been applied with a maximum design energy of $60 \unit{keV}$ \cite{Donath2009}.
-The challenge which limited the progress towards higher energies was mainly related to the manufacturing of gratings with high aspect ratios.
-The aspect ratio, given by
+Here, we introduce a method for phase-contrast imaging which is
+compatible with the entire diagnostic energy range of X-rays. Moreover, the
+method is fully compatible with compact imaging arrangements based on
+conventional X-ray tubes. The method is based on Talbot-Lau interferometry
+\cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
+arrangement. Up to now, Talbot-Lau interferometry has been applied with a
+maximum design energy of $\SI{60}{\kilo\electronvolt}$ \cite{Donath2009}.
+The challenge which limited the progress towards higher energies was mainly
+related to the manufacturing of gratings with high aspect ratios. The aspect
+ratio, given by
 \begin{equation}
- \textnormal{AR} = \frac{2h}{p},
+    \text{AR} = \frac{2h}{p},
 \end{equation}
-where $p$ is the grating period and $h$ the grating structure height, is normally limited by the lithographic process, as grating structures tend to collapse or to deform (e.g.
-through capillary forces) if the aspect ratio is too high.
-For a given setup distance and for $p \propto 1/\sqrt{E}$ and $h \propto E^3$, it can be shown that $\textnormal{AR} \propto E^{7/2}$, where $E$ is the design energy of the system \cite{Momose2003a}.
-If at $E=25 \unit{keV}$ an aspect ratio for the absorption grating of around $\textnormal{AR}=30$ is necessary for a reasonable length of the experimental arrangement, it would have to be at least $128$ for $E=100 \unit{keV}$.
-Moreover, when using a polychromatic spectrum, photons above the design energy should also be efficiently attenuated by the gratings to guarantee their contribution to the signal, which requires even higher aspect ratios.
-Maximum achievable aspect ratios of current grating fabrication techniques \cite{David2007,Kenntner2010} are approximately around 60, whereas such high values are often even beyond the limit and come at the expense of a poor grating quality and performance.
+where $p$ is the grating period and $h$ the grating structure
+height, is normally limited by the lithographic process, as grating
+structures tend to collapse or to deform (e.g. through capillary forces) if
+the aspect ratio is too high. For a given setup distance these parameters
+depend on the target energy $E$ according to $p \propto
+1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{AR}
+\propto E^{7/2}$\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
+for the absorption grating of around $\textnormal{AR}=30$ is necessary for a
+reasonable length of the experimental arrangement, it would have to be at
+least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
+broad spectrum, photons above the design energy should also be
+efficiently attenuated by the gratings, which requires even higher aspect ratios.
+Maximum achievable aspect ratios of current grating fabrication techniques
+\cite{David2007,Kenntner2010} are approximately around 60,
+larger values are often not achievable or come at the expense of a very poor
+grating quality and performance.
 
-Our approach is based on a new grating design which introduces the edge-on illumination of circularly aligned structures.
-Edge-on illumination, as opposed to face-on illumination, exploits the dimension along the grating lines to form a high aspect ratio of the structures in beam direction.
-The effective structure height of the grating is then determined by the grating dimension along the grating lines, which essentially allows arbitrarily high aspect ratios.
-FIG.~\ref{Fig:schematic} illustrates the edge-on illumination approach.
-\begin{figure} [ht]
-  \includegraphics[width = \linewidth]{figures/figure1.eps}
-  \caption{Schematic of a grating interferometer for high X-ray energies in edge-on illumination mode.
-The aspect ratio is defined by the ratio of the travelling distance along the grating lines and the period and can be arbitrarily long.
-In order to avoid a reduction of the field of view, the grating structures are aligned on an arc.}
+Our design introduces the edge-on
+illumination of circularly aligned structures. Edge-on illumination
+(figure~\ref{Fig:schematic}), as
+opposed to face-on illumination, exploits the dimension along the grating
+lines to form a high aspect ratio of the structures in direction of the beam. The
+effective structure height of the grating is then determined by the grating
+dimension along the grating lines, which essentially allows arbitrarily high
+aspect ratios. 
+\begin{figure}[ht]
+    \includegraphics[width=\linewidth]{figures/figure1.eps}
+    \caption{Schematic of a grating
+        interferometer for X-ray energies between 60 and
+        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
+        aspect ratio is defined by the ratio of the travelling distance along the
+        grating lines and the period and can be arbitrarily long. In order to avoid
+        a reduction of the field of view, the grating structures are aligned on an
+    arc.}
     \label{Fig:schematic}
@@
 
-Increasing the effective aspect ratio of the gratings typically leads to a reduction of the field of view due to the change of the grating transmission function at high incident angles, which has also been identified by using a glancing angle of the gratings between zero and $90$ degrees \cite{Stutman2012a}.
-In order to overcome this problem with edge-on illuminated gratings, the grating lines are circularly aligned (i.e.
-on an arc) with a radius equal to the distance to the source.
+Increasing the aspect ratio of the gratings typically leads to a
+reduction of the field of view due to the change of the grating transmission
+function at high incident angles, which has also been identified by using a
+glancing angle of the gratings between zero and \SI{90}{\degree}
+\cite{Stutman2012a}. In order to overcome this problem, the grating lines are circularly aligned 
+with a radius equal to the distance to the source.
 
-The combination of edge-on illumination and circularly aligned structures enables phase-contrast imaging at arbitrary design energies and with a maximum field of view in horizontal direction ($x$ direction).
-These advantages come at the expense of a limited field of view in the vertical direction ($y$ direction), which is, depending on the X-ray detector, typically a few pixels.
-However, radiographic 2D imaging is possible in scanning mode, without increasing dose.
-Similarly, for tomographic images, the approach allows single slice CT or full 3D imaging in scanning mode.
+The combination of edge-on illumination and circularly aligned structures
+enables phase-contrast imaging at arbitrary design energies and with a
+maximum field of view in the horizontal direction ($x$ direction). These
+advantages come at the expense of a limited field of view in the vertical
+direction ($y$ direction), which is, depending on the X-ray detector,
+typically a few pixels. However, radiographic 2D imaging is possible in
+scanning mode, without increasing dose. Similarly, for tomographic images,
+the approach allows single slice \ac{CT} or full 3D imaging in scanning mode.
 
-Grating design and fabrication is non-standard and involves a complex mask design, as shown in FIG.~\ref{Fig:grating_mask}.
-Each grating resides on a silicon chip and has its specific structure length and curvature.
-For the present experiments, a symmetric interferometer with a grating period of $p = 2.8 \unit{\upmu m}$ for all gratings has been used.
-The design energy is $100 \unit{keV}$ and the beam splitter grating periodically shifts the phase by zero and $\pi$ at this energy \cite{David2002}.
-Using gold as the phase shifting material, this requires a structure length of $h_1 = 19.8 \unit{\upmu m}$.
-The analyzer grating is an absorption mask for sensing slight changes of the interference pattern generated by the beam splitter \cite{Momose2003a}.
-With a structure length of $h_2 = 800 \unit{\upmu m}$, this grating has an aspect ratio of $2h/p \approx 570$ and thus sufficiently attenuates X-rays up to energies of around $160 \unit{keV}$.
-Beam splitter- and analyzer grating are separated at the first fractional Talbot order \cite{Weitkamp2005}, resulting in an inter-grating distance of $158 \unit{mm}$.
-The source grating splits the relatively large focal spot ($\sim 1 \unit{mm}$) into an array of individually coherent, but mutually incoherent sources \cite{Pfeiffer2006}.
-It is also made of gold structures with a structure length of $h_0 = h_2 = 800 \unit{\upmu m}$.
+Grating design and fabrication is nonstandard and involves a complex mask
+design, as shown in Figure~\ref{Fig:grating_mask}. Each grating resides on a
+silicon chip and has its specific structure length and curvature. For the
+current experiments, a symmetric interferometer with a grating period of $p
+= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
+is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
+shifts the phase by zero and $\pi$ at this energy \cite{David2002}. Using
+gold as the phase shifting material, this requires a structure length of
+$h_1 = \SI{19.8}{\micro \metre}$. The analyzer grating is an absorption mask
+for sensing slight changes of the interference pattern generated by the beam
+splitter \cite{Momose2003a}. With a structure length of $h_2 =
+\SI{800}{\micro \metre}$, this grating has an aspect ratio of $2h/p \approx
+570$ and thus sufficiently attenuates X-rays up to energies of 
+$\SI{160}{\kilo\electronvolt}$. Beam splitter- and analyzer grating are
+separated at the first fractional Talbot order \cite{Weitkamp2005},
+resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
+source grating splits the relatively large focal spot ($\sim
+\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
+incoherent sources \cite{Pfeiffer2006}. It is also made of gold structures
+with a structure length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
 \begin{figure} [ht]
-  \includegraphics[width = \linewidth]{figures/grating_mask.eps}
-  \caption{Grating design mask for the edge-on illumination approach.
-(a) Top part of the 4 inch wafer, showing five grating chips; one source grating, two beam splitter gratings and two analyzer gratings (from top to bottom).
-The gratings have different curvatures which are specific to the grating interferometer geometry.
-(b) Zoom into the grating structures, contain interrupting bridges used for stabilizing the grating structures in the lithographic process \cite{Kenntner2010}.}
+    \includegraphics[width=\linewidth]{figures/grating_mask.eps}
+    \caption{Grating design mask for
+        the edge-on illumination approach. (a) Top part of the 4 inch wafer,
+        showing five grating chips; one source grating, two beam splitter
+        gratings and two analyzer gratings (from top to bottom). The
+        gratings have different curvatures which are specific to the grating
+        interferometer geometry. (b) Zoom into the grating structures,
+        contain interrupting bridges used for stabilizing the grating
+        structures in the lithographic process \cite{Kenntner2010}.}
         \label{Fig:grating_mask}
@@
 
-Due to the high spectral acceptance \cite{Weitkamp2005,Thuering2013c} of the interferometer ($50 \unit{keV}$ to $>160 \unit{keV}$) and the high attenuation efficiencies of the source- and analyzer gratings ($>90\%$ up to $160 \unit{keV}$), the voltage of the X-ray source was set to the maximum of $160 \unit{kV}$.
-With a grating structure height of approx.
-$100 \unit{\upmu m}$, the field of view in the vertical direction is limited to one detector pixel row.
-In the horizontal direction, the field of view is limited by the grating size and the geometric magnification of the sample, yielding a maximum field of view of $30 \unit{mm}$.
-In addition to the standard components (source, camera, interferometer), two optical slits, one in front of the source grating, the other in front of the camera, were required for the collimation of the beam in the vertical direction.
-X-rays which are not travelling through all of the gratings do not contribute to the signal and are attenuated by the slits.
+Due to the high spectral acceptance \cite{Weitkamp2005,Thuering2013c} of the
+interferometer ($\SI{50}{\kilo\electronvolt}$ to
+$>\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
+the source- and analyzer gratings ($>90\%$ up to
+$\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
+the maximum of $\SI{160}{\kilo\volt}$. With a grating structure height of
+approx. $\SI{100}{\micro \metre}$, the field of view in the vertical
+direction is limited to one detector pixel row. In the horizontal direction,
+the field of view is limited by the grating size and the geometric
+magnification of the sample, yielding a maximum field of view of
+$\SI{30}{\milli\metre}$. In addition to the standard components (source,
+camera, interferometer), two optical slits, one in front of the source
+grating, the other in front of the camera, were required for the collimation
+of the beam in the vertical direction. X-rays which are not travelling
+through all of the gratings do not contribute to the signal and are
+attenuated by the slits.
 
-%Fig.
-3 shows a radiographic image of a metal screw in all three contrast modes, acquired with the $100 \unit{keV}$ setup.
-The images were acquired in scanning mode, using a step size of $100 \unit{\upmu m}$.
-The number of phase steps was 24 and the exposure time was 15 seconds per step.
-Grating interferometry at such a high diagnostic energy allows to examine more dense materials such as metals in phase contrast mode.
-At lower energies, the phase shifts of such materials would be too large and wrap over multiple periods of the analyzer grating.
+%Fig. 3 shows a radiographic image of a metal screw in all three contrast
+%modes, acquired with the $\SI{100}{\kilo\electronvolt}$ setup. The images
+%were acquired in scanning mode, using a step size of $\SI{100}{\micro
+%\metre}$. The number of phase steps was 24 and the exposure time was 15
+%seconds per step. Grating interferometry at such a high diagnostic energy
+%allows to examine more dense materials such as metals in phase contrast
+%mode. At lower energies, the phase shifts of such materials would be too
+%large and wrap over multiple periods of the analyzer grating.
 
 Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
-Several resistors and an integrated circuit are located on different layers on the chip.
-The images were acquired in scanning mode, using a step size of $100 \unit{\upmu m}$ in $y$-direction.
-For a better comparison of the magnified phase and attenuation images, the attenuation image has been replaced with the differential attenuation image, which was obtained by digital differentiation.
-In the attenuation image, the soldering points of the integrated circuit are hardly visible underneath the resistors, while in the phase image, they can clearly be identified.
-This clearly implies the benefit of the differential nature of the phase-contrast image, which may be useful to identify flaws in multi-layered structures such as electronic chips.
-\begin{figure} [ht]
-  \includegraphics[width = \linewidth]{figures/img_chip_dabs.pdf}
+Several resistors and an integrated circuits are located on different layers
+on the chip. The images were acquired in scanning mode, using a step size of
+$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
+magnified phase and attenuation images, the attenuation image has been
+replaced with the differential attenuation image, which was obtained by
+digital differentiation. In the attenuation image, the soldering points of
+the integrated circuit are hardly visible underneath the resistors, while in
+the phase image, they can clearly be identified. This shows the
+benefit of the differential nature of the phase-contrast image, which may be
+useful to identify flaws in multi-layered structures such as electronic
+chips.
+\begin{figure}[ht]
+    \includegraphics[width=\linewidth]{figures/img_chip_dabs.eps}
     \caption{}
@@
 
-Edge-on illuminated grating interferometry breaks the current limitations of phase-contrast imaging to the lower diagnostic energy range.
-Compact geometries  using conventional X-ray sources for design energies well above $100 \unit{keV}$ could be realized with the approach.
-This enables the examination of materials of higher density or thickness which would be intransparent at lower energies.
-Finally, the approach is not limited to X-ray imaging, but could easily be applied to other grating-based imaging modalities (e.g., with neutrons \cite{Grunzweig2008}) where high aspect ratios are required.
+Edge-on illuminated grating interferometry breaks the current limitations of
+phase-contrast imaging to the lower diagnostic energy range. Compact
+geometries  using conventional X-ray sources for design energies well above
+$\SI{100}{\kilo\electronvolt}$ could be realized with the approach. This
+enables the examination of materials of higher density or thickness which
+would be intransparent at lower energies. Finally, the approach is not
+limited to X-ray imaging, but could easily be applied to other grating-based
+imaging modalities (e.g., with neutrons \cite{Grunzweig2008}) where high
+aspect ratios are required.
 
 \section*{Methods}
-Edge-on illuminated gratings were manufactured by Micro Works GmbH, Germany, using a LIGA process \cite{Kenntner2010}.
-Each grating resides on a $5 \times 60 \unit{mm^2}$ silicon chip and several grating chips are fabricated on a single 4 inch silicon wafer.
-The experimental arrangement for a design energy at 100 keV is a symmetric Talbot-Lau interferometer with a grating period of $p = 2.8 \unit{\upmu m}$ for all gratings.
-The distance from the source grating to the analyzer grating is $32 \unit{cm}$ and the source grating is positioned $23 \unit{cm}$ away from the source.
-The number of phase steps for one projection was 24 \cite{Weitkamp2005} and the exposure time for the images was 15 seconds per phase steps.
+Edge-on illuminated gratings were manufactured by Micro
+Works GmbH, Germany, using a LIGA process \cite{Kenntner2010}. Each grating
+resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
+grating chips are fabricated on a single 4 inch silicon wafer. The
+experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
+is a symmetric Talbot-Lau interferometer with a grating period of $p =
+\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
+grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
+grating is positioned $\SI{23}{\centi\metre}$ away from the source. The
+number of phase steps for one projection was 24 \cite{Weitkamp2005} and the
+exposure time for the images was 15 seconds per phase step.
 
-The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output voltage of $160 \unit{kV}$.
-In the experiment, it was set to the maximum voltage.
-The focal spot size is approximately $1 \unit{mm}$.
-The detector is a CCD camera from Finger Lakes Instruments.
-A cesium iodide (CsI:Ti) scintillator of $600 \unit{\upmu m}$ thickness converts the X-rays to visible light and is coupled with an optical lens projecting the image onto the CCD.
-The effective pixel size is $80 \unit{\upmu m}$.
-The widths of the collimating slits are $25 \unit{\upmu m}$ and $100 \unit{\upmu m}$, respectively.
+The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
+voltage of $\SI{160}{\kilo\volt}$. In the experiment, it was set to the
+maximum voltage. The focal spot size is approximately
+$\SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
+Instruments. A cesium iodide (CsI:Ti) scintillator of $\SI{600}{\micro
+\metre}$ thickness converts the X-rays to visible light and is coupled with
+an optical lens projecting the image onto the CCD. The effective pixel size
+is $\SI{80}{\micro \metre}$. The widths of the collimating slits are
+$\SI{25}{\micro \metre}$ and $\SI{100}{\micro \metre}$, respectively.
 
-In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps \cite{Weitkamp2005} and an exposure time of 15 seconds per step.
+In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps
+\cite{Weitkamp2005} and an exposure time of 15 seconds per step.
 
-\section*{Acknowledgements}
-We thank Gordan Mikuljan from Paul Scherrer Institute, Switzerland, for his work on the mechanical design, Joachim Schulz and Marco Walter from Micro Works GmbH, Germany, for the competent support on grating design issues, Christian Kottler and Vincent Revol from Centre Suisse d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful discussions on the design of the system.
+\section*{Acknowledgements} We thank Gordan Mikuljan from Paul Scherrer
+Institute, Switzerland, for his work on the mechanical design, Joachim
+Schulz and Marco Walter from Micro Works GmbH, Germany, for the competent
+support on grating design issues, Christian Kottler and Vincent Revol from
+Centre Suisse d'Electronique et de Microtechnique (CSEM), Switzerland for
+the fruitful discussions on the design of the system.
 
-\bibliographystyle{apsrev4-1}
-\bibliography{library}
+\bibliographystyle{apsrev4-1} \bibliography{library}
 

### 2013-08-20 natphys/hedpc_natphys.tex
acronym not working

@@
 %\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}
-% for review and submission
+%for review and submission
 %\documentclass[aps,prl,preprint]{revtex4-1} 
 % for double-spaced preprint
+%\documentclass[aip,apl,amsmath,amssymb,floatfix,preprint,a4paper]{revtex4-1}
 \documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}
@@
 %% Packages
-\usepackage{graphicx}  %figures
-\usepackage{subfigure} %subfigures
-\usepackage{amssymb}   %math
-\usepackage[detect-all]{siunitx}
 \usepackage[utf8]{inputenc} %Umlaute
 \usepackage{acronym}
-
-%% hyphenation settings
-\hyphenation{ALPGEN} 
-\hyphenation{EVTGEN}
-\hyphenation{PYTHIA}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{graphicx}  %figures
+\usepackage[detect-all]{siunitx}
 
@@
 %% ----------------------------------------------------------------------------------------------------------------
+
 \begin{document}
@@
 
-\author{T.~Thüring} \affiliation{Paul Scherrer Institut, Villigen PSI,
-Switzerland} \affiliation{Institute for Biomedical Engineering, Swiss
-Federal Institute of Technology, Zurich, Switzerland} \author{M.~Abis}
+\author{T.~Thüring}
 \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
-\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute
-of Technology, Zurich, Switzerland} \author{Z.~Wang} \affiliation{Paul
-Scherrer Institut, Villigen PSI, Switzerland} \author{C.~David}
+\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
+\author{M.~Abis}
 \affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
-\author{M.~Stampanoni} \affiliation{Paul Scherrer Institut, Villigen PSI,
-Switzerland} \affiliation{Institute for Biomedical Engineering, Swiss
-Federal Institute of Technology, Zurich, Switzerland}
+\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
+\author{Z.~Wang}
+\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
+\author{C.~David}
+\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
+\author{M.~Stampanoni}
+\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
+\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
 
@@
 %% ----------------------------------------------------------------------------------------------------------------
-\begin{abstract} Phase contrast imaging with X-rays provides access to
+\begin{abstract}
+    Phase contrast imaging with X-rays provides access to
     complementary physical contrast mechanisms. Phase sensitive imaging in
@@
     high energies are required, such as medical computed tomography, chip
-    failure analysis or homeland security. \end{abstract}
+    failure analysis or homeland security.
+\end{abstract}
 
@@
     \includegraphics[width=\linewidth]{figures/img_chip_dabs.eps}
-    \caption{}
+    \caption{Radiographic scan of an electronic chip. The image was acquired
+        with 24 phase steps and an exposure time of \SI{15}{\second} per
+    step.}
     \label{Fig:img_chip}

### 2013-09-03 natphys/hedpc_natphys.tex
Marco's revision
- changed revtex output to double spaced one column
- compact setup in the abstract
- cite Ruiz poster on GI @123 keV at ESRF
- removed comments on the max energy of recent experiments other than GI at
  synchrotron or table top sources
- phase nature rather than differential nature of the DPC
- updated caption of chip image to include differential abs
- added comment on long exposure due to low visibility
- added grant in the acknowledgements

@@
 %for review and submission
-%\documentclass[aps,prl,preprint]{revtex4-1} 
+\documentclass[aps,prl,preprint]{revtex4-1} 
 % for double-spaced preprint
 %\documentclass[aip,apl,amsmath,amssymb,floatfix,preprint,a4paper]{revtex4-1}
-\documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}
+%\documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}
 
@@
     intrinsic reduction of the field of view which occurs for gratings with
-    such high aspect ratios. Using an imaging arrangement based on a
+    such high aspect ratios and allows for a very compact setup, with a
+    distance of \SI{31}{\centi\metre} between the source grating and the
+    analyzer grating. Using an imaging arrangement based on a
     conventional X-ray tube, phase and dark-field contrast imaging at
@@
 
-Phase-contrast imaging has so far been used in the energy
-range from $15$ up to $\SI{85}{\kilo\electronvolt}$. Talbot
-interferometry has been demonstrated using a synchrotron source at
-$\SI{82}{\kilo\electronvolt}$ \cite{Willner2013}. Also using a synchrotron
-source, phase-contrast imaging at $\SI{85}{\kilo\electronvolt}$ has been
-reported. Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
+Talbot interferometry has been demonstrated using a synchrotron source at
+$\SI{82}{\kilo\electronvolt}$ \cite{Willner2013} and
+$\SI{123}{\kilo\electronvolt}$\cite{Ruiz2013}.
+Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
 applied at $\SI{60}{\kilo\electronvolt}$ mean energy \cite{Donath2009}.
@@
 \cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
-arrangement. Up to now, Talbot-Lau interferometry has been applied with a
-maximum design energy of $\SI{60}{\kilo\electronvolt}$ \cite{Donath2009}.
+arrangement. 
 The challenge which limited the progress towards higher energies was mainly
@@
 \begin{figure}[ht]
-    \includegraphics[width=\linewidth]{figures/figure1.eps}
+    \includegraphics[width=.5\textwidth]{figures/figure1.eps}
     \caption{Schematic of a grating
@@
 \begin{figure} [ht]
-    \includegraphics[width=\linewidth]{figures/grating_mask.eps}
+    \includegraphics[width=.5\textwidth]{figures/grating_mask.eps}
     \caption{Grating design mask for
@@
 replaced with the differential attenuation image, which was obtained by
-digital differentiation. In the attenuation image, the soldering points of
-the integrated circuit are hardly visible underneath the resistors, while in
+digital differentiation. In the attenuation image, the contrast of the soldering points of
+the integrated circuit is reduced underneath the resistors, while in
 the phase image, they can clearly be identified. This shows the
-benefit of the differential nature of the phase-contrast image, which may be
-useful to identify flaws in multi-layered structures such as electronic
+benefit of the phase nature of the image, which may be
+useful to identify flaws in multilayered structures such as electronic
 chips.
 \begin{figure}[ht]
-    \includegraphics[width=\linewidth]{figures/img_chip_dabs.eps}
+    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
     \caption{Radiographic scan of an electronic chip. The image was acquired
         with 24 phase steps and an exposure time of \SI{15}{\second} per
-    step.}
+    step. The top right image shows the differential absorption image.}
     \label{Fig:img_chip}
@@
 In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps
-\cite{Weitkamp2005} and an exposure time of 15 seconds per step.
+\cite{Weitkamp2005} and an exposure time of 15 seconds per step. The long
+exposure times are mostly constrained by the low average visibility of the
+gratings (\SI{5}{\percent}). As the quality in the manufacturing of the
+structure increases, the exposure time can become substantially shorter.
 
@@
 Institute, Switzerland, for his work on the mechanical design, Joachim
-Schulz and Marco Walter from Micro Works GmbH, Germany, for the competent
+Schulz and Marco Walter from Microworks GmbH, Germany, for the competent
 support on grating design issues, Christian Kottler and Vincent Revol from
@@
 the fruitful discussions on the design of the system.
+Part of this work has been supported by the ERC Grant ERC-2012-StG 310005-PhaseX.
 

### 2013-09-04 natphys/hedpc_natphys.tex
Nature Physics guide compliance
    - caption, babel packages
    - FIG -> Figure
    - New abstract less than 150 words
    - Small changes to the introduction
    - no bibtex

@@
 %for review and submission
-\documentclass[aps,prl,preprint]{revtex4-1} 
+\documentclass[aps,prl,preprint,english]{revtex4-1} 
 % for double-spaced preprint
@@
 \usepackage[utf8]{inputenc} %Umlaute
+\usepackage{babel}
 \usepackage{acronym}
@@
 \usepackage{amssymb}
+\usepackage[bf,small,labelsep=period]{caption}
 \usepackage{graphicx}  %figures
@@
 
+\addto\captionsenglish{\renewcommand{\figurename}{Figure}}
 %% New commands
@@
 \author{T.~Thüring}
-\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
+\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
 \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
 \author{M.~Abis}
-\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
+\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
 \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
 \author{Z.~Wang}
-\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
+\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
 \author{C.~David}
-\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
+\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
 \author{M.~Stampanoni}
-\affiliation{Paul Scherrer Institut, Villigen PSI, Switzerland}
+\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
 \affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
@@
 \begin{abstract}
-    Phase contrast imaging with X-rays provides access to
-    complementary physical contrast mechanisms. Phase sensitive imaging in
-    the diagnostic energy range between $80$ and
-    $\SI{150}{\kilo\electronvolt}$ is still largely unexplored, as the
-    current methods typically entail severe technical challenges. A
-    phase-contrast technique at such high energies is of scientific and
-    industrial interest as it vastly expands the range of applications, for
-    instance, by the examination of materials of high density or thickness.
-    The approach includes a new design for the grating manufacturing in
-    Talbot-Lau interferometry, with an edge-on illumination and curved
-    structures to match the beam divergence. The edge-on approach breaks the
-    current limits of achievable grating aspect ratios, which has been a key
-    issue for a long time. The curvature of the gratings solves the
-    intrinsic reduction of the field of view which occurs for gratings with
-    such high aspect ratios and allows for a very compact setup, with a
-    distance of \SI{31}{\centi\metre} between the source grating and the
-    analyzer grating. Using an imaging arrangement based on a
-    conventional X-ray tube, phase and dark-field contrast imaging at
-    $\SI{100}{\kilo\electronvolt}$ is demonstrated. This achievement paves
-    the road for the transfer of phase-contrast imaging into fields where
-    high energies are required, such as medical computed tomography, chip
-    failure analysis or homeland security.
+    X-ray grating interferometry is a promising imaging technique sensitive to phase
+    shifts, attenuation and scattering of the radiation.
+    Applications of this technique in the diagnostically relevant energy range between $80$ and
+    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due
+    to the severe technical challenges.
+    A phase-contrast technique at such high energies is of scientific and
+    industrial interest for the analysis of materials of high atomic number or thickness
+    as well as medical imaging.
+    Here we show the design and operation of a Talbot-Lau
+    interferometer with a target energy of $\SI{100}{\kilo\electronvolt}$ on
+    a conventional X-ray tube and a compact geometry, with a total length of
+    \SI{54}{\centi\metre}.
+    The design features edge-on illumination in order to overcome the
+    current limitations in the manufacturing of the gratings, and curved
+    structures that match the beam divergence in order to allow for a large
+    field of view and a short setup.
 \end{abstract}
@@
 
-X-ray radiography and \ac{CT} are nowadays standard imaging techniques in
+X-ray radiography and \ac{CT} are standard imaging techniques in
 materials and life sciences for the nondestructive examination of samples or
@@
 or tissue types. The dominant physical effects contributing to attenuation
-are the photoelectric effect and incoherent (Compton) scattering. The sum of
-their contributions determines the attenuation coefficient, which is a
-wavelength dependent material parameter. Besides attenuation, the wave
+are the photoelectric effect and incoherent (Compton) scattering. Besides attenuation, the wave
 nature of X-rays reveals another contrast mechanism, which is the phase
@@
 
-Using the material parameter $n=1-\delta(\mathbf{r},\lambda) + i
-\beta(\mathbf{r},\lambda)$, known from X-ray wave optics as the complex
-index of refraction, the wavelength dependent attenuation and phase shift
-properties of an object at the spatial coordinate $\mathbf{r}$ are fully
-described. The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the
+The attenuation and phase shift properties are described by the complex index of refraction
+$n=1-\delta(\mathbf{r},\lambda) + i \beta(\mathbf{r},\lambda)$.
+The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the
 attenuation per unit length (attenuation coefficient) by $\mu = 4 \pi
@@
 \propto \log(I)$), the measurement of the phase shift integral $L_\phi$ is
-more challenging as there is no such simple relation. However, phase
-sensitive imaging is a desirable modality, as it can provide an enhanced
+more challenging as there is no such simple relation. However, phase-sensitive
+imaging is a desirable modality, as it can provide an enhanced
 \ac{CNR} in images compared to attenuation for certain
@@
 available only at synchrotron sources. Techniques which are compatible with
-an X-ray beam of low temporal coherence (broad bandwidth) are the in-line
+an X-ray beam of low temporal coherence (broad bandwidth) are the inline
 phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
@@
 
-\bibliographystyle{apsrev4-1} \bibliography{library}
+\bibliographystyle{apsrev4-1}
 
+%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (72) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{25}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Als-Nielsen}\ and\ \citenamefont
+  {McMorrow}(2011)}]{Als-Nielsen2011}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Als-Nielsen}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {McMorrow}},\ }\href
+  {http://books.google.com/books?hl=en\&lr=\&id=rlqlboWlTRMC\&oi=fnd\&pg=PA29\&dq=Elements+of+Modern+X-ray+Physics\&ots=P2D3XwrDgd\&sig=b3iO97q1hfsT8TkTYKxsvUbFink}
+  {\emph {\bibinfo {title} {{Elements of modern X-ray physics}}}}\ (\bibinfo
+  {year} {2011})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2007)\citenamefont
+  {Pfeiffer}, \citenamefont {Bunk}, \citenamefont {David}, \citenamefont
+  {Bech}, \citenamefont {{Le Duc}}, \citenamefont {Bravin},\ and\ \citenamefont
+  {Cloetens}}]{Pfeiffer2007a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {David}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Bech}}, \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {{Le Duc}}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Bravin}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Cloetens}},\ }\href {\doibase
+  10.1088/0031-9155/52/23/010} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physics in medicine and biology}\ }\textbf {\bibinfo {volume} {52}},\
+  \bibinfo {pages} {6923} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {McDonald}\ \emph {et~al.}(2009)\citenamefont
+  {McDonald}, \citenamefont {Marone}, \citenamefont {Hintermuller},
+  \citenamefont {Mikuljan}, \citenamefont {David}, \citenamefont {Pfeiffer},
+  \citenamefont {Stampanoni},\ and\ \citenamefont
+  {Hinterm\"{u}ller}}]{McDonald2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
+  {McDonald}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Marone}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Hintermuller}}, \bibinfo
+  {author} {\bibfnamefont {G.}~\bibnamefont {Mikuljan}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {David}}, \bibinfo {author} {\bibfnamefont
+  {F.}~\bibnamefont {Pfeiffer}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Stampanoni}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Hinterm\"{u}ller}},\ }\href {\doibase
+  10.1107/S0909049509017920} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of Synchrotron Radiation}\ }\textbf {\bibinfo {volume} {16}},\
+  \bibinfo {pages} {562} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Qi}\ \emph {et~al.}(2010)\citenamefont {Qi},
+  \citenamefont {Zambelli}, \citenamefont {Bevins},\ and\ \citenamefont
+  {Chen}}]{Qi2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
+  {Qi}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zambelli}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Bevins}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {G.-H.}\ \bibnamefont {Chen}},\ }\href {\doibase
+  10.1088/0031-9155/55/9/016} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physics in medicine and biology}\ }\textbf {\bibinfo {volume} {55}},\
+  \bibinfo {pages} {2669} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Davis}\ \emph {et~al.}(1995)\citenamefont {Davis},
+  \citenamefont {Gao}, \citenamefont {Gureyev}, \citenamefont {Stevenson},\
+  and\ \citenamefont {Wilkins}}]{Davis1995}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Davis}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Gao}}, \bibinfo
+  {author} {\bibfnamefont {T.}~\bibnamefont {Gureyev}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Stevenson}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Wilkins}},\ }\href
+  {http://imaging.sbes.vt.edu/laboratory/XGI/(1995 Gao).pdf} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {373}},\
+  \bibinfo {pages} {595} (\bibinfo {year} {1995})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chapman}\ \emph {et~al.}(1997)\citenamefont
+  {Chapman}, \citenamefont {Thomlinson}, \citenamefont {Johnston},
+  \citenamefont {Washburn}, \citenamefont {Pisano}, \citenamefont {Gm\"{u}r},
+  \citenamefont {Zhong}, \citenamefont {Menk}, \citenamefont {Arfelli},\ and\
+  \citenamefont {Sayers}}]{Chapman1997}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Chapman}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Thomlinson}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Johnston}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Washburn}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Pisano}}, \bibinfo {author} {\bibfnamefont
+  {N.}~\bibnamefont {Gm\"{u}r}}, \bibinfo {author} {\bibfnamefont
+  {Z.}~\bibnamefont {Zhong}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Menk}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Arfelli}}, \ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Sayers}},\ }\href {\doibase 10.1016/j.carj.2010.04.015} {\bibfield
+  {journal} {\bibinfo  {journal} {Physics in Medicine and Biology}\ }\textbf
+  {\bibinfo {volume} {42}},\ \bibinfo {pages} {2015} (\bibinfo {year}
+  {1997})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bonse}\ and\ \citenamefont {Hart}(1965)}]{Bonse1965}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.}~\bibnamefont
+  {Bonse}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Hart}},\
+  }\href {http://link.aip.org/link/?APPLAB/6/155/1} {\bibfield  {journal}
+  {\bibinfo  {journal} {Applied Physics Letters}\ }\textbf {\bibinfo {volume}
+  {6}},\ \bibinfo {pages} {155} (\bibinfo {year} {1965})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Momose}\ \emph {et~al.}(1996)\citenamefont {Momose},
+  \citenamefont {Takeda}, \citenamefont {Itai},\ and\ \citenamefont
+  {Hirano}}]{Momose1996}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Momose}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Takeda}},
+  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Itai}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Hirano}},\ }\href
+  {http://imaging.sbes.vt.edu/laboratory/XGI/(1996 Momose).pdf} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature Medicine}\ }\textbf {\bibinfo {volume}
+  {2}},\ \bibinfo {pages} {473} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Snigirev}\ \emph {et~al.}(1995)\citenamefont
+  {Snigirev}, \citenamefont {Snigireva}, \citenamefont {Kohn}, \citenamefont
+  {Kuznetsov},\ and\ \citenamefont {Schelokov}}]{Snigirev1995}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Snigirev}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Snigireva}},
+  \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Kohn}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Kuznetsov}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {I.}~\bibnamefont {Schelokov}},\ }\href
+  {http://kohnvict.narod.ru/articles/091.pdf} {\bibfield  {journal} {\bibinfo
+  {journal} {Review of Scientific Instruments}\ }\textbf {\bibinfo {volume}
+  {66}},\ \bibinfo {pages} {5486} (\bibinfo {year} {1995})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Wilkins}\ \emph {et~al.}(1996)\citenamefont
+  {Wilkins}, \citenamefont {Gureyev}, \citenamefont {Gao}, \citenamefont
+  {Pogany},\ and\ \citenamefont {Stevenson}}]{Wilkins1996}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Wilkins}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Gureyev}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Gao}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Pogany}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Stevenson}},\ }\href
+  {http://fisica.ufpr.br/lorxi/Rcf2/artigos/Wilkins.pdf} {\bibfield  {journal}
+  {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {384}},\ \bibinfo
+  {pages} {335} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cloetens}\ \emph {et~al.}(1996)\citenamefont
+  {Cloetens}, \citenamefont {Barrett}, \citenamefont {Baruchel}, \citenamefont
+  {Guigay},\ and\ \citenamefont {Schlenker}}]{Cloetens1996}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Cloetens}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Barrett}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Baruchel}}, \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Guigay}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Schlenker}},\ }\href
+  {http://iopscience.iop.org/0022-3727/29/1/023} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Physics D: Applied Physics}\ }\textbf
+  {\bibinfo {volume} {29}},\ \bibinfo {pages} {133} (\bibinfo {year}
+  {1996})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cloetens}\ \emph {et~al.}(1997)\citenamefont
+  {Cloetens}, \citenamefont {Guigay}, \citenamefont {{De Martino}},
+  \citenamefont {Baruchel},\ and\ \citenamefont {Schlenker}}]{Cloetens1997}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Cloetens}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Guigay}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {{De Martino}}}, \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Baruchel}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Schlenker}},\ }\href
+  {http://www.ncbi.nlm.nih.gov/pubmed/18185750} {\bibfield  {journal} {\bibinfo
+   {journal} {Optics letters}\ }\textbf {\bibinfo {volume} {22}},\ \bibinfo
+  {pages} {1059} (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {David}\ \emph {et~al.}(2002)\citenamefont {David},
+  \citenamefont {N\"{o}hammer}, \citenamefont {Solak},\ and\ \citenamefont
+  {Ziegler}}]{David2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {David}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {N\"{o}hammer}},
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Solak}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {E.}~\bibnamefont {Ziegler}},\ }\href {\doibase
+  10.1063/1.1516611} {\bibfield  {journal} {\bibinfo  {journal} {Applied
+  Physics Letters}\ }\textbf {\bibinfo {volume} {81}},\ \bibinfo {pages} {3287}
+  (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Momose}\ \emph {et~al.}(2003)\citenamefont {Momose},
+  \citenamefont {Kawamoto}, \citenamefont {Koyama}, \citenamefont {Hamaishi},
+  \citenamefont {Takai},\ and\ \citenamefont {Suzuki}}]{Momose2003a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Momose}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Kawamoto}},
+  \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Koyama}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Hamaishi}}, \bibinfo {author}
+  {\bibfnamefont {K.}~\bibnamefont {Takai}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Y.}~\bibnamefont {Suzuki}},\ }\href {\doibase
+  10.1143/JJAP.42.L866} {\bibfield  {journal} {\bibinfo  {journal} {Japanese
+  Journal of Applied Physics}\ }\textbf {\bibinfo {volume} {42}},\ \bibinfo
+  {pages} {L866} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2006)\citenamefont
+  {Pfeiffer}, \citenamefont {Weitkamp}, \citenamefont {Bunk},\ and\
+  \citenamefont {David}}]{Pfeiffer2006}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Weitkamp}},
+  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {C.}~\bibnamefont {David}},\ }\href {\doibase
+  10.1038/nphys265} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  Physics}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {258} (\bibinfo
+  {year} {2006})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Munro}\ \emph {et~al.}(2012)\citenamefont {Munro},
+  \citenamefont {Ignatyev}, \citenamefont {Speller},\ and\ \citenamefont
+  {Olivo}}]{Munro2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Munro}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Ignatyev}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Speller}}, \ and\
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Olivo}},\ }\href
+  {\doibase 10.1073/pnas.1205396109} {\bibfield  {journal} {\bibinfo  {journal}
+  {Proceedings of the National Academy of Sciences}\ }\textbf {\bibinfo
+  {volume} {2012}},\ \bibinfo {pages} {2} (\bibinfo {year} {2012})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Willner}\ \emph {et~al.}(2013)\citenamefont
+  {Willner}, \citenamefont {Bech}, \citenamefont {Herzen}, \citenamefont
+  {Zanette}, \citenamefont {Hahn}, \citenamefont {Kenntner}, \citenamefont
+  {Mohr}, \citenamefont {Rack}, \citenamefont {Weitkamp},\ and\ \citenamefont
+  {Pfeiffer}}]{Willner2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Willner}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bech}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Herzen}}, \bibinfo
+  {author} {\bibfnamefont {I.}~\bibnamefont {Zanette}}, \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {Hahn}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Kenntner}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Mohr}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Rack}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Weitkamp}}, \
+  and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Pfeiffer}},\ }\href
+  {http://www.ncbi.nlm.nih.gov/pubmed/23481949} {\bibfield  {journal} {\bibinfo
+   {journal} {Optics express}\ }\textbf {\bibinfo {volume} {21}},\ \bibinfo
+  {pages} {4155} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ruiz}\ \emph {et~al.}(2013)\citenamefont {Ruiz},
+  \citenamefont {Zanette}, \citenamefont {Chabior}, \citenamefont {Scherer},
+  \citenamefont {Mohr}, \citenamefont {Walter}, \citenamefont {Weitkamp},
+  \citenamefont {Rack},\ and\ \citenamefont {Pfeiffer}}]{Ruiz2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Ruiz}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Zanette}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Chabior}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Scherer}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Mohr}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Walter}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Weitkamp}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Rack}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {F.}~\bibnamefont {Pfeiffer}},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Poster, 2nd International Symposium on BioMedical
+  Applications of X-ray Phase Contrast Imaging, Germany, 24/25th January 2013}\
+  } (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Donath}\ \emph {et~al.}(2009)\citenamefont {Donath},
+  \citenamefont {Chabior}, \citenamefont {Pfeiffer}, \citenamefont {Bunk},
+  \citenamefont {Reznikova}, \citenamefont {Mohr}, \citenamefont {Hempel},
+  \citenamefont {Popescu}, \citenamefont {Hoheisel}, \citenamefont {Schuster},
+  \citenamefont {Baumann},\ and\ \citenamefont {David}}]{Donath2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Donath}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Chabior}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Pfeiffer}}, \bibinfo
+  {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Reznikova}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Mohr}}, \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Hempel}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Popescu}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Hoheisel}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Schuster}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Baumann}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {David}},\ }\href {\doibase 10.1063/1.3208052} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Applied Physics}\ }\textbf
+  {\bibinfo {volume} {106}},\ \bibinfo {pages} {054703} (\bibinfo {year}
+  {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {David}\ \emph {et~al.}(2007)\citenamefont {David},
+  \citenamefont {Bruder}, \citenamefont {Rohbeck}, \citenamefont
+  {Gr\"{u}nzweig}, \citenamefont {Kottler}, \citenamefont {Diaz}, \citenamefont
+  {Bunk},\ and\ \citenamefont {Pfeiffer}}]{David2007}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {David}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Bruder}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Rohbeck}}, \bibinfo
+  {author} {\bibfnamefont {C.}~\bibnamefont {Gr\"{u}nzweig}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Kottler}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Diaz}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
+  {Bunk}}, \ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Pfeiffer}},\ }\href {\doibase 10.1016/j.mee.2007.01.151} {\bibfield
+  {journal} {\bibinfo  {journal} {Microelectronic Engineering}\ }\textbf
+  {\bibinfo {volume} {84}},\ \bibinfo {pages} {1172} (\bibinfo {year}
+  {2007})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kenntner}\ \emph {et~al.}(2010)\citenamefont
+  {Kenntner}, \citenamefont {Grund}, \citenamefont {Matthis}, \citenamefont
+  {Boerner}, \citenamefont {Mohr}, \citenamefont {Scherer}, \citenamefont
+  {Walter}, \citenamefont {Willner}, \citenamefont {Tapfer}, \citenamefont
+  {Bech}, \citenamefont {Pfeiffer}, \citenamefont {Zanette},\ and\
+  \citenamefont {Weitkamp}}]{Kenntner2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Kenntner}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Grund}},
+  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Matthis}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Boerner}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Mohr}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Scherer}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Walter}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Willner}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Tapfer}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Bech}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Zanette}}, \
+  and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Weitkamp}},\ }in\
+  \href@noop {} {\emph {\bibinfo {booktitle} {Proceedings of SPIE}}},\ Vol.\
+  \bibinfo {volume} {7804}\ (\bibinfo {year} {2010})\ p.\ \bibinfo {pages}
+  {780408}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Stutman}\ and\ \citenamefont
+  {Finkenthal}(2012)}]{Stutman2012a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Stutman}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Finkenthal}},\ }\href {\doibase 10.1063/1.4748882} {\bibfield  {journal}
+  {\bibinfo  {journal} {Applied physics letters}\ }\textbf {\bibinfo {volume}
+  {101}},\ \bibinfo {pages} {91108} (\bibinfo {year} {2012})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Weitkamp}\ \emph {et~al.}(2005)\citenamefont
+  {Weitkamp}, \citenamefont {Diaz}, \citenamefont {David}, \citenamefont
+  {Pfeiffer}, \citenamefont {Stampanoni}, \citenamefont {Cloetens},\ and\
+  \citenamefont {Ziegler}}]{Weitkamp2005}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Weitkamp}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Diaz}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {David}}, \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Pfeiffer}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Stampanoni}}, \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Cloetens}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Ziegler}},\ }\href {\doibase
+  10.1364/OPEX.13.006296} {\bibfield  {journal} {\bibinfo  {journal} {Optics
+  Express}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {6296}
+  (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Thuering}\ \emph {et~al.}(2013)\citenamefont
+  {Thuering}, \citenamefont {Barber}, \citenamefont {Seo}, \citenamefont
+  {Alhassen}, \citenamefont {Iwanczyk},\ and\ \citenamefont
+  {Stampanoni}}]{Thuering2013c}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Thuering}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Barber}},
+  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Seo}}, \bibinfo {author}
+  {\bibfnamefont {F.}~\bibnamefont {Alhassen}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Iwanczyk}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Stampanoni}},\ }\href {\doibase
+  10.1063/1.4805073} {\bibfield  {journal} {\bibinfo  {journal} {Applied
+  Physics Letters}\ }\textbf {\bibinfo {volume} {102}},\ \bibinfo {pages}
+  {191113} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gr\"{u}nzweig}\ \emph {et~al.}(2008)\citenamefont
+  {Gr\"{u}nzweig}, \citenamefont {Pfeiffer}, \citenamefont {Bunk},
+  \citenamefont {Donath}, \citenamefont {K\"{u}hne}, \citenamefont {Frei},
+  \citenamefont {Dierolf},\ and\ \citenamefont {David}}]{Grunzweig2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Gr\"{u}nzweig}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Donath}}, \bibinfo
+  {author} {\bibfnamefont {G.}~\bibnamefont {K\"{u}hne}}, \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {Frei}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Dierolf}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {David}},\ }\href {\doibase 10.1063/1.2930866} {\bibfield
+  {journal} {\bibinfo  {journal} {The Review of scientific instruments}\
+  }\textbf {\bibinfo {volume} {79}},\ \bibinfo {pages} {053703} (\bibinfo
+  {year} {2008})}\BibitemShut {NoStop}%
+\end{thebibliography}%
 \end{document}

### 2013-09-06 hedpc_natphys.tex
Marcos abstract, removed useless folders

--- 2013-09-04 natphys/hedpc_natphys.tex
@@
 \begin{abstract}
-    X-ray grating interferometry is a promising imaging technique sensitive to phase
-    shifts, attenuation and scattering of the radiation.
-    Applications of this technique in the diagnostically relevant energy range between $80$ and
-    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due
-    to the severe technical challenges.
-    A phase-contrast technique at such high energies is of scientific and
-    industrial interest for the analysis of materials of high atomic number or thickness
-    as well as medical imaging.
-    Here we show the design and operation of a Talbot-Lau
-    interferometer with a target energy of $\SI{100}{\kilo\electronvolt}$ on
-    a conventional X-ray tube and a compact geometry, with a total length of
-    \SI{54}{\centi\metre}.
-    The design features edge-on illumination in order to overcome the
-    current limitations in the manufacturing of the gratings, and curved
-    structures that match the beam divergence in order to allow for a large
-    field of view and a short setup.
+    X-ray grating interferometry is a promising imaging technique sensitive
+    to attenuation, refraction and scattering of the radiation. Applications
+    of this technique in the energy range between $80$ and
+    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
+    severe technical challenges. Phase-contrast X-ray imaging at such high
+    energies is of relevant scientific and industrial interest, in
+    particular for the investigation of materials with high atomic number or
+    thickness as well as for medical imaging. Here we show the successful
+    implementation of a Talbot-Lau interferometer operated at
+    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
+    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
+    suggest edge-on illumination of the gratings to overcome their current
+    fabrication limits as well as curved structures, to match beam
+    divergence and allow large field of views on a short and efficient
+    setup.
 \end{abstract}
-
 \maketitle
@@
 \begin{figure}[ht]
-    \includegraphics[width=.5\textwidth]{figures/figure1.eps}
+    \includegraphics[width=.7\textwidth]{figures/figure1.eps}
     \caption{Schematic of a grating

### 2013-09-09 hedpc_natphys.tex
Zhentian's and Christian's review
- abstract: "present" edge-on illumination
- added very short description of the dark field
    "In addition to phase sensitivity, these techniques provide a dark-field
    contrast, also called scatter contrast or visibility-reduction contrast,
    that is proportional to the scatter strength of details in the
    sample\cite{Pfeiffer2008}."
- exposure time: 24 phase steps "per line" (both in methods and in caption)
- fixed Microworks spelling
- a more efficient detector can also shorten the exposure

- added bibtex Makefile target
- removed useless binaries

@@
     compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
-    suggest edge-on illumination of the gratings to overcome their current
+    present edge-on illumination of the gratings to overcome their current
     fabrication limits as well as curved structures, to match beam
@@
 of thickness $d$ can be described by the line integral $L_\mu = \int_0^d
-\mu(\mathbf{r},\lambda) \d l$. Similarly, the real part
+\mu(\mathbf{r},\lambda) \d{} \mathbf{r}$. Similarly, the real part
 $\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by
 $\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi =
-\int_0^d \phi(\mathbf{r}) \d l$.
+\int_0^d \phi(\mathbf{r}) \d{} \mathbf{r}$.
 
@@
 apertures \cite{Munro2012}.
+In addition to phase sensitivity, these techniques provide a dark-field
+contrast, also called scatter contrast or visibility-reduction contrast,
+that is proportional to the scatter strength of details in the sample\cite{Pfeiffer2008}.
 
 Talbot interferometry has been demonstrated using a synchrotron source at
-$\SI{82}{\kilo\electronvolt}$ \cite{Willner2013} and
+$\SI{82}{\kilo\electronvolt}$\cite{Willner2013} and
 $\SI{123}{\kilo\electronvolt}$\cite{Ruiz2013}.
@@
 broad spectrum, photons above the design energy should also be
-efficiently attenuated by the gratings, which requires even higher aspect ratios.
+efficiently blocked by the gratings, which requires even higher aspect ratios.
 Maximum achievable aspect ratios of current grating fabrication techniques
@@
 interferometer ($\SI{50}{\kilo\electronvolt}$ to
-$>\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
-the source- and analyzer gratings ($>90\%$ up to
+more than $\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
+the source and analyzer gratings ($>90\%$ up to
 $\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
@@
     \caption{Radiographic scan of an electronic chip. The image was acquired
-        with 24 phase steps and an exposure time of \SI{15}{\second} per
+        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
     step. The top right image shows the differential absorption image.}
@@
 \section*{Methods}
-Edge-on illuminated gratings were manufactured by Micro
-Works GmbH, Germany, using a LIGA process \cite{Kenntner2010}. Each grating
+Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process \cite{Kenntner2010}. Each grating
 resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
@@
 grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
-grating is positioned $\SI{23}{\centi\metre}$ away from the source. The
-number of phase steps for one projection was 24 \cite{Weitkamp2005} and the
-exposure time for the images was 15 seconds per phase step.
+grating is positioned $\SI{23}{\centi\metre}$ away from the source.
 
@@
 is $\SI{80}{\micro \metre}$. The widths of the collimating slits are
-$\SI{25}{\micro \metre}$ and $\SI{100}{\micro \metre}$, respectively.
+$\SI{25}{\micro \metre}$ and $\SI{100}{\micro\metre}$, respectively.
 
-In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps
-\cite{Weitkamp2005} and an exposure time of 15 seconds per step. The long
+In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps per
+line \cite{Weitkamp2005} and an exposure time of 15 seconds per step. The long
 exposure times are mostly constrained by the low average visibility of the
-gratings (\SI{5}{\percent}). As the quality in the manufacturing of the
-structure increases, the exposure time can become substantially shorter.
+gratings (\SI{5}{\percent}). The exposure time can be shortened with better
+gratings and an efficient detector.
 
@@
 \bibliographystyle{apsrev4-1}
+ %\bibliography{library}
 
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{25}%
+\begin{thebibliography}{26}%
 \makeatletter
@@
   {NoStop}%
+\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2008)\citenamefont
+  {Pfeiffer}, \citenamefont {Bech}, \citenamefont {Bunk}, \citenamefont
+  {Kraft}, \citenamefont {Eikenberry}, \citenamefont {Br\"{o}nnimann},
+  \citenamefont {Gr\"{u}nzweig},\ and\ \citenamefont {David}}]{Pfeiffer2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bech}},
+  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Kraft}}, \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Eikenberry}}, \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Br\"{o}nnimann}}, \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Gr\"{u}nzweig}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {David}},\ }\href {\doibase 10.1038/nmat2096} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature Materials}\ }\textbf {\bibinfo
+  {volume} {7}},\ \bibinfo {pages} {134} (\bibinfo {year} {2008})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Willner}\ \emph {et~al.}(2013)\citenamefont

### 2013-09-09 hedpc_natphys.tex
Changed figure 2 to SEM image. Added acknowledgements.
    - SEM image (Au_grating)
    - Acknowledge Peter, Istvan, CCMX
    - copied library.bib here (was simlink to cDPC project folder)

@@
 \begin{figure} [ht]
-    \includegraphics[width=.5\textwidth]{figures/grating_mask.eps}
+    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
     \caption{Grating design mask for
-        the edge-on illumination approach. (a) Top part of the 4 inch wafer,
-        showing five grating chips; one source grating, two beam splitter
-        gratings and two analyzer gratings (from top to bottom). The
+        the edge-on illumination approach and scanning electron microscope
+        image of the grating. The top part of the 4 inch wafer shows
+        five grating chips. The
         gratings have different curvatures which are specific to the grating
-        interferometer geometry. (b) Zoom into the grating structures,
-        contain interrupting bridges used for stabilizing the grating
-        structures in the lithographic process \cite{Kenntner2010}.}
+        interferometer geometry. 
+        The interrupting bridges used for stabilizing the grating
+        in the lithographic process can be seen with the SEM\cite{Kenntner2010}.}
         \label{Fig:grating_mask}
@@
 
-\section*{Acknowledgements} We thank Gordan Mikuljan from Paul Scherrer
-Institute, Switzerland, for his work on the mechanical design, Joachim
-Schulz and Marco Walter from Microworks GmbH, Germany, for the competent
-support on grating design issues, Christian Kottler and Vincent Revol from
-Centre Suisse d'Electronique et de Microtechnique (CSEM), Switzerland for
-the fruitful discussions on the design of the system.
-Part of this work has been supported by the ERC Grant ERC-2012-StG 310005-PhaseX.
+\section*{Acknowledgements}
+We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
+Scherrer Institute (PSI), Switzerland, for the
+work on the mechanical design, the scientific advice, and the SEM images
+respectively, Joachim Schulz and Marco Walter from
+Microworks GmbH, Germany, for the competent support on grating design
+issues, Christian Kottler and Vincent Revol from Centre Suisse
+d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
+discussions on the design of the system. This work has been partially
+supported by the Competence Centre for Materials Science and Technology
+(CCMX) of the ETH-Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.
 

### 2013-09-11 hedpc_natphys.tex
New cover letter, dark-field description and SEM caption

@@
 contrast, also called scatter contrast or visibility-reduction contrast,
-that is proportional to the scatter strength of details in the sample\cite{Pfeiffer2008}.
+that is proportional to the integrated local small angle scattering power
+from microscopic density fluctuations in a specimen\cite{Pfeiffer2008}.
 
@@
         interferometer geometry. 
-        The interrupting bridges used for stabilizing the grating
-        in the lithographic process can be seen with the SEM\cite{Kenntner2010}.}
+        The SEM image shows the gold structures and the interrupting bridges
+        that prevent the lamellae from collapsing\cite{Kenntner2010}.}
         \label{Fig:grating_mask}
@@
 attenuated by the slits.
-
-%Fig. 3 shows a radiographic image of a metal screw in all three contrast
-%modes, acquired with the $\SI{100}{\kilo\electronvolt}$ setup. The images
-%were acquired in scanning mode, using a step size of $\SI{100}{\micro
-%\metre}$. The number of phase steps was 24 and the exposure time was 15
-%seconds per step. Grating interferometry at such a high diagnostic energy
-%allows to examine more dense materials such as metals in phase contrast
-%mode. At lower energies, the phase shifts of such materials would be too
-%large and wrap over multiple periods of the analyzer grating.
 

### 2013-10-23 hedpc_natphys.tex
Appeal edits
    - include table top sources in title
    - shorten introduction
    - more small cosmetic rephrasings

@@
 \acrodef{CNR}{contrast-to-noise ratio}
+\acrodef{SEM}{scanning electron microscope}
 %% ----------------------------------------------------------------------------------------------------------------
@@
 
-\title{X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt}}
+\title{X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on
+table top sources}
 
@@
 The attenuation and phase shift properties are described by the complex index of refraction
-$n=1-\delta(\mathbf{r},\lambda) + i \beta(\mathbf{r},\lambda)$.
-The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the
-attenuation per unit length (attenuation coefficient) by $\mu = 4 \pi
-\beta(\mathbf{r},\lambda) / \lambda$ and the total attenuation by an object
-of thickness $d$ can be described by the line integral $L_\mu = \int_0^d
-\mu(\mathbf{r},\lambda) \d{} \mathbf{r}$. Similarly, the real part
-$\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by
-$\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi =
-\int_0^d \phi(\mathbf{r}) \d{} \mathbf{r}$.
+$n=1-\delta + i \beta$.
+The imaginary part $\beta$ is related to the
+attenuation coefficient by $\mu = 4 \pi
+\beta(\lambda) / \lambda$, while the real part
+$\delta(\lambda)$ determines the phase shift 
+$\phi = 2 \pi \delta(\lambda) / \lambda$
 
-While the attenuation line integral $L_\mu$ can be directly measured with an
-X-ray detector by measuring the reduction of the beam intensity $I$ ($L_\mu
-\propto \log(I)$), the measurement of the phase shift integral $L_\phi$ is
-more challenging as there is no such simple relation. However, phase-sensitive
-imaging is a desirable modality, as it can provide an enhanced
+While the attenuation can be measured with an
+X-ray detector as the reduction of the beam intensity, the phase
+is not directly observable. Therefore, an optical system is needed to
+convert the phase shift into intensity modulations.
+
+Phase-sensitive
+imaging is a desirable modality, as it can provide a complementary source of
+contrast with respect to absorption by providing direct access 
+to the electron density \cite{Als-Nielsen2011}. Moreover, the combination with
+attenuation enables the determination of the effective atomic
+number \cite{Qi2010}.
+An enhanced
 \ac{CNR} in images compared to attenuation for certain
-materials or in different tissues \cite{Pfeiffer2007a,McDonald2009}.
-Furthermore, the refractive index decrement $\delta$ provides direct access
-to the electron density \cite{Als-Nielsen2011} and in combination with
-attenuation, it further enables the determination of the effective atomic
-number of a material \cite{Qi2010}.
+materials or tissues \cite{Pfeiffer2007a,McDonald2009} has also been
+demonstrated.
 
-In the past, a lot of effort has been invested into the development of
-techniques which are sensitive to the phase shift. Since most of the
-available phase contrast techniques rely on interference and thus typically
-on optical hardware (e.g. crystals, gratings), they vary a lot in terms of
-sensitivity, practical applicability or achievable resolution. The vast
-majority of the methods, including crystal analyzer based
+The vast majority of phase-sensitive techniques, including crystal analyzer based
 \cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996}
 methods rely on X-ray beams of high spatial and temporal coherence, which is
-available only at synchrotron sources. Techniques which are compatible with
-an X-ray beam of low temporal coherence (broad bandwidth) are the inline
-phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
-Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
+available only at synchrotron sources. Inline
+phase contrast \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
+Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a} need high
+spatial coherence but are available on microfocus sources.
 Phase-contrast imaging using X-ray beams of low temporal \emph{and}
 spatial coherence such as conventional low-brilliance X-ray tubes have been
-demonstrated with Talbot-Lau interferometry \cite{Pfeiffer2006} and coded
-apertures \cite{Munro2012}.
+demonstrated with coded
+apertures \cite{Munro2012} and Talbot-Lau interferometry \cite{Pfeiffer2006}.
+
+WHAT IS TLINTERFEROMETER
+
 In addition to phase sensitivity, these techniques provide a dark-field
@@
 Here, we introduce a method for phase-contrast imaging which is
-compatible with the entire diagnostic energy range of X-rays. Moreover, the
-method is fully compatible with compact imaging arrangements based on
+compatible with the entire diagnostic energy range of X-rays, 
+compact imaging arrangements and 
 conventional X-ray tubes. The method is based on Talbot-Lau interferometry
@@
 \begin{equation}
-    \text{AR} = \frac{2h}{p},
+    \text{R} = \frac{2h}{p},
 \end{equation}
-where $p$ is the grating period and $h$ the grating structure
+where $p$ is the grating period and $h$ the  structure
 height, is normally limited by the lithographic process, as grating
-structures tend to collapse or to deform (e.g. through capillary forces) if
-the aspect ratio is too high. For a given setup distance these parameters
+structures tend to collapse or deform (e.g. due to capillary forces) if
+the aspect ratio is too high. For a given setup length these parameters
 depend on the target energy $E$ according to $p \propto
-1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{AR}
-\propto E^{7/2}$\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
-for the absorption grating of around $\textnormal{AR}=30$ is necessary for a
+1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
+\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
+for the absorption grating around $\textnormal{R}=30$ is necessary for a
 reasonable length of the experimental arrangement, it would have to be at
@@
 efficiently blocked by the gratings, which requires even higher aspect ratios.
-Maximum achievable aspect ratios of current grating fabrication techniques
-\cite{David2007,Kenntner2010} are approximately around 60,
-larger values are often not achievable or come at the expense of a very poor
-grating quality and performance.
+The maximum achievable aspect ratios of current fabrication techniques
+\cite{David2007,Kenntner2010} are around 60.
 
@@
 opposed to face-on illumination, exploits the dimension along the grating
-lines to form a high aspect ratio of the structures in direction of the beam. The
+lines to form a high aspect ratio of the structures in the direction of the beam. The
 effective structure height of the grating is then determined by the grating
@@
 reduction of the field of view due to the change of the grating transmission
-function at high incident angles, which has also been identified by using a
-glancing angle of the gratings between zero and \SI{90}{\degree}
-\cite{Stutman2012a}. In order to overcome this problem, the grating lines are circularly aligned 
+function at high incident angles. In order to overcome this problem, the grating lines are circularly aligned 
 with a radius equal to the distance to the source.
@@
 splitter \cite{Momose2003a}. With a structure length of $h_2 =
-\SI{800}{\micro \metre}$, this grating has an aspect ratio of $2h/p \approx
-570$ and thus sufficiently attenuates X-rays up to energies of 
-$\SI{160}{\kilo\electronvolt}$. Beam splitter- and analyzer grating are
+\SI{800}{\micro \metre}$
+it can sufficiently attenuate X-rays up to energies of 
+$\SI{160}{\kilo\electronvolt}$. Beam splitter and analyzer grating are
 separated at the first fractional Talbot order \cite{Weitkamp2005},
@@
 incoherent sources \cite{Pfeiffer2006}. It is also made of gold structures
-with a structure length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
+with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
 \begin{figure} [ht]
@@
     \caption{Grating design mask for
-        the edge-on illumination approach and scanning electron microscope
+        the edge-on illumination approach and \ac{SEM}
         image of the grating. The top part of the 4 inch wafer shows
@@
         interferometer geometry. 
-        The SEM image shows the gold structures and the interrupting bridges
+        The \ac{SEM} image shows the gold structures and the interrupting bridges
         that prevent the lamellae from collapsing\cite{Kenntner2010}.}
@@
 the maximum of $\SI{160}{\kilo\volt}$. With a grating structure height of
-approx. $\SI{100}{\micro \metre}$, the field of view in the vertical
+approximately $\SI{100}{\micro \metre}$, the field of view in the vertical
 direction is limited to one detector pixel row. In the horizontal direction,
@@
 grating, the other in front of the camera, were required for the collimation
-of the beam in the vertical direction. X-rays which are not travelling
-through all of the gratings do not contribute to the signal and are
-attenuated by the slits.
+of the beam in the vertical direction.
 
@@
 the integrated circuit is reduced underneath the resistors, while in
-the phase image, they can clearly be identified. This shows the
-benefit of the phase nature of the image, which may be
-useful to identify flaws in multilayered structures such as electronic
-chips.
+the phase image, they can clearly be identified. The reduced contrast of the 
+soldering points in the absorption image is due to beam hardening. The spectrum
+impinging on these soldering point is hardened by the resistors in the upper
+layer, resuluting in lower absorption contrast. Due to the weaker energy
+dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
+are less sensitive to beam hardening \cite{Chabior2011a}, which explains the
+lower contrast reduction of the soldering points underneath the resistors in the
+phase image of the chip. This result shows the benefit of the phase nature in
+high energy X-ray imaging, which may be useful to identify flaws in multilayered
+structures such as electronic chips.
 \begin{figure}[ht]
@@
 enables the examination of materials of higher density or thickness which
-would be intransparent at lower energies. Finally, the approach is not
-limited to X-ray imaging, but could easily be applied to other grating-based
+would be opaque at lower energies. Finally, the approach is not
+limited to X-ray imaging, but could be easily applied to other grating-based
 imaging modalities (e.g., with neutrons \cite{Grunzweig2008}) where high
@@
 In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps per
-line \cite{Weitkamp2005} and an exposure time of 15 seconds per step. The long
+line and an exposure time of 15 seconds per step. The long
 exposure times are mostly constrained by the low average visibility of the
@@
   {191113} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chabior}\ \emph {et~al.}(2011)\citenamefont
+  {Chabior}, \citenamefont {Donath}, \citenamefont {David}, \citenamefont
+  {Bunk}, \citenamefont {Schuster}, \citenamefont {Schroer},\ and\
+  \citenamefont {Pfeiffer}}]{Chabior2011a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Chabior}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Donath}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {David}}, \bibinfo
+  {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Schuster}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Schroer}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {F.}~\bibnamefont {Pfeiffer}},\ }\href {\doibase
+  10.1118/1.3553408} {\bibfield  {journal} {\bibinfo  {journal} {Medical
+  Physics}\ }\textbf {\bibinfo {volume} {38}},\ \bibinfo {pages} {1189}
+  (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Gr\"{u}nzweig}\ \emph {et~al.}(2008)\citenamefont

### 2013-10-23 point_by_point_response.tex
started point by point response

%        File: point_by_point_response.tex
%     Created: Wed Oct 23 05:00 PM 2013 C
% Last Change: Wed Oct 23 05:00 PM 2013 C
%
\documentclass[a4paper]{scrartcl}

\title{Point-by-point response to the reviewers}
\date{}
\begin{document}
\maketitle

\section*{Reviewer \#1}
We would like to provide more information on our experiments, as recommended
by the first reviewer.
\begin{quote}
    I could not find a significant advance in this work. X-ray Talbot-Lau interferometers with high-energy x-rays have been already reported (Ref. 18-20, 23, D. Stutman et al., Appl. Opt. 49 (2010) 4677 etc.). The authors mention that the edge-on- illuminated grating interferometry breaks the current limitations of x-ray phase-contrast imaging, but I don't think that there is clear evidence showing that the authors' method is much more promising than the methods reported in the previous papers. If the authors want to show that the edge-on-illumination method is by far the most promising for high-energy and large-field-of-view x-ray phase imaging, I think that the authors have to quantitatively compare the method with those previously reported in terms of the total exposure time, spatial resolution, signal-to-noise ratio, and so on, and show that the authors' method is much better than the others.
\end{quote}
We think that the experiments presented in the current manuscript show
indeed significant progress with respect to the cited references.
The method presented by Stutman et al. has a fundamental limitation that
prevents it from achieving curved structures and large aspect ratios.
Moreover, those experiments were performed on a source
with~\SI{60}{\kilo\volt\peak}, which is significantly lower than
the~\SI{160}{\kilo\volt\peak} of our source and the~\SI{100}{\kilo\eV} used
as the design energy for our interferometer.

The other works also present results in a much lower energy range or very
different conditions, thus preventing a meaningful comparison.
Reference~23 reported images taken at \num{30} and~\SI{60}{\kilo\eV},
reference~20 also has a design energy of~\SI{47.9}{\kilo\eV}. Finally,
references~18 and~19 present Talbot interferometry at~\num{82}
and~\SI{123}{\kilo\eV} respectively, but only the first result was published
in a peer reviewed journal, and both experiments were performed at the ESRF
synchrotron, with a monochromatic and coherent beam that is incomparable to
a conventional tube.

\begin{quote}
    Furthermore, the authors mention that the results in Fig. 3 show the benefit of the phase nature of the image, but I think that the authors should provide a more detailed explanation about the contrasts in the images because the contrast of soldering points underneath the resistors should not be reduced in the differential attenuation image for monochromatic x-rays. The authors should explain quantitatively why the contrast is reduced. Otherwise, the authors' assertion is suspicious.
\end{quote}

\section*{Reviewer \#2}
\begin{quote}
    However, this solution comes with significant drawbacks in terms of very
    limited fields of view~\SI{3}{\centi\metre} horizontally, a single detector pixel in the vertical direction), which at the moment seem hard to overcome.
\end{quote}
There is no fundamental limitation on the horizontal field of view in our
approach. On the contrary, our solution actually solves precisely this
issue, by easily matching the spherical wave front with the curved
structures. Any limitation to horizontal the field of view given by large glancing
angles is therefore removed.

The limitations in the vertical field of view do not come at the expense of
an increased dose with our proposed scanning solution. Larger areas could in
principle be scanned with short exposure times by stacking an array of
edge-illuminated gratings. This is already offered in some commercial X-ray
diagnostic devices such as the Philips MicroDose mammography system.

\begin{quote}
    Moreover, in the methods section the authors talk of a
    \SI{5}{\percent} visibility, which is even lower than that of the quoted papers by Pfeiffer's group (refs 18, 19), which, at least nominally, reach even higher energies (123 keV). Hence, the reduction in field-of-view does not seem to be counterbalanced by significant improvements in visibility. This is also supported by the relatively poor quality of the differential phase image compared to the derivative of the absorption image, where the only advantage seems to be the visibility of the soldering points beneath the resistors (primarily due to the fact that these do not produce area contrast in the DPC image), while everywhere else the contrast of the differentiated absorption image seems to be higher.
\end{quote}
The visibility in our experiment is still low, and this obviously
affects the quality of the images, but we also mentioned
that this is the first attempt in building gratings with our new design,
while the fabrication of traditional structures has been developed for over
a decade now. The remarks above about references~18 and~19 (synchrotron
source, unpublished results) should also be taken into account here.
\begin{quote}
Finally, the novelty of the result is diminished by previous demonstrations that high energies in phase-contrast x-ray imaging could be reached by other methods (e.g. Ignatyev et al JAP 110 (2011) 014906), albeit in that case image quality seems to be lower.     
\end{quote}
In the paper from Ignatyev et al., an admittedly lower image quality was
achieved again in a lower energy range, from~\num{60}
to~\SI{100}{\kilo\volt\peak}. Thus, we would like to claim that our results
are a significantly more promising than the technique described therein.

\section*{Reviewer \#3}

\begin{quote}
    An extended object is imaged by axial scanning, which results in very
    long exposure times due to phase stepping.  The legend of Fig. 3
    indicates that one image line of \SI{0.1}{\milli\metre} width is
    acquired in \SI{6}{\minute}.  The authors admit this situation in the last sentences of the manuscripts without giving a convincing solution to the problem.
\end{quote}
This is indeed an issue, as the exposure time is mostly affected by the low visibility. The manuscript
was amended to include a more detailed discussion of how we plan to reduce
the exposure time. We briefly mention here that raising the visibility to
\SI{15}{\percent}, a value already reached in lower energy experiments,
would immediately cut the exposure by \num{9} times.
\begin{quote}
    The authors suggest that the only imaging methods that can be used with
    conventional x-ray sources are the in-line phase contrast technique and
    Talbot interferometry. They fail to mention that analyzer-based imaging
    systems with x-ray tube sources have been built and successfully used
    for imaging rather large biological objects. The current exposure times
    are shorter or comparable to those of the present work, but there are
    clear indications how the exposure times in x-ray tube based ABI can be
    reduced by an order of magnitude or more. On the other hand, the upper
    limit of photon energy is that of the tungsten Kalpha line,
    \SI{60}{\kilo\eV}. For references, see Nesch et al.(2009), Rev. Sci. Instrum. 80, 093702, and Parham et al.(2009), Acad.Radiol. 16, 911-917.
\end{quote}
We now included references to these papers, but we point out that our
experiments do not have any intrinsical limit to the photon energy.
\end{document}

### 2013-10-23 hedpc_natphys.tex
started point by point response

@@
 \renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
+\DeclareSIUnit{\peak}{p}
 
@@
 \title{X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on
-table top sources}
+conventional sources}
 
@@
 apertures \cite{Munro2012} and Talbot-Lau interferometry \cite{Pfeiffer2006}.
-
-WHAT IS TLINTERFEROMETER
-
 In addition to phase sensitivity, these techniques provide a dark-field
@@
 radiography or \ac{CT} require energies between $100$ and
-$\SI{150}{\kilo\electronvolt}$. Other potential applications are homeland
+$\SI{150}{\kilo\volt\peak}$. Other potential applications are homeland
 security or chip failure analysis, which require high energies for the
@@
 exposure times are mostly constrained by the low average visibility of the
-gratings (\SI{5}{\percent}). The exposure time can be shortened with better
-gratings and an efficient detector.
+gratings (\SI{5}{\percent}). The exposure time was chosen in order to
+get a low noise in the differential phase image. The \ac{SNR} is
+proportional to the visibility and the square root of the exposure
+time~\cite{Raupach2011}.
+This implies that the exposure times can easily drop by an order of
+magnitude as these gratings become comparable in quality to those developed
+in the last ten years. 
+The detector is also relatively inefficient ($\approx \SI{30}{\percent})$
+leaving an additional margin for improvement.
 
@@
 supported by the Competence Centre for Materials Science and Technology
-(CCMX) of the ETH-Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.
+(CCMX) of the ETH Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.
 

### 2013-10-24 hedpc_natphys.tex
Added analyzer based on tube citations
    - added appeal letter in pdf
    - added point by point response pdf

@@
 %% Packages
+\usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc} %Umlaute
@@
 \renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
-\DeclareSIUnit{\peak}{p}
+\DeclareSIUnit{\voltpeak}{Vp}
 
@@
 shift. The interaction contributing to phase shifts is coherent (Rayleigh)
-scattering \cite{Als-Nielsen2011}.
+scattering~\cite{Als-Nielsen2011}.
 
@@
 contrast with respect to absorption by providing direct access 
-to the electron density \cite{Als-Nielsen2011}. Moreover, the combination with
+to the electron density~\cite{Als-Nielsen2011}. Moreover, the combination with
 attenuation enables the determination of the effective atomic
-number \cite{Qi2010}.
+number~\cite{Qi2010}.
 An enhanced
 \ac{CNR} in images compared to attenuation for certain
-materials or tissues \cite{Pfeiffer2007a,McDonald2009} has also been
+materials or tissues~\cite{Pfeiffer2007a,McDonald2009} has also been
 demonstrated.
 
-The vast majority of phase-sensitive techniques, including crystal analyzer based
-\cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996}
+The vast majority of phase-sensitive techniques, including crystal analyzer
+based~\cite{Davis1995,Chapman1997} or interferometric~\cite{Bonse1965,Momose1996}
 methods rely on X-ray beams of high spatial and temporal coherence, which is
 available only at synchrotron sources. Inline
-phase contrast \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
-Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a} need high
+phase contrast~\cite{Snigirev1995,Wilkins1996,Cloetens1996} and
+Talbot interferometry~\cite{Cloetens1997,David2002,Momose2003a} need high
 spatial coherence but are available on microfocus sources.
@@
 demonstrated with coded
-apertures \cite{Munro2012} and Talbot-Lau interferometry \cite{Pfeiffer2006}.
+apertures~\cite{Munro2012} and Talbot-Lau
+interferometry~\cite{Pfeiffer2006}. Analyzer-based systems have been
+recently extended to tube sources~\cite{Nesch2009,Parham2009}
+but the photon energy is limited
+to the tungsten $K_\alpha$ line at~\SI{60}{\kilo\eV}.
 In addition to phase sensitivity, these techniques provide a dark-field
@@
 that is proportional to the integrated local small angle scattering power
-from microscopic density fluctuations in a specimen\cite{Pfeiffer2008}.
+from microscopic density fluctuations in a specimen~\cite{Pfeiffer2008}.
 
 Talbot interferometry has been demonstrated using a synchrotron source at
-$\SI{82}{\kilo\electronvolt}$\cite{Willner2013} and
-$\SI{123}{\kilo\electronvolt}$\cite{Ruiz2013}.
+$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013} and
+$\SI{123}{\kilo\electronvolt}$~\cite{Ruiz2013}.
 Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
-applied at $\SI{60}{\kilo\electronvolt}$ mean energy \cite{Donath2009}.
+applied at $\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}.
 Medical imaging applications may benefit from phase contrast at higher
@@
 radiography or \ac{CT} require energies between $100$ and
-$\SI{150}{\kilo\volt\peak}$. Other potential applications are homeland
+$\SI{150}{\kilo\voltpeak}$. Other potential applications are homeland
 security or chip failure analysis, which require high energies for the
@@
 compact imaging arrangements and 
-conventional X-ray tubes. The method is based on Talbot-Lau interferometry
-\cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
+conventional X-ray tubes. The method is based on Talbot-Lau interferometry~\cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
 arrangement. 
@@
 efficiently blocked by the gratings, which requires even higher aspect ratios.
-The maximum achievable aspect ratios of current fabrication techniques
-\cite{David2007,Kenntner2010} are around 60.
+The maximum achievable aspect ratios of current fabrication techniques~\cite{David2007,Kenntner2010} are around 60.
 
@@
 is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
-shifts the phase by zero and $\pi$ at this energy \cite{David2002}. Using
-gold as the phase shifting material, this requires a structure length of
-$h_1 = \SI{19.8}{\micro \metre}$. The analyzer grating is an absorption mask
+shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
+gold as the phase shifting material, a structure length of
+$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
 for sensing slight changes of the interference pattern generated by the beam
-splitter \cite{Momose2003a}. With a structure length of $h_2 =
+splitter~\cite{Momose2003a}. With a structure length of $h_2 =
 \SI{800}{\micro \metre}$
@@
 $\SI{160}{\kilo\electronvolt}$. Beam splitter and analyzer grating are
-separated at the first fractional Talbot order \cite{Weitkamp2005},
+separated at the first fractional Talbot order~\cite{Weitkamp2005},
 resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
@@
 \SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
-incoherent sources \cite{Pfeiffer2006}. It is also made of gold structures
+incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
 with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
@@
         The \ac{SEM} image shows the gold structures and the interrupting bridges
-        that prevent the lamellae from collapsing\cite{Kenntner2010}.}
+        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}
         \label{Fig:grating_mask}
@@
 
-Due to the high spectral acceptance \cite{Weitkamp2005,Thuering2013c} of the
+Due to the high spectral acceptance~\cite{Weitkamp2005,Thuering2013c} of the
 interferometer ($\SI{50}{\kilo\electronvolt}$ to
@@
 dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
-are less sensitive to beam hardening \cite{Chabior2011a}, which explains the
+are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
 lower contrast reduction of the soldering points underneath the resistors in the
 phase image of the chip. This result shows the benefit of the phase nature in
-high energy X-ray imaging, which may be useful to identify flaws in multilayered
+high-energy X-ray imaging, which may be useful to identify flaws in multilayered
 structures such as electronic chips.
@@
 limited to X-ray imaging, but could be easily applied to other grating-based
-imaging modalities (e.g., with neutrons \cite{Grunzweig2008}) where high
+imaging modalities (e.g., with neutrons~\cite{Grunzweig2008}) where high
 aspect ratios are required.
@@
 \section*{Methods}
-Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process \cite{Kenntner2010}. Each grating
+Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
 resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
@@
 Scherrer Institute (PSI), Switzerland, for the
-work on the mechanical design, the scientific advice, and the SEM images
+work on the mechanical design, the scientific advice, and the \ac{SEM} images
 respectively, Joachim Schulz and Marco Walter from
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{26}%
+\begin{thebibliography}{29}%
 \makeatletter
@@
   {year} {2011})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Qi}\ \emph {et~al.}(2010)\citenamefont {Qi},
+  \citenamefont {Zambelli}, \citenamefont {Bevins},\ and\ \citenamefont
+  {Chen}}]{Qi2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
+  {Qi}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zambelli}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Bevins}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {G.-H.}\ \bibnamefont {Chen}},\ }\href {\doibase
+  10.1088/0031-9155/55/9/016} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physics in medicine and biology}\ }\textbf {\bibinfo {volume} {55}},\
+  \bibinfo {pages} {2669} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2007)\citenamefont
@@
   \bibinfo {pages} {562} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Qi}\ \emph {et~al.}(2010)\citenamefont {Qi},
-  \citenamefont {Zambelli}, \citenamefont {Bevins},\ and\ \citenamefont
-  {Chen}}]{Qi2010}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
-  {Qi}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zambelli}},
-  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Bevins}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {G.-H.}\ \bibnamefont {Chen}},\ }\href {\doibase
-  10.1088/0031-9155/55/9/016} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physics in medicine and biology}\ }\textbf {\bibinfo {volume} {55}},\
-  \bibinfo {pages} {2669} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Davis}\ \emph {et~al.}(1995)\citenamefont {Davis},
@@
   {pages} {L866} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2006)\citenamefont
-  {Pfeiffer}, \citenamefont {Weitkamp}, \citenamefont {Bunk},\ and\
-  \citenamefont {David}}]{Pfeiffer2006}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Weitkamp}},
-  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {C.}~\bibnamefont {David}},\ }\href {\doibase
-  10.1038/nphys265} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  Physics}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {258} (\bibinfo
-  {year} {2006})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Munro}\ \emph {et~al.}(2012)\citenamefont {Munro},
@@
   {NoStop}%
+\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2006)\citenamefont
+  {Pfeiffer}, \citenamefont {Weitkamp}, \citenamefont {Bunk},\ and\
+  \citenamefont {David}}]{Pfeiffer2006}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Weitkamp}},
+  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {C.}~\bibnamefont {David}},\ }\href {\doibase
+  10.1038/nphys265} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  Physics}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {258} (\bibinfo
+  {year} {2006})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Nesch}\ \emph {et~al.}(2009)\citenamefont {Nesch},
+  \citenamefont {Fogarty}, \citenamefont {Tzvetkov}, \citenamefont {Reinhart},
+  \citenamefont {Walus}, \citenamefont {Khelashvili}, \citenamefont
+  {Muehleman},\ and\ \citenamefont {Chapman}}]{Nesch2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Nesch}}, \bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont {Fogarty}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Tzvetkov}}, \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Reinhart}}, \bibinfo {author}
+  {\bibfnamefont {a.~C.}\ \bibnamefont {Walus}}, \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {Khelashvili}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Muehleman}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {Chapman}},\ }\href {\doibase
+  10.1063/1.3213621} {\bibfield  {journal} {\bibinfo  {journal} {The Review of
+  scientific instruments}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages}
+  {093702} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parham}\ \emph {et~al.}(2009)\citenamefont {Parham},
+  \citenamefont {Zhong}, \citenamefont {Connor}, \citenamefont {Chapman},\ and\
+  \citenamefont {Pisano}}]{Parham2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Parham}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Zhong}},
+  \bibinfo {author} {\bibfnamefont {D.~M.}\ \bibnamefont {Connor}}, \bibinfo
+  {author} {\bibfnamefont {L.~D.}\ \bibnamefont {Chapman}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {E.~D.}\ \bibnamefont {Pisano}},\ }\href
+  {http://linkinghub.elsevier.com/retrieve/pii/S1076633209001366?showall=true}
+  {\enquote {\bibinfo {title} {{Design and Implementation of a Compact Low-Dose
+  Diffraction Enhanced Medical Imaging System}},}\ } (\bibinfo {year}
+  {2009})\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2008)\citenamefont
@@
   {780408}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Stutman}\ and\ \citenamefont
-  {Finkenthal}(2012)}]{Stutman2012a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Stutman}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Finkenthal}},\ }\href {\doibase 10.1063/1.4748882} {\bibfield  {journal}
-  {\bibinfo  {journal} {Applied physics letters}\ }\textbf {\bibinfo {volume}
-  {101}},\ \bibinfo {pages} {91108} (\bibinfo {year} {2012})}\BibitemShut
-  {NoStop}%
 \bibitem [{\citenamefont {Weitkamp}\ \emph {et~al.}(2005)\citenamefont
@@
   {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Raupach}\ and\ \citenamefont
+  {Flohr}(2011)}]{Raupach2011}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Raupach}}\ and\ \bibinfo {author} {\bibfnamefont {T.~G.}\ \bibnamefont
+  {Flohr}},\ }\href {\doibase 10.1088/0031-9155/56/7/020} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physics in medicine and biology}\ }\textbf {\bibinfo
+  {volume} {56}},\ \bibinfo {pages} {2219} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
 \end{thebibliography}%

### 2013-10-24 point_by_point_response.tex
Added analyzer based on tube citations     - added appeal letter in pdf     - added point by point response pdf

@@
 %
-\documentclass[a4paper]{scrartcl}
+\documentclass[a4paper,english]{scrartcl}
+\usepackage[detect-all]{siunitx}
+\usepackage{babel}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc} %Umlaute
+
+\DeclareSIUnit{\voltpeak}{Vp}
 
@@
 \section*{Reviewer \#1}
-We would like to provide more information on our experiments, as recommended
-by the first reviewer.
 \begin{quote}
-    I could not find a significant advance in this work.
-X-ray Talbot-Lau interferometers with high-energy x-rays have been already reported (Ref.
-18-20, 23, D.
-Stutman et al., Appl.
-Opt.
-49 (2010) 4677 etc.).
-The authors mention that the edge-on- illuminated grating interferometry breaks the current limitations of x-ray phase-contrast imaging, but I don't think that there is clear evidence showing that the authors' method is much more promising than the methods reported in the previous papers.
-If the authors want to show that the edge-on-illumination method is by far the most promising for high-energy and large-field-of-view x-ray phase imaging, I think that the authors have to quantitatively compare the method with those previously reported in terms of the total exposure time, spatial resolution, signal-to-noise ratio, and so on, and show that the authors' method is much better than the others.
+    I could not find a significant advance in this work. X-ray Talbot-Lau
+    interferometers with high-energy x-rays have been already reported (Ref.
+    18-20, 23, D. Stutman et al., Appl. Opt. 49 (2010) 4677 etc.). The
+    authors mention that the edge-on- illuminated grating interferometry
+    breaks the current limitations of x-ray phase-contrast imaging, but I
+    don't think that there is clear evidence showing that the authors'
+    method is much more promising than the methods reported in the previous
+    papers. If the authors want to show that the edge-on-illumination method
+    is by far the most promising for high-energy and large-field-of-view
+    x-ray phase imaging, I think that the authors have to quantitatively
+    compare the method with those previously reported in terms of the total
+    exposure time, spatial resolution, signal-to-noise ratio, and so on, and
+    show that the authors' method is much better than the others.
 \end{quote}
@@
 Moreover, those experiments were performed on a source
-with~\SI{60}{\kilo\volt\peak}, which is significantly lower than
-the~\SI{160}{\kilo\volt\peak} of our source and the~\SI{100}{\kilo\eV} used
+with~\SI{60}{\kilo\voltpeak}, which is significantly lower than
+the~\SI{160}{\kilo\voltpeak} of our source and the~\SI{100}{\kilo\eV} used
 as the design energy for our interferometer.
@@
 references~18 and~19 present Talbot interferometry at~\num{82}
-and~\SI{123}{\kilo\eV} respectively, but only the first result was published
-in a peer reviewed journal, and both experiments were performed at the ESRF
+and~\SI{123}{\kilo\eV} respectively, but only the first result is published
+on a peer reviewed journal, and both experiments were performed at the ESRF
 synchrotron, with a monochromatic and coherent beam that is incomparable to
@@
 \end{quote}
+A paragraph was added to discuss the different beam hardening behaviour of
+the absorption and differential phase image to address the reviewer's
+concerns.
 
@@
 structures. Any limitation to horizontal the field of view given by large glancing
-angles is therefore removed.
+angles is therefore removed. The gratings could already be fabricated on
+larger wafers with the existing technology.
 
@@
 principle be scanned with short exposure times by stacking an array of
-edge-illuminated gratings. This is already offered in some commercial X-ray
-diagnostic devices such as the Philips MicroDose mammography system.
+edge-illuminated gratings. This scanning technique is already offered in commercial X-ray
+diagnostic devices, such as the Philips MicroDose mammography system, to
+reduce scattering.
 
@@
 In the paper from Ignatyev et al., an admittedly lower image quality was
-achieved again in a lower energy range, from~\num{60}
-to~\SI{100}{\kilo\volt\peak}. Thus, we would like to claim that our results
+achieved again with softer X-rays, from~\num{60}
+to~\SI{100}{\kilo\voltpeak}. Thus, we claim that our results
 are a significantly more promising than the technique described therein.
@@
 This is indeed an issue, as the exposure time is mostly affected by the low visibility. The manuscript
-was amended to include a more detailed discussion of how we plan to reduce
+was amended to include a more detailed discussion of our plans to reduce
 the exposure time. We briefly mention here that raising the visibility to
@@
     limit of photon energy is that of the tungsten Kalpha line,
-    \SI{60}{\kilo\eV}. For references, see Nesch et al.(2009), Rev. Sci. Instrum. 80, 093702, and Parham et al.(2009), Acad.Radiol. 16, 911-917.
+    \SI{60}{\kilo\eV}. For references, see Nesch et al.(2009), Rev. Sci.
+    Instrum. 80, 093702, and Parham et al.(2009), Acad.Radiol. 16, 911-917.
 \end{quote}

### 2013-10-24 appeal_letter.tex
Added analyzer based on tube citations     - added appeal letter in pdf     - added point by point response pdf

\documentclass[a4paper,english]{scrlttr2}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc} %Umlaute
\usepackage{babel}

\pagestyle{empty}

\begin{document}
\begin{letter}{Dr. Congcong Huang\\

Associate Editor\\
Nature Communications \\

Unit 10-11, 42F, The Center\\
989 Changle Road, Xuhui District\\
Shanghai, China, 200031}
    \opening{Dear Dr. Huang,}

We have recently received a negative decision on our
manuscript \textsc{NCOMMS-13-09247-T}. We would like to formally appeal this
decision and ask for the permission to submit a revised version of our
manuscript addressing the concerns of the reviewers. The reason for our
appeal is mainly driven by the motivations raised by the reviewers against
our work which we found not fully correct and, in some cases, even too
simplistic. For your convenience, we will briefly summarize our arguments in
the following lines.

Referee one would actually welcome a revised manuscript, addressing his/her
comments and is not advising a rejection a priori. The mentioned work of
Stutman et al has an intrinsic limitation (the tilt angle) which our
approach does not have. Exactly this issue prevents the methods of Stutman
to achieve sufficiently high-aspect ratio \emph{and} curved profiles at the same
time, something that our method easily can. The problem mentioned on the
contrast below the soldering points can be explained by beam-hardening in
the absorption image. We would amend the manuscript accordingly, providing
more information as requested.

Referee two is skeptical about the visibility achieved in our experiment
compared to the work from Pfeiffer's group. He/she might not have noticed
that our data have been obtained on a commercially available X-ray tube,
while the cited experiment of Pfeiffer's et al. has been carried out at a
    third generation synchrotron source, where notably unsurpassed beam
    conditions can be created which are far from what one can expect in real
    life (i.e. with conventional X-ray tubes). And, even if one would like
    to still carry out this (unfair) comparison, we should mention that our
    experiment is the \emph{first} measurement of its kind with the first
    generation of gratings made according to our innovative design.
    Pfeiffer's team uses gratings obtained after almost a decade of
    development and, despite this and the use of a synchrotron, they are not
    much further than us and still carry the intrinsic limitation of a
    limited grating height. We are perfectly aware that the quality of our
    images has still to be improved, but here we are presenting the first
    experiments with edge-on grating illumination, describing its great
    potential but also acknowledging its (temporary) limitations. The same
    reviewer also complain about the limited field-of-view and a potentially higher
    dose that our method would generate compared to previous solutions. Both
    arguments are wrong, since the horizontal field-of-view is just limited by the
    size of the wafer (as for other methods) while the vertical
    field-of-view is
    covered by a vertical scan of the sample, i.e. not limited at all, and,
    more important, it does not require a higher dose. Reviewer 2 finally
    admits that in comparison with a coded-aperture based experiment at 100
    kVp our images (taken at 160 kVp) are better, which we of course
    appreciate. We believe that novelty in the approach must be the driving
    factor in judging the suitability of our work for this journal and not
    the present limitations of the technology (which can be solved!), as
    reviewer 2 seems to conclude.

In our opinion, referee three weighed the technicalities and related
limitations of our experiment too much, without considering the innovative
solution that we are introducing. As mentioned above, we are perfectly aware
of the constraints of the present system but here we are showing the
feasibility of a novel approach, which of course needs to be optimized to
reach a broader usage. He/she mentions, as comparison, an ABI experiment
performed at the tungsten 60 keV $K_\alpha$ line. We appreciate this hint and
will be happy to integrate it in our revised discussion but we would like to
already point our that our experiment was carried out at 160 kVp, with a
nominal energy around 100 keV. This is significantly higher than 60 keV. We
are not aware of any ABI setup operated at 100 keV on a conventional X-ray
source, so the comparison does not sounds very fair either.

For the above mentioned reasons, we are gently asking you to reconsider our
manuscript and to give us a chance to resubmit a revised version.

\closing{On behalf of the authors,}

M. Stampanoni
\end{letter}
\end{document}

### 2013-10-24 appeal_letter.tex
latest appeal letter

@@
 
-We have recently received a negative decision on our
-manuscript \textsc{NCOMMS-13-09247-T}. We would like to formally appeal this
-decision and ask for the permission to submit a revised version of our
-manuscript addressing the concerns of the reviewers. The reason for our
-appeal is mainly driven by the motivations raised by the reviewers against
-our work which we found not fully correct and, in some cases, even too
-simplistic. For your convenience, we will briefly summarize our arguments in
-the following lines.
+We have recently received a negative decision on our manuscript NCOMMS-13-09247-T.
+We would like to formally appeal this decision and ask for the permission to submit a revised version of our manuscript addressing the concerns of the reviewers.
+The reason for our appeal is mainly driven by the motivations raised by the reviewers against our work which we found not fully correct and, in some cases, even too simplistic.
+For your convenience, we will briefly summarize our arguments in the following lines.
 
-Referee one would actually welcome a revised manuscript, addressing his/her
+Referee one actually would welcome a revised manuscript, addressing his/her
 comments and is not advising a rejection a priori. The mentioned work of
 Stutman et al has an intrinsic limitation (the tilt angle) which our
-approach does not have. Exactly this issue prevents the methods of Stutman
-to achieve sufficiently high-aspect ratio \emph{and} curved profiles at the same
-time, something that our method easily can. The problem mentioned on the
-contrast below the soldering points can be explained by beam-hardening in
-the absorption image. We would amend the manuscript accordingly, providing
-more information as requested.
+approach does not have. Exactly this issue prevents the method of Stutman to
+achieve sufficiently high-aspect ratio \emph{and} curved profiles at the same time, something that our method easily can.
+The problem mentioned on the contrast below the soldering points can be explained by beam-hardening in the absorption image.
+We would amend the manuscript accordingly, providing more information as requested.
 
 Referee two is skeptical about the visibility achieved in our experiment
-compared to the work from Pfeiffer's group. He/she might not have noticed
+compared with the work from Pfeiffer's group. He/she might not have noticed
 that our data have been obtained on a commercially available X-ray tube,
@@
 conditions can be created which are far from what one can expect in real
-    life (i.e. with conventional X-ray tubes). And, even if one would like
-    to still carry out this (unfair) comparison, we should mention that our
-    experiment is the \emph{first} measurement of its kind with the first
-    generation of gratings made according to our innovative design.
-    Pfeiffer's team uses gratings obtained after almost a decade of
-    development and, despite this and the use of a synchrotron, they are not
-    much further than us and still carry the intrinsic limitation of a
-    limited grating height. We are perfectly aware that the quality of our
-    images has still to be improved, but here we are presenting the first
-    experiments with edge-on grating illumination, describing its great
-    potential but also acknowledging its (temporary) limitations. The same
-    reviewer also complain about the limited field-of-view and a potentially higher
-    dose that our method would generate compared to previous solutions. Both
-    arguments are wrong, since the horizontal field-of-view is just limited by the
-    size of the wafer (as for other methods) while the vertical
-    field-of-view is
-    covered by a vertical scan of the sample, i.e. not limited at all, and,
-    more important, it does not require a higher dose. Reviewer 2 finally
-    admits that in comparison with a coded-aperture based experiment at 100
-    kVp our images (taken at 160 kVp) are better, which we of course
-    appreciate. We believe that novelty in the approach must be the driving
-    factor in judging the suitability of our work for this journal and not
-    the present limitations of the technology (which can be solved!), as
-    reviewer 2 seems to conclude.
+life (i.e. with conventional X-ray tubes). And, even if one would like to
+still carry out this (unfair) comparison, we should mention that our
+experiment is the \emph{first} measurement of its kind with the first generation of gratings made according to our innovative design.
+Pfeiffer's team uses gratings obtained after almost a decade of development and, despite this and the use of a synchrotron, they are not much further than us and still carry the intrinsic limitation of a limited grating height.
+We are perfectly aware that the quality of our images has still to be improved, but here we are presenting the first experiments with edge-on grating illumination: we describe its great potential but also mention its (temporary) limitations.
+The same reviewer also complains about the limited field-of-view our method is supposed to have.
+This is actually wrong, since the horizontal field-of-view is just limited by the size of the wafer (as for other methods) while the vertical field-of-view is covered by a vertical scan of the sample, i.e.
+not limited at all, and, even more important, it becomes very interesting when CT applications are considered (all modern CT systems combine a line (or few lines) detector with a patient translation).
+Reviewer 2 finally admits that in comparison with a coded-aperture based experiment at 100 kVp our images (taken at 160 kVp) are better, which we of course appreciate.
+We believe that novelty in the approach must be the driving factor in judging the suitability of our work for this journal and not the present limitations of the technology (which can be solved!), as reviewer 2 seems to conclude.
 
@@
 reach a broader usage. He/she mentions, as comparison, an ABI experiment
-performed at the tungsten 60 keV $K_\alpha$ line. We appreciate this hint and
-will be happy to integrate it in our revised discussion but we would like to
-already point our that our experiment was carried out at 160 kVp, with a
-nominal energy around 100 keV. This is significantly higher than 60 keV. We
-are not aware of any ABI setup operated at 100 keV on a conventional X-ray
-source, so the comparison does not sounds very fair either.
+performed at the tungsten 60 keV $K_\alpha$ line.
+We appreciate this hint and will be happy to integrate it in our revised discussion but we would like to already point our that our experiment was carried out at 160 kVp, with a nominal energy around 100 keV.
+This is significantly higher than 60 keV.
+We are not aware of any ABI setup operated at 100 keV on a conventional X-ray source, so the comparison does not sounds very fair either.
 
-For the above mentioned reasons, we are gently asking you to reconsider our
-manuscript and to give us a chance to resubmit a revised version.
+For the above mentioned reasons, we are gently asking you to reconsider our manuscript and to give us a chance to resubmit a revised version.
 

### 2013-10-24 hedpc_natphys.tex
thomas review of the changes

@@
 Talbot interferometry~\cite{Cloetens1997,David2002,Momose2003a} need high
-spatial coherence but are available on microfocus sources.
+spatial coherence but are available on polychromatic microfocus sources.
 Phase-contrast imaging using X-ray beams of low temporal \emph{and}
@@
 compact imaging arrangements and 
-conventional X-ray tubes. The method is based on Talbot-Lau interferometry~\cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
+conventional X-ray tubes. The method is based on Talbot-Lau
+interferometry~\cite{Pfeiffer2006} and employs an edge-on illumination approach for the grating design and
 arrangement. 
@@
 direction is limited to one detector pixel row. In the horizontal direction,
-the field of view is limited by the grating size and the geometric
-magnification of the sample, yielding a maximum field of view of
-$\SI{30}{\milli\metre}$. In addition to the standard components (source,
+the field of view is only limited by the grating size to
+$\SI{30}{\milli\metre}$, but wider gratings can be fabricated with this
+method and the available technology on larger wafers. In addition to the standard components (source,
 camera, interferometer), two optical slits, one in front of the source
@@
 impinging on these soldering point is hardened by the resistors in the upper
-layer, resuluting in lower absorption contrast. Due to the weaker energy
+layer, resulting in lower absorption contrast. Due to the weaker energy
 dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
@@
 in the last ten years. 
+Smaller regions of these gratings actually exhibit a visibility up
+to~\SI{14}{\percent} already, indicating that this goal is reachable as the
+fabrication becomes more reliable and uniform.
 The detector is also relatively inefficient ($\approx \SI{30}{\percent})$

### 2013-10-28 hedpc_natphys.tex
Marcos revision for the paper

@@
 materials and life sciences for the nondestructive examination of samples or
-the diagnosis of diseases in patients. The underlying contrast mechanism
+diagnostic tasks in medicine. The underlying contrast mechanism
 relies on the different X-ray attenuation properties of different materials
@@
 Phase-sensitive
-imaging is a desirable modality, as it can provide a complementary source of
+imaging is a desirable modality, as it delivers a complementary source of
 contrast with respect to absorption by providing direct access 
@@
 recently extended to tube sources~\cite{Nesch2009,Parham2009}
-but the photon energy is limited
+but only at energies up
 to the tungsten $K_\alpha$ line at~\SI{60}{\kilo\eV}.
-In addition to phase sensitivity, these techniques provide a dark-field
-contrast, also called scatter contrast or visibility-reduction contrast,
-that is proportional to the integrated local small angle scattering power
-from microscopic density fluctuations in a specimen~\cite{Pfeiffer2008}.
+In addition to phase sensitivity, analyzer-based, Talbot interferometry and
+coded-aperture approaches also provide (with different retrieval mechanisms)
+information about the integrated local small angle scattering power from
+microscopic density fluctuations in a specimen~\cite{Pfeiffer2008}. This signal is known under the name of dark-field, scatter or visibility reduction contrast.
 
-Talbot interferometry has been demonstrated using a synchrotron source at
+High-energy Talbot interferometry has been reported so far using a
+synchrotron source at nominal energies of
 $\SI{82}{\kilo\electronvolt}$~\cite{Willner2013} and 
@@
 Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
-applied at $\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}.
+applied so far at $\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}.
 Medical imaging applications may benefit from phase contrast at higher
@@
 
-Here, we introduce a method for phase-contrast imaging which is
-compatible with the entire diagnostic energy range of X-rays, 
-compact imaging arrangements and 
-conventional X-ray tubes. The method is based on Talbot-Lau
+Here we introduce a method for phase contrast imaging which works on
+conventional X-ray sources, covers the entire diagnostic X-ray energy range
+and is compatible with compact imaging arrangements. The approach is based
+on
+Talbot-Lau
 interferometry~\cite{Pfeiffer2006} and employs an edge-on illumination approach for the grating design and
 arrangement. 
-The challenge which limited the progress towards higher energies was mainly
-related to the manufacturing of gratings with high aspect ratios. The aspect
+Our solution removes one on the major hurdle which prevented grating interferometry to be applied at very high X-ray energies so far, namely the fabrication of gratings with high-aspect ratios.
+ The aspect
 ratio, given by
@@
 where $p$ is the grating period and $h$ the  structure
-height, is normally limited by the lithographic process, as grating
+height, is normally limited by the fabrication process, usually
+photolithography~\cite{David2002} or X-ray lithography~\cite{Mohr2012} as grating
 structures tend to collapse or deform (e.g. due to capillary forces) if
@@
 efficiently blocked by the gratings, which requires even higher aspect ratios.
-The maximum achievable aspect ratios of current fabrication techniques~\cite{David2007,Kenntner2010} are around 60.
+The largest aspect ratios achieved by current fabrication techniques~\cite{David2007,Kenntner2010} are around 60.
 
 Our design introduces the edge-on
-illumination of circularly aligned structures. Edge-on illumination
+illuminated,  circularly aligned structures. Edge-on illumination
 (figure~\ref{Fig:schematic}), as
@@
 function at high incident angles. In order to overcome this problem, the grating lines are circularly aligned 
-with a radius equal to the distance to the source.
+with a radius equal to the distance to the source. This cannot be done with
+the glancing angle approach~\cite{Stutman2012a}, and allows an arbitrarily
+large field-of-view in a fan beam geometry.
 
@@
 direction ($y$ direction), which is, depending on the X-ray detector,
-typically a few pixels. However, radiographic 2D imaging is possible in
-scanning mode, without increasing dose. Similarly, for tomographic images,
+typically a few pixels. 
+Radiographic 2D imaging can be obtained by scanning the sample or a thin fan
+beam. The scanning technique has been demonstrated to deliver less dose than
+the conventional approach based on the illumination of a large area. In
+digital mammography, for instance, where dose is a critical issue, Philips'
+MicroDose system combines a scanning approach with an highly collimated fan
+beam~\cite{Aslund2007}. Thanks to the high collimation, the dose deposited
+on  patients has been reported to be significantly lower than with other
+instruments based on the illumination of a large area
+detector~\cite{Oduko2010}.
+Similarly, for tomographic images,
 the approach allows single slice \ac{CT} or full 3D imaging in scanning mode.
@@
 Grating design and fabrication is nonstandard and involves a complex mask
-design, as shown in Figure~\ref{Fig:grating_mask}. Each grating resides on a
-silicon chip and has its specific structure length and curvature. For the
+design, as shown in Figure~\ref{Fig:grating_mask}. Multiple gratings can reside on a
+silicon chip with their specific structure length and curvature. For the
 current experiments, a symmetric interferometer with a grating period of $p
@@
 
-Edge-on illuminated grating interferometry breaks the current limitations of
-phase-contrast imaging to the lower diagnostic energy range. Compact
-geometries  using conventional X-ray sources for design energies well above
-$\SI{100}{\kilo\electronvolt}$ could be realized with the approach. This
-enables the examination of materials of higher density or thickness which
-would be opaque at lower energies. Finally, the approach is not
-limited to X-ray imaging, but could be easily applied to other grating-based
-imaging modalities (e.g., with neutrons~\cite{Grunzweig2008}) where high
-aspect ratios are required.
+Edge-on illuminated grating interferometry finally allows phase contrast
+imaging to be performed at high energies ($>\SI{100}{\kilo\eV}$) on conventional X-ray
+sources. With a circular distribution of the gratings, the diffracting and
+absorbing structures can be matched to the divergent beam, even for very
+compact geometries. Short, high-energy phase-contrast systems enable the
+efficient investigation of high-density materials or large thickness,
+adding information on electron density and integrated small angle scattering
+power to the conventional absorption based signal. This will improve
+material discrimination and density sensitivity capabilities in future
+X-rays or even neutron~\cite{Grunzweig2008} investigations.
 
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{29}%
+\begin{thebibliography}{33}%
 \makeatletter
@@
   {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mohr}\ \emph {et~al.}(2012)\citenamefont {Mohr},
+  \citenamefont {Grund}, \citenamefont {Kunka}, \citenamefont {Kenntner},
+  \citenamefont {Leuthold}, \citenamefont {Meiser}, \citenamefont {Schulz},\
+  and\ \citenamefont {Walter}}]{Mohr2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Mohr}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Grund}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Kunka}}, \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Kenntner}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Leuthold}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Meiser}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Schulz}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Walter}},\ }\href {\doibase 10.1063/1.4742267} {\ \textbf
+  {\bibinfo {volume} {41}},\ \bibinfo {pages} {41} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {David}\ \emph {et~al.}(2007)\citenamefont {David},
@@
   {780408}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Stutman}\ and\ \citenamefont
+  {Finkenthal}(2012)}]{Stutman2012a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Stutman}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Finkenthal}},\ }\href {\doibase 10.1063/1.4748882} {\bibfield  {journal}
+  {\bibinfo  {journal} {Applied physics letters}\ }\textbf {\bibinfo {volume}
+  {101}},\ \bibinfo {pages} {91108} (\bibinfo {year} {2012})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {{\AA slund, M}}(2007)}]{Aslund2007}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibnamefont {{\AA slund, M}}},\
+  }\emph {\bibinfo {title} {{Digital Mammography with a Photon Counting
+  Detector in a Scanned Multislit Geometry}}},\ \href@noop {} {Ph.D. thesis}
+  (\bibinfo {year} {2007})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Oduko}\ \emph {et~al.}(2010)\citenamefont {Oduko},
+  \citenamefont {Young},\ and\ \citenamefont {Burch}}]{Oduko2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
+  {Oduko}}, \bibinfo {author} {\bibfnamefont {K.~C.}\ \bibnamefont {Young}}, \
+  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Burch}},\ }in\ \href
+  {\doibase 10.1007/978-3-642-13666-5_49} {\emph {\bibinfo {booktitle} {Digital
+  Mammography}}},\ \bibinfo {series} {Lecture Notes in Computer Science}, Vol.\
+  \bibinfo {volume} {6136},\ \bibinfo {editor} {edited by\ \bibinfo {editor}
+  {\bibfnamefont {J.}~\bibnamefont {Martí}}, \bibinfo {editor} {\bibfnamefont
+  {A.}~\bibnamefont {Oliver}}, \bibinfo {editor} {\bibfnamefont
+  {J.}~\bibnamefont {Freixenet}}, \ and\ \bibinfo {editor} {\bibfnamefont
+  {R.}~\bibnamefont {Martí}}}\ (\bibinfo  {publisher} {Springer Berlin
+  Heidelberg},\ \bibinfo {year} {2010})\ pp.\ \bibinfo {pages}
+  {365--370}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Weitkamp}\ \emph {et~al.}(2005)\citenamefont

### 2013-10-28 point_by_point_response.tex
point by point with quotes

@@
 \DeclareSIUnit{\voltpeak}{Vp}
+\newenvironment{reviewerquote}{\begin{quote}\itshape}{\end{quote}}
 
@@
 
+The comments from the reviewers are quoted in \emph{italic}, whereas the
+revised article parts are reported in upright font.
 \section*{Reviewer \#1}
-\begin{quote}
+\begin{reviewerquote}
     I could not find a significant advance in this work. X-ray Talbot-Lau
@@
     show that the authors' method is much better than the others.
-\end{quote}
+\end{reviewerquote}
 We think that the experiments presented in the current manuscript show
@@
 
+In order to address the concerns of reviewer \#1, the short review of the
+previous results in the
+introductory paragraph has been updated:
 \begin{quote}
+The vast majority of phase-sensitive techniques, including crystal analyzer based [5, 6] or
+interferometric [7, 8] methods rely on X-ray beams of high spatial and temporal coherence,
+which is available only at synchrotron sources. Inline phase contrast [9–11] and Talbot interferometry [12–14] need high spatial coherence but are available on polychromatic microfocus
+sources. Phase-contrast imaging using X-ray beams of low temporal and spatial coherence
+such as conventional low-brilliance X-ray tubes have been demonstrated with coded apertures [15] and Talbot-Lau interferometry [16]. Analyzer-based systems have been recently
+extended to tube sources [17, 18] but only at energies up to the tungsten
+$K_\alpha$ line at 60 keV. In
+addition to phase sensitivity, analyzer-based, Talbot interferometry and coded-aperture approaches also provide (with different retrieval mechanisms) information about the integrated
+local small angle scattering power from microscopic density fluctuations in a specimen [19].
+This signal is known under the name of dark-field, scatter or visibility reduction contrast.
+High-energy Talbot interferometry has been reported so far using a synchrotron source
+at nominal energies of 82 keV [20] and 123 keV [21]. Using a low-brilliance X-ray tube,
+2
+Talbot-Lau interferometry was applied so far at 60 keV mean energy [22]. Medical imaging
+applications may benefit from phase contrast at higher energies: chest or abdominal radiography or CT require energies between 100 and 150 kVp. Other potential applications are
+homeland security or chip failure analysis, which require high energies for the visualization
+of materials of high density and atomic number.
+\end{quote}
+
+\begin{reviewerquote}
     Furthermore, the authors mention that the results in Fig.
@@
 Otherwise, the authors' assertion is suspicious.
+\end{reviewerquote}
+A paragraph has been added to discuss the different beam hardening behaviour of
+the absorption and differential phase image:
+\begin{quote}
+resistors, while in the phase image, they can clearly be identified. The reduced contrast
+of the soldering points in the absorption image is due to beam hardening. The spectrum
+impinging on these soldering point is hardened by the resistors in the upper layer, resulting
+in lower absorption contrast. Due to the weaker energy dependency of phase
+shifts ($1/E$
+compared to $1/E^3$), phase-contrast images are less sensitive to beam hardening [31], which
+explains the lower contrast reduction of the soldering points underneath the resistors in the
+phase image of the chip. This result shows the benefit of the phase nature in high-energy
+X-ray imaging, which may be useful to identify flaws in multilayered structures such as
+electronic chips.
 \end{quote}
-A paragraph was added to discuss the different beam hardening behaviour of
-the absorption and differential phase image to address the reviewer's
-concerns.
 
 \section*{Reviewer \#2}
-\begin{quote}
+\begin{reviewerquote}
     However, this solution comes with significant drawbacks in terms of very
     limited fields of view~\SI{3}{\centi\metre} horizontally, a single detector pixel in the vertical direction), which at the moment seem hard to overcome.
-\end{quote}
+\end{reviewerquote}
 There is no fundamental limitation on the horizontal field of view in our
@@
 diagnostic devices, such as the Philips MicroDose mammography system, to
-reduce scattering.
+reduce scattering. References are now provided in the following paragraph:
+\begin{quote}
+ Radiographic 2D imaging can be obtained by scanning the sample or a
+thin fan beam. The scanning technique has been demonstrated to deliver less dose than the
+conventional approach based on the illumination of a large area. In digital mammography,
+for instance, where dose is a critical issue, Philips’ MicroDose system combines a scanning
+approach with an highly collimated fan beam [27]. Thanks to the high collimation, the dose
+deposited on patients has been reported to be significantly lower than with other instruments
+based on the illumination of a large area detector [28]. 
+\end{quote}
 
-\begin{quote}
+\begin{reviewerquote}
     Moreover, in the methods section the authors talk of a
@@
 This is also supported by the relatively poor quality of the differential phase image compared to the derivative of the absorption image, where the only advantage seems to be the visibility of the soldering points beneath the resistors (primarily due to the fact that these do not produce area contrast in the DPC image), while everywhere else the contrast of the differentiated absorption image seems to be higher.
-\end{quote}
+\end{reviewerquote}
 The visibility in our experiment is still low, and this obviously
@@
 source, unpublished results) should also be taken into account here.
-\begin{quote}
+\begin{reviewerquote}
 Finally, the novelty of the result is diminished by previous demonstrations that high energies in phase-contrast x-ray imaging could be reached by other methods (e.g.
 Ignatyev et al JAP 110 (2011) 014906), albeit in that case image quality seems to be lower.
-\end{quote}
+\end{reviewerquote}
 In the paper from Ignatyev et al., an admittedly lower image quality was
@@
 
-\begin{quote}
+\begin{reviewerquote}
     An extended object is imaged by axial scanning, which results in very
@@
     acquired in \SI{6}{\minute}.  The authors admit this situation in the last sentences of the manuscripts without giving a convincing solution to the problem.
-\end{quote}
+\end{reviewerquote}
 This is indeed an issue, as the exposure time is mostly affected by the low visibility. The manuscript
 was amended to include a more detailed discussion of our plans to reduce
-the exposure time. We briefly mention here that raising the visibility to
-\SI{15}{\percent}, a value already reached in lower energy experiments,
-would immediately cut the exposure by \num{9} times.
+the exposure time. We mention now that raising the visibility to
+\SI{15}{\percent}, a value already reached in lower energy experiments and
+in some sections of our gratings,
+would immediately cut the exposure by \num{9} times:
 \begin{quote}
+visibility of the gratings (5 \%). The exposure time was chosen in order to get a low noise in
+the differential phase image. The signal-to-noise ratio (SNR) is proportional to the visibility
+and the square root of the exposure time [33]. This implies that the exposure times can
+easily drop by an order of magnitude as these gratings become comparable in quality to
+those developed in the last ten years. Smaller regions of these gratings actually exhibit a
+visibility up to 14 \% already, indicating that this goal is reachable as the fabrication becomes
+more reliable and uniform. The detector is also relatively inefficient (30
+\%) leaving an
+additional margin for improvement.
+\end{quote}
+\begin{reviewerquote}
     The authors suggest that the only imaging methods that can be used with
@@
     Instrum. 80, 093702, and Parham et al.(2009), Acad.Radiol. 16, 911-917.
-\end{quote}
-We now included references to these papers, but we point out that our
+\end{reviewerquote}
+We now included references to these papers (in the first paragraph above), but we point out that our
 experiments do not have any intrinsical limit to the photon energy.

### 2013-10-28 hedpc_natphys.tex
point by point with quotes

@@
 \title{X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on
-conventional sources}
+a conventional source}
 
@@
 an optical lens projecting the image onto the CCD. The effective pixel size
-is $\SI{80}{\micro \metre}$. The widths of the collimating slits are
-$\SI{25}{\micro \metre}$ and $\SI{100}{\micro\metre}$, respectively.
+is $\SI{80}{\micro \metre}$. The collimating slit right after the source is 
+$\SI{25}{\micro \metre}$ large, while the second slit before the detector is
+$\SI{100}{\micro\metre}$.
 

### 2013-10-28 point_by_point_response.tex
title changed in point by point

@@
 
+\noindent
 The comments from the reviewers are quoted in \emph{italic}, whereas the
@@
 a conventional tube.
+In order to emphasize this enormous difference between synchrotron sources
+and lab sources, the title has been changed to ``X-ray phase-contrast imaging at
+100 keV on
+a conventional source''.
 

### 2013-10-31 point_by_point_response.tex
dropped efficiency remarks on the detector

@@
 \title{Point-by-point response to the reviewers}
+\author{Revised manuscript NCOMMS-13-09247-T}
 \date{}
@@
 The comments from the reviewers are quoted in \emph{italic}, whereas the
-revised article parts are reported in upright font.
+revised article parts are reported in upright font in indented sections.
 \section*{Reviewer \#1}
@@
 \end{reviewerquote}
-We think that the experiments presented in the current manuscript show
-indeed significant progress with respect to the cited references.
-The method presented by Stutman et al. has a fundamental limitation that
-prevents it from achieving curved structures and large aspect ratios.
-Moreover, those experiments were performed on a source
-with~\SI{60}{\kilo\voltpeak}, which is significantly lower than
-the~\SI{160}{\kilo\voltpeak} of our source and the~\SI{100}{\kilo\eV} used
-as the design energy for our interferometer.
 
-The other works also present results in a much lower energy range or very
-different conditions, thus preventing a meaningful comparison.
+Stuntman et al.  present a method which increases the effective
+aspect ratio of the gratings by slightly rotating them along an axis
+perpendicular to the propagation direction. However, his method has
+the major limitation of not being compatible with divergent
+geometries. As a result, his interferometer will show a high
+visibility, although still limited compared to what we can achieve in
+theory, but its horizontal field of view will be strongly limited in
+case of divergent beams, as commonly found in any table-top device.
+Our solution, on the other hand, solves both issues at the same time,
+and therefore we consider this as a significant improvement with
+respect to Stuntman's work.  Moreover, the cited experiments were
+performed on a source with~\SI{60}{\kilo\voltpeak}, which is significantly lower than
+the~\SI{160}{\kilo\voltpeak} of our source and the~\SI{100}{\kilo\eV} used as the design energy
+for our interferometer. Reviewer \#1 further cites other related works
+which, however, where carried out either in much lower energy range or
+under very different imaging conditions, thus preventing a meaningful
+comparison.
+
 Reference~23 reported images taken at \num{30} and~\SI{60}{\kilo\eV},
@@
 $K_\alpha$ line at 60 keV. In
-addition to phase sensitivity, analyzer-based, Talbot interferometry and coded-aperture approaches also provide (with different retrieval mechanisms) information about the integrated
+addition to phase sensitivity, analyzer-based and Talbot interferometry also provide (with different retrieval mechanisms) information about the integrated
 local small angle scattering power from microscopic density fluctuations in a specimen [19].
@@
 at nominal energies of 82 keV [20] and 123 keV [21]. Using a low-brilliance X-ray tube,
-2
 Talbot-Lau interferometry was applied so far at 60 keV mean energy [22]. Medical imaging
-applications may benefit from phase contrast at higher energies: chest or abdominal radiography or CT require energies between 100 and 150 kVp. Other potential applications are
+applications may benefit from phase contrast at higher energies: chest or abdominal radiography or CT require an acceleration voltage between 100 and 150 kVp. Other potential applications are
 homeland security or chip failure analysis, which require high energies for the visualization
@@
 \begin{quote}
+In the attenuation image, the contrast of the soldering points of the integrated circuit is reduced underneath the
 resistors, while in the phase image, they can clearly be identified. The reduced contrast
@@
 structures. Any limitation to horizontal the field of view given by large glancing
-angles is therefore removed. The gratings could already be fabricated on
-larger wafers with the existing technology.
+angles is therefore removed. 
+Our approach removes any limitation to the horizontal field of view which would arise due to the large beam divergence.
+In addition, curved gratings can be easily stitched to cover an even larger field of view, if necessary.
 
-The limitations in the vertical field of view do not come at the expense of
+With our scanning solution, the limitation of the vertical field of view does not come at the expense of
 an increased dose with our proposed scanning solution. Larger areas could in
 principle be scanned with short exposure times by stacking an array of
-edge-illuminated gratings. This scanning technique is already offered in commercial X-ray
-diagnostic devices, such as the Philips MicroDose mammography system, to
-reduce scattering. References are now provided in the following paragraph:
+edge-illuminated gratings. 
+A similar scanning technique is already commercially offered in X-ray
+mammography systems, like the MicroDose instrument of Philips, with a
+significant reduction of the scattered radiation. We discussed this issue and
+amended the text accordingly.
 \begin{quote}
@@
 The visibility in our experiment is still low, and this obviously
-affects the quality of the images, but we also mentioned
-that this is the first attempt in building gratings with our new design,
-while the fabrication of traditional structures has been developed for over
-a decade now. The remarks above about references~18 and~19 (synchrotron
-source, unpublished results) should also be taken into account here.
+affects the quality of the images,
+
+We would like to remind to the reviewer \#2 that our data have been obtained on
+a commercially available X-ray tube, while the cited experiment of Pfeiffer's
+et al. has been carried out at a third generation synchrotron source, where
+notably unsurpassed beam conditions can be created which are far from what one
+can expect in real life (i.e. with conventional X-ray tubes). And, even if one
+would like to still carry out this (unfair) comparison, we should mention that
+our experiment is the first measurement of its kind with the first generation
+of gratings made according to our innovative design. Pfeiffer's team uses
+gratings obtained after almost a decade of development and, despite this and
+the use of a synchrotron, they are not really further than us while they still
+carry the intrinsic limitation of a limited grating height. We are well aware
+that the quality of our images has still to be improved, but here we are
+presenting the first experiments with edge-on grating illumination: we describe
+its great potential but also mention its (temporary) limitations.
 \begin{reviewerquote}
@@
 \end{reviewerquote}
-In the paper from Ignatyev et al., an admittedly lower image quality was
-achieved again with softer X-rays, from~\num{60}
-to~\SI{100}{\kilo\voltpeak}. Thus, we claim that our results
-are a significantly more promising than the technique described therein.
+Reviewer \#2 admits that in comparison with a coded-aperture based experiment at 100 kVp (Ignatyev et al.) our images (taken at 160 kVp) are better, which we of course appreciate.
 
@@
 in some sections of our gratings,
-would immediately cut the exposure by \num{9} times:
+would immediately cut the exposure by almost an order of magnitude:
 \begin{quote}
+The long exposure times are mostly constrained by the low average
 visibility of the gratings (5 \%). The exposure time was chosen in order to get a low noise in
@@
 visibility up to 14 \% already, indicating that this goal is reachable as the fabrication becomes
-more reliable and uniform. The detector is also relatively inefficient (30
-\%) leaving an
-additional margin for improvement.
+more reliable and uniform.
 \end{quote}
@@
 \end{reviewerquote}
-We now included references to these papers (in the first paragraph above), but we point out that our
-experiments do not have any intrinsical limit to the photon energy.
+We thank Reviewer \#3 for pointing out this issue. We amended the text
+accordingly, discussing specifically the cited analyzer-based imaging experiment. In particular,
+we highlight that the mentioned ABI investigation was carried out at 60 keV,
+far below our nominal energy of 100 keV. We are also not aware of any ABI
+operated at energies higher or equal to 100 keV on conventional X-ray sources. 
 \end{document}

### 2013-10-31 hedpc_natphys.tex
dropped efficiency remarks on the detector

@@
 to the tungsten $K_\alpha$ line at~\SI{60}{\kilo\eV}.
-In addition to phase sensitivity, analyzer-based, Talbot interferometry and
-coded-aperture approaches also provide (with different retrieval mechanisms)
+In addition to phase sensitivity, analyzer-based and Talbot interferometry 
+approaches also provide (with different retrieval mechanisms)
 information about the integrated local small angle scattering power from
@@
 illuminated,  circularly aligned structures. Edge-on illumination
-(figure~\ref{Fig:schematic}), as
+(Fig.~\ref{Fig:schematic}), as
 opposed to face-on illumination, exploits the dimension along the grating
@@
         aspect ratio is defined by the ratio of the travelling distance along the
-        grating lines and the period and can be arbitrarily long. In order to avoid
-        a reduction of the field of view, the grating structures are aligned on an
+        grating lines and the period and can be arbitrarily long. In order to maximise
+        the field of view, the grating structures are aligned on an
     arc.}
@@
 Grating design and fabrication is nonstandard and involves a complex mask
-design, as shown in Figure~\ref{Fig:grating_mask}. Multiple gratings can reside on a
+design, as shown in Fig.~\ref{Fig:grating_mask}. Multiple gratings can reside on a
 silicon chip with their specific structure length and curvature. For the
@@
 compact geometries. Short, high-energy phase-contrast systems enable the
-efficient investigation of high-density materials or large thickness,
+efficient investigation of high-density materials or thick samples,
 adding information on electron density and integrated small angle scattering
@@
 fabrication becomes more reliable and uniform.
-The detector is also relatively inefficient ($\approx \SI{30}{\percent})$
-leaving an additional margin for improvement.
 

### 2013-10-31 hedpc_natphys.tex
abstract typos

@@
     present edge-on illumination of the gratings to overcome their current
-    fabrication limits as well as curved structures, to match beam
-    divergence and allow large field of views on a short and efficient
+    fabrication limits as well as curved structures, to match the beam
+    divergence and allow a large field of view on a short and efficient
     setup.

### 2013-10-31 point_by_point_response.tex
response and paper typos

@@
 explains the lower contrast reduction of the soldering points underneath the resistors in the
-phase image of the chip. This result shows the benefit of the phase nature in high-energy
+phase image of the chip. This result shows the benefit of the phase contrast in high-energy
 X-ray imaging, which may be useful to identify flaws in multilayered structures such as
@@
 issue, by easily matching the spherical wave front with the curved
-structures. Any limitation to horizontal the field of view given by large glancing
-angles is therefore removed. 
+structures.
 Our approach removes any limitation to the horizontal field of view which would arise due to the large beam divergence.
@@
 With our scanning solution, the limitation of the vertical field of view does not come at the expense of
-an increased dose with our proposed scanning solution. Larger areas could in
-principle be scanned with short exposure times by stacking an array of
-edge-illuminated gratings. 
+an increased dose. 
 A similar scanning technique is already commercially offered in X-ray
@@
 \end{reviewerquote}
-The visibility in our experiment is still low, and this obviously
-affects the quality of the images,
-
 We would like to remind to the reviewer \#2 that our data have been obtained on

### 2013-10-31 hedpc_natphys.tex
response and paper typos

@@
 energies: chest or abdominal
-radiography or \ac{CT} require energies between $100$ and
+radiography or \ac{CT} require an acceleration voltage between \num{100} and
 $\SI{150}{\kilo\voltpeak}$. Other potential applications are homeland
@@
 function at high incident angles. In order to overcome this problem, the grating lines are circularly aligned 
-with a radius equal to the distance to the source. This cannot be done with
-the glancing angle approach~\cite{Stutman2012a}, and allows an arbitrarily
-large field-of-view in a fan beam geometry.
+with a radius equal to the distance to the source. 
+This allows to achieve an arbitrarily large field of view in a fan-beam
+geometry, a significant improvement compared to face-on based and glancing
+angle~\cite{Stutman2012a} approaches.
 
@@
 typically a few pixels. 
-Radiographic 2D imaging can be obtained by scanning the sample or a thin fan
+However, radiographic 2D imaging can be obtained by scanning the sample or a thin fan
 beam. The scanning technique has been demonstrated to deliver less dose than

### 2013-10-31 appeal_letter.tex
appeal letter typo, restored latex version

@@
 \usepackage{babel}
+\linespread{1.05}
 
 \pagestyle{empty}
+\setlength{\parskip}{.5\baselineskip}
 
+\date{\today}
 \begin{document}
@@
 
-We have recently received a negative decision on our manuscript NCOMMS-13-09247-T.
-We would like to formally appeal this decision and ask for the permission to submit a revised version of our manuscript addressing the concerns of the reviewers.
-The reason for our appeal is mainly driven by the motivations raised by the reviewers against our work which we found not fully correct and, in some cases, even too simplistic.
-For your convenience, we will briefly summarize our arguments in the following lines.
+We refer to your communication of October 23, concerning our appeal to the negative
+decision about our manuscript NCOMMS-13-09247-T. We are very happy to grasp that
+you are now essentially welcoming a revised version of our paper, provided we also
+submit a comprehensive, point-by-point reply to the reviewer’s comments as well as a
+letter explaining why we are strongly convinced that our manuscript warrants further
+consideration by Nature Communications. Our arguments on this are presented in the
+following. We would like to reiterate first the reasons for our appeal and then we would
+like to highlight the achievements obtained in our work to justify our claims for further
+consideration.
 
-Referee one actually would welcome a revised manuscript, addressing his/her
-comments and is not advising a rejection a priori. The mentioned work of
-Stutman et al has an intrinsic limitation (the tilt angle) which our
-approach does not have. Exactly this issue prevents the method of Stutman to
-achieve sufficiently high-aspect ratio \emph{and} curved profiles at the same time, something that our method easily can.
-The problem mentioned on the contrast below the soldering points can be explained by beam-hardening in the absorption image.
-We would amend the manuscript accordingly, providing more information as requested.
+The reason for our appeal was triggered by the motivations raised by the reviewers
+against our work, which we found not fully correct and, in some cases, even too
+simplistic or simply wrong.
 
-Referee two is skeptical about the visibility achieved in our experiment
-compared with the work from Pfeiffer's group. He/she might not have noticed
-that our data have been obtained on a commercially available X-ray tube,
-while the cited experiment of Pfeiffer's et al. has been carried out at a
-third generation synchrotron source, where notably unsurpassed beam
-conditions can be created which are far from what one can expect in real
-life (i.e. with conventional X-ray tubes). And, even if one would like to
-still carry out this (unfair) comparison, we should mention that our
-experiment is the \emph{first} measurement of its kind with the first generation of gratings made according to our innovative design.
-Pfeiffer's team uses gratings obtained after almost a decade of development and, despite this and the use of a synchrotron, they are not much further than us and still carry the intrinsic limitation of a limited grating height.
-We are perfectly aware that the quality of our images has still to be improved, but here we are presenting the first experiments with edge-on grating illumination: we describe its great potential but also mention its (temporary) limitations.
-The same reviewer also complains about the limited field-of-view our method is supposed to have.
-This is actually wrong, since the horizontal field-of-view is just limited by the size of the wafer (as for other methods) while the vertical field-of-view is covered by a vertical scan of the sample, i.e.
-not limited at all, and, even more important, it becomes very interesting when CT applications are considered (all modern CT systems combine a line (or few lines) detector with a patient translation).
-Reviewer 2 finally admits that in comparison with a coded-aperture based experiment at 100 kVp our images (taken at 160 kVp) are better, which we of course appreciate.
-We believe that novelty in the approach must be the driving factor in judging the suitability of our work for this journal and not the present limitations of the technology (which can be solved!), as reviewer 2 seems to conclude.
+Referee one would actually welcome a revised manuscript, which would address his/her
+comments and is not advising a rejection a priori. The mentioned work of Stutman et al.
+has an intrinsic limitation (the tilt angle) which our approach does not have. Exactly this
+issue prevents the method of Stutman to achieve sufficiently high-aspect ratio and curved
+profiles at the same time, something that our method easily can. The problem mentioned
+on the contrast below the soldering points can be explained by beam-hardening in the
+absorption image. We have amended the manuscript accordingly, providing more
+information as requested.
 
-In our opinion, referee three weighed the technicalities and related
-limitations of our experiment too much, without considering the innovative
-solution that we are introducing. As mentioned above, we are perfectly aware
-of the constraints of the present system but here we are showing the
-feasibility of a novel approach, which of course needs to be optimized to
-reach a broader usage. He/she mentions, as comparison, an ABI experiment
-performed at the tungsten 60 keV $K_\alpha$ line.
-We appreciate this hint and will be happy to integrate it in our revised discussion but we would like to already point our that our experiment was carried out at 160 kVp, with a nominal energy around 100 keV.
-This is significantly higher than 60 keV.
-We are not aware of any ABI setup operated at 100 keV on a conventional X-ray source, so the comparison does not sounds very fair either.
+Referee two is skeptical about the visibility achieved in our experiment compared with
+the work from Pfeiffer's group. He/she might not have noticed that our data have been
+obtained on a commercially available X-ray tube, while the cited experiment of Pfeiffer's
+et al. has been carried out at a third generation synchrotron source, where notably
+unsurpassed beam conditions can be created which are far from what one can expect in
+real life (i.e. with conventional X-ray tubes). And, even if one would like to still carry out
+this (unfair) comparison, we should mention that our experiment is the first measurement
+of its kind with the first generation of gratings made according to our innovative design.
+Pfeiffer's team uses gratings obtained after almost a decade of development and, despite
+this and the use of a synchrotron, they are not really further than us while they still carry
+the intrinsic limitation of a limited grating height. We are well aware that the quality of
+our images has still to be improved, but here we are presenting the first experiments with
+edge-on grating illumination: we describe its great potential but also mention its
+(temporary) limitations. The same reviewer also complains about the limited field of
+view (FOV) our method is supposed to have. This is actually wrong, since the horizontal
+FOV is just limited by the size of the wafer (as for other methods) while the vertical FOV
+is covered by a vertical scan of the sample, i.e. not limited at all, and, even more
+important, it becomes very interesting when CT applications are considered (all modern
+CT systems combine a line (or few lines) detector with a patient translation). Reviewer 2
+finally admits that in comparison with a coded-aperture based experiment at 100 kVp our
+images (taken at 160 kVp) are better, which we of course appreciate. We believe that
+novelty in the approach must be the driving factor in judging the suitability of our work
+for this journal and not the present limitations of the technology (which can be solved!),
+as reviewer 2 seems to conclude.
 
-For the above mentioned reasons, we are gently asking you to reconsider our manuscript and to give us a chance to resubmit a revised version.
+In our opinion, referee three weighed the technicalities and related limitations of our
+experiment too much, without considering the innovative solution that we are
+introducing. As mentioned above, we are perfectly aware of the constraints of the present
+system but here we are showing the feasibility of a novel approach, which of course
+needs to be optimized to reach a broader usage. He/she mentions, as comparison, an ABI
+experiment performed at the tungsten 60 keV $K_\alpha$ line. We appreciate this hint and
+will be happy to integrate it in our revised discussion but we would like to already point
+out that our experiment was carried out at 160 kVp, with a nominal energy around 100
+keV. This is significantly higher than 60 keV. We are not aware of any ABI setup
+operated at 100 keV on a conventional X-ray source, so the comparison does not sound
+very fair either.
+
+Finally, we would like to highlight the pioneering character of our work. All the gratingsbased
+X-ray phase contrast papers published in the past decade report on experiments
+carried out in the face-on-configuration or light modifications of such. We are the first
+team demonstrating that an edge-on approach can be successfully implemented and we
+clearly describe the advantages of this novel approach compared to the status quo. We are
+firmly convinced that the potential of our method is huge, since it can solve all the open
+issues (high-energy imaging, no intrinsic aspect ratio limitation in beam-direction,
+acceptance of spherical wave profile, scanning and spiral-CT compatible geometry just to
+cite a few) which have been preventing gratings-interferometry to establish itself on
+commercial, table-top X-ray systems so far.
+
+For the above-mentioned reasons, we are kindly asking you to consider our improved,
+revised manuscript for publication in Nature Communications.
 

### 2013-10-31 hedpc_natphys.tex
nature -> contrast

@@
 lower contrast reduction of the soldering points underneath the resistors in the
-phase image of the chip. This result shows the benefit of the phase nature in
+phase image of the chip. This result shows the benefit of the phase contrast in
 high-energy X-ray imaging, which may be useful to identify flaws in multilayered

### 2013-11-28 hedpc.tex
updated makefile

--- 2013-10-31 hedpc_natphys.tex
@@
-%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
-%% for review and submission
-%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}
-% for double-spaced preprint
-%\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}
-%for review and submission
-\documentclass[aps,prl,preprint,english]{revtex4-1} 
-% for double-spaced preprint
-%\documentclass[aip,apl,amsmath,amssymb,floatfix,preprint,a4paper]{revtex4-1}
-%\documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}
+\documentclass{pnastwo}
 
@@
 \usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc} %Umlaute
-\usepackage{babel}
-\usepackage{acronym}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage[bf,small,labelsep=period]{caption}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage{amssymb,amsfonts,amsmath}
 \usepackage{graphicx}  %figures
 \usepackage[detect-all]{siunitx}
-
-\addto\captionsenglish{\renewcommand{\figurename}{Figure}}
+%\usepackage{pnastwof}
+
 %% New commands
@@
 
-%acronyms
-\acrodef{CT}{computed tomography}
-\acrodef{SNR}{signal-to-noise ratio}
-\acrodef{CNR}{contrast-to-noise ratio}
-\acrodef{SEM}{scanning electron microscope}
-%% ----------------------------------------------------------------------------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Don't type in anything in the following section:
+%%%%%%%%%%%%
+%% For PNAS Only:
+\contributor{Submitted to Proceedings
+of the National Academy of Sciences of the United States of America}
+\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
+\copyrightyear{2008}
+\issuedate{Issue Date}
+\volume{Volume}
+\issuenumber{Issue Number}
+%%%%%%%%%%%%
 
@@
 
-\author{T.~Thüring}
-\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
-\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
-\author{M.~Abis}
-\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
-\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
+\author{T.~Thüring
+\affil{1}{Paul Scherrer Institute, 5232 Villigen, Switzerland}
+\affil{2}{Institute for Biomedical Engineering, Swiss Federal
+Institute of Technology,
+Gloriastrasse 35
+8092 Zurich, Switzerland}}
+\author{M.~Abis
+\affil{1}{}
+\affil{2}{}}
 \author{Z.~Wang}
-\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
+\affil{1}{}
 \author{C.~David}
-\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
-\author{M.~Stampanoni}
-\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
-\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
-
-\date{\today}
-
-%% ----------------------------------------------------------------------------------------------------------------
+\affil{1}{}
+\author{M.~Stampanoni
+\affil{1}{}
+\affil{2}{}}
+
+\author{}
+
+\contributor{Submitted to Proceedings of the National Academy of Sciences
+of the United States of America}
+
+%% The \maketitle command is necessary to build the title page.
+\maketitle
+
+\begin{article}
+
 \begin{abstract}
@@
 \end{abstract}
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Body of manuscript
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-X-ray radiography and \ac{CT} are standard imaging techniques in
+
+%% When adding keywords, separate each term with a straight line: |
+\keywords{X-ray phase contrast | grating interferometry | X-ray interferometry}
+
+%% Optional for entering abbreviations, separate the abbreviation from
+%% its definition with a comma, separate each pair with a semicolon:
+%% for example:
+%% \abbreviations{SAM, self-assembled monolayer; OTS,
+%% octadecyltrichlorosilane}
+
+\abbreviations{
+%acronyms
+CT,computed tomography;
+SNR,signal-to-noise ratio;
+CNR,contrast-to-noise ratio;
+SEM,scanning electron microscope;
+}
+%% ----------------------------------------------------------------------------------------------------------------
+%% The first letter of the article should be drop cap: \dropcap{}
+%\dropcap{I}n this article we study the evolution of ''almost-sharp'' fronts
+
+\section{Significance statement}
+Phase sensitive X-ray imaging provides access to additional information
+on the investigated samples with respect to the conventional absorption
+radiography and tomography.
+
+Here we show a grating interferometer with a new design of the optical
+elements that enables a large field of view and an efficient imaging at
+a target energy of~\SI{100}{\kilo\eV} on a conventional tube.
+
+Our results demonstrate that phase contrast can be achieved at these
+energies, which are relevant for many applications, ranging from medical
+diagnostics to nondestructive testing or homeland security.
+
+\section{}
+\dropcap{X}-ray radiography and CT are standard imaging techniques in
 materials and life sciences for the nondestructive examination of samples or
@@
 An enhanced
-\ac{CNR} in images compared to attenuation for certain
+CNR in images compared to attenuation for certain
 materials or tissues~\cite{Pfeiffer2007a,McDonald2009} has also been
@@
 synchrotron source at nominal energies of
-$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013} and 
-$\SI{123}{\kilo\electronvolt}$~\cite{Ruiz2013}.
+$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013}.
 Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
@@
 energies: chest or abdominal
-radiography or \ac{CT} require an acceleration voltage between \num{100} and
+radiography or CT require an acceleration voltage between \num{100} and
 $\SI{150}{\kilo\voltpeak}$. Other potential applications are homeland
@@
 aspect ratios.
-\begin{figure}[ht]
-    \includegraphics[width=.7\textwidth]{figures/figure1.eps}
-    \caption{Schematic of a grating
-        interferometer for X-ray energies between 60 and
-        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
-        aspect ratio is defined by the ratio of the travelling distance along the
-        grating lines and the period and can be arbitrarily long. In order to maximise
-        the field of view, the grating structures are aligned on an
-    arc.}
-    \label{Fig:schematic}
-\end{figure}
 
@@
 Similarly, for tomographic images,
-the approach allows single slice \ac{CT} or full 3D imaging in scanning mode.
+the approach allows single slice CT or full 3D imaging in scanning mode.
 
@@
 with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
-\begin{figure} [ht]
-    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
-    \caption{Grating design mask for
-        the edge-on illumination approach and \ac{SEM}
-        image of the grating. The top part of the 4 inch wafer shows
-        five grating chips. The
-        gratings have different curvatures which are specific to the grating
-        interferometer geometry. 
-        The \ac{SEM} image shows the gold structures and the interrupting bridges
-        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}
-        \label{Fig:grating_mask}
-\end{figure}
 
@@
 
+\section{Results and discussion}
 Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
@@
 structures such as electronic chips.
-\begin{figure}[ht]
-    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
-    \caption{Radiographic scan of an electronic chip. The image was acquired
-        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
-    step. The top right image shows the differential absorption image.}
-    \label{Fig:img_chip}
-\end{figure}
 
@@
 
-\section*{Methods}
+%% == end of paper:
+
+%% Optional Materials and Methods Section
+%% The Materials and Methods section header will be added automatically.
+
+%% Enter any subheads and the Materials and Methods text below.
+\begin{materials}
 Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
@@
 gratings (\SI{5}{\percent}). The exposure time was chosen in order to
-get a low noise in the differential phase image. The \ac{SNR} is
+get a low noise in the differential phase image. The SNR is
 proportional to the visibility and the square root of the exposure
@@
 fabrication becomes more reliable and uniform.
-
-\section*{Acknowledgements}
+\end{materials}
+
+%% Optional Appendix or Appendices
+%% \appendix Appendix text...
+%% or, for appendix with title, use square brackets:
+%% \appendix[Appendix Title]
+
+\begin{acknowledgments}
 We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
 Scherrer Institute (PSI), Switzerland, for the
-work on the mechanical design, the scientific advice, and the \ac{SEM} images
+work on the mechanical design, the scientific advice, and the SEM images
 respectively, Joachim Schulz and Marco Walter from
@@
 (CCMX) of the ETH Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.
-
-\bibliographystyle{apsrev4-1}
+\end{acknowledgments}
+
+%% PNAS does not support submission of supporting .tex files such as BibTeX.
+%% Instead all references must be included in the article .tex document. 
+%% If you currently use BibTeX, your bibliography is formed because the 
+%% command \verb+\bibliography{}+ brings the <filename>.bbl file into your
+%% .tex document. To conform to PNAS requirements, copy the reference listings
+%% from your .bbl file and add them to the article .tex file, using the
+%% bibliography environment described above.
+
+%%  Contact pnas@nas.edu if you need assistance with your
+%%  bibliography.
+
+% Sample bibliography item in PNAS format:
+%% \bibitem{in-text reference} comma-separated author names up to 5,
+%% for more than 5 authors use first author last name et al. (year published)
+%% article title  {\it Journal Name} volume #: start page-end page.
+%% ie,
+% \bibitem{Neuhaus} Neuhaus J-M, Sitcher L, Meins F, Jr, Boller T (1991) 
+% A short C-terminal sequence is necessary and sufficient for the
+% targeting of chitinases to the plant vacuole. 
+% {\it Proc Natl Acad Sci USA} 88:10362-10366.
+
+%% Enter the largest bibliography number in the facing curly brackets
+%% following \begin{thebibliography}
+
+%\bibliographystyle{pnas}
 %\bibliography{library}
-
-%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
-%Control: key (0)
-%Control: author (72) initials jnrlst
-%Control: editor formatted (1) identically to author
-%Control: production of article title (-1) disabled
-%Control: page (0) single
-%Control: year (1) truncated
-%Control: production of eprint (0) enabled
-\begin{thebibliography}{33}%
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{http://dx.doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-%</preamble>
-\bibitem [{\citenamefont {Als-Nielsen}\ and\ \citenamefont
-  {McMorrow}(2011)}]{Als-Nielsen2011}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Als-Nielsen}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {McMorrow}},\ }\href
-  {http://books.google.com/books?hl=en\&lr=\&id=rlqlboWlTRMC\&oi=fnd\&pg=PA29\&dq=Elements+of+Modern+X-ray+Physics\&ots=P2D3XwrDgd\&sig=b3iO97q1hfsT8TkTYKxsvUbFink}
-  {\emph {\bibinfo {title} {{Elements of modern X-ray physics}}}}\ (\bibinfo
-  {year} {2011})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Qi}\ \emph {et~al.}(2010)\citenamefont {Qi},
-  \citenamefont {Zambelli}, \citenamefont {Bevins},\ and\ \citenamefont
-  {Chen}}]{Qi2010}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
-  {Qi}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zambelli}},
-  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Bevins}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {G.-H.}\ \bibnamefont {Chen}},\ }\href {\doibase
-  10.1088/0031-9155/55/9/016} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physics in medicine and biology}\ }\textbf {\bibinfo {volume} {55}},\
-  \bibinfo {pages} {2669} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2007)\citenamefont
-  {Pfeiffer}, \citenamefont {Bunk}, \citenamefont {David}, \citenamefont
-  {Bech}, \citenamefont {{Le Duc}}, \citenamefont {Bravin},\ and\ \citenamefont
-  {Cloetens}}]{Pfeiffer2007a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {David}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Bech}}, \bibinfo {author}
-  {\bibfnamefont {G.}~\bibnamefont {{Le Duc}}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Bravin}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Cloetens}},\ }\href {\doibase
-  10.1088/0031-9155/52/23/010} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physics in medicine and biology}\ }\textbf {\bibinfo {volume} {52}},\
-  \bibinfo {pages} {6923} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {McDonald}\ \emph {et~al.}(2009)\citenamefont
-  {McDonald}, \citenamefont {Marone}, \citenamefont {Hintermuller},
-  \citenamefont {Mikuljan}, \citenamefont {David}, \citenamefont {Pfeiffer},
-  \citenamefont {Stampanoni},\ and\ \citenamefont
-  {Hinterm\"{u}ller}}]{McDonald2009}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-  {McDonald}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Marone}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Hintermuller}}, \bibinfo
-  {author} {\bibfnamefont {G.}~\bibnamefont {Mikuljan}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {David}}, \bibinfo {author} {\bibfnamefont
-  {F.}~\bibnamefont {Pfeiffer}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Stampanoni}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {C.}~\bibnamefont {Hinterm\"{u}ller}},\ }\href {\doibase
-  10.1107/S0909049509017920} {\bibfield  {journal} {\bibinfo  {journal}
-  {Journal of Synchrotron Radiation}\ }\textbf {\bibinfo {volume} {16}},\
-  \bibinfo {pages} {562} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Davis}\ \emph {et~al.}(1995)\citenamefont {Davis},
-  \citenamefont {Gao}, \citenamefont {Gureyev}, \citenamefont {Stevenson},\
-  and\ \citenamefont {Wilkins}}]{Davis1995}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Davis}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Gao}}, \bibinfo
-  {author} {\bibfnamefont {T.}~\bibnamefont {Gureyev}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Stevenson}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Wilkins}},\ }\href
-  {http://imaging.sbes.vt.edu/laboratory/XGI/(1995 Gao).pdf} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {373}},\
-  \bibinfo {pages} {595} (\bibinfo {year} {1995})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Chapman}\ \emph {et~al.}(1997)\citenamefont
-  {Chapman}, \citenamefont {Thomlinson}, \citenamefont {Johnston},
-  \citenamefont {Washburn}, \citenamefont {Pisano}, \citenamefont {Gm\"{u}r},
-  \citenamefont {Zhong}, \citenamefont {Menk}, \citenamefont {Arfelli},\ and\
-  \citenamefont {Sayers}}]{Chapman1997}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Chapman}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Thomlinson}},
-  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Johnston}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Washburn}}, \bibinfo {author}
-  {\bibfnamefont {E.}~\bibnamefont {Pisano}}, \bibinfo {author} {\bibfnamefont
-  {N.}~\bibnamefont {Gm\"{u}r}}, \bibinfo {author} {\bibfnamefont
-  {Z.}~\bibnamefont {Zhong}}, \bibinfo {author} {\bibfnamefont
-  {R.}~\bibnamefont {Menk}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Arfelli}}, \ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Sayers}},\ }\href {\doibase 10.1016/j.carj.2010.04.015} {\bibfield
-  {journal} {\bibinfo  {journal} {Physics in Medicine and Biology}\ }\textbf
-  {\bibinfo {volume} {42}},\ \bibinfo {pages} {2015} (\bibinfo {year}
-  {1997})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bonse}\ and\ \citenamefont {Hart}(1965)}]{Bonse1965}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.}~\bibnamefont
-  {Bonse}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Hart}},\
-  }\href {http://link.aip.org/link/?APPLAB/6/155/1} {\bibfield  {journal}
-  {\bibinfo  {journal} {Applied Physics Letters}\ }\textbf {\bibinfo {volume}
-  {6}},\ \bibinfo {pages} {155} (\bibinfo {year} {1965})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Momose}\ \emph {et~al.}(1996)\citenamefont {Momose},
-  \citenamefont {Takeda}, \citenamefont {Itai},\ and\ \citenamefont
-  {Hirano}}]{Momose1996}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Momose}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Takeda}},
-  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Itai}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {K.}~\bibnamefont {Hirano}},\ }\href
-  {http://imaging.sbes.vt.edu/laboratory/XGI/(1996 Momose).pdf} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Medicine}\ }\textbf {\bibinfo {volume}
-  {2}},\ \bibinfo {pages} {473} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Snigirev}\ \emph {et~al.}(1995)\citenamefont
-  {Snigirev}, \citenamefont {Snigireva}, \citenamefont {Kohn}, \citenamefont
-  {Kuznetsov},\ and\ \citenamefont {Schelokov}}]{Snigirev1995}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Snigirev}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Snigireva}},
-  \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Kohn}}, \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Kuznetsov}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {I.}~\bibnamefont {Schelokov}},\ }\href
-  {http://kohnvict.narod.ru/articles/091.pdf} {\bibfield  {journal} {\bibinfo
-  {journal} {Review of Scientific Instruments}\ }\textbf {\bibinfo {volume}
-  {66}},\ \bibinfo {pages} {5486} (\bibinfo {year} {1995})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Wilkins}\ \emph {et~al.}(1996)\citenamefont
-  {Wilkins}, \citenamefont {Gureyev}, \citenamefont {Gao}, \citenamefont
-  {Pogany},\ and\ \citenamefont {Stevenson}}]{Wilkins1996}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Wilkins}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Gureyev}},
-  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Gao}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Pogany}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Stevenson}},\ }\href
-  {http://fisica.ufpr.br/lorxi/Rcf2/artigos/Wilkins.pdf} {\bibfield  {journal}
-  {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {384}},\ \bibinfo
-  {pages} {335} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cloetens}\ \emph {et~al.}(1996)\citenamefont
-  {Cloetens}, \citenamefont {Barrett}, \citenamefont {Baruchel}, \citenamefont
-  {Guigay},\ and\ \citenamefont {Schlenker}}]{Cloetens1996}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Cloetens}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Barrett}},
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Baruchel}}, \bibinfo
-  {author} {\bibfnamefont {J.}~\bibnamefont {Guigay}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Schlenker}},\ }\href
-  {http://iopscience.iop.org/0022-3727/29/1/023} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of Physics D: Applied Physics}\ }\textbf
-  {\bibinfo {volume} {29}},\ \bibinfo {pages} {133} (\bibinfo {year}
-  {1996})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cloetens}\ \emph {et~al.}(1997)\citenamefont
-  {Cloetens}, \citenamefont {Guigay}, \citenamefont {{De Martino}},
-  \citenamefont {Baruchel},\ and\ \citenamefont {Schlenker}}]{Cloetens1997}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Cloetens}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Guigay}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {{De Martino}}}, \bibinfo
-  {author} {\bibfnamefont {J.}~\bibnamefont {Baruchel}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Schlenker}},\ }\href
-  {http://www.ncbi.nlm.nih.gov/pubmed/18185750} {\bibfield  {journal} {\bibinfo
-   {journal} {Optics letters}\ }\textbf {\bibinfo {volume} {22}},\ \bibinfo
-  {pages} {1059} (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {David}\ \emph {et~al.}(2002)\citenamefont {David},
-  \citenamefont {N\"{o}hammer}, \citenamefont {Solak},\ and\ \citenamefont
-  {Ziegler}}]{David2002}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {David}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {N\"{o}hammer}},
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Solak}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {E.}~\bibnamefont {Ziegler}},\ }\href {\doibase
-  10.1063/1.1516611} {\bibfield  {journal} {\bibinfo  {journal} {Applied
-  Physics Letters}\ }\textbf {\bibinfo {volume} {81}},\ \bibinfo {pages} {3287}
-  (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Momose}\ \emph {et~al.}(2003)\citenamefont {Momose},
-  \citenamefont {Kawamoto}, \citenamefont {Koyama}, \citenamefont {Hamaishi},
-  \citenamefont {Takai},\ and\ \citenamefont {Suzuki}}]{Momose2003a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Momose}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Kawamoto}},
-  \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Koyama}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Hamaishi}}, \bibinfo {author}
-  {\bibfnamefont {K.}~\bibnamefont {Takai}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {Y.}~\bibnamefont {Suzuki}},\ }\href {\doibase
-  10.1143/JJAP.42.L866} {\bibfield  {journal} {\bibinfo  {journal} {Japanese
-  Journal of Applied Physics}\ }\textbf {\bibinfo {volume} {42}},\ \bibinfo
-  {pages} {L866} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Munro}\ \emph {et~al.}(2012)\citenamefont {Munro},
-  \citenamefont {Ignatyev}, \citenamefont {Speller},\ and\ \citenamefont
-  {Olivo}}]{Munro2012}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Munro}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Ignatyev}},
-  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Speller}}, \ and\
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Olivo}},\ }\href
-  {\doibase 10.1073/pnas.1205396109} {\bibfield  {journal} {\bibinfo  {journal}
-  {Proceedings of the National Academy of Sciences}\ }\textbf {\bibinfo
-  {volume} {2012}},\ \bibinfo {pages} {2} (\bibinfo {year} {2012})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2006)\citenamefont
-  {Pfeiffer}, \citenamefont {Weitkamp}, \citenamefont {Bunk},\ and\
-  \citenamefont {David}}]{Pfeiffer2006}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Weitkamp}},
-  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {C.}~\bibnamefont {David}},\ }\href {\doibase
-  10.1038/nphys265} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  Physics}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {258} (\bibinfo
-  {year} {2006})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Nesch}\ \emph {et~al.}(2009)\citenamefont {Nesch},
-  \citenamefont {Fogarty}, \citenamefont {Tzvetkov}, \citenamefont {Reinhart},
-  \citenamefont {Walus}, \citenamefont {Khelashvili}, \citenamefont
-  {Muehleman},\ and\ \citenamefont {Chapman}}]{Nesch2009}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-  {Nesch}}, \bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont {Fogarty}},
-  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Tzvetkov}}, \bibinfo
-  {author} {\bibfnamefont {B.}~\bibnamefont {Reinhart}}, \bibinfo {author}
-  {\bibfnamefont {a.~C.}\ \bibnamefont {Walus}}, \bibinfo {author}
-  {\bibfnamefont {G.}~\bibnamefont {Khelashvili}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {Muehleman}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {Chapman}},\ }\href {\doibase
-  10.1063/1.3213621} {\bibfield  {journal} {\bibinfo  {journal} {The Review of
-  scientific instruments}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages}
-  {093702} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Parham}\ \emph {et~al.}(2009)\citenamefont {Parham},
-  \citenamefont {Zhong}, \citenamefont {Connor}, \citenamefont {Chapman},\ and\
-  \citenamefont {Pisano}}]{Parham2009}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Parham}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Zhong}},
-  \bibinfo {author} {\bibfnamefont {D.~M.}\ \bibnamefont {Connor}}, \bibinfo
-  {author} {\bibfnamefont {L.~D.}\ \bibnamefont {Chapman}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {E.~D.}\ \bibnamefont {Pisano}},\ }\href
-  {http://linkinghub.elsevier.com/retrieve/pii/S1076633209001366?showall=true}
-  {\enquote {\bibinfo {title} {{Design and Implementation of a Compact Low-Dose
-  Diffraction Enhanced Medical Imaging System}},}\ } (\bibinfo {year}
-  {2009})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2008)\citenamefont
-  {Pfeiffer}, \citenamefont {Bech}, \citenamefont {Bunk}, \citenamefont
-  {Kraft}, \citenamefont {Eikenberry}, \citenamefont {Br\"{o}nnimann},
-  \citenamefont {Gr\"{u}nzweig},\ and\ \citenamefont {David}}]{Pfeiffer2008}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bech}},
-  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Kraft}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Eikenberry}}, \bibinfo {author} {\bibfnamefont
-  {C.}~\bibnamefont {Br\"{o}nnimann}}, \bibinfo {author} {\bibfnamefont
-  {C.}~\bibnamefont {Gr\"{u}nzweig}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {C.}~\bibnamefont {David}},\ }\href {\doibase 10.1038/nmat2096} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Materials}\ }\textbf {\bibinfo
-  {volume} {7}},\ \bibinfo {pages} {134} (\bibinfo {year} {2008})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Willner}\ \emph {et~al.}(2013)\citenamefont
-  {Willner}, \citenamefont {Bech}, \citenamefont {Herzen}, \citenamefont
-  {Zanette}, \citenamefont {Hahn}, \citenamefont {Kenntner}, \citenamefont
-  {Mohr}, \citenamefont {Rack}, \citenamefont {Weitkamp},\ and\ \citenamefont
-  {Pfeiffer}}]{Willner2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Willner}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bech}},
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Herzen}}, \bibinfo
-  {author} {\bibfnamefont {I.}~\bibnamefont {Zanette}}, \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {Hahn}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Kenntner}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Mohr}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Rack}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Weitkamp}}, \
-  and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Pfeiffer}},\ }\href
-  {http://www.ncbi.nlm.nih.gov/pubmed/23481949} {\bibfield  {journal} {\bibinfo
-   {journal} {Optics express}\ }\textbf {\bibinfo {volume} {21}},\ \bibinfo
-  {pages} {4155} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ruiz}\ \emph {et~al.}(2013)\citenamefont {Ruiz},
-  \citenamefont {Zanette}, \citenamefont {Chabior}, \citenamefont {Scherer},
-  \citenamefont {Mohr}, \citenamefont {Walter}, \citenamefont {Weitkamp},
-  \citenamefont {Rack},\ and\ \citenamefont {Pfeiffer}}]{Ruiz2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Ruiz}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Zanette}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Chabior}}, \bibinfo
-  {author} {\bibfnamefont {K.}~\bibnamefont {Scherer}}, \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Mohr}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Walter}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Weitkamp}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Rack}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {F.}~\bibnamefont {Pfeiffer}},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Poster, 2nd International Symposium on BioMedical
-  Applications of X-ray Phase Contrast Imaging, Germany, 24/25th January 2013}\
-  } (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Donath}\ \emph {et~al.}(2009)\citenamefont {Donath},
-  \citenamefont {Chabior}, \citenamefont {Pfeiffer}, \citenamefont {Bunk},
-  \citenamefont {Reznikova}, \citenamefont {Mohr}, \citenamefont {Hempel},
-  \citenamefont {Popescu}, \citenamefont {Hoheisel}, \citenamefont {Schuster},
-  \citenamefont {Baumann},\ and\ \citenamefont {David}}]{Donath2009}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Donath}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Chabior}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Pfeiffer}}, \bibinfo
-  {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \bibinfo {author}
-  {\bibfnamefont {E.}~\bibnamefont {Reznikova}}, \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Mohr}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Hempel}}, \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {Popescu}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Hoheisel}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Schuster}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Baumann}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {C.}~\bibnamefont {David}},\ }\href {\doibase 10.1063/1.3208052} {\bibfield
-  {journal} {\bibinfo  {journal} {Journal of Applied Physics}\ }\textbf
-  {\bibinfo {volume} {106}},\ \bibinfo {pages} {054703} (\bibinfo {year}
-  {2009})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mohr}\ \emph {et~al.}(2012)\citenamefont {Mohr},
-  \citenamefont {Grund}, \citenamefont {Kunka}, \citenamefont {Kenntner},
-  \citenamefont {Leuthold}, \citenamefont {Meiser}, \citenamefont {Schulz},\
-  and\ \citenamefont {Walter}}]{Mohr2012}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Mohr}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Grund}},
-  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Kunka}}, \bibinfo
-  {author} {\bibfnamefont {J.}~\bibnamefont {Kenntner}}, \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Leuthold}}, \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Meiser}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Schulz}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Walter}},\ }\href {\doibase 10.1063/1.4742267} {\ \textbf
-  {\bibinfo {volume} {41}},\ \bibinfo {pages} {41} (\bibinfo {year}
-  {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {David}\ \emph {et~al.}(2007)\citenamefont {David},
-  \citenamefont {Bruder}, \citenamefont {Rohbeck}, \citenamefont
-  {Gr\"{u}nzweig}, \citenamefont {Kottler}, \citenamefont {Diaz}, \citenamefont
-  {Bunk},\ and\ \citenamefont {Pfeiffer}}]{David2007}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {David}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Bruder}},
-  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Rohbeck}}, \bibinfo
-  {author} {\bibfnamefont {C.}~\bibnamefont {Gr\"{u}nzweig}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {Kottler}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Diaz}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-  {Bunk}}, \ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Pfeiffer}},\ }\href {\doibase 10.1016/j.mee.2007.01.151} {\bibfield
-  {journal} {\bibinfo  {journal} {Microelectronic Engineering}\ }\textbf
-  {\bibinfo {volume} {84}},\ \bibinfo {pages} {1172} (\bibinfo {year}
-  {2007})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kenntner}\ \emph {et~al.}(2010)\citenamefont
-  {Kenntner}, \citenamefont {Grund}, \citenamefont {Matthis}, \citenamefont
-  {Boerner}, \citenamefont {Mohr}, \citenamefont {Scherer}, \citenamefont
-  {Walter}, \citenamefont {Willner}, \citenamefont {Tapfer}, \citenamefont
-  {Bech}, \citenamefont {Pfeiffer}, \citenamefont {Zanette},\ and\
-  \citenamefont {Weitkamp}}]{Kenntner2010}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Kenntner}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Grund}},
-  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Matthis}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Boerner}}, \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Mohr}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Scherer}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Walter}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Willner}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Tapfer}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Bech}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Zanette}}, \
-  and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Weitkamp}},\ }in\
-  \href@noop {} {\emph {\bibinfo {booktitle} {Proceedings of SPIE}}},\ Vol.\
-  \bibinfo {volume} {7804}\ (\bibinfo {year} {2010})\ p.\ \bibinfo {pages}
-  {780408}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Stutman}\ and\ \citenamefont
-  {Finkenthal}(2012)}]{Stutman2012a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Stutman}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Finkenthal}},\ }\href {\doibase 10.1063/1.4748882} {\bibfield  {journal}
-  {\bibinfo  {journal} {Applied physics letters}\ }\textbf {\bibinfo {volume}
-  {101}},\ \bibinfo {pages} {91108} (\bibinfo {year} {2012})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {{\AA slund, M}}(2007)}]{Aslund2007}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibnamefont {{\AA slund, M}}},\
-  }\emph {\bibinfo {title} {{Digital Mammography with a Photon Counting
-  Detector in a Scanned Multislit Geometry}}},\ \href@noop {} {Ph.D. thesis}
-  (\bibinfo {year} {2007})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Oduko}\ \emph {et~al.}(2010)\citenamefont {Oduko},
-  \citenamefont {Young},\ and\ \citenamefont {Burch}}]{Oduko2010}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Oduko}}, \bibinfo {author} {\bibfnamefont {K.~C.}\ \bibnamefont {Young}}, \
-  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Burch}},\ }in\ \href
-  {\doibase 10.1007/978-3-642-13666-5_49} {\emph {\bibinfo {booktitle} {Digital
-  Mammography}}},\ \bibinfo {series} {Lecture Notes in Computer Science}, Vol.\
-  \bibinfo {volume} {6136},\ \bibinfo {editor} {edited by\ \bibinfo {editor}
-  {\bibfnamefont {J.}~\bibnamefont {Martí}}, \bibinfo {editor} {\bibfnamefont
-  {A.}~\bibnamefont {Oliver}}, \bibinfo {editor} {\bibfnamefont
-  {J.}~\bibnamefont {Freixenet}}, \ and\ \bibinfo {editor} {\bibfnamefont
-  {R.}~\bibnamefont {Martí}}}\ (\bibinfo  {publisher} {Springer Berlin
-  Heidelberg},\ \bibinfo {year} {2010})\ pp.\ \bibinfo {pages}
-  {365--370}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Weitkamp}\ \emph {et~al.}(2005)\citenamefont
-  {Weitkamp}, \citenamefont {Diaz}, \citenamefont {David}, \citenamefont
-  {Pfeiffer}, \citenamefont {Stampanoni}, \citenamefont {Cloetens},\ and\
-  \citenamefont {Ziegler}}]{Weitkamp2005}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Weitkamp}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Diaz}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {David}}, \bibinfo
-  {author} {\bibfnamefont {F.}~\bibnamefont {Pfeiffer}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Stampanoni}}, \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Cloetens}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {E.}~\bibnamefont {Ziegler}},\ }\href {\doibase
-  10.1364/OPEX.13.006296} {\bibfield  {journal} {\bibinfo  {journal} {Optics
-  Express}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages} {6296}
-  (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Thuering}\ \emph {et~al.}(2013)\citenamefont
-  {Thuering}, \citenamefont {Barber}, \citenamefont {Seo}, \citenamefont
-  {Alhassen}, \citenamefont {Iwanczyk},\ and\ \citenamefont
-  {Stampanoni}}]{Thuering2013c}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Thuering}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Barber}},
-  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Seo}}, \bibinfo {author}
-  {\bibfnamefont {F.}~\bibnamefont {Alhassen}}, \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Iwanczyk}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Stampanoni}},\ }\href {\doibase
-  10.1063/1.4805073} {\bibfield  {journal} {\bibinfo  {journal} {Applied
-  Physics Letters}\ }\textbf {\bibinfo {volume} {102}},\ \bibinfo {pages}
-  {191113} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Chabior}\ \emph {et~al.}(2011)\citenamefont
-  {Chabior}, \citenamefont {Donath}, \citenamefont {David}, \citenamefont
-  {Bunk}, \citenamefont {Schuster}, \citenamefont {Schroer},\ and\
-  \citenamefont {Pfeiffer}}]{Chabior2011a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Chabior}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Donath}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {David}}, \bibinfo
-  {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Schuster}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {Schroer}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {F.}~\bibnamefont {Pfeiffer}},\ }\href {\doibase
-  10.1118/1.3553408} {\bibfield  {journal} {\bibinfo  {journal} {Medical
-  Physics}\ }\textbf {\bibinfo {volume} {38}},\ \bibinfo {pages} {1189}
-  (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gr\"{u}nzweig}\ \emph {et~al.}(2008)\citenamefont
-  {Gr\"{u}nzweig}, \citenamefont {Pfeiffer}, \citenamefont {Bunk},
-  \citenamefont {Donath}, \citenamefont {K\"{u}hne}, \citenamefont {Frei},
-  \citenamefont {Dierolf},\ and\ \citenamefont {David}}]{Grunzweig2008}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Gr\"{u}nzweig}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}},
-  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Donath}}, \bibinfo
-  {author} {\bibfnamefont {G.}~\bibnamefont {K\"{u}hne}}, \bibinfo {author}
-  {\bibfnamefont {G.}~\bibnamefont {Frei}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Dierolf}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {C.}~\bibnamefont {David}},\ }\href {\doibase 10.1063/1.2930866} {\bibfield
-  {journal} {\bibinfo  {journal} {The Review of scientific instruments}\
-  }\textbf {\bibinfo {volume} {79}},\ \bibinfo {pages} {053703} (\bibinfo
-  {year} {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Raupach}\ and\ \citenamefont
-  {Flohr}(2011)}]{Raupach2011}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Raupach}}\ and\ \bibinfo {author} {\bibfnamefont {T.~G.}\ \bibnamefont
-  {Flohr}},\ }\href {\doibase 10.1088/0031-9155/56/7/020} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physics in medicine and biology}\ }\textbf {\bibinfo
-  {volume} {56}},\ \bibinfo {pages} {2219} (\bibinfo {year}
-  {2011})}\BibitemShut {NoStop}%
-\end{thebibliography}%
+\begin{thebibliography}{10}
+
+\bibitem{Als-Nielsen2011}
+Als-Nielsen J, McMorrow D (2011) {\em {Elements of modern X-ray physics}}.
+
+\bibitem{Qi2010}
+Qi Z, Zambelli J, Bevins N, Chen GH (2010) {Quantitative imaging of electron
+  density and effective atomic number using phase contrast CT.}
+\newblock {\em Physics in medicine and biology} 55:2669--77.
+
+\bibitem{Pfeiffer2007a}
+Pfeiffer F et~al. (2007) {High-resolution brain tumor visualization using
+  three-dimensional x-ray phase contrast tomography.}
+\newblock {\em Physics in medicine and biology} 52:6923--6930.
+
+\bibitem{McDonald2009}
+McDonald SA et~al. (2009) {Advanced phase-contrast imaging using a grating
+  interferometer}.
+\newblock {\em Journal of Synchrotron Radiation} 16:562--572.
+
+\bibitem{Davis1995}
+Davis T, Gao D, Gureyev T, Stevenson A, Wilkins S (1995) {Phase-contrast
+  imaging of weakly absorbing materials using hard X-rays}.
+\newblock {\em Nature} 373:595--598.
+
+\bibitem{Chapman1997}
+Chapman D et~al. (1997) {Diffraction enhanced x-ray imaging}.
+\newblock {\em Physics in Medicine and Biology} 42:2015--2025.
+
+\bibitem{Bonse1965}
+Bonse U, Hart M (1965) {An x-ray interferometer}.
+\newblock {\em Applied Physics Letters} 6:155--156.
+
+\bibitem{Momose1996}
+Momose A, Takeda T, Itai Y, Hirano K (1996) {Phase-contrast X-ray computed
+  tomography for observing biological soft tissues}.
+\newblock {\em Nature Medicine} 2:473--475.
+
+\bibitem{Snigirev1995}
+Snigirev A, Snigireva I, Kohn V, Kuznetsov S, Schelokov I (1995) {On the
+  possibilities of x-ray phase contrast microimaging by coherent high-energy
+  synchrotron radiation}.
+\newblock {\em Review of Scientific Instruments} 66:5486--5492.
+
+\bibitem{Wilkins1996}
+Wilkins S, Gureyev T, Gao D, Pogany A, Stevenson A (1996) {Phase-contrast
+  imaging using polychromatic hard X-rays}.
+\newblock {\em Nature} 384:335--338.
+
+\bibitem{Cloetens1996}
+Cloetens P, Barrett R, Baruchel J, Guigay J, Schlenker M (1996) {Phase objects
+  in synchrotron radiation hard x-ray imaging}.
+\newblock {\em Journal of Physics D: Applied Physics} 29:133--146.
+
+\bibitem{Cloetens1997}
+Cloetens P, Guigay J, {De Martino} C, Baruchel J, Schlenker M (1997)
+  {Fractional Talbot imaging of phase gratings with hard x rays.}
+\newblock {\em Optics letters} 22:1059--61.
+
+\bibitem{David2002}
+David C, N\"{o}hammer B, Solak H, Ziegler E (2002) {Differential x-ray phase
+  contrast imaging using a shearing interferometer}.
+\newblock {\em Applied Physics Letters} 81:3287--3289.
+
+\bibitem{Momose2003a}
+Momose A et~al. (2003) {Demonstration of X-Ray Talbot Interferometry}.
+\newblock {\em Japanese Journal of Applied Physics} 42:L866--L868.
+
+\bibitem{Munro2012}
+Munro P, Ignatyev K, Speller R, Olivo A (2012) {Phase and absorption retrieval
+  using incoherent X-ray sources}.
+\newblock {\em Proceedings of the National Academy of Sciences} 2012:2--7.
+
+\bibitem{Pfeiffer2006}
+Pfeiffer F, Weitkamp T, Bunk O, David C (2006) {Phase retrieval and
+  differential phase-contrast imaging with low-brilliance X-ray sources}.
+\newblock {\em Nature Physics} 2:258--261.
+
+\bibitem{Nesch2009}
+Nesch I et~al. (2009) {The design and application of an in-laboratory
+  diffraction-enhanced x-ray imaging instrument.}
+\newblock {\em The Review of scientific instruments} 80:093702.
+
+\bibitem{Parham2009}
+Parham C, Zhong Z, Connor DM, Chapman LD, Pisano ED (2009) {Design and
+  Implementation of a Compact Low-Dose Diffraction Enhanced Medical Imaging
+  System}.
+
+\bibitem{Pfeiffer2008}
+Pfeiffer F et~al. (2008) {Hard-X-ray dark-field imaging using a grating
+  interferometer}.
+\newblock {\em Nature Materials} 7:134--137.
+
+\bibitem{Willner2013}
+Willner M et~al. (2013) {Quantitative X-ray phase-contrast computed tomography
+  at 82 keV}.
+\newblock {\em Optics express} 21:4155--4166.
+
+\bibitem{Donath2009}
+Donath T et~al. (2009) {Inverse geometry for grating-based x-ray phase-contrast
+  imaging}.
+\newblock {\em Journal of Applied Physics} 106:054703.
+
+\bibitem{Mohr2012}
+Mohr J et~al. (2012) {High aspect ratio gratings for X-ray phase contrast
+  imaging}.
+\newblock 41:41--50.
+
+\bibitem{David2007}
+David C et~al. (2007) {Fabrication of diffraction gratings for hard X-ray phase
+  contrast imaging}.
+\newblock {\em Microelectronic Engineering} 84:1172--1177.
+
+\bibitem{Kenntner2010}
+Kenntner J et~al. (2010) {\em {Front- and backside structuring of gratings for
+  phase contrast imaging with x-ray tubes}}.
+\newblock Vol.{} 7804, p. 780408.
+
+\bibitem{Stutman2012a}
+Stutman D, Finkenthal M (2012) {Glancing angle Talbot-Lau grating
+  interferometers for phase contrast imaging at high x-ray energy}.
+\newblock {\em Applied physics letters} 101:91108.
+
+\bibitem{Aslund2007}
+{\AA slund, M} (2007) Ph.D. thesis.
+
+\bibitem{Oduko2010}
+Oduko JM, Young KC, Burch A (2010) in {\em Digital Mammography}, Lecture Notes
+  in Computer Science, eds.{} Martí J, Oliver A, Freixenet J, Martí R.
+\newblock (Springer Berlin Heidelberg) Vol.{} 6136, pp. 365--370.
+
+\bibitem{Weitkamp2005}
+Weitkamp T et~al. (2005) {X-ray phase imaging with a grating interferometer}.
+\newblock {\em Optics Express} 13:6296--6304.
+
+\bibitem{Thuering2013c}
+Thuering T et~al. (2013) {Energy resolved X-ray grating interferometry}.
+\newblock {\em Applied Physics Letters} 102:191113.
+
+\bibitem{Chabior2011a}
+Chabior M et~al. (2011) {Beam hardening effects in grating-based x-ray
+  phase-contrast imaging}.
+\newblock {\em Medical Physics} 38:1189.
+
+\bibitem{Grunzweig2008}
+Gr\"{u}nzweig C et~al. (2008) {Design, fabrication, and characterization of
+  diffraction gratings for neutron phase contrast imaging.}
+\newblock {\em The Review of scientific instruments} 79:053703.
+
+\bibitem{Raupach2011}
+Raupach R, Flohr TG (2011) {Analytical evaluation of the signal and noise
+  propagation in x-ray differential phase-contrast computed tomography.}
+\newblock {\em Physics in medicine and biology} 56:2219--2244.
+
+\end{thebibliography}
+\begin{thebibliography}{10}
+
+\bibitem{Als-Nielsen2011}
+Als-Nielsen J, McMorrow D (2011) {\em {Elements of modern X-ray physics}}.
+
+\bibitem{Qi2010}
+Qi Z, Zambelli J, Bevins N, Chen GH (2010) {Quantitative imaging of electron
+  density and effective atomic number using phase contrast CT.}
+\newblock {\em Physics in medicine and biology} 55:2669--77.
+
+\bibitem{Pfeiffer2007a}
+Pfeiffer F et~al. (2007) {High-resolution brain tumor visualization using
+  three-dimensional x-ray phase contrast tomography.}
+\newblock {\em Physics in medicine and biology} 52:6923--6930.
+
+\bibitem{McDonald2009}
+McDonald SA et~al. (2009) {Advanced phase-contrast imaging using a grating
+  interferometer}.
+\newblock {\em Journal of Synchrotron Radiation} 16:562--572.
+
+\bibitem{Davis1995}
+Davis T, Gao D, Gureyev T, Stevenson A, Wilkins S (1995) {Phase-contrast
+  imaging of weakly absorbing materials using hard X-rays}.
+\newblock {\em Nature} 373:595--598.
+
+\bibitem{Chapman1997}
+Chapman D et~al. (1997) {Diffraction enhanced x-ray imaging}.
+\newblock {\em Physics in Medicine and Biology} 42:2015--2025.
+
+\bibitem{Bonse1965}
+Bonse U, Hart M (1965) {An x-ray interferometer}.
+\newblock {\em Applied Physics Letters} 6:155--156.
+
+\bibitem{Momose1996}
+Momose A, Takeda T, Itai Y, Hirano K (1996) {Phase-contrast X-ray computed
+  tomography for observing biological soft tissues}.
+\newblock {\em Nature Medicine} 2:473--475.
+
+\bibitem{Snigirev1995}
+Snigirev A, Snigireva I, Kohn V, Kuznetsov S, Schelokov I (1995) {On the
+  possibilities of x-ray phase contrast microimaging by coherent high-energy
+  synchrotron radiation}.
+\newblock {\em Review of Scientific Instruments} 66:5486--5492.
+
+\bibitem{Wilkins1996}
+Wilkins S, Gureyev T, Gao D, Pogany A, Stevenson A (1996) {Phase-contrast
+  imaging using polychromatic hard X-rays}.
+\newblock {\em Nature} 384:335--338.
+
+\bibitem{Cloetens1996}
+Cloetens P, Barrett R, Baruchel J, Guigay J, Schlenker M (1996) {Phase objects
+  in synchrotron radiation hard x-ray imaging}.
+\newblock {\em Journal of Physics D: Applied Physics} 29:133--146.
+
+\bibitem{Cloetens1997}
+Cloetens P, Guigay J, {De Martino} C, Baruchel J, Schlenker M (1997)
+  {Fractional Talbot imaging of phase gratings with hard x rays.}
+\newblock {\em Optics letters} 22:1059--61.
+
+\bibitem{David2002}
+David C, N\"{o}hammer B, Solak H, Ziegler E (2002) {Differential x-ray phase
+  contrast imaging using a shearing interferometer}.
+\newblock {\em Applied Physics Letters} 81:3287--3289.
+
+\bibitem{Momose2003a}
+Momose A et~al. (2003) {Demonstration of X-Ray Talbot Interferometry}.
+\newblock {\em Japanese Journal of Applied Physics} 42:L866--L868.
+
+\bibitem{Munro2012}
+Munro P, Ignatyev K, Speller R, Olivo A (2012) {Phase and absorption retrieval
+  using incoherent X-ray sources}.
+\newblock {\em Proceedings of the National Academy of Sciences} 2012:2--7.
+
+\bibitem{Pfeiffer2006}
+Pfeiffer F, Weitkamp T, Bunk O, David C (2006) {Phase retrieval and
+  differential phase-contrast imaging with low-brilliance X-ray sources}.
+\newblock {\em Nature Physics} 2:258--261.
+
+\bibitem{Nesch2009}
+Nesch I et~al. (2009) {The design and application of an in-laboratory
+  diffraction-enhanced x-ray imaging instrument.}
+\newblock {\em The Review of scientific instruments} 80:093702.
+
+\bibitem{Parham2009}
+Parham C, Zhong Z, Connor DM, Chapman LD, Pisano ED (2009) {Design and
+  Implementation of a Compact Low-Dose Diffraction Enhanced Medical Imaging
+  System}.
+
+\bibitem{Pfeiffer2008}
+Pfeiffer F et~al. (2008) {Hard-X-ray dark-field imaging using a grating
+  interferometer}.
+\newblock {\em Nature Materials} 7:134--137.
+
+\bibitem{Willner2013}
+Willner M et~al. (2013) {Quantitative X-ray phase-contrast computed tomography
+  at 82 keV}.
+\newblock {\em Optics express} 21:4155--4166.
+
+\bibitem{Donath2009}
+Donath T et~al. (2009) {Inverse geometry for grating-based x-ray phase-contrast
+  imaging}.
+\newblock {\em Journal of Applied Physics} 106:054703.
+
+\bibitem{Mohr2012}
+Mohr J et~al. (2012) {High aspect ratio gratings for X-ray phase contrast
+  imaging}.
+\newblock 41:41--50.
+
+\bibitem{David2007}
+David C et~al. (2007) {Fabrication of diffraction gratings for hard X-ray phase
+  contrast imaging}.
+\newblock {\em Microelectronic Engineering} 84:1172--1177.
+
+\bibitem{Kenntner2010}
+Kenntner J et~al. (2010) {\em {Front- and backside structuring of gratings for
+  phase contrast imaging with x-ray tubes}}.
+\newblock Vol.{} 7804, p. 780408.
+
+\bibitem{Stutman2012a}
+Stutman D, Finkenthal M (2012) {Glancing angle Talbot-Lau grating
+  interferometers for phase contrast imaging at high x-ray energy}.
+\newblock {\em Applied physics letters} 101:91108.
+
+\bibitem{Aslund2007}
+{\AA slund, M} (2007) Ph.D. thesis.
+
+\bibitem{Oduko2010}
+Oduko JM, Young KC, Burch A (2010) in {\em Digital Mammography}, Lecture Notes
+  in Computer Science, eds.{} Martí J, Oliver A, Freixenet J, Martí R.
+\newblock (Springer Berlin Heidelberg) Vol.{} 6136, pp. 365--370.
+
+\bibitem{Weitkamp2005}
+Weitkamp T et~al. (2005) {X-ray phase imaging with a grating interferometer}.
+\newblock {\em Optics Express} 13:6296--6304.
+
+\bibitem{Thuering2013c}
+Thuering T et~al. (2013) {Energy resolved X-ray grating interferometry}.
+\newblock {\em Applied Physics Letters} 102:191113.
+
+\bibitem{Chabior2011a}
+Chabior M et~al. (2011) {Beam hardening effects in grating-based x-ray
+  phase-contrast imaging}.
+\newblock {\em Medical Physics} 38:1189.
+
+\bibitem{Grunzweig2008}
+Gr\"{u}nzweig C et~al. (2008) {Design, fabrication, and characterization of
+  diffraction gratings for neutron phase contrast imaging.}
+\newblock {\em The Review of scientific instruments} 79:053703.
+
+\bibitem{Raupach2011}
+Raupach R, Flohr TG (2011) {Analytical evaluation of the signal and noise
+  propagation in x-ray differential phase-contrast computed tomography.}
+\newblock {\em Physics in medicine and biology} 56:2219--2244.
+
+\end{thebibliography}
+\begin{thebibliography}{10}
+
+\bibitem{Als-Nielsen2011}
+Als-Nielsen J, McMorrow D (2011) {\em {Elements of modern X-ray physics}}.
+
+\bibitem{Qi2010}
+Qi Z, Zambelli J, Bevins N, Chen GH (2010) {Quantitative imaging of electron
+  density and effective atomic number using phase contrast CT.}
+\newblock {\em Physics in medicine and biology} 55:2669--77.
+
+\bibitem{Pfeiffer2007a}
+Pfeiffer F et~al. (2007) {High-resolution brain tumor visualization using
+  three-dimensional x-ray phase contrast tomography.}
+\newblock {\em Physics in medicine and biology} 52:6923--6930.
+
+\bibitem{McDonald2009}
+McDonald SA et~al. (2009) {Advanced phase-contrast imaging using a grating
+  interferometer}.
+\newblock {\em Journal of Synchrotron Radiation} 16:562--572.
+
+\bibitem{Davis1995}
+Davis T, Gao D, Gureyev T, Stevenson A, Wilkins S (1995) {Phase-contrast
+  imaging of weakly absorbing materials using hard X-rays}.
+\newblock {\em Nature} 373:595--598.
+
+\bibitem{Chapman1997}
+Chapman D et~al. (1997) {Diffraction enhanced x-ray imaging}.
+\newblock {\em Physics in Medicine and Biology} 42:2015--2025.
+
+\bibitem{Bonse1965}
+Bonse U, Hart M (1965) {An x-ray interferometer}.
+\newblock {\em Applied Physics Letters} 6:155--156.
+
+\bibitem{Momose1996}
+Momose A, Takeda T, Itai Y, Hirano K (1996) {Phase-contrast X-ray computed
+  tomography for observing biological soft tissues}.
+\newblock {\em Nature Medicine} 2:473--475.
+
+\bibitem{Snigirev1995}
+Snigirev A, Snigireva I, Kohn V, Kuznetsov S, Schelokov I (1995) {On the
+  possibilities of x-ray phase contrast microimaging by coherent high-energy
+  synchrotron radiation}.
+\newblock {\em Review of Scientific Instruments} 66:5486--5492.
+
+\bibitem{Wilkins1996}
+Wilkins S, Gureyev T, Gao D, Pogany A, Stevenson A (1996) {Phase-contrast
+  imaging using polychromatic hard X-rays}.
+\newblock {\em Nature} 384:335--338.
+
+\bibitem{Cloetens1996}
+Cloetens P, Barrett R, Baruchel J, Guigay J, Schlenker M (1996) {Phase objects
+  in synchrotron radiation hard x-ray imaging}.
+\newblock {\em Journal of Physics D: Applied Physics} 29:133--146.
+
+\bibitem{Cloetens1997}
+Cloetens P, Guigay J, {De Martino} C, Baruchel J, Schlenker M (1997)
+  {Fractional Talbot imaging of phase gratings with hard x rays.}
+\newblock {\em Optics letters} 22:1059--61.
+
+\bibitem{David2002}
+David C, N\"{o}hammer B, Solak H, Ziegler E (2002) {Differential x-ray phase
+  contrast imaging using a shearing interferometer}.
+\newblock {\em Applied Physics Letters} 81:3287--3289.
+
+\bibitem{Momose2003a}
+Momose A et~al. (2003) {Demonstration of X-Ray Talbot Interferometry}.
+\newblock {\em Japanese Journal of Applied Physics} 42:L866--L868.
+
+\bibitem{Munro2012}
+Munro P, Ignatyev K, Speller R, Olivo A (2012) {Phase and absorption retrieval
+  using incoherent X-ray sources}.
+\newblock {\em Proceedings of the National Academy of Sciences} 2012:2--7.
+
+\bibitem{Pfeiffer2006}
+Pfeiffer F, Weitkamp T, Bunk O, David C (2006) {Phase retrieval and
+  differential phase-contrast imaging with low-brilliance X-ray sources}.
+\newblock {\em Nature Physics} 2:258--261.
+
+\bibitem{Nesch2009}
+Nesch I et~al. (2009) {The design and application of an in-laboratory
+  diffraction-enhanced x-ray imaging instrument.}
+\newblock {\em The Review of scientific instruments} 80:093702.
+
+\bibitem{Parham2009}
+Parham C, Zhong Z, Connor DM, Chapman LD, Pisano ED (2009) {Design and
+  Implementation of a Compact Low-Dose Diffraction Enhanced Medical Imaging
+  System}.
+
+\bibitem{Pfeiffer2008}
+Pfeiffer F et~al. (2008) {Hard-X-ray dark-field imaging using a grating
+  interferometer}.
+\newblock {\em Nature Materials} 7:134--137.
+
+\bibitem{Willner2013}
+Willner M et~al. (2013) {Quantitative X-ray phase-contrast computed tomography
+  at 82 keV}.
+\newblock {\em Optics express} 21:4155--4166.
+
+\bibitem{Donath2009}
+Donath T et~al. (2009) {Inverse geometry for grating-based x-ray phase-contrast
+  imaging}.
+\newblock {\em Journal of Applied Physics} 106:054703.
+
+\bibitem{Mohr2012}
+Mohr J et~al. (2012) {High aspect ratio gratings for X-ray phase contrast
+  imaging}.
+\newblock 41:41--50.
+
+\bibitem{David2007}
+David C et~al. (2007) {Fabrication of diffraction gratings for hard X-ray phase
+  contrast imaging}.
+\newblock {\em Microelectronic Engineering} 84:1172--1177.
+
+\bibitem{Kenntner2010}
+Kenntner J et~al. (2010) {\em {Front- and backside structuring of gratings for
+  phase contrast imaging with x-ray tubes}}.
+\newblock Vol.{} 7804, p. 780408.
+
+\bibitem{Stutman2012a}
+Stutman D, Finkenthal M (2012) {Glancing angle Talbot-Lau grating
+  interferometers for phase contrast imaging at high x-ray energy}.
+\newblock {\em Applied physics letters} 101:91108.
+
+\bibitem{Aslund2007}
+{\AA slund, M} (2007) Ph.D. thesis.
+
+\bibitem{Oduko2010}
+Oduko JM, Young KC, Burch A (2010) in {\em Digital Mammography}, Lecture Notes
+  in Computer Science, eds.{} Martí J, Oliver A, Freixenet J, Martí R.
+\newblock (Springer Berlin Heidelberg) Vol.{} 6136, pp. 365--370.
+
+\bibitem{Weitkamp2005}
+Weitkamp T et~al. (2005) {X-ray phase imaging with a grating interferometer}.
+\newblock {\em Optics Express} 13:6296--6304.
+
+\bibitem{Thuering2013c}
+Thuering T et~al. (2013) {Energy resolved X-ray grating interferometry}.
+\newblock {\em Applied Physics Letters} 102:191113.
+
+\bibitem{Chabior2011a}
+Chabior M et~al. (2011) {Beam hardening effects in grating-based x-ray
+  phase-contrast imaging}.
+\newblock {\em Medical Physics} 38:1189.
+
+\bibitem{Grunzweig2008}
+Gr\"{u}nzweig C et~al. (2008) {Design, fabrication, and characterization of
+  diffraction gratings for neutron phase contrast imaging.}
+\newblock {\em The Review of scientific instruments} 79:053703.
+
+\bibitem{Raupach2011}
+Raupach R, Flohr TG (2011) {Analytical evaluation of the signal and noise
+  propagation in x-ray differential phase-contrast computed tomography.}
+\newblock {\em Physics in medicine and biology} 56:2219--2244.
+
+\end{thebibliography}
+\begin{thebibliography}{10}
+
+\bibitem{Als-Nielsen2011}
+Als-Nielsen J, McMorrow D (2011) {\em {Elements of modern X-ray physics}}.
+
+\bibitem{Qi2010}
+Qi Z, Zambelli J, Bevins N, Chen GH (2010) {Quantitative imaging of electron
+  density and effective atomic number using phase contrast CT.}
+\newblock {\em Physics in medicine and biology} 55:2669--77.
+
+\bibitem{Pfeiffer2007a}
+Pfeiffer F et~al. (2007) {High-resolution brain tumor visualization using
+  three-dimensional x-ray phase contrast tomography.}
+\newblock {\em Physics in medicine and biology} 52:6923--6930.
+
+\bibitem{McDonald2009}
+McDonald SA et~al. (2009) {Advanced phase-contrast imaging using a grating
+  interferometer}.
+\newblock {\em Journal of Synchrotron Radiation} 16:562--572.
+
+\bibitem{Davis1995}
+Davis T, Gao D, Gureyev T, Stevenson A, Wilkins S (1995) {Phase-contrast
+  imaging of weakly absorbing materials using hard X-rays}.
+\newblock {\em Nature} 373:595--598.
+
+\bibitem{Chapman1997}
+Chapman D et~al. (1997) {Diffraction enhanced x-ray imaging}.
+\newblock {\em Physics in Medicine and Biology} 42:2015--2025.
+
+\bibitem{Bonse1965}
+Bonse U, Hart M (1965) {An x-ray interferometer}.
+\newblock {\em Applied Physics Letters} 6:155--156.
+
+\bibitem{Momose1996}
+Momose A, Takeda T, Itai Y, Hirano K (1996) {Phase-contrast X-ray computed
+  tomography for observing biological soft tissues}.
+\newblock {\em Nature Medicine} 2:473--475.
+
+\bibitem{Snigirev1995}
+Snigirev A, Snigireva I, Kohn V, Kuznetsov S, Schelokov I (1995) {On the
+  possibilities of x-ray phase contrast microimaging by coherent high-energy
+  synchrotron radiation}.
+\newblock {\em Review of Scientific Instruments} 66:5486--5492.
+
+\bibitem{Wilkins1996}
+Wilkins S, Gureyev T, Gao D, Pogany A, Stevenson A (1996) {Phase-contrast
+  imaging using polychromatic hard X-rays}.
+\newblock {\em Nature} 384:335--338.
+
+\bibitem{Cloetens1996}
+Cloetens P, Barrett R, Baruchel J, Guigay J, Schlenker M (1996) {Phase objects
+  in synchrotron radiation hard x-ray imaging}.
+\newblock {\em Journal of Physics D: Applied Physics} 29:133--146.
+
+\bibitem{Cloetens1997}
+Cloetens P, Guigay J, {De Martino} C, Baruchel J, Schlenker M (1997)
+  {Fractional Talbot imaging of phase gratings with hard x rays.}
+\newblock {\em Optics letters} 22:1059--61.
+
+\bibitem{David2002}
+David C, N\"{o}hammer B, Solak H, Ziegler E (2002) {Differential x-ray phase
+  contrast imaging using a shearing interferometer}.
+\newblock {\em Applied Physics Letters} 81:3287--3289.
+
+\bibitem{Momose2003a}
+Momose A et~al. (2003) {Demonstration of X-Ray Talbot Interferometry}.
+\newblock {\em Japanese Journal of Applied Physics} 42:L866--L868.
+
+\bibitem{Munro2012}
+Munro P, Ignatyev K, Speller R, Olivo A (2012) {Phase and absorption retrieval
+  using incoherent X-ray sources}.
+\newblock {\em Proceedings of the National Academy of Sciences} 2012:2--7.
+
+\bibitem{Pfeiffer2006}
+Pfeiffer F, Weitkamp T, Bunk O, David C (2006) {Phase retrieval and
+  differential phase-contrast imaging with low-brilliance X-ray sources}.
+\newblock {\em Nature Physics} 2:258--261.
+
+\bibitem{Nesch2009}
+Nesch I et~al. (2009) {The design and application of an in-laboratory
+  diffraction-enhanced x-ray imaging instrument.}
+\newblock {\em The Review of scientific instruments} 80:093702.
+
+\bibitem{Parham2009}
+Parham C, Zhong Z, Connor DM, Chapman LD, Pisano ED (2009) {Design and
+  Implementation of a Compact Low-Dose Diffraction Enhanced Medical Imaging
+  System}.
+
+\bibitem{Pfeiffer2008}
+Pfeiffer F et~al. (2008) {Hard-X-ray dark-field imaging using a grating
+  interferometer}.
+\newblock {\em Nature Materials} 7:134--137.
+
+\bibitem{Willner2013}
+Willner M et~al. (2013) {Quantitative X-ray phase-contrast computed tomography
+  at 82 keV}.
+\newblock {\em Optics express} 21:4155--4166.
+
+\bibitem{Donath2009}
+Donath T et~al. (2009) {Inverse geometry for grating-based x-ray phase-contrast
+  imaging}.
+\newblock {\em Journal of Applied Physics} 106:054703.
+
+\bibitem{Mohr2012}
+Mohr J et~al. (2012) {High aspect ratio gratings for X-ray phase contrast
+  imaging}.
+\newblock 41:41--50.
+
+\bibitem{David2007}
+David C et~al. (2007) {Fabrication of diffraction gratings for hard X-ray phase
+  contrast imaging}.
+\newblock {\em Microelectronic Engineering} 84:1172--1177.
+
+\bibitem{Kenntner2010}
+Kenntner J et~al. (2010) {\em {Front- and backside structuring of gratings for
+  phase contrast imaging with x-ray tubes}}.
+\newblock Vol.{} 7804, p. 780408.
+
+\bibitem{Stutman2012a}
+Stutman D, Finkenthal M (2012) {Glancing angle Talbot-Lau grating
+  interferometers for phase contrast imaging at high x-ray energy}.
+\newblock {\em Applied physics letters} 101:91108.
+
+\bibitem{Aslund2007}
+{\AA slund, M} (2007) Ph.D. thesis.
+
+\bibitem{Oduko2010}
+Oduko JM, Young KC, Burch A (2010) in {\em Digital Mammography}, Lecture Notes
+  in Computer Science, eds.{} Martí J, Oliver A, Freixenet J, Martí R.
+\newblock (Springer Berlin Heidelberg) Vol.{} 6136, pp. 365--370.
+
+\bibitem{Weitkamp2005}
+Weitkamp T et~al. (2005) {X-ray phase imaging with a grating interferometer}.
+\newblock {\em Optics Express} 13:6296--6304.
+
+\bibitem{Thuering2013c}
+Thuering T et~al. (2013) {Energy resolved X-ray grating interferometry}.
+\newblock {\em Applied Physics Letters} 102:191113.
+
+\bibitem{Chabior2011a}
+Chabior M et~al. (2011) {Beam hardening effects in grating-based x-ray
+  phase-contrast imaging}.
+\newblock {\em Medical Physics} 38:1189.
+
+\bibitem{Grunzweig2008}
+Gr\"{u}nzweig C et~al. (2008) {Design, fabrication, and characterization of
+  diffraction gratings for neutron phase contrast imaging.}
+\newblock {\em The Review of scientific instruments} 79:053703.
+
+\bibitem{Raupach2011}
+Raupach R, Flohr TG (2011) {Analytical evaluation of the signal and noise
+  propagation in x-ray differential phase-contrast computed tomography.}
+\newblock {\em Physics in medicine and biology} 56:2219--2244.
+
+\end{thebibliography}
+\begin{thebibliography}{10}
+
+\bibitem{Als-Nielsen2011}
+Als-Nielsen J, McMorrow D (2011) {\em {Elements of modern X-ray physics}}.
+
+\bibitem{Qi2010}
+Qi Z, Zambelli J, Bevins N, Chen GH (2010) {Quantitative imaging of electron
+  density and effective atomic number using phase contrast CT.}
+\newblock {\em Physics in medicine and biology} 55:2669--77.
+
+\bibitem{Pfeiffer2007a}
+Pfeiffer F et~al. (2007) {High-resolution brain tumor visualization using
+  three-dimensional x-ray phase contrast tomography.}
+\newblock {\em Physics in medicine and biology} 52:6923--6930.
+
+\bibitem{McDonald2009}
+McDonald SA et~al. (2009) {Advanced phase-contrast imaging using a grating
+  interferometer}.
+\newblock {\em Journal of Synchrotron Radiation} 16:562--572.
+
+\bibitem{Davis1995}
+Davis T, Gao D, Gureyev T, Stevenson A, Wilkins S (1995) {Phase-contrast
+  imaging of weakly absorbing materials using hard X-rays}.
+\newblock {\em Nature} 373:595--598.
+
+\bibitem{Chapman1997}
+Chapman D et~al. (1997) {Diffraction enhanced x-ray imaging}.
+\newblock {\em Physics in Medicine and Biology} 42:2015--2025.
+
+\bibitem{Bonse1965}
+Bonse U, Hart M (1965) {An x-ray interferometer}.
+\newblock {\em Applied Physics Letters} 6:155--156.
+
+\bibitem{Momose1996}
+Momose A, Takeda T, Itai Y, Hirano K (1996) {Phase-contrast X-ray computed
+  tomography for observing biological soft tissues}.
+\newblock {\em Nature Medicine} 2:473--475.
+
+\bibitem{Snigirev1995}
+Snigirev A, Snigireva I, Kohn V, Kuznetsov S, Schelokov I (1995) {On the
+  possibilities of x-ray phase contrast microimaging by coherent high-energy
+  synchrotron radiation}.
+\newblock {\em Review of Scientific Instruments} 66:5486--5492.
+
+\bibitem{Wilkins1996}
+Wilkins S, Gureyev T, Gao D, Pogany A, Stevenson A (1996) {Phase-contrast
+  imaging using polychromatic hard X-rays}.
+\newblock {\em Nature} 384:335--338.
+
+\bibitem{Cloetens1996}
+Cloetens P, Barrett R, Baruchel J, Guigay J, Schlenker M (1996) {Phase objects
+  in synchrotron radiation hard x-ray imaging}.
+\newblock {\em Journal of Physics D: Applied Physics} 29:133--146.
+
+\bibitem{Cloetens1997}
+Cloetens P, Guigay J, {De Martino} C, Baruchel J, Schlenker M (1997)
+  {Fractional Talbot imaging of phase gratings with hard x rays.}
+\newblock {\em Optics letters} 22:1059--61.
+
+\bibitem{David2002}
+David C, N\"{o}hammer B, Solak H, Ziegler E (2002) {Differential x-ray phase
+  contrast imaging using a shearing interferometer}.
+\newblock {\em Applied Physics Letters} 81:3287--3289.
+
+\bibitem{Momose2003a}
+Momose A et~al. (2003) {Demonstration of X-Ray Talbot Interferometry}.
+\newblock {\em Japanese Journal of Applied Physics} 42:L866--L868.
+
+\bibitem{Munro2012}
+Munro P, Ignatyev K, Speller R, Olivo A (2012) {Phase and absorption retrieval
+  using incoherent X-ray sources}.
+\newblock {\em Proceedings of the National Academy of Sciences} 2012:2--7.
+
+\bibitem{Pfeiffer2006}
+Pfeiffer F, Weitkamp T, Bunk O, David C (2006) {Phase retrieval and
+  differential phase-contrast imaging with low-brilliance X-ray sources}.
+\newblock {\em Nature Physics} 2:258--261.
+
+\bibitem{Nesch2009}
+Nesch I et~al. (2009) {The design and application of an in-laboratory
+  diffraction-enhanced x-ray imaging instrument.}
+\newblock {\em The Review of scientific instruments} 80:093702.
+
+\bibitem{Parham2009}
+Parham C, Zhong Z, Connor DM, Chapman LD, Pisano ED (2009) {Design and
+  Implementation of a Compact Low-Dose Diffraction Enhanced Medical Imaging
+  System}.
+
+\bibitem{Pfeiffer2008}
+Pfeiffer F et~al. (2008) {Hard-X-ray dark-field imaging using a grating
+  interferometer}.
+\newblock {\em Nature Materials} 7:134--137.
+
+\bibitem{Willner2013}
+Willner M et~al. (2013) {Quantitative X-ray phase-contrast computed tomography
+  at 82 keV}.
+\newblock {\em Optics express} 21:4155--4166.
+
+\bibitem{Donath2009}
+Donath T et~al. (2009) {Inverse geometry for grating-based x-ray phase-contrast
+  imaging}.
+\newblock {\em Journal of Applied Physics} 106:054703.
+
+\bibitem{Mohr2012}
+Mohr J et~al. (2012) {High aspect ratio gratings for X-ray phase contrast
+  imaging}.
+\newblock 41:41--50.
+
+\bibitem{David2007}
+David C et~al. (2007) {Fabrication of diffraction gratings for hard X-ray phase
+  contrast imaging}.
+\newblock {\em Microelectronic Engineering} 84:1172--1177.
+
+\bibitem{Kenntner2010}
+Kenntner J et~al. (2010) {\em {Front- and backside structuring of gratings for
+  phase contrast imaging with x-ray tubes}}.
+\newblock Vol.{} 7804, p. 780408.
+
+\bibitem{Stutman2012a}
+Stutman D, Finkenthal M (2012) {Glancing angle Talbot-Lau grating
+  interferometers for phase contrast imaging at high x-ray energy}.
+\newblock {\em Applied physics letters} 101:91108.
+
+\bibitem{Aslund2007}
+{\AA slund, M} (2007) Ph.D. thesis.
+
+\bibitem{Oduko2010}
+Oduko JM, Young KC, Burch A (2010) in {\em Digital Mammography}, Lecture Notes
+  in Computer Science, eds.{} Martí J, Oliver A, Freixenet J, Martí R.
+\newblock (Springer Berlin Heidelberg) Vol.{} 6136, pp. 365--370.
+
+\bibitem{Weitkamp2005}
+Weitkamp T et~al. (2005) {X-ray phase imaging with a grating interferometer}.
+\newblock {\em Optics Express} 13:6296--6304.
+
+\bibitem{Thuering2013c}
+Thuering T et~al. (2013) {Energy resolved X-ray grating interferometry}.
+\newblock {\em Applied Physics Letters} 102:191113.
+
+\bibitem{Chabior2011a}
+Chabior M et~al. (2011) {Beam hardening effects in grating-based x-ray
+  phase-contrast imaging}.
+\newblock {\em Medical Physics} 38:1189.
+
+\bibitem{Grunzweig2008}
+Gr\"{u}nzweig C et~al. (2008) {Design, fabrication, and characterization of
+  diffraction gratings for neutron phase contrast imaging.}
+\newblock {\em The Review of scientific instruments} 79:053703.
+
+\bibitem{Raupach2011}
+Raupach R, Flohr TG (2011) {Analytical evaluation of the signal and noise
+  propagation in x-ray differential phase-contrast computed tomography.}
+\newblock {\em Physics in medicine and biology} 56:2219--2244.
+
+\end{thebibliography}
+
+\end{article}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Adding Figure and Table References
+%% Be sure to add figures and tables after \end{article}
+%% and before \end{document}
+
+%% For figures, put the caption below the illustration.
+%%
+%% \begin{figure}
+%% \caption{Almost Sharp Front}\label{afoto}
+%% \end{figure}
+
+%% For Tables, put caption above table
+%%
+%% Table caption should start with a capital letter, continue with lower case
+%% and not have a period at the end
+%% Using @{\vrule height ?? depth ?? width0pt} in the tabular preamble will
+%% keep that much space between every line in the table.
+
+%% \begin{table}
+%% \caption{Repeat length of longer allele by age of onset class}
+%% \begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
+%% table text
+%% \end{tabular}
+%% \end{table}
+
+%% For two column figures and tables, use the following:
+
+%% \begin{figure*}
+%% \caption{Almost Sharp Front}\label{afoto}
+%% \end{figure*}
+
+%% \begin{table*}
+%% \caption{Repeat length of longer allele by age of onset class}
+%% \begin{tabular}{ccc}
+%% table text
+%% \end{tabular}
+%% \end{table*}
+
+\begin{figure}
+    \includegraphics[width=.5\textwidth]{figures/figure1.eps}
+    \caption{Schematic of a grating
+        interferometer for X-ray energies between 60 and
+        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
+        aspect ratio is defined by the ratio of the travelling distance along the
+        grating lines and the period and can be arbitrarily long. In order to maximise
+        the field of view, the grating structures are aligned on an
+    arc.}
+    \label{Fig:schematic}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=.5\textwidth]{figures/grating_mask.eps}
+    \caption{Grating design mask for
+        the edge-on illumination approach and SEM
+        image of the grating. The top part of the 4 inch wafer shows
+        five grating chips. The
+        gratings have different curvatures which are specific to the grating
+        interferometer geometry. 
+        The SEM image shows the gold structures and the interrupting bridges
+        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}
+        \label{Fig:grating_mask}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
+    \caption{Radiographic scan of an electronic chip. The image was acquired
+        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
+    step. The top right image shows the differential absorption image.}
+    \label{Fig:img_chip}
+\end{figure}
+
 \end{document}

### 2013-11-29 hedpc.tex
Marco's significance statement, latex style fixes
    - Marco's edits to the significance statement
    - Authors correctly shown under the title
    - Fixed bold font in article body
    - Added corresponding author

@@
 \usepackage{graphicx}  %figures
-\usepackage[detect-all]{siunitx}
 %\usepackage{pnastwof}
@@
 %%%%%%%%%%%%
+\footlineauthor{ Corresponding author:
+    M. Abis, 
+    matteo.abis@psi.ch
+}
 
@@
 
-\title{X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on
-a conventional source}
+\title{X-ray phase-contrast imaging at 100 keV on a conventional source}
 
-\author{T.~Thüring
-\affil{1}{Paul Scherrer Institute, 5232 Villigen, Switzerland}
-\affil{2}{Institute for Biomedical Engineering, Swiss Federal
-Institute of Technology,
-Gloriastrasse 35
-8092 Zurich, Switzerland}}
-\author{M.~Abis
-\affil{1}{}
+\author{T.~Thüring%
+\affil{1}{Paul Scherrer Institute, 5232 Villigen, Switzerland}%
+\affil{2}{Institute for Biomedical Engineering,
+    Swiss Federal Institute of Technology,
+    Gloriastrasse 35,
+8092 Zurich, Switzerland},%
+M.~Abis%%
+\affil{1}{}%
+\affil{2}{},%
+Z.~Wang%
+\affil{1}{},%
+C.~David%
+\affil{1}{},%
+\and%
+M.~Stampanoni%
+\affil{1}{}%
 \affil{2}{}}
-\author{Z.~Wang}
-\affil{1}{}
-\author{C.~David}
-\affil{1}{}
-\author{M.~Stampanoni
-\affil{1}{}
-\affil{2}{}}
-
-\author{}
 
@@
     of this technique in the energy range between $80$ and
-    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
+    \SI{150}{\kilo\electronvolt} are still largely unexplored due to the
     severe technical challenges. Phase-contrast X-ray imaging at such high
@@
 %acronyms
-CT,computed tomography;
-SNR,signal-to-noise ratio;
-CNR,contrast-to-noise ratio;
-SEM,scanning electron microscope;
+CT, computed tomography;
+SNR, signal-to-noise ratio;
+CNR, contrast-to-noise ratio;
+SEM, scanning electron microscope;
 }
@@
 \section{Significance statement}
-Phase sensitive X-ray imaging provides access to additional information
-on the investigated samples with respect to the conventional absorption
-radiography and tomography.
 
-Here we show a grating interferometer with a new design of the optical
-elements that enables a large field of view and an efficient imaging at
-a target energy of~\SI{100}{\kilo\eV} on a conventional tube.
+Phase sensitive X-ray imaging techniques provide access to new and
+invaluable information compared to traditional absorption-based radiography
+and tomography.
 
-Our results demonstrate that phase contrast can be achieved at these
-energies, which are relevant for many applications, ranging from medical
-diagnostics to nondestructive testing or homeland security.
+Here we show a Talbot-Lau grating interferometer based on a novel optical
+design, enabling imaging at X-ray energies of~\SI{100}{\kilo\eV} and above
+with a large field of view as well as a very compact and efficient geometry.
+
+Our results demonstrate, for the first time, that phase contrast X-ray
+imaging can be successfully performed at diagnostically relevant energies
+using a conventional X-ray tube, with potential applications spanning from
+medical imaging to nondestructive testing or homeland security.
 
@@
 
-%% Enter the largest bibliography number in the facing curly brackets
-%% following \begin{thebibliography}
-
 %\bibliographystyle{pnas}
 %\bibliography{library}
-\begin{thebibliography}{10}
-
-\bibitem{Als-Nielsen2011}
-Als-Nielsen J, McMorrow D (2011) {\em {Elements of modern X-ray physics}}.
-
-\bibitem{Qi2010}
-Qi Z, Zambelli J, Bevins N, Chen GH (2010) {Quantitative imaging of electron
-  density and effective atomic number using phase contrast CT.}
-\newblock {\em Physics in medicine and biology} 55:2669--77.
-
-\bibitem{Pfeiffer2007a}
-Pfeiffer F et~al. (2007) {High-resolution brain tumor visualization using
-  three-dimensional x-ray phase contrast tomography.}
-\newblock {\em Physics in medicine and biology} 52:6923--6930.
-
-\bibitem{McDonald2009}
-McDonald SA et~al. (2009) {Advanced phase-contrast imaging using a grating
-  interferometer}.
-\newblock {\em Journal of Synchrotron Radiation} 16:562--572.
-
-\bibitem{Davis1995}
-Davis T, Gao D, Gureyev T, Stevenson A, Wilkins S (1995) {Phase-contrast
-  imaging of weakly absorbing materials using hard X-rays}.
-\newblock {\em Nature} 373:595--598.
-
-\bibitem{Chapman1997}
-Chapman D et~al. (1997) {Diffraction enhanced x-ray imaging}.
-\newblock {\em Physics in Medicine and Biology} 42:2015--2025.
-
-\bibitem{Bonse1965}
-Bonse U, Hart M (1965) {An x-ray interferometer}.
-\newblock {\em Applied Physics Letters} 6:155--156.
-
-\bibitem{Momose1996}
-Momose A, Takeda T, Itai Y, Hirano K (1996) {Phase-contrast X-ray computed
-  tomography for observing biological soft tissues}.
-\newblock {\em Nature Medicine} 2:473--475.
-
-\bibitem{Snigirev1995}
-Snigirev A, Snigireva I, Kohn V, Kuznetsov S, Schelokov I (1995) {On the
-  possibilities of x-ray phase contrast microimaging by coherent high-energy
-  synchrotron radiation}.
-\newblock {\em Review of Scientific Instruments} 66:5486--5492.
-
-\bibitem{Wilkins1996}
-Wilkins S, Gureyev T, Gao D, Pogany A, Stevenson A (1996) {Phase-contrast
-  imaging using polychromatic hard X-rays}.
-\newblock {\em Nature} 384:335--338.
-
-\bibitem{Cloetens1996}
-Cloetens P, Barrett R, Baruchel J, Guigay J, Schlenker M (1996) {Phase objects
-  in synchrotron radiation hard x-ray imaging}.
-\newblock {\em Journal of Physics D: Applied Physics} 29:133--146.
-
-\bibitem{Cloetens1997}
-Cloetens P, Guigay J, {De Martino} C, Baruchel J, Schlenker M (1997)
-  {Fractional Talbot imaging of phase gratings with hard x rays.}
-\newblock {\em Optics letters} 22:1059--61.
-
-\bibitem{David2002}
-David C, N\"{o}hammer B, Solak H, Ziegler E (2002) {Differential x-ray phase
-  contrast imaging using a shearing interferometer}.
-\newblock {\em Applied Physics Letters} 81:3287--3289.
-
-\bibitem{Momose2003a}
-Momose A et~al. (2003) {Demonstration of X-Ray Talbot Interferometry}.
-\newblock {\em Japanese Journal of Applied Physics} 42:L866--L868.
-
-\bibitem{Munro2012}
-Munro P, Ignatyev K, Speller R, Olivo A (2012) {Phase and absorption retrieval
-  using incoherent X-ray sources}.
-\newblock {\em Proceedings of the National Academy of Sciences} 2012:2--7.
-
-\bibitem{Pfeiffer2006}
-Pfeiffer F, Weitkamp T, Bunk O, David C (2006) {Phase retrieval and
-  differential phase-contrast imaging with low-brilliance X-ray sources}.
-\newblock {\em Nature Physics} 2:258--261.
-
-\bibitem{Nesch2009}
-Nesch I et~al. (2009) {The design and application of an in-laboratory
-  diffraction-enhanced x-ray imaging instrument.}
-\newblock {\em The Review of scientific instruments} 80:093702.
-
-\bibitem{Parham2009}
-Parham C, Zhong Z, Connor DM, Chapman LD, Pisano ED (2009) {Design and
-  Implementation of a Compact Low-Dose Diffraction Enhanced Medical Imaging
-  System}.
-
-\bibitem{Pfeiffer2008}
-Pfeiffer F et~al. (2008) {Hard-X-ray dark-field imaging using a grating
-  interferometer}.
-\newblock {\em Nature Materials} 7:134--137.
-
-\bibitem{Willner2013}
-Willner M et~al. (2013) {Quantitative X-ray phase-contrast computed tomography
-  at 82 keV}.
-\newblock {\em Optics express} 21:4155--4166.
-
-\bibitem{Donath2009}
-Donath T et~al. (2009) {Inverse geometry for grating-based x-ray phase-contrast
-  imaging}.
-\newblock {\em Journal of Applied Physics} 106:054703.
-
-\bibitem{Mohr2012}
-Mohr J et~al. (2012) {High aspect ratio gratings for X-ray phase contrast
-  imaging}.
-\newblock 41:41--50.
-
-\bibitem{David2007}
-David C et~al. (2007) {Fabrication of diffraction gratings for hard X-ray phase
-  contrast imaging}.
-\newblock {\em Microelectronic Engineering} 84:1172--1177.
-
-\bibitem{Kenntner2010}
-Kenntner J et~al. (2010) {\em {Front- and backside structuring of gratings for
-  phase contrast imaging with x-ray tubes}}.
-\newblock Vol.{} 7804, p. 780408.
-
-\bibitem{Stutman2012a}
-Stutman D, Finkenthal M (2012) {Glancing angle Talbot-Lau grating
-  interferometers for phase contrast imaging at high x-ray energy}.
-\newblock {\em Applied physics letters} 101:91108.
-
-\bibitem{Aslund2007}
-{\AA slund, M} (2007) Ph.D. thesis.
-
-\bibitem{Oduko2010}
-Oduko JM, Young KC, Burch A (2010) in {\em Digital Mammography}, Lecture Notes
-  in Computer Science, eds.{} Martí J, Oliver A, Freixenet J, Martí R.
-\newblock (Springer Berlin Heidelberg) Vol.{} 6136, pp. 365--370.
-
-\bibitem{Weitkamp2005}
-Weitkamp T et~al. (2005) {X-ray phase imaging with a grating interferometer}.
-\newblock {\em Optics Express} 13:6296--6304.
-
-\bibitem{Thuering2013c}
-Thuering T et~al. (2013) {Energy resolved X-ray grating interferometry}.
-\newblock {\em Applied Physics Letters} 102:191113.
-
-\bibitem{Chabior2011a}
-Chabior M et~al. (2011) {Beam hardening effects in grating-based x-ray
-  phase-contrast imaging}.
-\newblock {\em Medical Physics} 38:1189.
-
-\bibitem{Grunzweig2008}
-Gr\"{u}nzweig C et~al. (2008) {Design, fabrication, and characterization of
-  diffraction gratings for neutron phase contrast imaging.}
-\newblock {\em The Review of scientific instruments} 79:053703.
-
-\bibitem{Raupach2011}
-Raupach R, Flohr TG (2011) {Analytical evaluation of the signal and noise
-  propagation in x-ray differential phase-contrast computed tomography.}
-\newblock {\em Physics in medicine and biology} 56:2219--2244.
-
-\end{thebibliography}
-\begin{thebibliography}{10}
-
-\bibitem{Als-Nielsen2011}
-Als-Nielsen J, McMorrow D (2011) {\em {Elements of modern X-ray physics}}.
-
-\bibitem{Qi2010}
-Qi Z, Zambelli J, Bevins N, Chen GH (2010) {Quantitative imaging of electron
-  density and effective atomic number using phase contrast CT.}
-\newblock {\em Physics in medicine and biology} 55:2669--77.
-
-\bibitem{Pfeiffer2007a}
-Pfeiffer F et~al. (2007) {High-resolution brain tumor visualization using
-  three-dimensional x-ray phase contrast tomography.}
-\newblock {\em Physics in medicine and biology} 52:6923--6930.
-
-\bibitem{McDonald2009}
-McDonald SA et~al. (2009) {Advanced phase-contrast imaging using a grating
-  interferometer}.
-\newblock {\em Journal of Synchrotron Radiation} 16:562--572.
-
-\bibitem{Davis1995}
-Davis T, Gao D, Gureyev T, Stevenson A, Wilkins S (1995) {Phase-contrast
-  imaging of weakly absorbing materials using hard X-rays}.
-\newblock {\em Nature} 373:595--598.
-
-\bibitem{Chapman1997}
-Chapman D et~al. (1997) {Diffraction enhanced x-ray imaging}.
-\newblock {\em Physics in Medicine and Biology} 42:2015--2025.
-
-\bibitem{Bonse1965}
-Bonse U, Hart M (1965) {An x-ray interferometer}.
-\newblock {\em Applied Physics Letters} 6:155--156.
-
-\bibitem{Momose1996}
-Momose A, Takeda T, Itai Y, Hirano K (1996) {Phase-contrast X-ray computed
-  tomography for observing biological soft tissues}.
-\newblock {\em Nature Medicine} 2:473--475.
-
-\bibitem{Snigirev1995}
-Snigirev A, Snigireva I, Kohn V, Kuznetsov S, Schelokov I (1995) {On the
-  possibilities of x-ray phase contrast microimaging by coherent high-energy
-  synchrotron radiation}.
-\newblock {\em Review of Scientific Instruments} 66:5486--5492.
-
-\bibitem{Wilkins1996}
-Wilkins S, Gureyev T, Gao D, Pogany A, Stevenson A (1996) {Phase-contrast
-  imaging using polychromatic hard X-rays}.
-\newblock {\em Nature} 384:335--338.
-
-\bibitem{Cloetens1996}
-Cloetens P, Barrett R, Baruchel J, Guigay J, Schlenker M (1996) {Phase objects
-  in synchrotron radiation hard x-ray imaging}.
-\newblock {\em Journal of Physics D: Applied Physics} 29:133--146.
-
-\bibitem{Cloetens1997}
-Cloetens P, Guigay J, {De Martino} C, Baruchel J, Schlenker M (1997)
-  {Fractional Talbot imaging of phase gratings with hard x rays.}
-\newblock {\em Optics letters} 22:1059--61.
-
-\bibitem{David2002}
-David C, N\"{o}hammer B, Solak H, Ziegler E (2002) {Differential x-ray phase
-  contrast imaging using a shearing interferometer}.
-\newblock {\em Applied Physics Letters} 81:3287--3289.
-
-\bibitem{Momose2003a}
-Momose A et~al. (2003) {Demonstration of X-Ray Talbot Interferometry}.
-\newblock {\em Japanese Journal of Applied Physics} 42:L866--L868.
-
-\bibitem{Munro2012}
-Munro P, Ignatyev K, Speller R, Olivo A (2012) {Phase and absorption retrieval
-  using incoherent X-ray sources}.
-\newblock {\em Proceedings of the National Academy of Sciences} 2012:2--7.
-
-\bibitem{Pfeiffer2006}
-Pfeiffer F, Weitkamp T, Bunk O, David C (2006) {Phase retrieval and
-  differential phase-contrast imaging with low-brilliance X-ray sources}.
-\newblock {\em Nature Physics} 2:258--261.
-
-\bibitem{Nesch2009}
-Nesch I et~al. (2009) {The design and application of an in-laboratory
-  diffraction-enhanced x-ray imaging instrument.}
-\newblock {\em The Review of scientific instruments} 80:093702.
-
-\bibitem{Parham2009}
-Parham C, Zhong Z, Connor DM, Chapman LD, Pisano ED (2009) {Design and
-  Implementation of a Compact Low-Dose Diffraction Enhanced Medical Imaging
-  System}.
-
-\bibitem{Pfeiffer2008}
-Pfeiffer F et~al. (2008) {Hard-X-ray dark-field imaging using a grating
-  interferometer}.
-\newblock {\em Nature Materials} 7:134--137.
-
-\bibitem{Willner2013}
-Willner M et~al. (2013) {Quantitative X-ray phase-contrast computed tomography
-  at 82 keV}.
-\newblock {\em Optics express} 21:4155--4166.
-
-\bibitem{Donath2009}
-Donath T et~al. (2009) {Inverse geometry for grating-based x-ray phase-contrast
-  imaging}.
-\newblock {\em Journal of Applied Physics} 106:054703.
-
-\bibitem{Mohr2012}
-Mohr J et~al. (2012) {High aspect ratio gratings for X-ray phase contrast
-  imaging}.
-\newblock 41:41--50.
-
-\bibitem{David2007}
-David C et~al. (2007) {Fabrication of diffraction gratings for hard X-ray phase
-  contrast imaging}.
-\newblock {\em Microelectronic Engineering} 84:1172--1177.
-
-\bibitem{Kenntner2010}
-Kenntner J et~al. (2010) {\em {Front- and backside structuring of gratings for
-  phase contrast imaging with x-ray tubes}}.
-\newblock Vol.{} 7804, p. 780408.
-
-\bibitem{Stutman2012a}
-Stutman D, Finkenthal M (2012) {Glancing angle Talbot-Lau grating
-  interferometers for phase contrast imaging at high x-ray energy}.
-\newblock {\em Applied physics letters} 101:91108.
-
-\bibitem{Aslund2007}
-{\AA slund, M} (2007) Ph.D. thesis.
-
-\bibitem{Oduko2010}
-Oduko JM, Young KC, Burch A (2010) in {\em Digital Mammography}, Lecture Notes
-  in Computer Science, eds.{} Martí J, Oliver A, Freixenet J, Martí R.
-\newblock (Springer Berlin Heidelberg) Vol.{} 6136, pp. 365--370.
-
-\bibitem{Weitkamp2005}
-Weitkamp T et~al. (2005) {X-ray phase imaging with a grating interferometer}.
-\newblock {\em Optics Express} 13:6296--6304.
-
-\bibitem{Thuering2013c}
-Thuering T et~al. (2013) {Energy resolved X-ray grating interferometry}.
-\newblock {\em Applied Physics Letters} 102:191113.
-
-\bibitem{Chabior2011a}
-Chabior M et~al. (2011) {Beam hardening effects in grating-based x-ray
-  phase-contrast imaging}.
-\newblock {\em Medical Physics} 38:1189.
-
-\bibitem{Grunzweig2008}
-Gr\"{u}nzweig C et~al. (2008) {Design, fabrication, and characterization of
-  diffraction gratings for neutron phase contrast imaging.}
-\newblock {\em The Review of scientific instruments} 79:053703.
-
-\bibitem{Raupach2011}
-Raupach R, Flohr TG (2011) {Analytical evaluation of the signal and noise
-  propagation in x-ray differential phase-contrast computed tomography.}
-\newblock {\em Physics in medicine and biology} 56:2219--2244.
-
-\end{thebibliography}
-\begin{thebibliography}{10}
-
-\bibitem{Als-Nielsen2011}
-Als-Nielsen J, McMorrow D (2011) {\em {Elements of modern X-ray physics}}.
-
-\bibitem{Qi2010}
-Qi Z, Zambelli J, Bevins N, Chen GH (2010) {Quantitative imaging of electron
-  density and effective atomic number using phase contrast CT.}
-\newblock {\em Physics in medicine and biology} 55:2669--77.
-
-\bibitem{Pfeiffer2007a}
-Pfeiffer F et~al. (2007) {High-resolution brain tumor visualization using
-  three-dimensional x-ray phase contrast tomography.}
-\newblock {\em Physics in medicine and biology} 52:6923--6930.
-
-\bibitem{McDonald2009}
-McDonald SA et~al. (2009) {Advanced phase-contrast imaging using a grating
-  interferometer}.
-\newblock {\em Journal of Synchrotron Radiation} 16:562--572.
-
-\bibitem{Davis1995}
-Davis T, Gao D, Gureyev T, Stevenson A, Wilkins S (1995) {Phase-contrast
-  imaging of weakly absorbing materials using hard X-rays}.
-\newblock {\em Nature} 373:595--598.
-
-\bibitem{Chapman1997}
-Chapman D et~al. (1997) {Diffraction enhanced x-ray imaging}.
-\newblock {\em Physics in Medicine and Biology} 42:2015--2025.
-
-\bibitem{Bonse1965}
-Bonse U, Hart M (1965) {An x-ray interferometer}.
-\newblock {\em Applied Physics Letters} 6:155--156.
-
-\bibitem{Momose1996}
-Momose A, Takeda T, Itai Y, Hirano K (1996) {Phase-contrast X-ray computed
-  tomography for observing biological soft tissues}.
-\newblock {\em Nature Medicine} 2:473--475.
-
-\bibitem{Snigirev1995}
-Snigirev A, Snigireva I, Kohn V, Kuznetsov S, Schelokov I (1995) {On the
-  possibilities of x-ray phase contrast microimaging by coherent high-energy
-  synchrotron radiation}.
-\newblock {\em Review of Scientific Instruments} 66:5486--5492.
-
-\bibitem{Wilkins1996}
-Wilkins S, Gureyev T, Gao D, Pogany A, Stevenson A (1996) {Phase-contrast
-  imaging using polychromatic hard X-rays}.
-\newblock {\em Nature} 384:335--338.
-
-\bibitem{Cloetens1996}
-Cloetens P, Barrett R, Baruchel J, Guigay J, Schlenker M (1996) {Phase objects
-  in synchrotron radiation hard x-ray imaging}.
-\newblock {\em Journal of Physics D: Applied Physics} 29:133--146.
-
-\bibitem{Cloetens1997}
-Cloetens P, Guigay J, {De Martino} C, Baruchel J, Schlenker M (1997)
-  {Fractional Talbot imaging of phase gratings with hard x rays.}
-\newblock {\em Optics letters} 22:1059--61.
-
-\bibitem{David2002}
-David C, N\"{o}hammer B, Solak H, Ziegler E (2002) {Differential x-ray phase
-  contrast imaging using a shearing interferometer}.
-\newblock {\em Applied Physics Letters} 81:3287--3289.
-
-\bibitem{Momose2003a}
-Momose A et~al. (2003) {Demonstration of X-Ray Talbot Interferometry}.
-\newblock {\em Japanese Journal of Applied Physics} 42:L866--L868.
-
-\bibitem{Munro2012}
-Munro P, Ignatyev K, Speller R, Olivo A (2012) {Phase and absorption retrieval
-  using incoherent X-ray sources}.
-\newblock {\em Proceedings of the National Academy of Sciences} 2012:2--7.
-
-\bibitem{Pfeiffer2006}
-Pfeiffer F, Weitkamp T, Bunk O, David C (2006) {Phase retrieval and
-  differential phase-contrast imaging with low-brilliance X-ray sources}.
-\newblock {\em Nature Physics} 2:258--261.
-
-\bibitem{Nesch2009}
-Nesch I et~al. (2009) {The design and application of an in-laboratory
-  diffraction-enhanced x-ray imaging instrument.}
-\newblock {\em The Review of scientific instruments} 80:093702.
-
-\bibitem{Parham2009}
-Parham C, Zhong Z, Connor DM, Chapman LD, Pisano ED (2009) {Design and
-  Implementation of a Compact Low-Dose Diffraction Enhanced Medical Imaging
-  System}.
-
-\bibitem{Pfeiffer2008}
-Pfeiffer F et~al. (2008) {Hard-X-ray dark-field imaging using a grating
-  interferometer}.
-\newblock {\em Nature Materials} 7:134--137.
-
-\bibitem{Willner2013}
-Willner M et~al. (2013) {Quantitative X-ray phase-contrast computed tomography
-  at 82 keV}.
-\newblock {\em Optics express} 21:4155--4166.
-
-\bibitem{Donath2009}
-Donath T et~al. (2009) {Inverse geometry for grating-based x-ray phase-contrast
-  imaging}.
-\newblock {\em Journal of Applied Physics} 106:054703.
-
-\bibitem{Mohr2012}
-Mohr J et~al. (2012) {High aspect ratio gratings for X-ray phase contrast
-  imaging}.
-\newblock 41:41--50.
-
-\bibitem{David2007}
-David C et~al. (2007) {Fabrication of diffraction gratings for hard X-ray phase
-  contrast imaging}.
-\newblock {\em Microelectronic Engineering} 84:1172--1177.
-
-\bibitem{Kenntner2010}
-Kenntner J et~al. (2010) {\em {Front- and backside structuring of gratings for
-  phase contrast imaging with x-ray tubes}}.
-\newblock Vol.{} 7804, p. 780408.
-
-\bibitem{Stutman2012a}
-Stutman D, Finkenthal M (2012) {Glancing angle Talbot-Lau grating
-  interferometers for phase contrast imaging at high x-ray energy}.
-\newblock {\em Applied physics letters} 101:91108.
-
-\bibitem{Aslund2007}
-{\AA slund, M} (2007) Ph.D. thesis.
-
-\bibitem{Oduko2010}
-Oduko JM, Young KC, Burch A (2010) in {\em Digital Mammography}, Lecture Notes
-  in Computer Science, eds.{} Martí J, Oliver A, Freixenet J, Martí R.
-\newblock (Springer Berlin Heidelberg) Vol.{} 6136, pp. 365--370.
-
-\bibitem{Weitkamp2005}
-Weitkamp T et~al. (2005) {X-ray phase imaging with a grating interferometer}.
-\newblock {\em Optics Express} 13:6296--6304.
-
-\bibitem{Thuering2013c}
-Thuering T et~al. (2013) {Energy resolved X-ray grating interferometry}.
-\newblock {\em Applied Physics Letters} 102:191113.
-
-\bibitem{Chabior2011a}
-Chabior M et~al. (2011) {Beam hardening effects in grating-based x-ray
-  phase-contrast imaging}.
-\newblock {\em Medical Physics} 38:1189.
-
-\bibitem{Grunzweig2008}
-Gr\"{u}nzweig C et~al. (2008) {Design, fabrication, and characterization of
-  diffraction gratings for neutron phase contrast imaging.}
-\newblock {\em The Review of scientific instruments} 79:053703.
-
-\bibitem{Raupach2011}
-Raupach R, Flohr TG (2011) {Analytical evaluation of the signal and noise
-  propagation in x-ray differential phase-contrast computed tomography.}
-\newblock {\em Physics in medicine and biology} 56:2219--2244.
-
-\end{thebibliography}
-\begin{thebibliography}{10}
-
-\bibitem{Als-Nielsen2011}
-Als-Nielsen J, McMorrow D (2011) {\em {Elements of modern X-ray physics}}.
-
-\bibitem{Qi2010}
-Qi Z, Zambelli J, Bevins N, Chen GH (2010) {Quantitative imaging of electron
-  density and effective atomic number using phase contrast CT.}
-\newblock {\em Physics in medicine and biology} 55:2669--77.
-
-\bibitem{Pfeiffer2007a}
-Pfeiffer F et~al. (2007) {High-resolution brain tumor visualization using
-  three-dimensional x-ray phase contrast tomography.}
-\newblock {\em Physics in medicine and biology} 52:6923--6930.
-
-\bibitem{McDonald2009}
-McDonald SA et~al. (2009) {Advanced phase-contrast imaging using a grating
-  interferometer}.
-\newblock {\em Journal of Synchrotron Radiation} 16:562--572.
-
-\bibitem{Davis1995}
-Davis T, Gao D, Gureyev T, Stevenson A, Wilkins S (1995) {Phase-contrast
-  imaging of weakly absorbing materials using hard X-rays}.
-\newblock {\em Nature} 373:595--598.
-
-\bibitem{Chapman1997}
-Chapman D et~al. (1997) {Diffraction enhanced x-ray imaging}.
-\newblock {\em Physics in Medicine and Biology} 42:2015--2025.
-
-\bibitem{Bonse1965}
-Bonse U, Hart M (1965) {An x-ray interferometer}.
-\newblock {\em Applied Physics Letters} 6:155--156.
-
-\bibitem{Momose1996}
-Momose A, Takeda T, Itai Y, Hirano K (1996) {Phase-contrast X-ray computed
-  tomography for observing biological soft tissues}.
-\newblock {\em Nature Medicine} 2:473--475.
-
-\bibitem{Snigirev1995}
-Snigirev A, Snigireva I, Kohn V, Kuznetsov S, Schelokov I (1995) {On the
-  possibilities of x-ray phase contrast microimaging by coherent high-energy
-  synchrotron radiation}.
-\newblock {\em Review of Scientific Instruments} 66:5486--5492.
-
-\bibitem{Wilkins1996}
-Wilkins S, Gureyev T, Gao D, Pogany A, Stevenson A (1996) {Phase-contrast
-  imaging using polychromatic hard X-rays}.
-\newblock {\em Nature} 384:335--338.
-
-\bibitem{Cloetens1996}
-Cloetens P, Barrett R, Baruchel J, Guigay J, Schlenker M (1996) {Phase objects
-  in synchrotron radiation hard x-ray imaging}.
-\newblock {\em Journal of Physics D: Applied Physics} 29:133--146.
-
-\bibitem{Cloetens1997}
-Cloetens P, Guigay J, {De Martino} C, Baruchel J, Schlenker M (1997)
-  {Fractional Talbot imaging of phase gratings with hard x rays.}
-\newblock {\em Optics letters} 22:1059--61.
-
-\bibitem{David2002}
-David C, N\"{o}hammer B, Solak H, Ziegler E (2002) {Differential x-ray phase
-  contrast imaging using a shearing interferometer}.
-\newblock {\em Applied Physics Letters} 81:3287--3289.
-
-\bibitem{Momose2003a}
-Momose A et~al. (2003) {Demonstration of X-Ray Talbot Interferometry}.
-\newblock {\em Japanese Journal of Applied Physics} 42:L866--L868.
-
-\bibitem{Munro2012}
-Munro P, Ignatyev K, Speller R, Olivo A (2012) {Phase and absorption retrieval
-  using incoherent X-ray sources}.
-\newblock {\em Proceedings of the National Academy of Sciences} 2012:2--7.
-
-\bibitem{Pfeiffer2006}
-Pfeiffer F, Weitkamp T, Bunk O, David C (2006) {Phase retrieval and
-  differential phase-contrast imaging with low-brilliance X-ray sources}.
-\newblock {\em Nature Physics} 2:258--261.
-
-\bibitem{Nesch2009}
-Nesch I et~al. (2009) {The design and application of an in-laboratory
-  diffraction-enhanced x-ray imaging instrument.}
-\newblock {\em The Review of scientific instruments} 80:093702.
-
-\bibitem{Parham2009}
-Parham C, Zhong Z, Connor DM, Chapman LD, Pisano ED (2009) {Design and
-  Implementation of a Compact Low-Dose Diffraction Enhanced Medical Imaging
-  System}.
-
-\bibitem{Pfeiffer2008}
-Pfeiffer F et~al. (2008) {Hard-X-ray dark-field imaging using a grating
-  interferometer}.
-\newblock {\em Nature Materials} 7:134--137.
-
-\bibitem{Willner2013}
-Willner M et~al. (2013) {Quantitative X-ray phase-contrast computed tomography
-  at 82 keV}.
-\newblock {\em Optics express} 21:4155--4166.
-
-\bibitem{Donath2009}
-Donath T et~al. (2009) {Inverse geometry for grating-based x-ray phase-contrast
-  imaging}.
-\newblock {\em Journal of Applied Physics} 106:054703.
-
-\bibitem{Mohr2012}
-Mohr J et~al. (2012) {High aspect ratio gratings for X-ray phase contrast
-  imaging}.
-\newblock 41:41--50.
-
-\bibitem{David2007}
-David C et~al. (2007) {Fabrication of diffraction gratings for hard X-ray phase
-  contrast imaging}.
-\newblock {\em Microelectronic Engineering} 84:1172--1177.
-
-\bibitem{Kenntner2010}
-Kenntner J et~al. (2010) {\em {Front- and backside structuring of gratings for
-  phase contrast imaging with x-ray tubes}}.
-\newblock Vol.{} 7804, p. 780408.
-
-\bibitem{Stutman2012a}
-Stutman D, Finkenthal M (2012) {Glancing angle Talbot-Lau grating
-  interferometers for phase contrast imaging at high x-ray energy}.
-\newblock {\em Applied physics letters} 101:91108.
-
-\bibitem{Aslund2007}
-{\AA slund, M} (2007) Ph.D. thesis.
-
-\bibitem{Oduko2010}
-Oduko JM, Young KC, Burch A (2010) in {\em Digital Mammography}, Lecture Notes
-  in Computer Science, eds.{} Martí J, Oliver A, Freixenet J, Martí R.
-\newblock (Springer Berlin Heidelberg) Vol.{} 6136, pp. 365--370.
-
-\bibitem{Weitkamp2005}
-Weitkamp T et~al. (2005) {X-ray phase imaging with a grating interferometer}.
-\newblock {\em Optics Express} 13:6296--6304.
-
-\bibitem{Thuering2013c}
-Thuering T et~al. (2013) {Energy resolved X-ray grating interferometry}.
-\newblock {\em Applied Physics Letters} 102:191113.
-
-\bibitem{Chabior2011a}
-Chabior M et~al. (2011) {Beam hardening effects in grating-based x-ray
-  phase-contrast imaging}.
-\newblock {\em Medical Physics} 38:1189.
-
-\bibitem{Grunzweig2008}
-Gr\"{u}nzweig C et~al. (2008) {Design, fabrication, and characterization of
-  diffraction gratings for neutron phase contrast imaging.}
-\newblock {\em The Review of scientific instruments} 79:053703.
-
-\bibitem{Raupach2011}
-Raupach R, Flohr TG (2011) {Analytical evaluation of the signal and noise
-  propagation in x-ray differential phase-contrast computed tomography.}
-\newblock {\em Physics in medicine and biology} 56:2219--2244.
-
-\end{thebibliography}
 \begin{thebibliography}{10}

### 2013-11-29 hedpc.tex
no siunitx

@@
 \usepackage{graphicx}  %figures
+\usepackage{upgreek}
+\usepackage{xspace}
 %\usepackage{pnastwof}
@@
 %% New commands
+\newcommand{\micro}{\ensuremath{\upmu}}
+\newcommand{\percent}{\%\xspace}
 \newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
 \renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
-\DeclareSIUnit{\voltpeak}{Vp}
 
@@
     to attenuation, refraction and scattering of the radiation. Applications
-    of this technique in the energy range between $80$ and
-    \SI{150}{\kilo\electronvolt} are still largely unexplored due to the
+    of this technique in the energy range between 80 and
+    150 keV are still largely unexplored due to the
     severe technical challenges. Phase-contrast X-ray imaging at such high
@@
     implementation of a Talbot-Lau interferometer operated at
-    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
-    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
+    100 keV using a conventional X-ray tube and a
+    compact geometry, with a total length of 54 cm. We
     present edge-on illumination of the gratings to overcome their current
@@
 Here we show a Talbot-Lau grating interferometer based on a novel optical
-design, enabling imaging at X-ray energies of~\SI{100}{\kilo\eV} and above
+design, enabling imaging at X-ray energies of~100 keV and above
 with a large field of view as well as a very compact and efficient geometry.
@@
 but only at energies up
-to the tungsten $K_\alpha$ line at~\SI{60}{\kilo\eV}.
+to the tungsten $K_\alpha$ line at~60 keV.
 In addition to phase sensitivity, analyzer-based and Talbot interferometry 
@@
 synchrotron source at nominal energies of
-$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013}.
+82 keV~\cite{Willner2013}.
 Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
-applied so far at $\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}.
+applied so far at 60 keV mean energy~\cite{Donath2009}.
 Medical imaging applications may benefit from phase contrast at higher
 energies: chest or abdominal
-radiography or CT require an acceleration voltage between \num{100} and
-$\SI{150}{\kilo\voltpeak}$. Other potential applications are homeland
+radiography or CT require an acceleration voltage between 100 and
+150 kVpeak. Other potential applications are homeland
 security or chip failure analysis, which require high energies for the
@@
 1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
-\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
+\propto E^{7/2}$~\cite{Momose2003a}. If at $E=25 keV$ an aspect ratio
 for the absorption grating around $\textnormal{R}=30$ is necessary for a
 reasonable length of the experimental arrangement, it would have to be at
-least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
+least $128$ for $E=100 keV$. Moreover, when using a
 broad spectrum, photons above the design energy should also be
@@
 current experiments, a symmetric interferometer with a grating period of $p
-= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
-is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
+= 2.8 \micro m$ for all gratings has been used. The design energy
+is 100 keV and the beam splitter grating periodically
 shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
 gold as the phase shifting material, a structure length of
-$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
+$h_1 = 19.8 \micro m$ is required. The analyzer grating is an absorption mask
 for sensing slight changes of the interference pattern generated by the beam
 splitter~\cite{Momose2003a}. With a structure length of $h_2 =
-\SI{800}{\micro \metre}$
+800 \micro m$
 it can sufficiently attenuate X-rays up to energies of 
-$\SI{160}{\kilo\electronvolt}$. Beam splitter and analyzer grating are
+160 keV. Beam splitter and analyzer grating are
 separated at the first fractional Talbot order~\cite{Weitkamp2005},
-resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
+resulting in an intergrating distance of 158 mm. The
 source grating splits the relatively large focal spot ($\sim
-\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
+1 mm$) into an array of individually coherent, but mutually
 incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
-with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
+with a length of $h_0 = h_2 = 800 \micro m$.
 
 Due to the high spectral acceptance~\cite{Weitkamp2005,Thuering2013c} of the
-interferometer ($\SI{50}{\kilo\electronvolt}$ to
-more than $\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
+interferometer (50 keV to
+more than 160 keV) and the high attenuation efficiencies of
 the source and analyzer gratings ($>90\%$ up to
-$\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
-the maximum of $\SI{160}{\kilo\volt}$. With a grating structure height of
-approximately $\SI{100}{\micro \metre}$, the field of view in the vertical
+160 keV), the voltage of the X-ray source was set to
+the maximum of 160 kV. With a grating structure height of
+approximately 100 \micro m, the field of view in the vertical
 direction is limited to one detector pixel row. In the horizontal direction,
 the field of view is only limited by the grating size to
-$\SI{30}{\milli\metre}$, but wider gratings can be fabricated with this
+30 mm, but wider gratings can be fabricated with this
 method and the available technology on larger wafers. In addition to the standard components (source,
@@
 on the chip. The images were acquired in scanning mode, using a step size of
-$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
+100 \micro m along the $y$ axis. For a better comparison of the
 magnified phase and attenuation images, the attenuation image has been
@@
 Edge-on illuminated grating interferometry finally allows phase contrast
-imaging to be performed at high energies ($>\SI{100}{\kilo\eV}$) on conventional X-ray
+imaging to be performed at high energies ($>100 keV$) on conventional X-ray
 sources. With a circular distribution of the gratings, the diffracting and
@@
 Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
-resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
+resides on a $5 \times 60 mm^2$ silicon chip and several
 grating chips are fabricated on a single 4 inch silicon wafer. The
-experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
+experimental arrangement for a design energy at 100 keV
 is a symmetric Talbot-Lau interferometer with a grating period of $p =
-\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
-grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
-grating is positioned $\SI{23}{\centi\metre}$ away from the source.
+2.8 \micro m$ for all gratings. The distance from the source
+grating to the analyzer grating is 32 cm and the source
+grating is positioned 23 cm away from the source.
 
 The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
-voltage of $\SI{160}{\kilo\volt}$. In the experiment, it was set to the
+voltage of 160 kV. In the experiment, it was set to the
 maximum voltage. The focal spot size is approximately
-$\SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
-Instruments. A cesium iodide (CsI:Ti) scintillator of $\SI{600}{\micro
-\metre}$ thickness converts the X-rays to visible light and is coupled with
+1 mm. The detector is a CCD camera from Finger Lakes
+Instruments. A cesium iodide (CsI:Ti) scintillator of 600 \micro m
+thickness converts the X-rays to visible light and is coupled with
 an optical lens projecting the image onto the CCD. The effective pixel size
-is $\SI{80}{\micro \metre}$. The collimating slit right after the source is 
-$\SI{25}{\micro \metre}$ large, while the second slit before the detector is
-$\SI{100}{\micro\metre}$.
+is 80 \micro m. The collimating slit right after the source is 
+25 \micro m large, while the second slit before the detector is
+100 \micro m.
 
@@
 exposure times are mostly constrained by the low average visibility of the
-gratings (\SI{5}{\percent}). The exposure time was chosen in order to
+gratings (5 \percent). The exposure time was chosen in order to
 get a low noise in the differential phase image. The SNR is
@@
 Smaller regions of these gratings actually exhibit a visibility up
-to~\SI{14}{\percent} already, indicating that this goal is reachable as the
+to~14 \percent already, indicating that this goal is reachable as the
 fabrication becomes more reliable and uniform.
@@
         interferometer for X-ray energies between 60 and
-        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
+        150 keV in edge-on illumination mode. The
         aspect ratio is defined by the ratio of the travelling distance along the
@@
     \caption{Radiographic scan of an electronic chip. The image was acquired
-        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
+        with 24 phase steps per line and an exposure time of 15 s per
     step. The top right image shows the differential absorption image.}

### 2013-11-29 hedpc.tex
restored siunitx with scriptscriptsize in the methods section

--- 2013-11-29 hedpc.tex
@@
 \usepackage{graphicx}  %figures
+\usepackage[detect-all]{siunitx}
 %\usepackage{pnastwof}
+
+\DeclareMathSizes{10}{18}{12}{7}
 
@@
 Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
-resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
+resides on a $\scriptscriptstyle 5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
 grating chips are fabricated on a single 4 inch silicon wafer. The
-experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
-is a symmetric Talbot-Lau interferometer with a grating period of $p =
-\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
-grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
-grating is positioned $\SI{23}{\centi\metre}$ away from the source.
+experimental arrangement for a design energy at $\scriptscriptstyle
+\SI{100}{\kilo\electronvolt}$
+is a symmetric Talbot-Lau interferometer with a grating period of $\scriptscriptstyle p = \SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
+grating to the analyzer grating is $\scriptscriptstyle \SI{32}{\centi\metre}$ and the source
+grating is positioned $\scriptscriptstyle \SI{23}{\centi\metre}$ away from the source.
 
 The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
-voltage of $\SI{160}{\kilo\volt}$. In the experiment, it was set to the
+voltage of $\scriptscriptstyle \SI{160}{\kilo\volt}$. In the experiment, it was set to the
 maximum voltage. The focal spot size is approximately
-$\SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
-Instruments. A cesium iodide (CsI:Ti) scintillator of $\SI{600}{\micro
+$\scriptscriptstyle \SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
+Instruments. A cesium iodide (CsI:Ti) scintillator of $\scriptscriptstyle \SI{600}{\micro
 \metre}$ thickness converts the X-rays to visible light and is coupled with
 an optical lens projecting the image onto the CCD. The effective pixel size
-is $\SI{80}{\micro \metre}$. The collimating slit right after the source is 
-$\SI{25}{\micro \metre}$ large, while the second slit before the detector is
-$\SI{100}{\micro\metre}$.
+is $\scriptscriptstyle \SI{80}{\micro \metre}$. The collimating slit right after the source is 
+$\scriptscriptstyle \SI{25}{\micro \metre}$ large, while the second slit before the detector is
+$\scriptscriptstyle \SI{100}{\micro\metre}$.
 
@@
 exposure times are mostly constrained by the low average visibility of the
-gratings (\SI{5}{\percent}). The exposure time was chosen in order to
+gratings ($\scriptscriptstyle \SI{5}{\percent}$). The exposure time was chosen in order to
 get a low noise in the differential phase image. The SNR is
@@
 Smaller regions of these gratings actually exhibit a visibility up
-to~\SI{14}{\percent} already, indicating that this goal is reachable as the
+to~$\scriptscriptstyle \SI{14}{\percent}$ already, indicating that this goal is reachable as the
 fabrication becomes more reliable and uniform.
@@
 issues, Christian Kottler and Vincent Revol from Centre Suisse
-d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
+d'\'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
 discussions on the design of the system. This work has been partially

### 2013-11-29 hedpc.tex
new cover letter, added medical imaging keyword, fixed thomas name

@@
 
-\author{T.~Thüring%
+\author{T.~Thuering%
 \affil{1}{Paul Scherrer Institute, 5232 Villigen, Switzerland}%
@@
     Gloriastrasse 35,
-8092 Zurich, Switzerland},%
+8092 Zurich, Switzerland},
 M.~Abis%%
 \affil{1}{}%
-\affil{2}{},%
+\affil{2}{},
 Z.~Wang%
-\affil{1}{},%
+\affil{1}{},
 C.~David%
-\affil{1}{},%
+\affil{1}{},
 \and%
@@
 %% When adding keywords, separate each term with a straight line: |
-\keywords{X-ray phase contrast | grating interferometry | X-ray interferometry}
+\keywords{X-ray phase contrast | grating interferometry | X-ray
+interferometry | medical imaging}
 

### 2013-12-16 hedpc.tex
typo
pnas last version, starting SR version
Initial SR quality check
- bibliography format
- author contributions
- financial interest statement

--- 2013-11-29 hedpc.tex
@@
-\documentclass{pnastwo}
+%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
+%% for review and submission
+%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}
+% for double-spaced preprint
+%\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}
+%for review and submission
+\documentclass[english]{nature} 
+% for double-spaced preprint
+%\documentclass[aip,apl,amsmath,amssymb,floatfix,preprint,a4paper]{revtex4-1}
+%\documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}
 
@@
 \usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{amssymb,amsfonts,amsmath}
+\usepackage[utf8]{inputenc} %Umlaute
+\usepackage{babel}
+\usepackage{acronym}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage[bf,small,labelsep=period]{caption}
 \usepackage{graphicx}  %figures
 \usepackage[detect-all]{siunitx}
-%\usepackage{pnastwof}
-
-\DeclareMathSizes{10}{18}{12}{7}
+\usepackage[affil-it]{authblk}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Don't type in anything in the following section:
-%%%%%%%%%%%%
-%% For PNAS Only:
-\contributor{Submitted to Proceedings
-of the National Academy of Sciences of the United States of America}
-\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
-\copyrightyear{2008}
-\issuedate{Issue Date}
-\volume{Volume}
-\issuenumber{Issue Number}
-%%%%%%%%%%%%
-\footlineauthor{ Corresponding author:
-    M. Abis, 
-    matteo.abis@psi.ch
-}
+%acronyms
+\acrodef{CT}{computed tomography}
+\acrodef{SNR}{signal-to-noise ratio}
+\acrodef{CNR}{contrast-to-noise ratio}
+\acrodef{SEM}{scanning electron microscope}
+%% ----------------------------------------------------------------------------------------------------------------
 
@@
 
-\title{X-ray phase-contrast imaging at 100 keV on a conventional source}
+\title{X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on
+a conventional source}
 
-\author{T.~Thüring%
-\affil{1}{Paul Scherrer Institute, 5232 Villigen, Switzerland}%
-\affil{2}{Institute for Biomedical Engineering,
-    Swiss Federal Institute of Technology,
-    Gloriastrasse 35,
-8092 Zurich, Switzerland},%
-M.~Abis%%
-\affil{1}{}%
-\affil{2}{},%
-Z.~Wang%
-\affil{1}{},%
-C.~David%
-\affil{1}{},%
-\and%
-M.~Stampanoni%
-\affil{1}{}%
-\affil{2}{}}
+\author[1,2]{T.~Thüring}
+\author[1,2]{M.~Abis}
+\author[1]{Z.~Wang}
+\author[1]{C.~David}
+\author[1,2]{M.~Stampanoni}
+\affil[1]{Paul Scherrer Institute, Villigen PSI, Switzerland}
+\affil[2]{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
 
-\contributor{Submitted to Proceedings of the National Academy of Sciences
-of the United States of America}
+\date{\today}
 
-%% The \maketitle command is necessary to build the title page.
 \maketitle
 
-\begin{article}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Body of manuscript
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%% ----------------------------------------------------------------------------------------------------------------
 \begin{abstract}
@@
     to attenuation, refraction and scattering of the radiation. Applications
-    of this technique in the energy range between 80 and
-    150 keV are still largely unexplored due to the
+    of this technique in the energy range between $\num{80}$ and
+    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
     severe technical challenges. Phase-contrast X-ray imaging at such high
@@
     implementation of a Talbot-Lau interferometer operated at
-    100 keV using a conventional X-ray tube and a
-    compact geometry, with a total length of 54 cm. We
+    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
+    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
     present edge-on illumination of the gratings to overcome their current
@@
 
-%% When adding keywords, separate each term with a straight line: |
-\keywords{X-ray phase contrast | grating interferometry | X-ray interferometry}
-
-%% Optional for entering abbreviations, separate the abbreviation from
-%% its definition with a comma, separate each pair with a semicolon:
-%% for example:
-%% \abbreviations{SAM, self-assembled monolayer; OTS,
-%% octadecyltrichlorosilane}
-
-\abbreviations{
-%acronyms
-CT, computed tomography;
-SNR, signal-to-noise ratio;
-CNR, contrast-to-noise ratio;
-SEM, scanning electron microscope;
-}
-%% ----------------------------------------------------------------------------------------------------------------
-%% The first letter of the article should be drop cap: \dropcap{}
-%\dropcap{I}n this article we study the evolution of ''almost-sharp'' fronts
-
-\section{Significance statement}
-
-Phase sensitive X-ray imaging techniques provide access to new and
-invaluable information compared to traditional absorption-based radiography
-and tomography.
-
-Here we show a Talbot-Lau grating interferometer based on a novel optical
-design, enabling imaging at X-ray energies of~\SI{100}{\kilo\eV} and above
-with a large field of view as well as a very compact and efficient geometry.
-
-Our results demonstrate, for the first time, that phase contrast X-ray
-imaging can be successfully performed at diagnostically relevant energies
-using a conventional X-ray tube, with potential applications spanning from
-medical imaging to nondestructive testing or homeland security.
-
-\section{}
-\dropcap{X}-ray radiography and CT are standard imaging techniques in
+X-ray radiography and \ac{CT} are standard imaging techniques in
 materials and life sciences for the nondestructive examination of samples or
@@
 
-The attenuation and phase shift properties are described by the complex index of refraction
-$n=1-\delta + i \beta$.
-The imaginary part $\beta$ is related to the
-attenuation coefficient by $\mu = 4 \pi
-\beta(\lambda) / \lambda$, while the real part
-$\delta(\lambda)$ determines the phase shift 
-$\phi = 2 \pi \delta(\lambda) / \lambda$
+The attenuation and phase shift properties are described by the complex
+index of refraction $n=1 - \delta + i \beta$. The imaginary part $\beta$ is
+related to the attenuation coefficient by $\mu = 4 \pi \beta(\lambda) /
+\lambda$, while the real part $\delta(\lambda)$ determines the phase shift
+$\phi = 2 \pi \delta(\lambda) / \lambda$.
 
-While the attenuation can be measured with an
-X-ray detector as the reduction of the beam intensity, the phase
-is not directly observable. Therefore, an optical system is needed to
-convert the phase shift into intensity modulations.
+While the attenuation can be measured with an X-ray detector as the
+reduction of the beam intensity, the phase is not directly observable.
+Therefore, an optical system is needed to convert the phase shift into
+intensity modulations.
 
-Phase-sensitive
-imaging is a desirable modality, as it delivers a complementary source of
-contrast with respect to absorption by providing direct access 
-to the electron density~\cite{Als-Nielsen2011}. Moreover, the combination with
-attenuation enables the determination of the effective atomic
-number~\cite{Qi2010}.
-An enhanced
-CNR in images compared to attenuation for certain
-materials or tissues~\cite{Pfeiffer2007a,McDonald2009} has also been
-demonstrated.
+Phase-sensitive imaging is a desirable modality, as it delivers a
+complementary source of contrast with respect to absorption by providing
+direct access to the electron density~\cite{Als-Nielsen2011}. Moreover, the
+combination with attenuation enables the determination of the effective
+atomic number~\cite{Qi2010}. An enhanced \ac{CNR} in images compared to
+attenuation for certain materials or
+tissues~\cite{Pfeiffer2007a,McDonald2009} has also been demonstrated.
 
 The vast majority of phase-sensitive techniques, including crystal analyzer
-based~\cite{Davis1995,Chapman1997} or interferometric~\cite{Bonse1965,Momose1996}
-methods rely on X-ray beams of high spatial and temporal coherence, which is
-available only at synchrotron sources. Inline
-phase contrast~\cite{Snigirev1995,Wilkins1996,Cloetens1996} and
-Talbot interferometry~\cite{Cloetens1997,David2002,Momose2003a} need high
-spatial coherence but are available on polychromatic microfocus sources.
-Phase-contrast imaging using X-ray beams of low temporal \emph{and}
+based~\cite{Davis1995,Chapman1997} or
+interferometric~\cite{Bonse1965,Momose1996} methods rely on X-ray beams of
+high spatial and temporal coherence, which is available only at synchrotron
+sources. Inline phase contrast~\cite{Snigirev1995,Wilkins1996,Cloetens1996}
+and Talbot interferometry~\cite{Cloetens1997,David2002,Momose2003a} need
+high spatial coherence but are available on polychromatic microfocus
+sources. Phase-contrast imaging using X-ray beams of low temporal \emph{and}
 spatial coherence such as conventional low-brilliance X-ray tubes have been
-demonstrated with coded
-apertures~\cite{Munro2012} and Talbot-Lau
+demonstrated with coded apertures~\cite{Munro2012} and Talbot-Lau
 interferometry~\cite{Pfeiffer2006}. Analyzer-based systems have been
-recently extended to tube sources~\cite{Nesch2009,Parham2009}
-but only at energies up
-to the tungsten $K_\alpha$ line at~\SI{60}{\kilo\eV}.
-In addition to phase sensitivity, analyzer-based and Talbot interferometry 
-approaches also provide (with different retrieval mechanisms)
-information about the integrated local small angle scattering power from
-microscopic density fluctuations in a specimen~\cite{Pfeiffer2008}. This signal is known under the name of dark-field, scatter or visibility reduction contrast.
+recently extended to tube sources~\cite{Nesch2009,Parham2009} but only at
+energies up to the tungsten $K_\alpha$ line at~\SI{60}{\kilo\eV}. In
+addition to phase sensitivity, analyzer-based and Talbot interferometry
+approaches also provide (with different retrieval mechanisms) information
+about the integrated local small angle scattering power from microscopic
+density fluctuations in a specimen~\cite{Pfeiffer2008}. This signal is known
+under the name of dark-field, scatter or visibility reduction contrast.
 
@@
 synchrotron source at nominal energies of
-$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013}.
-Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
-applied so far at $\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}.
-Medical imaging applications may benefit from phase contrast at higher
-energies: chest or abdominal
-radiography or CT require an acceleration voltage between \num{100} and
-$\SI{150}{\kilo\voltpeak}$. Other potential applications are homeland
-security or chip failure analysis, which require high energies for the
-visualization of materials of high density and atomic number.
+$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013}. Using a low-brilliance
+X-ray tube, Talbot-Lau interferometry was applied so far at
+$\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}. Medical imaging
+applications may benefit from phase contrast at higher energies: chest or
+abdominal radiography or \ac{CT} require an acceleration voltage between
+\num{100} and $\SI{150}{\kilo\voltpeak}$. Other potential applications are
+homeland security or chip failure analysis, which require high energies for
+the visualization of materials of high density and atomic number.
 
@@
 and is compatible with compact imaging arrangements. The approach is based
-on
-Talbot-Lau
-interferometry~\cite{Pfeiffer2006} and employs an edge-on illumination approach for the grating design and
-arrangement. 
-Our solution removes one on the major hurdle which prevented grating interferometry to be applied at very high X-ray energies so far, namely the fabrication of gratings with high-aspect ratios.
- The aspect
-ratio, given by
-\begin{equation}
-    \text{R} = \frac{2h}{p},
-\end{equation}
-where $p$ is the grating period and $h$ the  structure
-height, is normally limited by the fabrication process, usually
-photolithography~\cite{David2002} or X-ray lithography~\cite{Mohr2012} as grating
-structures tend to collapse or deform (e.g. due to capillary forces) if
-the aspect ratio is too high. For a given setup length these parameters
-depend on the target energy $E$ according to $p \propto
-1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
-\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
-for the absorption grating around $\textnormal{R}=30$ is necessary for a
-reasonable length of the experimental arrangement, it would have to be at
-least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
-broad spectrum, photons above the design energy should also be
-efficiently blocked by the gratings, which requires even higher aspect ratios.
-The largest aspect ratios achieved by current fabrication techniques~\cite{David2007,Kenntner2010} are around 60.
+on Talbot-Lau interferometry~\cite{Pfeiffer2006} and employs an edge-on
+illumination approach for the grating design and arrangement. Our solution
+removes one on the major hurdle which prevented grating interferometry to be
+applied at very high X-ray energies so far, namely the fabrication of
+gratings with high-aspect ratios. The aspect ratio, given by
+\begin{equation} \text{R} = \frac{2h}{p}, \end{equation} where $p$ is the
+grating period and $h$ the  structure height, is normally limited by the
+fabrication process, usually photolithography~\cite{David2002} or X-ray
+lithography~\cite{Mohr2012} as grating structures tend to collapse or deform
+(e.g.\ due to capillary forces) if the aspect ratio is too high. For a given
+setup length these parameters depend on the target energy $E$ according to
+$p \propto 1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
+\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$
+an aspect ratio for the absorption grating around $\textnormal{R}=30$ is
+necessary for a reasonable length of the experimental arrangement, it would
+have to be at least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover,
+when using a broad spectrum, photons above the design energy should also be
+efficiently blocked by the gratings, which requires even higher aspect
+ratios. The largest aspect ratios achieved by current fabrication
+techniques~\cite{David2007,Kenntner2010} are around 60.
 
@@
 aspect ratios. 
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=.7\textwidth]{figures/figure1.eps}
+    \caption{Schematic of a grating
+        interferometer for X-ray energies between 60 and
+        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
+        aspect ratio is defined by the ratio of the travelling distance along the
+        grating lines and the period and can be arbitrarily long. In order to maximise
+        the field of view, the grating structures are aligned on an
+    arc.}%
+\label{Fig:schematic}
+\end{figure}
 
@@
 Similarly, for tomographic images,
-the approach allows single slice CT or full 3D imaging in scanning mode.
+the approach allows single slice \ac{CT} or full 3D imaging in scanning mode.
 
@@
 with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
+    \caption{Grating design mask for
+        the edge-on illumination approach and \ac{SEM}
+        image of the grating. The top part of the 4 inch wafer shows
+        five grating chips. The
+        gratings have different curvatures which are specific to the grating
+        interferometer geometry. 
+        The \ac{SEM} image shows the gold structures and the interrupting bridges
+        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}\label{Fig:grating_mask}
+\end{figure}
 
@@
 
-\section{Results and discussion}
 Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
@@
 structures such as electronic chips.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
+    \caption{Radiographic scan of an electronic chip. The image was acquired
+        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
+    step. The top right image shows the differential absorption image.}\label{Fig:img_chip}
+\end{figure}
 
@@
 
-%% == end of paper:
-
-%% Optional Materials and Methods Section
-%% The Materials and Methods section header will be added automatically.
-
-%% Enter any subheads and the Materials and Methods text below.
-\begin{materials}
+\section*{Methods}
 Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
-resides on a $\scriptscriptstyle 5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
+resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
 grating chips are fabricated on a single 4 inch silicon wafer. The
-experimental arrangement for a design energy at $\scriptscriptstyle
-\SI{100}{\kilo\electronvolt}$
-is a symmetric Talbot-Lau interferometer with a grating period of $\scriptscriptstyle p = \SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
-grating to the analyzer grating is $\scriptscriptstyle \SI{32}{\centi\metre}$ and the source
-grating is positioned $\scriptscriptstyle \SI{23}{\centi\metre}$ away from the source.
+experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
+is a symmetric Talbot-Lau interferometer with a grating period of $p =
+\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
+grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
+grating is positioned $\SI{23}{\centi\metre}$ away from the source.
 
 The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
-voltage of $\scriptscriptstyle \SI{160}{\kilo\volt}$. In the experiment, it was set to the
+voltage of $\SI{160}{\kilo\volt}$. In the experiment, it was set to the
 maximum voltage. The focal spot size is approximately
-$\scriptscriptstyle \SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
-Instruments. A cesium iodide (CsI:Ti) scintillator of $\scriptscriptstyle \SI{600}{\micro
+$\SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
+Instruments. A cesium iodide (CsI:Ti) scintillator of $\SI{600}{\micro
 \metre}$ thickness converts the X-rays to visible light and is coupled with
-an optical lens projecting the image onto the CCD. The effective pixel size
-is $\scriptscriptstyle \SI{80}{\micro \metre}$. The collimating slit right after the source is 
-$\scriptscriptstyle \SI{25}{\micro \metre}$ large, while the second slit before the detector is
-$\scriptscriptstyle \SI{100}{\micro\metre}$.
+an optical lens projecting the image onto the CCD\@. The effective pixel size
+is $\SI{80}{\micro\metre}$. The collimating slit right after the source is 
+$\SI{25}{\micro\metre}$ large, while the second slit before the detector is
+$\SI{100}{\micro\metre}$.
 
@@
 exposure times are mostly constrained by the low average visibility of the
-gratings ($\scriptscriptstyle \SI{5}{\percent}$). The exposure time was chosen in order to
-get a low noise in the differential phase image. The SNR is
+gratings (\SI{5}{\percent}). The exposure time was chosen in order to
+get a low noise in the differential phase image. The \ac{SNR} is
 proportional to the visibility and the square root of the exposure
@@
 Smaller regions of these gratings actually exhibit a visibility up
-to~$\scriptscriptstyle \SI{14}{\percent}$ already, indicating that this goal is reachable as the
+to~\SI{14}{\percent} already, indicating that this goal is reachable as the
 fabrication becomes more reliable and uniform.
-\end{materials}
 
-%% Optional Appendix or Appendices
-%% \appendix Appendix text...
-%% or, for appendix with title, use square brackets:
-%% \appendix[Appendix Title]
-
-\begin{acknowledgments}
+\section*{Acknowledgements}
 We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
 Scherrer Institute (PSI), Switzerland, for the
-work on the mechanical design, the scientific advice, and the SEM images
+work on the mechanical design, the scientific advice, and the \ac{SEM} images
 respectively, Joachim Schulz and Marco Walter from
@@
 issues, Christian Kottler and Vincent Revol from Centre Suisse
-d'\'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
+d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
 discussions on the design of the system. This work has been partially
@@
 (CCMX) of the ETH Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.
-\end{acknowledgments}
 
-%% PNAS does not support submission of supporting .tex files such as BibTeX.
-%% Instead all references must be included in the article .tex document. 
-%% If you currently use BibTeX, your bibliography is formed because the 
-%% command \verb+\bibliography{}+ brings the <filename>.bbl file into your
-%% .tex document. To conform to PNAS requirements, copy the reference listings
-%% from your .bbl file and add them to the article .tex file, using the
-%% bibliography environment described above.
+\section*{Competing financial interests}
+The authors declare no competing financial interests.
 
-%%  Contact pnas@nas.edu if you need assistance with your
-%%  bibliography.
-
-% Sample bibliography item in PNAS format:
-%% \bibitem{in-text reference} comma-separated author names up to 5,
-%% for more than 5 authors use first author last name et al. (year published)
-%% article title  {\it Journal Name} volume #: start page-end page.
-%% ie,
-% \bibitem{Neuhaus} Neuhaus J-M, Sitcher L, Meins F, Jr, Boller T (1991) 
-% A short C-terminal sequence is necessary and sufficient for the
-% targeting of chitinases to the plant vacuole. 
-% {\it Proc Natl Acad Sci USA} 88:10362-10366.
-
-%\bibliographystyle{pnas}
+%\bibliographystyle{naturemag-nourl}
 %\bibliography{library}
 \begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\providecommand{\bibinfo}[2]{#2}
+\providecommand{\eprint}[2][]{\url{#2}}
 
 \bibitem{Als-Nielsen2011}
-Als-Nielsen J, McMorrow D (2011) {\em {Elements of modern X-ray physics}}.
+\bibinfo{author}{Als-Nielsen, J.} \& \bibinfo{author}{McMorrow, D.}
+\newblock \emph{\bibinfo{title}{{Elements of modern X-ray physics}}}
+  (\bibinfo{year}{2011}).
 
 \bibitem{Qi2010}
-Qi Z, Zambelli J, Bevins N, Chen GH (2010) {Quantitative imaging of electron
-  density and effective atomic number using phase contrast CT.}
-\newblock {\em Physics in medicine and biology} 55:2669--77.
+\bibinfo{author}{Qi, Z.}, \bibinfo{author}{Zambelli, J.},
+  \bibinfo{author}{Bevins, N.} \& \bibinfo{author}{Chen, G.-H.}
+\newblock \bibinfo{title}{{Quantitative imaging of electron density and
+  effective atomic number using phase contrast CT.}}
+\newblock \emph{\bibinfo{journal}{Physics in medicine and biology}}
+  \textbf{\bibinfo{volume}{55}}, \bibinfo{pages}{2669--77}
+  (\bibinfo{year}{2010}).
 
 \bibitem{Pfeiffer2007a}
-Pfeiffer F et~al. (2007) {High-resolution brain tumor visualization using
-  three-dimensional x-ray phase contrast tomography.}
-\newblock {\em Physics in medicine and biology} 52:6923--6930.
+\bibinfo{author}{Pfeiffer, F.} \emph{et~al.}
+\newblock \bibinfo{title}{{High-resolution brain tumor visualization using
+  three-dimensional x-ray phase contrast tomography.}}
+\newblock \emph{\bibinfo{journal}{Physics in medicine and biology}}
+  \textbf{\bibinfo{volume}{52}}, \bibinfo{pages}{6923--6930}
+  (\bibinfo{year}{2007}).
 
 \bibitem{McDonald2009}
-McDonald SA et~al. (2009) {Advanced phase-contrast imaging using a grating
-  interferometer}.
-\newblock {\em Journal of Synchrotron Radiation} 16:562--572.
+\bibinfo{author}{McDonald, S.~A.} \emph{et~al.}
+\newblock \bibinfo{title}{{Advanced phase-contrast imaging using a grating
+  interferometer}}.
+\newblock \emph{\bibinfo{journal}{Journal of Synchrotron Radiation}}
+  \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{562--572}
+  (\bibinfo{year}{2009}).
 
 \bibitem{Davis1995}
-Davis T, Gao D, Gureyev T, Stevenson A, Wilkins S (1995) {Phase-contrast
-  imaging of weakly absorbing materials using hard X-rays}.
-\newblock {\em Nature} 373:595--598.
+\bibinfo{author}{Davis, T.}, \bibinfo{author}{Gao, D.},
+  \bibinfo{author}{Gureyev, T.}, \bibinfo{author}{Stevenson, A.} \&
+  \bibinfo{author}{Wilkins, S.}
+\newblock \bibinfo{title}{{Phase-contrast imaging of weakly absorbing materials
+  using hard X-rays}}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{373}},
+  \bibinfo{pages}{595--598} (\bibinfo{year}{1995}).
 
 \bibitem{Chapman1997}
-Chapman D et~al. (1997) {Diffraction enhanced x-ray imaging}.
-\newblock {\em Physics in Medicine and Biology} 42:2015--2025.
+\bibinfo{author}{Chapman, D.} \emph{et~al.}
+\newblock \bibinfo{title}{{Diffraction enhanced x-ray imaging}}.
+\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
+  \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{2015--2025}
+  (\bibinfo{year}{1997}).
 
 \bibitem{Bonse1965}
-Bonse U, Hart M (1965) {An x-ray interferometer}.
-\newblock {\em Applied Physics Letters} 6:155--156.
+\bibinfo{author}{Bonse, U.} \& \bibinfo{author}{Hart, M.}
+\newblock \bibinfo{title}{{An x-ray interferometer}}.
+\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
+  \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{155--156}
+  (\bibinfo{year}{1965}).
 
 \bibitem{Momose1996}
-Momose A, Takeda T, Itai Y, Hirano K (1996) {Phase-contrast X-ray computed
-  tomography for observing biological soft tissues}.
-\newblock {\em Nature Medicine} 2:473--475.
+\bibinfo{author}{Momose, A.}, \bibinfo{author}{Takeda, T.},
+  \bibinfo{author}{Itai, Y.} \& \bibinfo{author}{Hirano, K.}
+\newblock \bibinfo{title}{{Phase-contrast X-ray computed tomography for
+  observing biological soft tissues}}.
+\newblock \emph{\bibinfo{journal}{Nature Medicine}}
+  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{473--475}
+  (\bibinfo{year}{1996}).
 
 \bibitem{Snigirev1995}
-Snigirev A, Snigireva I, Kohn V, Kuznetsov S, Schelokov I (1995) {On the
-  possibilities of x-ray phase contrast microimaging by coherent high-energy
-  synchrotron radiation}.
-\newblock {\em Review of Scientific Instruments} 66:5486--5492.
+\bibinfo{author}{Snigirev, A.}, \bibinfo{author}{Snigireva, I.},
+  \bibinfo{author}{Kohn, V.}, \bibinfo{author}{Kuznetsov, S.} \&
+  \bibinfo{author}{Schelokov, I.}
+\newblock \bibinfo{title}{{On the possibilities of x-ray phase contrast
+  microimaging by coherent high-energy synchrotron radiation}}.
+\newblock \emph{\bibinfo{journal}{Review of Scientific Instruments}}
+  \textbf{\bibinfo{volume}{66}}, \bibinfo{pages}{5486--5492}
+  (\bibinfo{year}{1995}).
 
 \bibitem{Wilkins1996}
-Wilkins S, Gureyev T, Gao D, Pogany A, Stevenson A (1996) {Phase-contrast
-  imaging using polychromatic hard X-rays}.
-\newblock {\em Nature} 384:335--338.
+\bibinfo{author}{Wilkins, S.}, \bibinfo{author}{Gureyev, T.},
+  \bibinfo{author}{Gao, D.}, \bibinfo{author}{Pogany, A.} \&
+  \bibinfo{author}{Stevenson, A.}
+\newblock \bibinfo{title}{{Phase-contrast imaging using polychromatic hard
+  X-rays}}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{384}},
+  \bibinfo{pages}{335--338} (\bibinfo{year}{1996}).
 
 \bibitem{Cloetens1996}
-Cloetens P, Barrett R, Baruchel J, Guigay J, Schlenker M (1996) {Phase objects
-  in synchrotron radiation hard x-ray imaging}.
-\newblock {\em Journal of Physics D: Applied Physics} 29:133--146.
+\bibinfo{author}{Cloetens, P.}, \bibinfo{author}{Barrett, R.},
+  \bibinfo{author}{Baruchel, J.}, \bibinfo{author}{Guigay, J.} \&
+  \bibinfo{author}{Schlenker, M.}
+\newblock \bibinfo{title}{{Phase objects in synchrotron radiation hard x-ray
+  imaging}}.
+\newblock \emph{\bibinfo{journal}{Journal of Physics D: Applied Physics}}
+  \textbf{\bibinfo{volume}{29}}, \bibinfo{pages}{133--146}
+  (\bibinfo{year}{1996}).
 
 \bibitem{Cloetens1997}
-Cloetens P, Guigay J, {De Martino} C, Baruchel J, Schlenker M (1997)
-  {Fractional Talbot imaging of phase gratings with hard x rays.}
-\newblock {\em Optics letters} 22:1059--61.
+\bibinfo{author}{Cloetens, P.}, \bibinfo{author}{Guigay, J.},
+  \bibinfo{author}{{De Martino}, C.}, \bibinfo{author}{Baruchel, J.} \&
+  \bibinfo{author}{Schlenker, M.}
+\newblock \bibinfo{title}{{Fractional Talbot imaging of phase gratings with
+  hard x rays.}}
+\newblock \emph{\bibinfo{journal}{Optics letters}}
+  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{1059--61}
+  (\bibinfo{year}{1997}).
 
 \bibitem{David2002}
-David C, N\"{o}hammer B, Solak H, Ziegler E (2002) {Differential x-ray phase
-  contrast imaging using a shearing interferometer}.
-\newblock {\em Applied Physics Letters} 81:3287--3289.
+\bibinfo{author}{David, C.}, \bibinfo{author}{N\"{o}hammer, B.},
+  \bibinfo{author}{Solak, H.} \& \bibinfo{author}{Ziegler, E.}
+\newblock \bibinfo{title}{{Differential x-ray phase contrast imaging using a
+  shearing interferometer}}.
+\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
+  \textbf{\bibinfo{volume}{81}}, \bibinfo{pages}{3287--3289}
+  (\bibinfo{year}{2002}).
 
 \bibitem{Momose2003a}
-Momose A et~al. (2003) {Demonstration of X-Ray Talbot Interferometry}.
-\newblock {\em Japanese Journal of Applied Physics} 42:L866--L868.
+\bibinfo{author}{Momose, A.} \emph{et~al.}
+\newblock \bibinfo{title}{{Demonstration of X-Ray Talbot Interferometry}}.
+\newblock \emph{\bibinfo{journal}{Japanese Journal of Applied Physics}}
+  \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{L866--L868}
+  (\bibinfo{year}{2003}).
 
 \bibitem{Munro2012}
-Munro P, Ignatyev K, Speller R, Olivo A (2012) {Phase and absorption retrieval
-  using incoherent X-ray sources}.
-\newblock {\em Proceedings of the National Academy of Sciences} 2012:2--7.
+\bibinfo{author}{Munro, P.}, \bibinfo{author}{Ignatyev, K.},
+  \bibinfo{author}{Speller, R.} \& \bibinfo{author}{Olivo, A.}
+\newblock \bibinfo{title}{{Phase and absorption retrieval using incoherent
+  X-ray sources}}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+  Sciences}} \textbf{\bibinfo{volume}{2012}}, \bibinfo{pages}{2--7}
+  (\bibinfo{year}{2012}).
 
 \bibitem{Pfeiffer2006}
-Pfeiffer F, Weitkamp T, Bunk O, David C (2006) {Phase retrieval and
-  differential phase-contrast imaging with low-brilliance X-ray sources}.
-\newblock {\em Nature Physics} 2:258--261.
+\bibinfo{author}{Pfeiffer, F.}, \bibinfo{author}{Weitkamp, T.},
+  \bibinfo{author}{Bunk, O.} \& \bibinfo{author}{David, C.}
+\newblock \bibinfo{title}{{Phase retrieval and differential phase-contrast
+  imaging with low-brilliance X-ray sources}}.
+\newblock \emph{\bibinfo{journal}{Nature Physics}}
+  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{258--261}
+  (\bibinfo{year}{2006}).
 
 \bibitem{Nesch2009}
-Nesch I et~al. (2009) {The design and application of an in-laboratory
-  diffraction-enhanced x-ray imaging instrument.}
-\newblock {\em The Review of scientific instruments} 80:093702.
+\bibinfo{author}{Nesch, I.} \emph{et~al.}
+\newblock \bibinfo{title}{{The design and application of an in-laboratory
+  diffraction-enhanced x-ray imaging instrument.}}
+\newblock \emph{\bibinfo{journal}{The Review of scientific instruments}}
+  \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{093702}
+  (\bibinfo{year}{2009}).
 
 \bibitem{Parham2009}
-Parham C, Zhong Z, Connor DM, Chapman LD, Pisano ED (2009) {Design and
-  Implementation of a Compact Low-Dose Diffraction Enhanced Medical Imaging
-  System}.
+\bibinfo{author}{Parham, C.}, \bibinfo{author}{Zhong, Z.},
+  \bibinfo{author}{Connor, D.~M.}, \bibinfo{author}{Chapman, L.~D.} \&
+  \bibinfo{author}{Pisano, E.~D.}
+\newblock \bibinfo{title}{Design and implementation of a compact low-dose
+  diffraction enhanced medical imaging system}.
+\newblock \emph{\bibinfo{journal}{Academic Radiology}}
+  \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{911 -- 917}
+  (\bibinfo{year}{2009}).
 
 \bibitem{Pfeiffer2008}
-Pfeiffer F et~al. (2008) {Hard-X-ray dark-field imaging using a grating
-  interferometer}.
-\newblock {\em Nature Materials} 7:134--137.
+\bibinfo{author}{Pfeiffer, F.} \emph{et~al.}
+\newblock \bibinfo{title}{{Hard-X-ray dark-field imaging using a grating
+  interferometer}}.
+\newblock \emph{\bibinfo{journal}{Nature Materials}}
+  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{134--137}
+  (\bibinfo{year}{2008}).
 
 \bibitem{Willner2013}
-Willner M et~al. (2013) {Quantitative X-ray phase-contrast computed tomography
-  at 82 keV}.
-\newblock {\em Optics express} 21:4155--4166.
+\bibinfo{author}{Willner, M.} \emph{et~al.}
+\newblock \bibinfo{title}{{Quantitative X-ray phase-contrast computed
+  tomography at 82 keV}}.
+\newblock \emph{\bibinfo{journal}{Optics express}}
+  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{4155--4166}
+  (\bibinfo{year}{2013}).
 
 \bibitem{Donath2009}
-Donath T et~al. (2009) {Inverse geometry for grating-based x-ray phase-contrast
-  imaging}.
-\newblock {\em Journal of Applied Physics} 106:054703.
+\bibinfo{author}{Donath, T.} \emph{et~al.}
+\newblock \bibinfo{title}{{Inverse geometry for grating-based x-ray
+  phase-contrast imaging}}.
+\newblock \emph{\bibinfo{journal}{Journal of Applied Physics}}
+  \textbf{\bibinfo{volume}{106}}, \bibinfo{pages}{054703}
+  (\bibinfo{year}{2009}).
 
 \bibitem{Mohr2012}
-Mohr J et~al. (2012) {High aspect ratio gratings for X-ray phase contrast
+\bibinfo{author}{Mohr, J.} \emph{et~al.}
+\newblock \bibinfo{title}{High aspect ratio gratings for x-ray phase contrast
   imaging}.
-\newblock 41:41--50.
+\newblock \emph{\bibinfo{journal}{AIP Conference Proceedings}}
+  \textbf{\bibinfo{volume}{1466}}, \bibinfo{pages}{41--50}
+  (\bibinfo{year}{2012}).
 
 \bibitem{David2007}
-David C et~al. (2007) {Fabrication of diffraction gratings for hard X-ray phase
-  contrast imaging}.
-\newblock {\em Microelectronic Engineering} 84:1172--1177.
+\bibinfo{author}{David, C.} \emph{et~al.}
+\newblock \bibinfo{title}{{Fabrication of diffraction gratings for hard X-ray
+  phase contrast imaging}}.
+\newblock \emph{\bibinfo{journal}{Microelectronic Engineering}}
+  \textbf{\bibinfo{volume}{84}}, \bibinfo{pages}{1172--1177}
+  (\bibinfo{year}{2007}).
 
 \bibitem{Kenntner2010}
-Kenntner J et~al. (2010) {\em {Front- and backside structuring of gratings for
+\bibinfo{author}{Kenntner, J.} \emph{et~al.}
+\newblock \bibinfo{title}{{Front- and backside structuring of gratings for
   phase contrast imaging with x-ray tubes}}.
-\newblock Vol.{} 7804, p. 780408.
+\newblock In \emph{\bibinfo{booktitle}{Proceedings of SPIE}}, vol.
+  \bibinfo{volume}{7804}, \bibinfo{pages}{780408} (\bibinfo{year}{2010}).
 
 \bibitem{Stutman2012a}
-Stutman D, Finkenthal M (2012) {Glancing angle Talbot-Lau grating
-  interferometers for phase contrast imaging at high x-ray energy}.
-\newblock {\em Applied physics letters} 101:91108.
+\bibinfo{author}{Stutman, D.} \& \bibinfo{author}{Finkenthal, M.}
+\newblock \bibinfo{title}{{Glancing angle Talbot-Lau grating interferometers
+  for phase contrast imaging at high x-ray energy}}.
+\newblock \emph{\bibinfo{journal}{Applied physics letters}}
+  \textbf{\bibinfo{volume}{101}}, \bibinfo{pages}{91108}
+  (\bibinfo{year}{2012}).
 
 \bibitem{Aslund2007}
-{\AA slund, M} (2007) Ph.D. thesis.
+\bibinfo{author}{{\AA slund, M}}.
+\newblock \emph{\bibinfo{title}{{Digital Mammography with a Photon Counting
+  Detector in a Scanned Multislit Geometry}}}.
+\newblock Ph.D. thesis (\bibinfo{year}{2007}).
 
 \bibitem{Oduko2010}
-Oduko JM, Young KC, Burch A (2010) in {\em Digital Mammography}, Lecture Notes
-  in Computer Science, eds.{} Martí J, Oliver A, Freixenet J, Martí R.
-\newblock (Springer Berlin Heidelberg) Vol.{} 6136, pp. 365--370.
+\bibinfo{author}{Oduko, J.~M.}, \bibinfo{author}{Young, K.~C.} \&
+  \bibinfo{author}{Burch, A.}
+\newblock \bibinfo{title}{A survey of patient doses from digital mammography
+  systems in the uk in 2007 to 2009}.
+\newblock In \bibinfo{editor}{Martí, J.}, \bibinfo{editor}{Oliver, A.},
+  \bibinfo{editor}{Freixenet, J.} \& \bibinfo{editor}{Martí, R.} (eds.)
+  \emph{\bibinfo{booktitle}{Digital Mammography}}, vol. \bibinfo{volume}{6136}
+  of \emph{\bibinfo{series}{Lecture Notes in Computer Science}},
+  \bibinfo{pages}{365--370} (\bibinfo{publisher}{Springer Berlin Heidelberg},
+  \bibinfo{year}{2010}).
 
 \bibitem{Weitkamp2005}
-Weitkamp T et~al. (2005) {X-ray phase imaging with a grating interferometer}.
-\newblock {\em Optics Express} 13:6296--6304.
+\bibinfo{author}{Weitkamp, T.} \emph{et~al.}
+\newblock \bibinfo{title}{{X-ray phase imaging with a grating interferometer}}.
+\newblock \emph{\bibinfo{journal}{Optics Express}}
+  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{6296--6304}
+  (\bibinfo{year}{2005}).
 
 \bibitem{Thuering2013c}
-Thuering T et~al. (2013) {Energy resolved X-ray grating interferometry}.
-\newblock {\em Applied Physics Letters} 102:191113.
+\bibinfo{author}{Thuering, T.} \emph{et~al.}
+\newblock \bibinfo{title}{{Energy resolved X-ray grating interferometry}}.
+\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
+  \textbf{\bibinfo{volume}{102}}, \bibinfo{pages}{191113}
+  (\bibinfo{year}{2013}).
 
 \bibitem{Chabior2011a}
-Chabior M et~al. (2011) {Beam hardening effects in grating-based x-ray
-  phase-contrast imaging}.
-\newblock {\em Medical Physics} 38:1189.
+\bibinfo{author}{Chabior, M.} \emph{et~al.}
+\newblock \bibinfo{title}{{Beam hardening effects in grating-based x-ray
+  phase-contrast imaging}}.
+\newblock \emph{\bibinfo{journal}{Medical Physics}}
+  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{1189} (\bibinfo{year}{2011}).
 
 \bibitem{Grunzweig2008}
-Gr\"{u}nzweig C et~al. (2008) {Design, fabrication, and characterization of
-  diffraction gratings for neutron phase contrast imaging.}
-\newblock {\em The Review of scientific instruments} 79:053703.
+\bibinfo{author}{Gr\"{u}nzweig, C.} \emph{et~al.}
+\newblock \bibinfo{title}{{Design, fabrication, and characterization of
+  diffraction gratings for neutron phase contrast imaging.}}
+\newblock \emph{\bibinfo{journal}{The Review of scientific instruments}}
+  \textbf{\bibinfo{volume}{79}}, \bibinfo{pages}{053703}
+  (\bibinfo{year}{2008}).
 
 \bibitem{Raupach2011}
-Raupach R, Flohr TG (2011) {Analytical evaluation of the signal and noise
-  propagation in x-ray differential phase-contrast computed tomography.}
-\newblock {\em Physics in medicine and biology} 56:2219--2244.
+\bibinfo{author}{Raupach, R.} \& \bibinfo{author}{Flohr, T.~G.}
+\newblock \bibinfo{title}{{Analytical evaluation of the signal and noise
+  propagation in x-ray differential phase-contrast computed tomography.}}
+\newblock \emph{\bibinfo{journal}{Physics in medicine and biology}}
+  \textbf{\bibinfo{volume}{56}}, \bibinfo{pages}{2219--2244}
+  (\bibinfo{year}{2011}).
 
 \end{thebibliography}
-
-\end{article}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Adding Figure and Table References
-%% Be sure to add figures and tables after \end{article}
-%% and before \end{document}
-
-%% For figures, put the caption below the illustration.
-%%
-%% \begin{figure}
-%% \caption{Almost Sharp Front}\label{afoto}
-%% \end{figure}
-
-%% For Tables, put caption above table
-%%
-%% Table caption should start with a capital letter, continue with lower case
-%% and not have a period at the end
-%% Using @{\vrule height ?? depth ?? width0pt} in the tabular preamble will
-%% keep that much space between every line in the table.
-
-%% \begin{table}
-%% \caption{Repeat length of longer allele by age of onset class}
-%% \begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
-%% table text
-%% \end{tabular}
-%% \end{table}
-
-%% For two column figures and tables, use the following:
-
-%% \begin{figure*}
-%% \caption{Almost Sharp Front}\label{afoto}
-%% \end{figure*}
-
-%% \begin{table*}
-%% \caption{Repeat length of longer allele by age of onset class}
-%% \begin{tabular}{ccc}
-%% table text
-%% \end{tabular}
-%% \end{table*}
-
-\begin{figure}
-    \includegraphics[width=.5\textwidth]{figures/figure1.eps}
-    \caption{Schematic of a grating
-        interferometer for X-ray energies between 60 and
-        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
-        aspect ratio is defined by the ratio of the travelling distance along the
-        grating lines and the period and can be arbitrarily long. In order to maximise
-        the field of view, the grating structures are aligned on an
-    arc.}
-    \label{Fig:schematic}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=.5\textwidth]{figures/grating_mask.eps}
-    \caption{Grating design mask for
-        the edge-on illumination approach and SEM
-        image of the grating. The top part of the 4 inch wafer shows
-        five grating chips. The
-        gratings have different curvatures which are specific to the grating
-        interferometer geometry. 
-        The SEM image shows the gold structures and the interrupting bridges
-        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}
-        \label{Fig:grating_mask}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
-    \caption{Radiographic scan of an electronic chip. The image was acquired
-        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
-    step. The top right image shows the differential absorption image.}
-    \label{Fig:img_chip}
-\end{figure}
-
+\section*{Author contributions}
+TT and AM wrote the manuscript text and performed the experiments. All
+authors reviewed the manuscript.
 \end{document}

### 2013-12-16 hedpc.tex
marcos letter

@@
 
-\section*{Competing financial interests}
+\section*{Additional information}
 The authors declare no competing financial interests.
@@
 \end{thebibliography}
+
 \section*{Author contributions}
-TT and AM wrote the manuscript text and performed the experiments. All
+T.T. and M.A. wrote the manuscript text and performed the experiments. All
 authors reviewed the manuscript.

### 2014-03-03 hedpc.tex
cesium iodide
better captions on fig 1/2/3

@@
 
+\section*{Results}
 Here we introduce a method for phase contrast imaging which works on
@@
         the field of view, the grating structures are aligned on an
-    arc.}%
+        arc. A \SI{100}{\kilo\eV} setup was realised where the distance
+        between the source and the source grating is \SI{23}{\centi\metre}
+    and the distance between the source grating and the phase grating is
+    \SI{16}{\centi\metre}. That is also the distance from the phase grating
+to the analyzer grating.}%
 \label{Fig:schematic}
@@
         image of the grating. The top part of the 4 inch wafer shows
-        five grating chips. The
+        five grating chips. From top to bottom, one source grating, two
+        phase gratings and two analyzer gratings. The
         gratings have different curvatures which are specific to the grating
@@
 
-Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
-Several resistors and an integrated circuits are located on different layers
-on the chip. The images were acquired in scanning mode, using a step size of
+\section*{Discussion}
+Several resistors and an integrated circuit are located on different layers
+on the electronic chip in fig.~\ref{Fig:img_chip}. The radiographs were
+acquired in scanning mode, using a step size of
 $\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
@@
 replaced with the differential attenuation image, which was obtained by
-digital differentiation. In the attenuation image, the contrast of the soldering points of
+calculating the derivative along the horizontal axis. In the attenuation
+image, the contrast of the soldering points of
 the integrated circuit is reduced underneath the resistors, while in
@@
 $\SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
-Instruments. A cesium iodide (CsI:Ti) scintillator of $\SI{600}{\micro
+Instruments. A cesium iodide (CsI:Tl) scintillator of $\SI{600}{\micro
 \metre}$ thickness converts the X-rays to visible light and is coupled with

### 2014-03-03 hedpc.tex
language edits

@@
     of this technique in the energy range between $\num{80}$ and
-    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
-    severe technical challenges. Phase-contrast X-ray imaging at such high
+    $\SI{150}{\kilo\electronvolt}$ pose severe technical challenges, and are
+    still mostly unexplored. Phase-contrast X-ray imaging at such high
     energies is of relevant scientific and industrial interest, in
-    particular for the investigation of materials with high atomic number or
-    thickness as well as for medical imaging. Here we show the successful
+    particular for the investigation of strongly absorbing or thick materials 
+    as well as for medical imaging. Here we show the successful
     implementation of a Talbot-Lau interferometer operated at
@@
     compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
-    present edge-on illumination of the gratings to overcome their current
-    fabrication limits as well as curved structures, to match the beam
-    divergence and allow a large field of view on a short and efficient
-    setup.
+    present the edge-on illumination of the gratings in order to overcome
+    the current fabrication limits. Finally, the curved structures match
+    the beam divergence and allow a large field of view on a short and
+    efficient setup.
 \end{abstract}
@@
 The attenuation and phase shift properties are described by the complex
-index of refraction $n=1 - \delta + i \beta$. The imaginary part $\beta$ is
+refractive index $n=1 - \delta + i \beta$. The imaginary part $\beta$ is
 related to the attenuation coefficient by $\mu = 4 \pi \beta(\lambda) /
@@
 
-Phase-sensitive imaging is a desirable modality, as it delivers a
+Phase-sensitive imaging is a desirable modality, since it delivers a
 complementary source of contrast with respect to absorption by providing
@@
 combination with attenuation enables the determination of the effective
-atomic number~\cite{Qi2010}. An enhanced \ac{CNR} in images compared to
+atomic number~\cite{Qi2010}. An enhanced \ac{CNR} compared to
 attenuation for certain materials or
@@
 interferometric~\cite{Bonse1965,Momose1996} methods rely on X-ray beams of
-high spatial and temporal coherence, which is available only at synchrotron
+high spatial and temporal coherence, which are available only at synchrotron
 sources. Inline phase contrast~\cite{Snigirev1995,Wilkins1996,Cloetens1996}
@@
 energies up to the tungsten $K_\alpha$ line at~\SI{60}{\kilo\eV}. In
-addition to phase sensitivity, analyzer-based and Talbot interferometry
-approaches also provide (with different retrieval mechanisms) information
+addition to phase sensitivity, crystal analyzers and Talbot interferometers
+also provide --- with different retrieval mechanisms --- information
 about the integrated local small angle scattering power from microscopic
@@
 \section*{Results}
-Here we introduce a method for phase contrast imaging which works on
+We introduce a method for phase contrast imaging which works on
 conventional X-ray sources, covers the entire diagnostic X-ray energy range
@@
 illumination approach for the grating design and arrangement. Our solution
-removes one on the major hurdle which prevented grating interferometry to be
-applied at very high X-ray energies so far, namely the fabrication of
-gratings with high-aspect ratios. The aspect ratio, given by
-\begin{equation} \text{R} = \frac{2h}{p}, \end{equation} where $p$ is the
-grating period and $h$ the  structure height, is normally limited by the
+removes one of the major hurdles which prevented grating interferometry from
+being
+applied at high energies so far, namely the fabrication of
+gratings with high aspect ratios. The aspect ratio, given by
+\begin{equation}
+    \text{R} = \frac{2h}{p},
+\end{equation}
+where $p$ is the
+grating period and $h$ the  structure height, is limited by the
 fabrication process, usually photolithography~\cite{David2002} or X-ray
-lithography~\cite{Mohr2012} as grating structures tend to collapse or deform
+lithography~\cite{Mohr2012} since grating structures tend to collapse or deform
 (e.g.\ due to capillary forces) if the aspect ratio is too high. For a given
@@
 an aspect ratio for the absorption grating around $\textnormal{R}=30$ is
-necessary for a reasonable length of the experimental arrangement, it would
+sufficient, it would
 have to be at least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover,
 when using a broad spectrum, photons above the design energy should also be
-efficiently blocked by the gratings, which requires even higher aspect
+efficiently blocked by the gratings, thus requiring even higher aspect
 ratios. The largest aspect ratios achieved by current fabrication
@@
 
-Our design introduces the edge-on
-illuminated,  circularly aligned structures. Edge-on illumination
+Our design introduces edge-on illuminated,  circularly aligned structures. Edge-on illumination
 (Fig.~\ref{Fig:schematic}), as
@@
 \SI{800}{\micro \metre}$
-it can sufficiently attenuate X-rays up to energies of 
-$\SI{160}{\kilo\electronvolt}$. Beam splitter and analyzer grating are
+it can absorb more than \SI{70}{\percent} of the incoming X-rays up to energies of 
+$\SI{160}{\kilo\electronvolt}$. The beam splitter and analyzer grating are
 separated at the first fractional Talbot order~\cite{Weitkamp2005},
@@
 
-Due to the high spectral acceptance~\cite{Weitkamp2005,Thuering2013c} of the
+Due to the large spectral acceptance~\cite{Weitkamp2005,Thuering2013c} of the
 interferometer ($\SI{50}{\kilo\electronvolt}$ to
@@
 $\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
-the maximum of $\SI{160}{\kilo\volt}$. With a grating structure height of
+the maximum of $\SI{160}{\kilo\volt}$. With a structure height of
 approximately $\SI{100}{\micro \metre}$, the field of view in the vertical
@@
 the field of view is only limited by the grating size to
-$\SI{30}{\milli\metre}$, but wider gratings can be fabricated with this
+$\SI{30}{\milli\metre}$, but wider gratings can be fabricated with the same
 method and the available technology on larger wafers. In addition to the standard components (source,
@@
 layer, resulting in lower absorption contrast. Due to the weaker energy
-dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
+dependence of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
 are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
@@
 imaging to be performed at high energies ($>\SI{100}{\kilo\eV}$) on conventional X-ray
-sources. With a circular distribution of the gratings, the diffracting and
+sources. With a circular alignment of the gratings, the diffracting and
 absorbing structures can be matched to the divergent beam, even for very
@@
 Instruments. A cesium iodide (CsI:Tl) scintillator of $\SI{600}{\micro
-\metre}$ thickness converts the X-rays to visible light and is coupled with
+\metre}$ thickness converts the X-rays to visible light and is coupled to
 an optical lens projecting the image onto the CCD\@. The effective pixel size
 is $\SI{80}{\micro\metre}$. The collimating slit right after the source is 
-$\SI{25}{\micro\metre}$ large, while the second slit before the detector is
+$\SI{25}{\micro\metre}$ wide, while the second slit before the detector is
 $\SI{100}{\micro\metre}$.
@@
 in the last ten years. 
-Smaller regions of these gratings actually exhibit a visibility up
-to~\SI{14}{\percent} already, indicating that this goal is reachable as the
+Smaller regions of these gratings already exhibit a visibility up
+to~\SI{14}{\percent}, indicating that this goal is reachable as the
 fabrication becomes more reliable and uniform.

### 2014-03-03 hedpc.tex
new author contributions

@@
 \section*{Author contributions}
-T.T. and M.A. wrote the manuscript text and performed the experiments. All
-authors reviewed the manuscript.
+CD and MS conceived the edge-on illumination scheme for grating interferometry.
+TT, ZW and MA designed the first experiment.
+TT and MA performed the experiment and analyzed the data.
+TT and MA wrote the manuscript with contributions from all authors.
 \end{document}

### 2014-03-04 hedpc.tex
arrow in figure 2, comparison of AR

@@
 sufficient, it would
-have to be at least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover,
+have to be at least $\num{128}$ for $E=\SI{100}{\kilo\electronvolt}$. This
+is the case for the synchrotron interferometer with a design energy
+of~\SI{82}{\kilo\eV}~\cite{Willner2013}, where an aspect ratio of \num{21}
+is reported with a transmission of \SI{20}{\percent}. The aspect ratio in
+the present experiment reaches \num{143}. Moreover,
 when using a broad spectrum, photons above the design energy should also be

### 2014-03-04 hedpc.tex
added intro to discussion

@@
 lithography~\cite{Mohr2012} since grating structures tend to collapse or deform
-(e.g.\ due to capillary forces) if the aspect ratio is too high. For a given
-setup length these parameters depend on the target energy $E$ according to
-$p \propto 1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
-\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$
-an aspect ratio for the absorption grating around $\textnormal{R}=30$ is
-sufficient, it would
-have to be at least $\num{128}$ for $E=\SI{100}{\kilo\electronvolt}$. This
-is the case for the synchrotron interferometer with a design energy
-of~\SI{82}{\kilo\eV}~\cite{Willner2013}, where an aspect ratio of \num{21}
-is reported with a transmission of \SI{20}{\percent}. The aspect ratio in
-the present experiment reaches \num{143}. Moreover,
-when using a broad spectrum, photons above the design energy should also be
-efficiently blocked by the gratings, thus requiring even higher aspect
-ratios. The largest aspect ratios achieved by current fabrication
-techniques~\cite{David2007,Kenntner2010} are around 60.
+(e.g.\ due to capillary forces) if the aspect ratio is too high.
+Moreover, when using a broad spectrum, photons above the design energy
+should also be efficiently blocked by the gratings, thus requiring even
+higher aspect ratios. The largest aspect ratios achieved by current
+fabrication techniques~\cite{David2007,Kenntner2010} are around 60.
+For a given setup length these parameters depend on the target energy $E$
+according to $p \propto 1/\sqrt{E}$ and $h \propto E^3$, and therefore
+$\textnormal{R} \propto E^{7/2}$~\cite{Momose2003a}. If at
+$E=\SI{25}{\kilo\electronvolt}$ an aspect ratio for the absorption grating
+around $\textnormal{R}=30$ is sufficient, it would have to be at least
+$\num{128}$ for $E=\SI{100}{\kilo\electronvolt}$. With our design, we reach
+an aspect ratio of \num{143}, satisfying the above condition with a
+transmission of less than \SI{1}{\percent} at \SI{100}{\kilo\eV}. As a
+comparison, a recent interferometer implemented at a third generation
+synchrotron facility~\cite{Willner2013} reported an aspect ratio of
+\num{21} with a transmission as large as \SI{20}{\percent}
+at~\SI{82}{\kilo\eV}.
 
@@
 \SI{800}{\micro \metre}$
-it can absorb more than \SI{70}{\percent} of the incoming X-rays up to energies of 
+it can absorb more than \SI{90}{\percent} of the incoming X-rays up to energies of 
 $\SI{160}{\kilo\electronvolt}$. The beam splitter and analyzer grating are
@@
 more than $\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
-the source and analyzer gratings ($>90\%$ up to
+the source and analyzer gratings (more than $90\%$ up to
 $\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
@@
 \section*{Discussion}
-Several resistors and an integrated circuit are located on different layers
-on the electronic chip in fig.~\ref{Fig:img_chip}. The radiographs were
-acquired in scanning mode, using a step size of
+This work develops Talbot-Lau interferometry to a regime of
+high photon energies.
+High energies are required for the operation of computed
+tomography and security scanners, in order to
+penetrate materials with large thicknesses or high atomic number.
+
+Additionally, the dose delivered to the patients could be reduced through
+phase sensitivity at high energies: the dose depends mainly on the
+absorption and it decreases with the third power of the photon energy~\cite{Momose2005}. On
+the other hand, the phase interaction is only inversely proportional to the
+energy and is therefore relatively much more relevant than absorption as the
+energy increases, possibly leading to a decreased exposure for an equivalent
+image quality.
+
+We show the first images on a conventional laboratory source in this energy
+range. In fig.~\ref{Fig:img_chip}, several resistors and an integrated
+circuit are located on different layers on an electronic chip. The
+radiographs were acquired in scanning mode, using a step size of
 $\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
@@
 Edge-on illuminated grating interferometry finally allows phase contrast
-imaging to be performed at high energies ($>\SI{100}{\kilo\eV}$) on conventional X-ray
+imaging to be performed at high energies ($>\SI{100}{\kilo\eV}$) on
+conventional X-ray
 sources. With a circular alignment of the gratings, the diffracting and
@@
 
+\bibitem{Momose2005}
+\bibinfo{author}{Momose, A.}
+\newblock \bibinfo{title}{{Recent Advances in X-ray Phase Imaging}}.
+\newblock \emph{\bibinfo{journal}{Japanese Journal of Applied Physics}}
+  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{6355--6367}
+  (\bibinfo{year}{2005}).
+
 \bibitem{Chabior2011a}

### 2014-03-04 hedpc.tex
added G012 / to image 2

@@
 X-ray tube, Talbot-Lau interferometry was applied so far at
-$\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}. Medical imaging
+$\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009a}. Medical imaging
 applications may benefit from phase contrast at higher energies: chest or
@@
         gratings have different curvatures which are specific to the grating
-        interferometer geometry. 
+        interferometer geometry. Multiple gratings for more than one setup
+        geometry are fabricated on a single wafer.
         The \ac{SEM} image shows the gold structures and the interrupting bridges
@@
 
-\bibitem{Donath2009}
+\bibitem{Donath2009a}
 \bibinfo{author}{Donath, T.} \emph{et~al.}
-\newblock \bibinfo{title}{{Inverse geometry for grating-based x-ray
-  phase-contrast imaging}}.
-\newblock \emph{\bibinfo{journal}{Journal of Applied Physics}}
-  \textbf{\bibinfo{volume}{106}}, \bibinfo{pages}{054703}
+\newblock \bibinfo{title}{{Phase-contrast imaging and tomography at 60 keV
+  using a conventional x-ray tube source.}}
+\newblock \emph{\bibinfo{journal}{The Review of scientific instruments}}
+  \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{053701}
   (\bibinfo{year}{2009}).

### 2014-03-04 hedpc.tex
marcos review of results and discussion

@@
 
-\section*{Discussion}
-This work develops Talbot-Lau interferometry to a regime of
-high photon energies.
-High energies are required for the operation of computed
-tomography and security scanners, in order to
-penetrate materials with large thicknesses or high atomic number.
-
-Additionally, the dose delivered to the patients could be reduced through
-phase sensitivity at high energies: the dose depends mainly on the
-absorption and it decreases with the third power of the photon energy~\cite{Momose2005}. On
-the other hand, the phase interaction is only inversely proportional to the
-energy and is therefore relatively much more relevant than absorption as the
-energy increases, possibly leading to a decreased exposure for an equivalent
-image quality.
-
-We show the first images on a conventional laboratory source in this energy
-range. In fig.~\ref{Fig:img_chip}, several resistors and an integrated
-circuit are located on different layers on an electronic chip. The
-radiographs were acquired in scanning mode, using a step size of
-$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
-magnified phase and attenuation images, the attenuation image has been
-replaced with the differential attenuation image, which was obtained by
-calculating the derivative along the horizontal axis. In the attenuation
-image, the contrast of the soldering points of
-the integrated circuit is reduced underneath the resistors, while in
-the phase image, they can clearly be identified. The reduced contrast of the 
-soldering points in the absorption image is due to beam hardening. The spectrum
-impinging on these soldering point is hardened by the resistors in the upper
-layer, resulting in lower absorption contrast. Due to the weaker energy
-dependence of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
-are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
-lower contrast reduction of the soldering points underneath the resistors in the
-phase image of the chip. This result shows the benefit of the phase contrast in
-high-energy X-ray imaging, which may be useful to identify flaws in multilayered
-structures such as electronic chips.
+Fig.~\ref{Fig:img_chip} shows the first X-ray images acquired with our new setup, based on
+edge-on illuminated grating interferometry powered by a conventional X-ray
+source operated at \SI{160}{\kilo\voltpeak} and with a design energy of
+\SI{100}{\kilo\eV}.  
 \begin{figure}[h!]
@@
 \end{figure}
+Several resistors and integrated circuits located on different
+layers on an electronic chip can be identified. The radiographs were acquired in scanning
+mode, using a step size of \SI{100}{\micro\metre} along the $y$ axis, covering a total imaging
+area of $2 \times \SI{2}{\centi\metre^2}$. For a better comparison of the magnified phase and
+attenuation images, the latter has been replaced with the differential
+attenuation image, which was obtained by calculating the derivative along
+the horizontal axis. In the attenuation image, the contrast of the soldering
+points of the integrated circuit is reduced underneath the resistors, while
+in the phase image, they can clearly be identified. The reduced contrast of
+the soldering points in the absorption image is due to beam hardening. The
+spectrum impinging on these soldering point is hardened by the resistors in
+the upper layer, resulting in lower absorption contrast. Due to the weaker
+energy dependence of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast
+images are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the lower
+contrast reduction of the soldering points under the resistors in the
+phase image of the chip. This example shows one of the potential benefits of
+phase contrast X-ray imaging at high energies, which may be useful to
+identify flaws in multilayered structures such as electronic chips.
 
-Edge-on illuminated grating interferometry finally allows phase contrast
-imaging to be performed at high energies ($>\SI{100}{\kilo\eV}$) on
-conventional X-ray
-sources. With a circular alignment of the gratings, the diffracting and
-absorbing structures can be matched to the divergent beam, even for very
-compact geometries. Short, high-energy phase-contrast systems enable the
-efficient investigation of high-density materials or thick samples,
-adding information on electron density and integrated small angle scattering
-power to the conventional absorption based signal. This will improve
-material discrimination and density sensitivity capabilities in future
-X-rays or even neutron~\cite{Grunzweig2008} investigations.
+\section*{Discussion}
+
+Possible usages of edge-on grating interferometry encompasse applications
+ranging from medical imaging to non-destructive testing and homeland
+security. All these applications seek for high (greater than
+\SI{100}{\kilo\eV}) nominal energies
+and compact designs. Particularly for medical application, the operation of
+a phase contrast imaging device at high energies is imperative. When imaging
+patients, a crucial issue is the dose, which depends mainly on the
+absorption of the X-rays and decreases with the third power of the photon
+energy~\cite{Momose2005}. On the other hand, the phase interaction is only inversely
+proportional to the energy and is therefore relatively much more relevant
+than absorption as the energy increases, possibly leading to a decreased
+exposure for an equivalent image quality. Clinical operation of such a
+device will imply measuring patients who normally breath, move and shake.
+Fast acquisitions are therefore required, in order to keep the images sharp
+and artefact free. As a consequence, compact, efficient imaging systems need
+to be developed to provide imaging capabilities at sufficient speed. Our
+circular grating alignment matches the structures of the diffracting and
+absorbing elements to the divergent beam, especially for compact geometries.
+In conclusion, short, high-energy phase-contrast systems will enable the
+efficient investigation of high-density materials or thick samples, adding
+information on electron density and integrated small-angle scattering power
+to the conventional absorption-based signal. This will improve material
+discrimination and density sensitivity in future X-ray or even
+neutron~\cite{Grunzweig2008} investigations.
 
@@
 
+\bibitem{Chabior2011a}
+\bibinfo{author}{Chabior, M.} \emph{et~al.}
+\newblock \bibinfo{title}{{Beam hardening effects in grating-based x-ray
+  phase-contrast imaging}}.
+\newblock \emph{\bibinfo{journal}{Medical Physics}}
+  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{1189} (\bibinfo{year}{2011}).
+
 \bibitem{Momose2005}
@@
   (\bibinfo{year}{2005}).
-
-\bibitem{Chabior2011a}
-\bibinfo{author}{Chabior, M.} \emph{et~al.}
-\newblock \bibinfo{title}{{Beam hardening effects in grating-based x-ray
-  phase-contrast imaging}}.
-\newblock \emph{\bibinfo{journal}{Medical Physics}}
-  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{1189} (\bibinfo{year}{2011}).
 

### 2014-03-04 hedpc.tex
typo + white G012 in fig 2

@@
 
-Possible usages of edge-on grating interferometry encompasse applications
+Possible usages of edge-on grating interferometry encompass applications
 ranging from medical imaging to non-destructive testing and homeland

### 2014-03-05 point_by_point_response.tex
point by point response to the SR reviewers

--- 2013-10-28 point_by_point_response.tex
@@
 \usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc} %Umlaute
+\usepackage[utf8]{inputenc}
 
 \DeclareSIUnit{\voltpeak}{Vp}
+\newcommand{\reviewer}[1]{\emph{#1}}
 \newenvironment{reviewerquote}{\begin{quote}\itshape}{\end{quote}}
@@
 \title{Point-by-point response to the reviewers}
+\author{Revised manuscript SREP-13-06290-T}
 \date{}
@@
 \noindent
+The manuscript has been revised in order to address the editor's and the reviewers'
+comments.
 The comments from the reviewers are quoted in \emph{italic}, whereas the
-revised article parts are reported in upright font.
-\section*{Reviewer \#1}
+revised article parts are reported in upright font in indented sections.
+\section*{Reviewer \#2}
 \begin{reviewerquote}
-    I could not find a significant advance in this work. X-ray Talbot-Lau
-    interferometers with high-energy x-rays have been already reported (Ref.
-    18-20, 23, D. Stutman et al., Appl. Opt. 49 (2010) 4677 etc.). The
-    authors mention that the edge-on- illuminated grating interferometry
-    breaks the current limitations of x-ray phase-contrast imaging, but I
-    don't think that there is clear evidence showing that the authors'
-    method is much more promising than the methods reported in the previous
-    papers. If the authors want to show that the edge-on-illumination method
-    is by far the most promising for high-energy and large-field-of-view
-    x-ray phase imaging, I think that the authors have to quantitatively
-    compare the method with those previously reported in terms of the total
-    exposure time, spatial resolution, signal-to-noise ratio, and so on, and
-    show that the authors' method is much better than the others.
+    A single wafer contains multiple gratings that are designed for a specific distance from the source.
+In figure 1, the designed distance from the source to each grating must be indicated, in order to make things clear for the readers.
+Please also explain how robust imaging quality is with mis-alignment of the grating with respect to the working distance from the source.
 \end{reviewerquote}
-We think that the experiments presented in the current manuscript show
-indeed significant progress with respect to the cited references.
-The method presented by Stutman et al. has a fundamental limitation that
-prevents it from achieving curved structures and large aspect ratios.
-Moreover, those experiments were performed on a source
-with~\SI{60}{\kilo\voltpeak}, which is significantly lower than
-the~\SI{160}{\kilo\voltpeak} of our source and the~\SI{100}{\kilo\eV} used
-as the design energy for our interferometer.
-
-The other works also present results in a much lower energy range or very
-different conditions, thus preventing a meaningful comparison.
-Reference~23 reported images taken at \num{30} and~\SI{60}{\kilo\eV},
-reference~20 also has a design energy of~\SI{47.9}{\kilo\eV}. Finally,
-references~18 and~19 present Talbot interferometry at~\num{82}
-and~\SI{123}{\kilo\eV} respectively, but only the first result is published
-on a peer reviewed journal, and both experiments were performed at the ESRF
-synchrotron, with a monochromatic and coherent beam that is incomparable to
-a conventional tube.
-In order to emphasize this enormous difference between synchrotron sources
-and lab sources, the title has been changed to ``X-ray phase-contrast imaging at
-100 keV on
-a conventional source''.
-
-In order to address the concerns of reviewer \#1, the short review of the
-previous results in the
-introductory paragraph has been updated:
+The figures and captions have been improved in order to address the
+reviewer's concerns. In particular, the distances have been added to the
+caption of fig. 1:
 \begin{quote}
-The vast majority of phase-sensitive techniques, including crystal analyzer based [5, 6] or
-interferometric [7, 8] methods rely on X-ray beams of high spatial and temporal coherence,
-which is available only at synchrotron sources. Inline phase contrast [9–11] and Talbot interferometry [12–14] need high spatial coherence but are available on polychromatic microfocus
-sources. Phase-contrast imaging using X-ray beams of low temporal and spatial coherence
-such as conventional low-brilliance X-ray tubes have been demonstrated with coded apertures [15] and Talbot-Lau interferometry [16]. Analyzer-based systems have been recently
-extended to tube sources [17, 18] but only at energies up to the tungsten
-$K_\alpha$ line at 60 keV. In
-addition to phase sensitivity, analyzer-based, Talbot interferometry and coded-aperture approaches also provide (with different retrieval mechanisms) information about the integrated
-local small angle scattering power from microscopic density fluctuations in a specimen [19].
-This signal is known under the name of dark-field, scatter or visibility reduction contrast.
-High-energy Talbot interferometry has been reported so far using a synchrotron source
-at nominal energies of 82 keV [20] and 123 keV [21]. Using a low-brilliance X-ray tube,
-2
-Talbot-Lau interferometry was applied so far at 60 keV mean energy [22]. Medical imaging
-applications may benefit from phase contrast at higher energies: chest or abdominal radiography or CT require energies between 100 and 150 kVp. Other potential applications are
-homeland security or chip failure analysis, which require high energies for the visualization
-of materials of high density and atomic number.
+    A \SI{100}{\kilo\eV} setup was realised where the distance
+        between the source and the source grating is \SI{23}{\centi\metre}
+    and the distance between the source grating and the phase grating is
+    \SI{16}{\centi\metre}. That is also the distance from the phase grating
+to the analyzer grating.
+\end{quote}
+In the text, we also included a measurement of the variation of the
+visibility as the integrating distance is changed:
+\begin{quote}
+    The precise position of the analyzer grating along the beam axis is not
+critical, and a change in visibility of less than \SI{1}{\percent} is
+observed by displacing it by as much as \SI{5}{\milli\metre}.
+\end{quote}
+\begin{reviewerquote}
+    Figure 2 shows five gratings.
+Based on figure 1, only three gratings are needed.
+Label the gratings in Figure (source grating, beam splitter grating, analyzer grating).
+What is the purpose of the other two gratings shown in Figure 2?
+\end{reviewerquote}
+The gratings in the figure have been labelled and the caption makes clear
+that many sets of gratings can be fabricated simultaneously on a
+single wafer:
+\begin{quote}
+    The top part of the 4 inch wafer shows
+        five grating chips. From top to bottom, one source grating, two
+        phase gratings and two analyzer gratings. The
+        gratings have different curvatures which are specific to the grating
+        interferometer geometry. Multiple gratings for more than one setup
+        geometry are fabricated on a single wafer.
+\end{quote}
+\begin{reviewerquote}
+    Figure 3 shows "differential" attenuation image. Please explain what this exactly is. The text is extremely vague.
+\end{reviewerquote}
+The derivative of the attenuation image is now described in more detail:
+\begin{quote}
+    For a better comparison of the magnified phase and
+attenuation images, the latter has been replaced with the differential
+attenuation image, which was obtained by calculating the derivative along
+the horizontal axis.
 \end{quote}
 
-\begin{reviewerquote}
-    Furthermore, the authors mention that the results in Fig.
-3 show the benefit of the phase nature of the image, but I think that the authors should provide a more detailed explanation about the contrasts in the images because the contrast of soldering points underneath the resistors should not be reduced in the differential attenuation image for monochromatic x-rays.
-The authors should explain quantitatively why the contrast is reduced.
-Otherwise, the authors' assertion is suspicious.
-\end{reviewerquote}
-A paragraph has been added to discuss the different beam hardening behaviour of
-the absorption and differential phase image:
-\begin{quote}
-resistors, while in the phase image, they can clearly be identified. The reduced contrast
-of the soldering points in the absorption image is due to beam hardening. The spectrum
-impinging on these soldering point is hardened by the resistors in the upper layer, resulting
-in lower absorption contrast. Due to the weaker energy dependency of phase
-shifts ($1/E$
-compared to $1/E^3$), phase-contrast images are less sensitive to beam hardening [31], which
-explains the lower contrast reduction of the soldering points underneath the resistors in the
-phase image of the chip. This result shows the benefit of the phase nature in high-energy
-X-ray imaging, which may be useful to identify flaws in multilayered structures such as
-electronic chips.
-\end{quote}
+\section*{Reviewer \#3}
+We thank Reviewer 3 for his or her critical reading.
 
-\section*{Reviewer \#2}
-\begin{reviewerquote}
-    However, this solution comes with significant drawbacks in terms of very
-    limited fields of view~\SI{3}{\centi\metre} horizontally, a single detector pixel in the vertical direction), which at the moment seem hard to overcome.
-\end{reviewerquote}
-There is no fundamental limitation on the horizontal field of view in our
-approach. On the contrary, our solution actually solves precisely this
-issue, by easily matching the spherical wave front with the curved
-structures. Any limitation to horizontal the field of view given by large glancing
-angles is therefore removed. The gratings could already be fabricated on
-larger wafers with the existing technology.
+Medical X-ray imaging is intrinsically related to dose issues, and dose
+strongly depends on the attenuation properties of the patient.
+Therefore, it does not sound reasonable to develop X-ray diagnostic
+techniques operating at lower energies than those available now, since this will
+increase the dose imparted to the patient significantly. This is why at
+present, worldwide efforts in
+X-ray imaging --- both in CT and in 2D radiography, including
+mammography ---
+are focused on the reduction of the dose. Most of the players are working on
+the development of reconstruction algorithms dealing with fewer
+projections, different acquisition schemes or improved detectors. The
+contrast mechanism, however, is always the well-known absorption. Our team,
+as well as other groups around the world, works on a more fundamental
+aspect, trying to obtain contrast  from refraction and scattering phenomena
+rather than absorption. Moreover, it is a general established concept that
+phase contrast is expected to provide better contrast for equal or smaller dose
+at the same X-ray energy. This is now explained in more detail in the
+discussion section.
 
-The limitations in the vertical field of view do not come at the expense of
-an increased dose with our proposed scanning solution. Larger areas could in
-principle be scanned with short exposure times by stacking an array of
-edge-illuminated gratings. This scanning technique is already offered in commercial X-ray
-diagnostic devices, such as the Philips MicroDose mammography system, to
-reduce scattering. References are now provided in the following paragraph:
-\begin{quote}
- Radiographic 2D imaging can be obtained by scanning the sample or a
-thin fan beam. The scanning technique has been demonstrated to deliver less dose than the
-conventional approach based on the illumination of a large area. In digital mammography,
-for instance, where dose is a critical issue, Philips’ MicroDose system combines a scanning
-approach with an highly collimated fan beam [27]. Thanks to the high collimation, the dose
-deposited on patients has been reported to be significantly lower than with other instruments
-based on the illumination of a large area detector [28]. 
-\end{quote}
+The reviewer argues that
+there is no need to increase the energy up to \SI{100}{\kilo\eV} in order to
+\reviewer{translate
+this technology to clinic} while at the same acknowledging that 
+an increase to \SI{60}{\kilo\eV} would be good for mammography. But
+\SI{60}{\kilo\eV} is almost twice
+the energy that is used today for conventional mammography
+investigations. This comment is in contradiction with his or her first
+statement but clearly supports and justifies our efforts to push phase-contrast
+imaging up to energies around \SI{100}{\kilo\eV} or higher as those are the energies
+relevant for medical applications, without considering the mammography
+\emph{niche}
+
+ The reviewer also states that efforts devoted to reduce the
+ source-to-detector distance would not be supported by industry
+ (\reviewer{discouraged industry applications}). Even though we agree that there
+ might be several applications --- nondestructive testing and homeland
+ security for instance --- where a source-to-detector distance of
+ \SI{2}{\metre} would be
+ desired, we would like to point out the crucial issue of detector
+ efficiency which, combined with the inverse-square law of flux reduction,
+ significantly affects the total time one X-ray investigation takes. Time is
+ an issue, as patients move and affect the final image quality. Last but not
+ least, there is an economic factor to take into account: no hospital will
+ buy a system which is ten times slower than the already available technology.
+
+ On this respect, but considering a different aspect of our new technology,
+ the reviewer is indeed mentioning the potential bottleneck
+ of the edge-on approach, namely the 
+ (slow) scanning geometry. The
+ main reason for a scanning geometry is that for this proof of principle we just fabricated one set of
+ gratings. Obviously, one can consider stacking such gratings and aligning
+ them to a multi-line detector following the  principle of spiral CT when
+ operated with multiline detectors: this would speed up acquisition
+ significantly.
+
+ For 2D radiography, the commercially available MicroDose System of
+ Philips with a scanning geometry and a strongly collimated beam 
+ results in a reduced dose to the patient. It follows that having a scanning
+ geometry could result in a lower dose deposition when compared with a 2D
+ area illumination, without an impractical increase in exposure time.
 
  \begin{reviewerquote}
-    Moreover, in the methods section the authors talk of a
-    \SI{5}{\percent} visibility, which is even lower than that of the quoted papers by Pfeiffer's group (refs 18, 19), which, at least nominally, reach even higher energies (123 keV).
-Hence, the reduction in field-of-view does not seem to be counterbalanced by significant improvements in visibility.
-This is also supported by the relatively poor quality of the differential phase image compared to the derivative of the absorption image, where the only advantage seems to be the visibility of the soldering points beneath the resistors (primarily due to the fact that these do not produce area contrast in the DPC image), while everywhere else the contrast of the differentiated absorption image seems to be higher.
+     This is perhaps the reason that in spite of large
+     scale effort by industrial leaders in radiology, the phase contrast
+     radiology still remains as academic research.
  \end{reviewerquote}
-The visibility in our experiment is still low, and this obviously
-affects the quality of the images, but we also mentioned
-that this is the first attempt in building gratings with our new design,
-while the fabrication of traditional structures has been developed for over
-a decade now. The remarks above about references~18 and~19 (synchrotron
-source, unpublished results) should also be taken into account here.
-\begin{reviewerquote}
-Finally, the novelty of the result is diminished by previous demonstrations that high energies in phase-contrast x-ray imaging could be reached by other methods (e.g.
-Ignatyev et al JAP 110 (2011) 014906), albeit in that case image quality seems to be lower.
-\end{reviewerquote}
-In the paper from Ignatyev et al., an admittedly lower image quality was
-achieved again with softer X-rays, from~\num{60}
-to~\SI{100}{\kilo\voltpeak}. Thus, we claim that our results
-are a significantly more promising than the technique described therein.
+ Since we just mentioned a big player in the medical imaging field, we
+ would like to point out our disagreement with this statement. While it is
+ true that most of the efforts are still carried out at academic sites,
+ industrial activities on phase contrast within companies like Philips,
+ General Electrics, Konica-Minolta, Siemens, Zeiss and Brucker are reported
+ regularly at international conferences.
 
-\section*{Reviewer \#3}
+Finally, the reviewer raises some doubts about the novelty of the edge-on geometry of our
+gratings, by taking examples from
+X-ray optics, namely multilayer Laue mirrors. We acknowledge
+(also in the manuscript) that previous work reported the usage of tilted
+gratings, i.e. Stuntman \emph{et al}.
+, but we also clearly explain
+ how much our edge-on approach is superior with
+respect to previous solutions, mostly because of the unrestricted field of
+view given by the matching of the curved wave front. We do not think that the comparison with the Laue
+mirrors is fair as the length scales are far from those
+related to our experiment. We diffract against micrometer-sized structure
+while multilayers are devices with structures in the nanometer-scale.
 
-\begin{reviewerquote}
-    An extended object is imaged by axial scanning, which results in very
-    long exposure times due to phase stepping.  The legend of Fig. 3
-    indicates that one image line of \SI{0.1}{\milli\metre} width is
-    acquired in \SI{6}{\minute}.  The authors admit this situation in the last sentences of the manuscripts without giving a convincing solution to the problem.
-\end{reviewerquote}
-This is indeed an issue, as the exposure time is mostly affected by the low visibility. The manuscript
-was amended to include a more detailed discussion of our plans to reduce
-the exposure time. We mention now that raising the visibility to
-\SI{15}{\percent}, a value already reached in lower energy experiments and
-in some sections of our gratings,
-would immediately cut the exposure by \num{9} times:
-\begin{quote}
-visibility of the gratings (5 \%). The exposure time was chosen in order to get a low noise in
-the differential phase image. The signal-to-noise ratio (SNR) is proportional to the visibility
-and the square root of the exposure time [33]. This implies that the exposure times can
-easily drop by an order of magnitude as these gratings become comparable in quality to
-those developed in the last ten years. Smaller regions of these gratings actually exhibit a
-visibility up to 14 \% already, indicating that this goal is reachable as the fabrication becomes
-more reliable and uniform. The detector is also relatively inefficient (30
-\%) leaving an
-additional margin for improvement.
-\end{quote}
-\begin{reviewerquote}
-    The authors suggest that the only imaging methods that can be used with
-    conventional x-ray sources are the in-line phase contrast technique and
-    Talbot interferometry. They fail to mention that analyzer-based imaging
-    systems with x-ray tube sources have been built and successfully used
-    for imaging rather large biological objects. The current exposure times
-    are shorter or comparable to those of the present work, but there are
-    clear indications how the exposure times in x-ray tube based ABI can be
-    reduced by an order of magnitude or more. On the other hand, the upper
-    limit of photon energy is that of the tungsten Kalpha line,
-    \SI{60}{\kilo\eV}. For references, see Nesch et al.(2009), Rev. Sci.
-    Instrum. 80, 093702, and Parham et al.(2009), Acad.Radiol. 16, 911-917.
-\end{reviewerquote}
-We now included references to these papers (in the first paragraph above), but we point out that our
-experiments do not have any intrinsical limit to the photon energy.
+For these reasons, we cannot share the statements of the reviewer when arguing
+about the innovation degree of our work. We believe that high-energy phase
+contrast on compact, clinically relevant geometries is achievable with our
+approach and therefore we are convinced about the relevance and the
+breakthrough character of our results: they show, for the first time,
+results at \SI{100}{\kilo\eV} on short distances using a conventional X-ray source.
 \end{document}

### 2014-03-06 point_by_point_response.tex
point by point response setup length

@@
  \SI{2}{\metre} would be
- desired, we would like to point out the crucial issue of detector
- efficiency which, combined with the inverse-square law of flux reduction,
- significantly affects the total time one X-ray investigation takes. Time is
- an issue, as patients move and affect the final image quality. Last but not
- least, there is an economic factor to take into account: no hospital will
- buy a system which is ten times slower than the already available technology.
+ desired, we would like to point out that our technique has no fundamental
+ limitations with respect to the setup length. While a short prototype is
+ demonstrated here, longer systems can be designed, in fact with fewer
+ constraints on the grating pitch, leading to a less problematic fabrication
+ process.
 
- On this respect, but considering a different aspect of our new technology,
- the reviewer is indeed mentioning the potential bottleneck
+ The reviewer is also mentioning the potential bottleneck
  of the edge-on approach, namely the 

### 2014-03-06 hedpc.tex
added visibility change for tr z of G2
response to sr

@@
 separated at the first fractional Talbot order~\cite{Weitkamp2005},
-resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
+resulting in an intergrating distance of $\SI{158}{\milli\metre}$. However,
+the precise position of the analyzer grating along the beam axis is not
+critical, and a change in visibility of less than \SI{1}{\percent} is
+observed by displacing it by as much as \SI{5}{\milli\metre}. The
 source grating splits the relatively large focal spot ($\sim
@@
   effective atomic number using phase contrast CT.}}
-\newblock \emph{\bibinfo{journal}{Physics in medicine and biology}}
+\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
   \textbf{\bibinfo{volume}{55}}, \bibinfo{pages}{2669--77}
@@
   three-dimensional x-ray phase contrast tomography.}}
-\newblock \emph{\bibinfo{journal}{Physics in medicine and biology}}
+\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
   \textbf{\bibinfo{volume}{52}}, \bibinfo{pages}{6923--6930}
@@
   hard x rays.}}
-\newblock \emph{\bibinfo{journal}{Optics letters}}
+\newblock \emph{\bibinfo{journal}{Optics Letters}}
   \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{1059--61}
@@
   diffraction-enhanced x-ray imaging instrument.}}
-\newblock \emph{\bibinfo{journal}{The Review of scientific instruments}}
+\newblock \emph{\bibinfo{journal}{The Review of Scientific Instruments}}
   \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{093702}
@@
   tomography at 82 keV}}.
-\newblock \emph{\bibinfo{journal}{Optics express}}
+\newblock \emph{\bibinfo{journal}{Optics Express}}
   \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{4155--4166}
@@
   using a conventional x-ray tube source.}}
-\newblock \emph{\bibinfo{journal}{The Review of scientific instruments}}
+\newblock \emph{\bibinfo{journal}{The Review of Scientific Instruments}}
   \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{053701}
@@
   for phase contrast imaging at high x-ray energy}}.
-\newblock \emph{\bibinfo{journal}{Applied physics letters}}
+\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
   \textbf{\bibinfo{volume}{101}}, \bibinfo{pages}{91108}
@@
   diffraction gratings for neutron phase contrast imaging.}}
-\newblock \emph{\bibinfo{journal}{The Review of scientific instruments}}
+\newblock \emph{\bibinfo{journal}{The Review of Scientific Instruments}}
   \textbf{\bibinfo{volume}{79}}, \bibinfo{pages}{053703}
@@
   propagation in x-ray differential phase-contrast computed tomography.}}
-\newblock \emph{\bibinfo{journal}{Physics in medicine and biology}}
+\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
   \textbf{\bibinfo{volume}{56}}, \bibinfo{pages}{2219--2244}

### 2014-03-10 hedpc.tex
abbreviated journals

@@
 \usepackage{babel}
+\usepackage{jabbrv}
 \usepackage{acronym}
@@
 \DeclareSIUnit{\voltpeak}{Vp}
+
+\DefineJournalPartialAbbreviation{Medicine}{Med}
+\DefineJournalPartialAbbreviation{Instrumentation}{Instr}
+\DefineJournalPartialAbbreviation{Instruments}{Instr}
+\DefineJournalPartialAbbreviation{Express}{Expr}
+\DefineJournalPartialAbbreviation{Synchrotron}{Synch}
 
@@
 \author[1,2]{T.~Thüring}
-\author[1,2]{M.~Abis}
+\author[1,2]{M.~Abis\thanks{\texttt{matteo.abis@psi.ch}; Corresponding author.}}
 \author[1]{Z.~Wang}
@@
 shift. The interaction contributing to phase shifts is coherent (Rayleigh)
-scattering~\cite{Als-Nielsen2011}.
+scattering~\cite[extras={, p.~280}]{Als-Nielsen2011}.
 
@@
 complementary source of contrast with respect to absorption by providing
-direct access to the electron density~\cite{Als-Nielsen2011}. Moreover, the
+direct access to the electron density~\cite[extras{, p.71}]{Als-Nielsen2011}. Moreover, the
 combination with attenuation enables the determination of the effective
@@
 \newblock \emph{\bibinfo{title}{{Elements of modern X-ray physics}}}
-  (\bibinfo{year}{2011}).
+  (\bibinfo{publisher}{Wiley}, \bibinfo{address}{London},
+  \bibinfo{year}{2011}), \bibinfo{edition}{2nd} edn.
 
@@
   effective atomic number using phase contrast CT.}}
-\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
-  \textbf{\bibinfo{volume}{55}}, \bibinfo{pages}{2669--77}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Physics in Medicine and
+  Biology}}} \textbf{\bibinfo{volume}{55}}, \bibinfo{pages}{2669--77}
   (\bibinfo{year}{2010}).
@@
   three-dimensional x-ray phase contrast tomography.}}
-\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
-  \textbf{\bibinfo{volume}{52}}, \bibinfo{pages}{6923--6930}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Physics in Medicine and
+  Biology}}} \textbf{\bibinfo{volume}{52}}, \bibinfo{pages}{6923--6930}
   (\bibinfo{year}{2007}).
@@
   interferometer}}.
-\newblock \emph{\bibinfo{journal}{Journal of Synchrotron Radiation}}
-  \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{562--572}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Journal of Synchrotron
+  Radiation}}} \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{562--572}
   (\bibinfo{year}{2009}).
@@
   using hard X-rays}}.
-\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{373}},
-  \bibinfo{pages}{595--598} (\bibinfo{year}{1995}).
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Nature}}}
+  \textbf{\bibinfo{volume}{373}}, \bibinfo{pages}{595--598}
+  (\bibinfo{year}{1995}).
 
@@
 \newblock \bibinfo{title}{{Diffraction enhanced x-ray imaging}}.
-\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
-  \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{2015--2025}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Physics in Medicine and
+  Biology}}} \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{2015--2025}
   (\bibinfo{year}{1997}).
@@
 \newblock \bibinfo{title}{{An x-ray interferometer}}.
-\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Applied Physics Letters}}}
   \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{155--156}
@@
   observing biological soft tissues}}.
-\newblock \emph{\bibinfo{journal}{Nature Medicine}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Nature Medicine}}}
   \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{473--475}
@@
   microimaging by coherent high-energy synchrotron radiation}}.
-\newblock \emph{\bibinfo{journal}{Review of Scientific Instruments}}
-  \textbf{\bibinfo{volume}{66}}, \bibinfo{pages}{5486--5492}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Review of Scientific
+  Instruments}}} \textbf{\bibinfo{volume}{66}}, \bibinfo{pages}{5486--5492}
   (\bibinfo{year}{1995}).
@@
   X-rays}}.
-\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{384}},
-  \bibinfo{pages}{335--338} (\bibinfo{year}{1996}).
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Nature}}}
+  \textbf{\bibinfo{volume}{384}}, \bibinfo{pages}{335--338}
+  (\bibinfo{year}{1996}).
 
@@
   imaging}}.
-\newblock \emph{\bibinfo{journal}{Journal of Physics D: Applied Physics}}
-  \textbf{\bibinfo{volume}{29}}, \bibinfo{pages}{133--146}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Journal of Physics D: Applied
+  Physics}}} \textbf{\bibinfo{volume}{29}}, \bibinfo{pages}{133--146}
   (\bibinfo{year}{1996}).
@@
   hard x rays.}}
-\newblock \emph{\bibinfo{journal}{Optics Letters}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Optics Letters}}}
   \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{1059--61}
@@
   shearing interferometer}}.
-\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Appl. Phys. Lett.}}}
   \textbf{\bibinfo{volume}{81}}, \bibinfo{pages}{3287--3289}
@@
 \newblock \bibinfo{title}{{Demonstration of X-Ray Talbot Interferometry}}.
-\newblock \emph{\bibinfo{journal}{Japanese Journal of Applied Physics}}
-  \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{L866--L868}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Japanese Journal of Applied
+  Physics}}} \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{L866--L868}
   (\bibinfo{year}{2003}).
@@
   X-ray sources}}.
-\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
-  Sciences}} \textbf{\bibinfo{volume}{2012}}, \bibinfo{pages}{2--7}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Proceedings of the National
+  Academy of Sciences}}} \textbf{\bibinfo{volume}{2012}}, \bibinfo{pages}{2--7}
   (\bibinfo{year}{2012}).
@@
   imaging with low-brilliance X-ray sources}}.
-\newblock \emph{\bibinfo{journal}{Nature Physics}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Nature Physics}}}
   \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{258--261}
@@
   diffraction-enhanced x-ray imaging instrument.}}
-\newblock \emph{\bibinfo{journal}{The Review of Scientific Instruments}}
-  \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{093702}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{The Review of Scientific
+  Instruments}}} \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{093702}
   (\bibinfo{year}{2009}).
@@
   diffraction enhanced medical imaging system}.
-\newblock \emph{\bibinfo{journal}{Academic Radiology}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Academic Radiology}}}
   \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{911 -- 917}
@@
   interferometer}}.
-\newblock \emph{\bibinfo{journal}{Nature Materials}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Nature Materials}}}
   \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{134--137}
@@
   tomography at 82 keV}}.
-\newblock \emph{\bibinfo{journal}{Optics Express}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Optics Express}}}
   \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{4155--4166}
@@
   using a conventional x-ray tube source.}}
-\newblock \emph{\bibinfo{journal}{The Review of Scientific Instruments}}
-  \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{053701}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{The Review of Scientific
+  Instruments}}} \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{053701}
   (\bibinfo{year}{2009}).
@@
   imaging}.
-\newblock \emph{\bibinfo{journal}{AIP Conference Proceedings}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{AIP Conference Proceedings}}}
   \textbf{\bibinfo{volume}{1466}}, \bibinfo{pages}{41--50}
@@
   phase contrast imaging}}.
-\newblock \emph{\bibinfo{journal}{Microelectronic Engineering}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Microelectronic Engineering}}}
   \textbf{\bibinfo{volume}{84}}, \bibinfo{pages}{1172--1177}
@@
   for phase contrast imaging at high x-ray energy}}.
-\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Applied Physics Letters}}}
   \textbf{\bibinfo{volume}{101}}, \bibinfo{pages}{91108}
@@
 \newblock \bibinfo{title}{{X-ray phase imaging with a grating interferometer}}.
-\newblock \emph{\bibinfo{journal}{Optics Express}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Optics Express}}}
   \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{6296--6304}
@@
 \newblock \bibinfo{title}{{Energy resolved X-ray grating interferometry}}.
-\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Applied Physics Letters}}}
   \textbf{\bibinfo{volume}{102}}, \bibinfo{pages}{191113}
@@
   phase-contrast imaging}}.
-\newblock \emph{\bibinfo{journal}{Medical Physics}}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Medical Physics}}}
   \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{1189} (\bibinfo{year}{2011}).
@@
 \newblock \bibinfo{title}{{Recent Advances in X-ray Phase Imaging}}.
-\newblock \emph{\bibinfo{journal}{Japanese Journal of Applied Physics}}
-  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{6355--6367}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Japanese Journal of Applied
+  Physics}}} \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{6355--6367}
   (\bibinfo{year}{2005}).
@@
   diffraction gratings for neutron phase contrast imaging.}}
-\newblock \emph{\bibinfo{journal}{The Review of Scientific Instruments}}
-  \textbf{\bibinfo{volume}{79}}, \bibinfo{pages}{053703}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{The Review of Scientific
+  Instruments}}} \textbf{\bibinfo{volume}{79}}, \bibinfo{pages}{053703}
   (\bibinfo{year}{2008}).
@@
   propagation in x-ray differential phase-contrast computed tomography.}}
-\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
-  \textbf{\bibinfo{volume}{56}}, \bibinfo{pages}{2219--2244}
+\newblock \emph{\JournalTitle{\bibinfo{journal}{Physics in Medicine and
+  Biology}}} \textbf{\bibinfo{volume}{56}}, \bibinfo{pages}{2219--2244}
   (\bibinfo{year}{2011}).

### 2014-04-09 point_by_point_response.tex
draft of answer to sr rev3

@@
 
-\title{Point-by-point response to the reviewers}
-\author{Revised manuscript SREP-13-06290-T}
+\title{Response to reviewer \#3}
+\author{Revised manuscript SREP-13-06290}
 \date{}
@@
 \noindent
-The manuscript has been revised in order to address the editor's and the reviewers'
-comments.
-The comments from the reviewers are quoted in \emph{italic}, whereas the
-revised article parts are reported in upright font in indented sections.
-\section*{Reviewer \#2}
-\begin{reviewerquote}
-    A single wafer contains multiple gratings that are designed for a specific distance from the source.
-In figure 1, the designed distance from the source to each grating must be indicated, in order to make things clear for the readers.
-Please also explain how robust imaging quality is with mis-alignment of the grating with respect to the working distance from the source.
-\end{reviewerquote}
-The figures and captions have been improved in order to address the
-reviewer's concerns. In particular, the distances have been added to the
-caption of fig. 1:
-\begin{quote}
-    A \SI{100}{\kilo\eV} setup was realised where the distance
-        between the source and the source grating is \SI{23}{\centi\metre}
-    and the distance between the source grating and the phase grating is
-    \SI{16}{\centi\metre}. That is also the distance from the phase grating
-to the analyzer grating.
-\end{quote}
-In the text, we also included a measurement of the variation of the
-visibility as the integrating distance is changed:
-\begin{quote}
-    The precise position of the analyzer grating along the beam axis is not
-critical, and a change in visibility of less than \SI{1}{\percent} is
-observed by displacing it by as much as \SI{5}{\milli\metre}.
-\end{quote}
-\begin{reviewerquote}
-    Figure 2 shows five gratings.
-Based on figure 1, only three gratings are needed.
-Label the gratings in Figure (source grating, beam splitter grating, analyzer grating).
-What is the purpose of the other two gratings shown in Figure 2?
-\end{reviewerquote}
-The gratings in the figure have been labelled and the caption makes clear
-that many sets of gratings can be fabricated simultaneously on a
-single wafer:
-\begin{quote}
-    The top part of the 4 inch wafer shows
-        five grating chips. From top to bottom, one source grating, two
-        phase gratings and two analyzer gratings. The
-        gratings have different curvatures which are specific to the grating
-        interferometer geometry. Multiple gratings for more than one setup
-        geometry are fabricated on a single wafer.
-\end{quote}
-\begin{reviewerquote}
-    Figure 3 shows "differential" attenuation image. Please explain what this exactly is. The text is extremely vague.
-\end{reviewerquote}
-The derivative of the attenuation image is now described in more detail:
-\begin{quote}
-    For a better comparison of the magnified phase and
-attenuation images, the latter has been replaced with the differential
-attenuation image, which was obtained by calculating the derivative along
-the horizontal axis.
-\end{quote}
 
-\section*{Reviewer \#3}
-We thank Reviewer 3 for his or her critical reading.
+The authors obviously share most of the concerns raised by the reviewer, but
+there has been some misunderstanding on our side on the main points raised
+with his or her latest comments.
+We are confident we can thoroughly address them here.
 
-Medical X-ray imaging is intrinsically related to dose issues, and dose
-strongly depends on the attenuation properties of the patient.
-Therefore, it does not sound reasonable to develop X-ray diagnostic
-techniques operating at lower energies than those available now, since this will
-increase the dose imparted to the patient significantly. This is why at
-present, worldwide efforts in
-X-ray imaging --- both in CT and in 2D radiography, including
-mammography ---
-are focused on the reduction of the dose. Most of the players are working on
-the development of reconstruction algorithms dealing with fewer
-projections, different acquisition schemes or improved detectors. The
-contrast mechanism, however, is always the well-known absorption. Our team,
-as well as other groups around the world, works on a more fundamental
-aspect, trying to obtain contrast  from refraction and scattering phenomena
-rather than absorption. Moreover, it is a general established concept that
-phase contrast is expected to provide better contrast for equal or smaller dose
-at the same X-ray energy. This is now explained in more detail in the
-discussion section.
-
-The reviewer argues that
-there is no need to increase the energy up to \SI{100}{\kilo\eV} in order to
-\reviewer{translate
-this technology to clinic} while at the same acknowledging that 
-an increase to \SI{60}{\kilo\eV} would be good for mammography. But
-\SI{60}{\kilo\eV} is almost twice
-the energy that is used today for conventional mammography
-investigations. This comment is in contradiction with his or her first
-statement but clearly supports and justifies our efforts to push phase-contrast
-imaging up to energies around \SI{100}{\kilo\eV} or higher as those are the energies
-relevant for medical applications, without considering the mammography
-\emph{niche}
-
- The reviewer also states that efforts devoted to reduce the
- source-to-detector distance would not be supported by industry
- (\reviewer{discouraged industry applications}). Even though we agree that there
- might be several applications --- nondestructive testing and homeland
- security for instance --- where a source-to-detector distance of
- \SI{2}{\metre} would be
- desired, we would like to point out that our technique has no fundamental
- limitations with respect to the setup length. While a short prototype is
- demonstrated here, longer systems can be designed, in fact with fewer
- constraints on the grating pitch, leading to a less problematic fabrication
- process.
-
- The reviewer is also mentioning the potential bottleneck
- of the edge-on approach, namely the 
- (slow) scanning geometry. The
- main reason for a scanning geometry is that for this proof of principle we just fabricated one set of
- gratings. Obviously, one can consider stacking such gratings and aligning
- them to a multi-line detector following the  principle of spiral CT when
- operated with multiline detectors: this would speed up acquisition
- significantly.
-
- For 2D radiography, the commercially available MicroDose System of
- Philips with a scanning geometry and a strongly collimated beam 
- results in a reduced dose to the patient. It follows that having a scanning
- geometry could result in a lower dose deposition when compared with a 2D
- area illumination, without an impractical increase in exposure time.
+The most important issue is
 
 \begin{reviewerquote}
-     This is perhaps the reason that in spite of large
-     scale effort by industrial leaders in radiology, the phase contrast
-     radiology still remains as academic research.
+    this referee questioned if the photon energy (not being high enough) and
+    the distance (not being short enough) between detector and specimen, are
+    the key barriers to the translation of grating base phase contrast
+    radiology to clinic. The major barrier prevent the phase contrast
+    imaging methods, re-invented more than 20 years ago with the birth of
+    new synchrotron facility, to be transfer away from synchrotron and to
+    make an impact to clinical application at this moment, is the long
+    exposure time required to obtained the phase information by either high
+    quality sources (in-line) or treatment to the exit waves. Talbot-Lau
+    method promises phase contrast using conventional X-ray sources by
+    slotting the large source into small ones which could potentially enable
+    the phase retrieval. However, the requirement of scanning the gratings,
+    in the case reported here (24 steps), inevitably increases the dose as
+    well as the image acquisition time which put this technique only in the
+    research laboratory at the moment. [\ldots] In the long list of "major
+    players" and with all their effort contributing to the international
+    conferences, is there any one ready to commit this technology as their
+    product roadmaps? This work therefore promises a potential benefit on a
+    potential technique which is certainly valuable from the instrumentation
+    point of view and not likely to generate much interest of readers of
+    Scientific Reports.
 \end{reviewerquote}
- Since we just mentioned a big player in the medical imaging field, we
- would like to point out our disagreement with this statement. While it is
- true that most of the efforts are still carried out at academic sites,
- industrial activities on phase contrast within companies like Philips,
- General Electrics, Konica-Minolta, Siemens, Zeiss and Brucker are reported
- regularly at international conferences.
 
-Finally, the reviewer raises some doubts about the novelty of the edge-on geometry of our
-gratings, by taking examples from
-X-ray optics, namely multilayer Laue mirrors. We acknowledge
-(also in the manuscript) that previous work reported the usage of tilted
-gratings, i.e. Stuntman \emph{et al}.
-, but we also clearly explain
- how much our edge-on approach is superior with
-respect to previous solutions, mostly because of the unrestricted field of
-view given by the matching of the curved wave front. We do not think that the comparison with the Laue
-mirrors is fair as the length scales are far from those
-related to our experiment. We diffract against micrometer-sized structure
-while multilayers are devices with structures in the nanometer-scale.
+While most of the industrial research and product development is obviously
+unknown to the general public, at least two products roadmaps have been presented in
+the last months. An upgrade of the Philips MicroDose mammography system into a
+Talbot-Lau interferometer was shown by the company at the SPIE 
+2014 conference\cite{Roessl2014}. Moreover, clinical trials are currently
+ongoing on patients and healthy volunteers in Japan with a Talbot-Lau interferometer
+developed as a collaboration between the University of Tohoku and Konica
+Minolta~\cite{Momose06032014}. This last machine operates with an
+acceleration voltage of~\SI{40}{\kilo\voltpeak} and with an acceptable
+exposure time (\SI{19}{\second}) and dose (under \SI{10}{\milli\gray}).
 
-For these reasons, we cannot share the statements of the reviewer when arguing
-about the innovation degree of our work. We believe that high-energy phase
-contrast on compact, clinically relevant geometries is achievable with our
-approach and therefore we are convinced about the relevance and the
-breakthrough character of our results: they show, for the first time,
-results at \SI{100}{\kilo\eV} on short distances using a conventional X-ray source.
+We think that this is convincing evidence that this technique already belongs to the
+hospitals and not only to the research laboratories, as well as being a hot
+topic of recent industrial and scientific development.
+
+However, the reviewer is right when he points out that the work presented in
+the manuscript is still far from applications. At the same time, I think he
+or she can agree on the fact that sources with~\num{100}-\SI{120}{\kilo\eV} are needed in
+hospitals for tomography and even higher voltages are required for security
+inspections or material sciences investigations.
+This is why we think that, besides reduction of dose and exposure times for
+existing setups, the exploration of a new energy range is a fundamental
+research topic. Indeed, up to now, no system in the world was able to
+produce images at energies around~\SI{100}{\kilo\eV}. Even with a high
+dose or long exposure
+this was simply impossible because of the unavailability of the optical
+elements, which we could overcome.
+
+Finally, low-energy grating interferometry is in fact making its appearance
+in hospitals in dedicated areas (cartilage and mammography), and developing
+high-energy systems is key to expanding its applications, as well as
+potentially giving
+additional benefits in terms of phase contrast and dose reduction as shown
+in the manuscript.
+This study is of course a first step toward this goal and,
+while we could claim a successful design and operation of the machine, we
+could conclude at this stage that we can have a high imaging quality with
+clinically compatible exposures.
+
+\begin{reviewerquote}
+     The efforts are trying to "improve", if it is indeed an improvement, a
+     technology (the grating base phase contrast radiology) that is
+     interesting only for its promised clinical application which otherwise
+     offers no fundamental innovation for the phase retrieval scheme in
+     X-ray imaging (it took advantage of a known theory in optics to shorter
+     wavelength).
+\end{reviewerquote}
+The same comment applies to the whole field of grating interferometry, as the
+theory in optics is known since the 19th century, although at the time it
+was only applied to longer wavelengths. We would like to point out again
+that the promised clinical applications are coming true, and that the
+realization of this experiment had its remarkable challenges, despite being
+known in theory.
+
+\begin{reviewerquote}
+there is no mention about the exact photon energy or range actually used.
+Referring to manufactures data and provide a few more words than ``designed
+energy of 100 keV'' would be more quantitative.
+\end{reviewerquote}
+
+More details on the source, such as the material of the anode and the
+current have been added to the manuscript. The energy range is not changed
+afterwards by any means, so this is indeed the full
+information needed to reproduce the experiment on any similar generator.
+The design energy is a property of the interferometer, and is defined in the
+manuscript as the energy at which ``the beam splitter grating periodically
+shifts the phase by zero and $\pi$''. We suggest that this is already a
+precise statement.
+
+\begin{reviewerquote}
+    how can an improvement from 5\% (device reported here) to 14\% (current best technology) reaching one order of magnitude, "easily"?
+\end{reviewerquote}
+
+This is because, as explained in the methods section, some smaller section
+of our current gratings already have a visibility of \SI{14}{\percent}. This
+means it is almost three times as good as the average, and since the
+signal-to-noise ratio drops with the square root of the exposure time, but
+proportionally to the visibility, we claim that improving the visibility by
+a factor of three allows us to shorten the exposure time by a factor of
+nine.
+
+\begin{reviewerquote}
+    The fabrication of the grating is not described specifically, other than
+    saying ``Grating design and fabrication is nonstandard and involves a
+    complex mask design'' with a reference to a fabrication company.
+\end{reviewerquote}
+
+The fabrication through lithography and electroplating is not the main topic
+of this manuscript, hence it is only cited in 22, 23, 24. The mask design
+was carried out by MicroWorks GmbH, but it is a very technical detail that
+we think bears no impact on the reproducibility of the experiment: any
+design that reliably builds the described circularly arranged pattern will
+produce usable gratings.
+
+\begin{reviewerquote}
+    The SEM image on a selected portion of a grating already shows a rather
+    poor quality placement of \SI{}{\micro\meter} size structures, no mention about
+    how the precision of these structure could affect the imaging or the
+    phase retrieval.
+\end{reviewerquote}
+
+We mention in the manuscript that these irregularities are responsible for the limited
+visibility of the interferometer, and the connection of this value to the signal-to-noise
+ratio in the images.
+
+\bibliography{library}
+\bibliographystyle{plain}
 \end{document}

### 2014-04-09 hedpc.tex
draft of answer to sr rev3

@@
 X-ray tube, Talbot-Lau interferometry was applied so far at
-$\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009a}. Medical imaging
+$\SI{60}{\kilo\electronvolt}$ design energy~\cite{Donath2009a}. Medical imaging
 applications may benefit from phase contrast at higher energies: chest or
@@
 
-The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
-voltage of $\SI{160}{\kilo\volt}$. In the experiment, it was set to the
+The X-ray source is a tungsten target COMET MXR-160HP/11 X-ray tube with a maximum output
+voltage of $\SI{160}{\kilo\volt}$ and a current of $\SI{10}{\milli\ampere}$. In the experiment, it was set to the
 maximum voltage. The focal spot size is approximately

### 2014-04-14 point_by_point_response.tex
matteos proposal

@@
 While most of the industrial research and product development is obviously
-unknown to the general public, at least two products roadmaps have been presented in
+unknown to the general public, at least two product roadmaps have been presented in
 the last months. An upgrade of the Philips MicroDose mammography system into a
@@
 the manuscript is still far from applications. At the same time, I think he
-or she can agree on the fact that sources with~\num{100}-\SI{120}{\kilo\eV} are needed in
+or she can agree on the fact that sources
+with~\num{100}-\SI{120}{\kilo\voltpeak} are needed in
 hospitals for tomography and even higher voltages are required for security
@@
 
+The units for the energy of the
+photons were checked once more, and the authors could not find any
+occurrence where they are confused or incorrectly used, as suggested by the
+reviewer.
+
 \begin{reviewerquote}
@@
 
-This is because, as explained in the methods section, some smaller section
+This is because, as explained in the methods section and reference 33, some smaller section
 of our current gratings already have a visibility of \SI{14}{\percent}. This

### 2014-04-14 point_by_point_response.tex
marcos draft

--- 2014-04-09 point_by_point_response.tex
@@
-%        File: point_by_point_response.tex
-%     Created: Wed Oct 23 05:00 PM 2013 C
-% Last Change: Wed Oct 23 05:00 PM 2013 C
+%        File: point_by_point_response.tex Created: Wed Oct 23 05:00 PM 2013
+%        C Last Change: Wed Oct 23 05:00 PM 2013 C
 %
-\documentclass[a4paper,english]{scrartcl}
-\usepackage[detect-all]{siunitx}
-\usepackage{babel}
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
+\documentclass[a4paper,english]{scrartcl} \usepackage[detect-all]{siunitx}
+\usepackage{babel} \usepackage[T1]{fontenc} \usepackage[utf8]{inputenc}
 
-\DeclareSIUnit{\voltpeak}{Vp}
-\newcommand{\reviewer}[1]{\emph{#1}}
+\DeclareSIUnit{\voltpeak}{Vp} \newcommand{\reviewer}[1]{\emph{#1}}
 \newenvironment{reviewerquote}{\begin{quote}\itshape}{\end{quote}}
 
-\title{Response to reviewer \#3}
-\author{Revised manuscript SREP-13-06290}
-\date{}
-\begin{document}
-\maketitle
+\title{Response to reviewer \#3} \author{Revised manuscript SREP-13-06290}
+\date{} \begin{document} \maketitle
 
@@
 
-The authors obviously share most of the concerns raised by the reviewer, but
-there has been some misunderstanding on our side on the main points raised
-with his or her latest comments.
-We are confident we can thoroughly address them here.
+Reply to Review 3
+=================
 
-The most important issue is
+We would like to thank reviewer 3 for his/her detailed feedback on our
+latest revision. We actually share most of his/her concerns but we also see
+that there have been some misunderstanding on our side on the main points
+raised by his/her latest comments. We would like to address them in the
+following.
 
-\begin{reviewerquote}
-    this referee questioned if the photon energy (not being high enough) and
-    the distance (not being short enough) between detector and specimen, are
-    the key barriers to the translation of grating base phase contrast
-    radiology to clinic. The major barrier prevent the phase contrast
-    imaging methods, re-invented more than 20 years ago with the birth of
-    new synchrotron facility, to be transfer away from synchrotron and to
-    make an impact to clinical application at this moment, is the long
-    exposure time required to obtained the phase information by either high
-    quality sources (in-line) or treatment to the exit waves. Talbot-Lau
-    method promises phase contrast using conventional X-ray sources by
-    slotting the large source into small ones which could potentially enable
-    the phase retrieval. However, the requirement of scanning the gratings,
-    in the case reported here (24 steps), inevitably increases the dose as
-    well as the image acquisition time which put this technique only in the
-    research laboratory at the moment. [\ldots] In the long list of "major
-    players" and with all their effort contributing to the international
-    conferences, is there any one ready to commit this technology as their
-    product roadmaps? This work therefore promises a potential benefit on a
-    potential technique which is certainly valuable from the instrumentation
-    point of view and not likely to generate much interest of readers of
-    Scientific Reports.
-\end{reviewerquote}
+Referee 3: "It is disappointing that the authors misinterpreted the
+questions and the arguments this referee raised against the major claims of
+this work. This referee did not say: "there is no need to increase the
+energy to 100 keV in order to translate this technology to clinic" but
+rather question that is not the major factor. This referee did not
+"acknowledge(ing) that an increase to 60 keV would be good for mammography",
+even though it could be. The main point of the argument is if the
+contribution made by this work important or significant. The conclusion of
+the first review was not enough for a journal cover all different areas of
+basic science. It is probably not even sufficient to attract to readers in
+the same research area of X-ray imaging. The authors reply did not change
+this concern by quoting an "improvement" of increasing photon energy to 60
+keV for mammography, or to higher photon energy in general for radiology in
+general, a well-established and widely implemented for human health care for
+decades."
 
-While most of the industrial research and product development is obviously
-unknown to the general public, at least two products roadmaps have been presented in
-the last months. An upgrade of the Philips MicroDose mammography system into a
-Talbot-Lau interferometer was shown by the company at the SPIE 
-2014 conference\cite{Roessl2014}. Moreover, clinical trials are currently
-ongoing on patients and healthy volunteers in Japan with a Talbot-Lau interferometer
-developed as a collaboration between the University of Tohoku and Konica
-Minolta~\cite{Momose06032014}. This last machine operates with an
-acceleration voltage of~\SI{40}{\kilo\voltpeak} and with an acceptable
-exposure time (\SI{19}{\second}) and dose (under \SI{10}{\milli\gray}).
+Our answer: “Apparently, we have mis-interpreted the message of Reviewer 3
+and we thank him/her for his effort to clarify his/her opinion. In his/her
+first part of the argumentations, Reviewer 3 questions whether our
+contribution is "important of significant". This is a remark which in
+principle can be made to any scientific contribution, independently to its
+degree of novelty, difficulty or outreach. It has a strong subjective
+component, as demonstrated by the fact that two others reviewers found our
+work more than worth to be published in SciRep while Reviewer 3 still has
+several concerns. Therefore, we would like to reiterate here that our work
+is a step towards the implementation of phase contrast imaging on clinical
+systems which we believe might contribute to improve image contrast while
+keeping the dose under reasonable control. Those systems are compact and are
+operated at high-energies, or at least at energies much higher than those
+that have been used for any phase-contrast experiment so far (to the best of
+our knowledge). We are not claiming that we found the ultimate solution to
+it, but we present an experimental solution to address two major concerns
+(high-energy and compactness) which are presently limiting the broad
+application of phase contrast imaging outside the synchrotron community.”
 
-We think that this is convincing evidence that this technique already belongs to the
-hospitals and not only to the research laboratories, as well as being a hot
-topic of recent industrial and scientific development.
+Referee 3: "Specifically, this referee questioned if the photon energy (not
+being high enough) and the distance (not being short enough) between
+detector and specimen, are the key barriers to the translation of grating
+base phase contrast radiology to clinic. The major barrier prevent the phase
+contrast imaging methods, re-invented more than 20 years ago with the birth
+of new synchrotron facility, to be transfer away from synchrotron and to
+make an impact to clinical application at this moment, is the long exposure
+time required to obtained the phase information by either high quality
+sources (in-line) or treatment to the exit waves. Talbot-Lau method promises
+phase contrast using conventional X-ray sources by slotting the large source
+into small ones which could potentially enable the phase retrieval. However,
+the requirement of scanning the gratings, in the case reported here (24
+steps), inevitably increases the dose as well as the image acquisition time
+which put this technique only in the research laboratory at the moment."
 
-However, the reviewer is right when he points out that the work presented in
-the manuscript is still far from applications. At the same time, I think he
-or she can agree on the fact that sources with~\num{100}-\SI{120}{\kilo\eV} are needed in
+Our answer: (*Still need to work on this…any suggestions welcomed*)
+
+Referee 3: “This referee knows and agree that the radiation dose is critical
+for medical application, but that was exactly where the usefulness of this
+work is quested. It is well accepted that no new X-ray imaging technology is
+likely be implemented for clinic with dose penalties. There is even more
+fundamental question on if the phase information can really benefit clinical
+diagnosis even at the same dose. Instead of tackling the main challenges on
+reducing the scanning time or on demonstrating that phase contrast indeed
+give better visibility at the same dose than those without phase contrast on
+critical applications such as for medical imaging, device inspection and
+security inspection...,
+
+Our reply: "Clinical relevance of phase contrast is a fundamental question
+and we addressed this in several works, specifically on mammography,
+published elsewhere (InvRad 1, InvRad 2, NatComm). We are very well aware
+about the importance of assessing the advantages of phase contrast imaging
+with respect to existing diagnostic procedures, in particular when dealing
+with dose issues. However, the main subject of the present manuscript is
+different and addresses a very practical aspect: we will not even be able to
+discuss about clinical relevance of phase contrast if we cannot operate
+phase contrast in a clinical environment at all! With our work we want to
+show a possible solution to implement phase contrast imaging in clinics and
+addressing high energies and compact systems seem to us to be two
+fundamental points.
+
+Referee 3: "…suggested secondary problems, such as photon energy and the
+total dimension requirement for the instrument are targeted. The efforts are
+trying to "improve", if it is indeed an improvement, a technology (the
+grating base phase contrast radiology) that is interesting only for its
+promised clinical application which otherwise offers no fundamental
+innovation for the phase retrieval scheme in X-ray imaging (it took
+advantage of a known theory in optics to shorter wavelength).”
+
+Our reply “We do not believe that photon energy and total dimension
+requirements are secondary problems. As mentioned before, the penetration
+power of the probing radiation is rather a primary issue as we need
+sufficient photon statistics to be generated after penetrating a whole human
+body in order to measure a signal and, this, independently from whether we
+do absorption or phase contrast imaging. The comments on whether the phase
+retrieval procedure is innovative or not could actually be extended to the
+whole field of grating interferometry, as the theory in optics is known
+since the 19th century, although at the time it was only applied to longer
+wavelengths. We would like to point out again that the promised clinical
+applications are coming true, and that the realization of this experiment
+had its remarkable challenges, despite being known in theory.”
+
+Referee 3: “In the long list of "major players" and with all their effort
+contributing to the international conferences, is there any one ready to
+commit this technology as their product roadmaps? This work therefore
+promises a potential benefit on a potential technique which is certainly
+valuable from the instrumentation point of view and not likely to generate
+much interest of readers of Scientific Reports.”
+
+Our reply: "While most of the industrial research and product development is
+obviously unknown to the general public, at least two products roadmaps have
+been presented in the last months. An upgrade of the Philips MicroDose
+mammography system into a Talbot-Lau interferometer was shown by the company
+at the SPIE 2014 conference [2] (please add here the reference mentioned by
+Zhentian). Moreover, clinical trials are currently ongoing on patients and
+healthy volunteers in Japan (*give here the name of the hospital, from XNPIG
+proceedings*) with a Talbot-Lau interferometer developed as a collaboration
+between the University of Tohoku and Konica Minolta [1]. This last machine
+operates with an acceleration voltage of 40 kVp and with an acceptable
+exposure time (19 s) and dose (under 10 mGy). We think that this is
+convincing evidence that this technique already belongs to the hospitals and
+not only to the research laboratories, as well as being a hot topic of
+recent industrial and scientific development and interest. However, the
+reviewer is right when he points out that the work presented in our
+manuscript is still far from applications. At the same time, we think he or
+she can agree on the fact that sources with 100-120 keV are needed in
 hospitals for tomography and even higher voltages are required for security
-inspections or material sciences investigations.
-This is why we think that, besides reduction of dose and exposure times for
-existing setups, the exploration of a new energy range is a fundamental
-research topic. Indeed, up to now, no system in the world was able to
-produce images at energies around~\SI{100}{\kilo\eV}. Even with a high
-dose or long exposure
-this was simply impossible because of the unavailability of the optical
-elements, which we could overcome.
+inspections or material sciences investigations. This is why we think that,
+besides reduction of dose and exposure times for existing setups, the
+exploration of a new energy range is a fundamental research topic. Indeed,
+it is worth to mention that to now, no system in the world was able to
+produce images at energies around 100 keV. Even with a high dose or long
+exposure this was simply impossible because of the unavailability of the
+optical elements, which we could overcome in our work. Finally, low-energy
+grating interferometry is in fact making its appearance in hospitals in
+dedicated areas (cartilage and mammography), and developing high-energy
+systems is key to expanding its applications, as well as potentially giving
+additional benefits in terms of phase contrast and dose reduction as shown
+in the manuscript. This study is of course a first step toward this goal
+and, while we could claim a successful design and operation of the machine,
+we cannot conclude at this stage that we can have a high imaging quality
+with clinically compatible exposures. (*Matteo: do you agree with this
+latest sentence? You wrote “we could conclude…” but I think this was
+wrong…”*).
 
-Finally, low-energy grating interferometry is in fact making its appearance
-in hospitals in dedicated areas (cartilage and mammography), and developing
-high-energy systems is key to expanding its applications, as well as
-potentially giving
-additional benefits in terms of phase contrast and dose reduction as shown
-in the manuscript.
-This study is of course a first step toward this goal and,
-while we could claim a successful design and operation of the machine, we
-could conclude at this stage that we can have a high imaging quality with
-clinically compatible exposures.
+Referee 3: "Although Scientific Reports requests evaluation on the
+scientific rigorousness, over claiming the potential on clinical, device and
+homeland security applications is not rigorous. The hastiness of the
+presentation does not make their work rigorous, either. There is no analysis
+presented on the only image result, other than just pointing out the
+differential phase effect and merging images of different contrast. The
+authors argued that the reduced visibility in the attenuation contrast is
+due to the stronger X-ray hardening effect than that of phase contrast. This
+cannot be correctly evaluated by the referees and readers without knowing
+the size (along to the beam direction) of the structure of the chip,
+including the solders and resistors, and the absolute gray scale of those
+images. Without giving detailed analysis of the contrast on a set of poor
+quality images, and perhaps compare them with lower, say 80 keV photons, it
+is not convincing that the work does indeed improve the imaging quality of
+visibility for their targeted applications.”
 
-\begin{reviewerquote}
-     The efforts are trying to "improve", if it is indeed an improvement, a
-     technology (the grating base phase contrast radiology) that is
-     interesting only for its promised clinical application which otherwise
-     offers no fundamental innovation for the phase retrieval scheme in
-     X-ray imaging (it took advantage of a known theory in optics to shorter
-     wavelength).
-\end{reviewerquote}
-The same comment applies to the whole field of grating interferometry, as the
-theory in optics is known since the 19th century, although at the time it
-was only applied to longer wavelengths. We would like to point out again
-that the promised clinical applications are coming true, and that the
-realization of this experiment had its remarkable challenges, despite being
-known in theory.
+Our reply: (*This is difficult. I do not know how to rebuttal this, beside
+telling that going from 100 to 80 is not simple (new gratings, different
+distances, complicated alignment…) Any suggestion??*)
 
-\begin{reviewerquote}
-there is no mention about the exact photon energy or range actually used.
-Referring to manufactures data and provide a few more words than ``designed
-energy of 100 keV'' would be more quantitative.
-\end{reviewerquote}
+Referee 3: “There are also other flaws of this presentation, which were not
+pointed out in the first round reviewer's report. First of all, there is no
+mention about the exact photon energy or range actually used. Referring to
+manufactures data and provide a few more words than "designed energy of 100
+keV" would be more quantitative. The accelerating energy and photon energy
+are used in a confusion fashion of kV, kVp and keV for non-specialists. If
+the average photon energy is ~100 keV then the author must demonstrate
+significant difference in terms of the image quality between previous
+reports of 82keV and 60 keV using synchrotron and Talbot-Lau methods. If
+photon energy is one of the major claim of advantage of this paper, the
+authors cannot escape this comparison by just saying they are done with
+synchrotron or by other type of grating arrangements”
 
-More details on the source, such as the material of the anode and the
-current have been added to the manuscript. The energy range is not changed
-afterwards by any means, so this is indeed the full
-information needed to reproduce the experiment on any similar generator.
-The design energy is a property of the interferometer, and is defined in the
-manuscript as the energy at which ``the beam splitter grating periodically
-shifts the phase by zero and $\pi$''. We suggest that this is already a
-precise statement.
+Our reply: "More details on the source, such as the material of the anode
+and the current have been added to the manuscript. The energy range is not
+changed afterwards by any means, so this is indeed the full information
+needed to reproduce the experiment on any similar generator. The design
+energy is a property of the interferometer, and is defined in the manuscript
+as the energy at which “the beam splitter grating periodically shifts the
+phase by zero and Pi”. We suggest that this is already a precise
+statement. Concerning the comparison with synchrotron experiments, we think
+that at this stage of the developments, it should be sufficient to show that
+we can generate phase contrast images at 100 keV on a conventional source
+and to provide the discussion the way and extend we did. The differences in
+flux, coherence and monochromaticity between a synchrotron- and a tube-
+based experiment are so huge that the fact already that we were able to
+obtain phase image should be considered as a success and worth to be
+published. Again, to now, nobody was able to achieve this. And, it is not
+just “an other type of grating arrangement”. We tried to explain that our
+suggestion  allows to perform phase contrast imaging at really high
+energies, i.e., this might be “THE” arrangement.
 
-\begin{reviewerquote}
-    how can an improvement from 5\% (device reported here) to 14\% (current best technology) reaching one order of magnitude, "easily"?
-\end{reviewerquote}
+Referee 3: “The claim of potential having an order of magnitude decrease in
+the scanning time is not supported by their own argument. If it is indeed
+limited by the visibility of the grating, how can an improvement from 5%
+(device reported here) to 14% (current best technology) reaching one order
+of magnitude, "easily”?
 
-This is because, as explained in the methods section, some smaller section
-of our current gratings already have a visibility of \SI{14}{\percent}. This
-means it is almost three times as good as the average, and since the
+Our reply: “This is because, as explained in the methods section, some
+smaller section of our current gratings already have a visibility of 14 %.
+This means it is almost three times as good as the average, and since the
 signal-to-noise ratio drops with the square root of the exposure time, but
 proportionally to the visibility, we claim that improving the visibility by
-a factor of three allows us to shorten the exposure time by a factor of
-nine.
+a factor of three allows us to shorten the exposure time by a factor of nine
+(*As Zhentian suggested, please add here a reference..."
 
-\begin{reviewerquote}
-    The fabrication of the grating is not described specifically, other than
-    saying ``Grating design and fabrication is nonstandard and involves a
-    complex mask design'' with a reference to a fabrication company.
-\end{reviewerquote}
+Referee 3: "Even with one order of magnitude improvement, could they obtain
+an image with scanning at a speed fast enough to match the desired
+motion-free imaging? “
 
-The fabrication through lithography and electroplating is not the main topic
-of this manuscript, hence it is only cited in 22, 23, 24. The mask design
-was carried out by MicroWorks GmbH, but it is a very technical detail that
-we think bears no impact on the reproducibility of the experiment: any
-design that reliably builds the described circularly arranged pattern will
-produce usable gratings.
+Our reply: "The Reviewer should agree that if we were already able to do
+this, the focus and the cut of our publication would be completely
+different. Namely, we would be already there were we are aiming at: phase
+contrast imaging at high-energy, on compact systems, fast and, ideally, with
+same or lower dose. We can only hypothesize that, with the suggested grating
+design, there are no indications against reaching the theoretical maximal
+visibility one might expect at 100 keV. This would be physically the best
+result achievable. If, in that case, the hardware around the gratings will
+be carefully selected, we do not see why we should not be able to acquire
+tomographic slices with speed as present, absorption-based systems."
 
-\begin{reviewerquote}
-    The SEM image on a selected portion of a grating already shows a rather
-    poor quality placement of \SI{}{\micro\meter} size structures, no mention about
-    how the precision of these structure could affect the imaging or the
-    phase retrieval.
-\end{reviewerquote}
+Referee 3: "The authors argued (in their reply) that they can increase the
+acquisition efficiency by stacking the grating. In this case, there will be
+200 such devices needed to be stacked to cover a 2 cm wide area, which they
+have to consider the curvature in this direction as well. At the same time
+they argued that scanning a small beam (a line illumination in this case) is
+better than full field imaging. They quote a commercial system claiming
+reduction of dose which is likely, as pointed out by the author, due to the
+strongly collimation, therefore, is irrelevant to the comparison.”
 
-We mention in the manuscript that these irregularities are responsible for the limited
-visibility of the interferometer, and the connection of this value to the signal-to-noise
-ratio in the images.
+Our reply: The dose argument between scanning, highly collimated systems
+(Philips Microdose) versus others, based on full-area imaging, is not
+irrelevant, as this is one of the major selling arguments for the low-dose
+Philips systems. Therefore, if we combine a series of collimated, fan beams
+with our gratings geometry and scan them to cover a larger area, we will
+indeed have less dose delivered to the specimen/patient compared to a
+cone-beam approach, requiring a full illumination of the sample. Covering a
+2cm wide area in one direction would indeed be a challenge, we agree. The
+question is whether we would need to really cover a 2cm wide area or if we
+could obtain acceptable results with less (while scanning longer). We also
+have to consider the size of the pixel we are aiming for, which might be
+slightly larger than 100 microns, at least for a human CT system.
 
-\bibliography{library}
-\bibliographystyle{plain}
+Referee 3: “The fabrication of the grating is not described specifically,
+other than saying "Grating design and fabrication is nonstandard and
+involves a complex mask design" with a reference to a fabrication company.
+It is not likely one can follow the actual process with just these
+information.
+
+Our reply: “The fabrication through lithography and electroplating is not
+the main topic of this manuscript, hence it is only cited in 22, 23, 24. The
+mask design was carried out by MicroWorks GmbH, but it is a very technical
+detail that we think bears no impact on the reproducibility of the
+experiment: any design that reliably builds the described circularly
+arranged pattern will produce usable gratings"
+
+Referee 3: "The SEM image on a selected portion of a grating already shows a
+rather poor quality placement of um size structures, no mention about how
+the precision of these structure could affect the imaging or the phase
+retrieval."
+
+Our reply: “We mention in the manuscript that these irregularities are
+responsible for the limited visibility of the interferometer, and the
+connection of this value to the signal-to-noise ratio in the images."
+
+Referee 3: “In terms of the innovation in the arrangement the grating in the
+"edge-on" fashion, Ref. 25 indeed reported a similar arrangement to overcome
+the aspect ratio limitation. As to the adoption of a curved structures, it
+was also proposed in the fabrication of multilayer Laue lens to deal with
+the similar problem by tilting, wedging or curving the nanostructures.
+Therefore, the work indeed puts these ingredients together to realize the
+device, but does not reach high innovation level by applying it to a device
+at different, actually easier, length scale"
+
+Our reply: “We do not claim to have reached a high-innovation level with our
+suggested grating arrangement. But we present  phase contrast images at 100
+keV on a compact system. To the best of our knowledge this is novel and, as
+we tried to explain, could have a huge impact.”
+
+Referee 3: “With these observations, this referee argues that this paper
+does not meet the high scientific or innovation value of Scientific Reports.
+The presentation of the results is not rigorous which is not likely be
+corrected without much more investigation to build a better publishable
+case. The rebuttal did not address the main concern of the last review,
+therefore, this referee does not consider this work after revision
+publishable for Scientific Reports.”
+
+Our reply: “We hope to have addressed in our present reply the major
+concerns of the reviewer. We tried to clarify where we see our work to be
+novel and where we discuss the potential benefits of our approach. The
+generation of a phase contrast image at 100 keV using a conventional X-ray
+tube in a compact setup is something which was never done before and that
+intrinsically carries a high potential for medical applications and beyond.
+This is our message and we are convinced of its relevance and impact which
+seems to be well matched to the requests of Scientific Reports a journal
+which, to the best of our knowledge, has no absolute novelty criterion as a
+pre-requisited for a manuscript to be eligible for publication."
 \end{document}

### 2014-04-14 point_by_point_response.tex
matteos merge of marcos and zhentians comments

--- 2014-04-14 point_by_point_response.tex
@@
-%        File: point_by_point_response.tex
-%     Created: Wed Oct 23 05:00 PM 2013 C
-% Last Change: Wed Oct 23 05:00 PM 2013 C
+%        File: point_by_point_response.tex Created: Wed Oct 23 05:00 PM 2013
+%        C Last Change: Wed Oct 23 05:00 PM 2013 C
 %
@@
 
-\DeclareSIUnit{\voltpeak}{Vp}
-\newcommand{\reviewer}[1]{\emph{#1}}
+\DeclareSIUnit{\voltpeak}{Vp} \newcommand{\reviewer}[1]{\emph{#1}}
 \newenvironment{reviewerquote}{\begin{quote}\itshape}{\end{quote}}
 
-\title{Response to reviewer \#3}
+\title{Response to the reviewer}
 \author{Revised manuscript SREP-13-06290}
@@
 
-The authors obviously share most of the concerns raised by the reviewer, but
-there has been some misunderstanding on our side on the main points raised
-with his or her latest comments.
-We are confident we can thoroughly address them here.
-
-The most important issue is
+We would like to thank reviewer \#3 for the detailed feedback on our
+latest revision. We actually share most of his or her concerns but we also see
+that there have been some misunderstanding on our side on the main points
+raised by his or her latest comments. We would like to address them in the
+following.
 
 \begin{reviewerquote}
-    this referee questioned if the photon energy (not being high enough) and
-    the distance (not being short enough) between detector and specimen, are
-    the key barriers to the translation of grating base phase contrast
-    radiology to clinic. The major barrier prevent the phase contrast
-    imaging methods, re-invented more than 20 years ago with the birth of
-    new synchrotron facility, to be transfer away from synchrotron and to
-    make an impact to clinical application at this moment, is the long
-    exposure time required to obtained the phase information by either high
-    quality sources (in-line) or treatment to the exit waves. Talbot-Lau
-    method promises phase contrast using conventional X-ray sources by
-    slotting the large source into small ones which could potentially enable
-    the phase retrieval. However, the requirement of scanning the gratings,
-    in the case reported here (24 steps), inevitably increases the dose as
-    well as the image acquisition time which put this technique only in the
-    research laboratory at the moment. [\ldots] In the long list of "major
-    players" and with all their effort contributing to the international
-    conferences, is there any one ready to commit this technology as their
-    product roadmaps? This work therefore promises a potential benefit on a
-    potential technique which is certainly valuable from the instrumentation
-    point of view and not likely to generate much interest of readers of
-    Scientific Reports.
+It is disappointing that the authors misinterpreted the
+questions and the arguments this referee raised against the major claims of
+this work. This referee did not say: "there is no need to increase the
+energy to \SI{100}{\kilo\eV} in order to translate this technology to clinic" but
+rather question that is not the major factor. This referee did not
+"acknowledge(ing) that an increase to \SI{60}{\kilo\eV} would be good for mammography",
+even though it could be. The main point of the argument is if the
+contribution made by this work important or significant. The conclusion of
+the first review was not enough for a journal cover all different areas of
+basic science. It is probably not even sufficient to attract to readers in
+the same research area of X-ray imaging. The authors reply did not change
+this concern by quoting an "improvement" of increasing photon energy to 60
+keV for mammography, or to higher photon energy in general for radiology in
+general, a well-established and widely implemented for human health care for
+decades.
+
+Specifically, this referee questioned if the photon energy (not
+being high enough) and the distance (not being short enough) between
+detector and specimen, are the key barriers to the translation of grating
+base phase contrast radiology to clinic. The major barrier prevent the phase
+contrast imaging methods, re-invented more than 20 years ago with the birth
+of new synchrotron facility, to be transfer away from synchrotron and to
+make an impact to clinical application at this moment, is the long exposure
+time required to obtained the phase information by either high quality
+sources (in-line) or treatment to the exit waves. Talbot-Lau method promises
+phase contrast using conventional X-ray sources by slotting the large source
+into small ones which could potentially enable the phase retrieval. However,
+the requirement of scanning the gratings, in the case reported here (24
+steps), inevitably increases the dose as well as the image acquisition time
+which put this technique only in the research laboratory at the moment.
 \end{reviewerquote}
+
+Apparently, we have misinterpreted the message of reviewer \#3
+and we thank him or her for the effort in clarifying the comments. In the
+first part of the argumentations, reviewer \#3 questions whether our
+contribution is ``important of significant''. This is a remark which in
+principle can be made to any scientific contribution, independently to its
+degree of novelty, difficulty or outreach. It has a strong subjective
+component, as demonstrated by the fact that two others reviewers found our
+work more than worth to be published in Scientific Reports while reviewer \#3 still has
+several concerns. Therefore, we would like to reiterate here that our work
+is a step towards the implementation of phase contrast imaging on clinical
+systems which we believe might contribute to improve image contrast while
+keeping the dose under reasonable control. Those systems are compact and are
+operated at high energies, or at least at energies much higher than those
+that have been used for any phase-contrast experiment so far to the best of
+our knowledge. We are not claiming that we found the ultimate solution to
+it, but we present an experimental that addresses to address two major concerns
+(high energy and compactness) which are presently limiting the broad
+application of phase contrast imaging outside the synchrotron community.
 
@@
 Talbot-Lau interferometer was shown by the company at the SPIE
-2014 conference\cite{Roessl2014}. Moreover, clinical trials are currently
-ongoing on patients and healthy volunteers in Japan with a Talbot-Lau interferometer
+2014 conference\cite{Roessl2014,Roessl06032014}. Moreover, clinical trials are currently
+ongoing on patients and healthy volunteers in the hospital of the Saitama
+Medical University with a Talbot-Lau interferometer
 developed as a collaboration between the University of Tohoku and Konica
@@
 while we could claim a successful design and operation of the machine, we
-could conclude at this stage that we can have a high imaging quality with
+cannot conclude at this stage that we can have a high imaging quality with
 clinically compatible exposures.
@@
 \begin{reviewerquote}
-     The efforts are trying to "improve", if it is indeed an improvement, a
-     technology (the grating base phase contrast radiology) that is
-     interesting only for its promised clinical application which otherwise
-     offers no fundamental innovation for the phase retrieval scheme in
-     X-ray imaging (it took advantage of a known theory in optics to shorter
-     wavelength).
+This referee knows and agree that the radiation dose is critical
+for medical application, but that was exactly where the usefulness of this
+work is quested. It is well accepted that no new X-ray imaging technology is
+likely be implemented for clinic with dose penalties. There is even more
+fundamental question on if the phase information can really benefit clinical
+diagnosis even at the same dose. Instead of tackling the main challenges on
+reducing the scanning time or on demonstrating that phase contrast indeed
+give better visibility at the same dose than those without phase contrast on
+critical applications such as for medical imaging, device inspection and
+security inspection.
 \end{reviewerquote}
-The same comment applies to the whole field of grating interferometry, as the
-theory in optics is known since the 19th century, although at the time it
-was only applied to longer wavelengths. We would like to point out again
-that the promised clinical applications are coming true, and that the
-realization of this experiment had its remarkable challenges, despite being
-known in theory.
+
+Clinical relevance of phase contrast is a fundamental question
+and we addressed this in several works, specifically on mammography,
+published elsewhere (InvRad 1, InvRad 2, NatComm). We are very well aware
+about the importance of assessing the advantages of phase contrast imaging
+with respect to existing diagnostic procedures, in particular when dealing
+with dose issues. However, the main subject of the present manuscript is
+different and addresses a very practical aspect: we will not even be able to
+discuss about clinical relevance of phase contrast if we cannot operate
+phase contrast in a clinical environment at all. With our work we want to
+show a possible solution to implement phase contrast imaging in clinics and
+addressing high energies and compact systems seem to us to be two
+fundamental points.
 
 \begin{reviewerquote}
-there is no mention about the exact photon energy or range actually used.
-Referring to manufactures data and provide a few more words than ``designed
-energy of 100 keV'' would be more quantitative.
+suggested secondary problems, such as photon energy and the
+total dimension requirement for the instrument are targeted. The efforts are
+trying to "improve", if it is indeed an improvement, a technology (the
+grating base phase contrast radiology) that is interesting only for its
+promised clinical application which otherwise offers no fundamental
+innovation for the phase retrieval scheme in X-ray imaging (it took
+advantage of a known theory in optics to shorter wavelength).
+\end{reviewerquote}
+
+We do not believe that photon energy and total dimension
+requirements are secondary problems. As mentioned before, the penetration
+power of the probing radiation is rather a primary issue as we need
+sufficient photon statistics to be generated after penetrating a whole human
+body in order to measure a signal, whether we
+perform absorption or phase-contrast imaging. The comments on whether the phase
+retrieval procedure is innovative or not could actually be extended to the
+whole field of grating interferometry, as the theory in optics is known
+since the 19th century, although at the time it was only applied to longer
+wavelengths. We would like to point out again that the promised clinical
+applications are coming true, and that the realization of this experiment
+had its remarkable challenges, despite being known in theory.
+
+\begin{reviewerquote}
+Although Scientific Reports requests evaluation on the
+scientific rigorousness, over claiming the potential on clinical, device and
+homeland security applications is not rigorous. The hastiness of the
+presentation does not make their work rigorous, either. There is no analysis
+presented on the only image result, other than just pointing out the
+differential phase effect and merging images of different contrast. The
+authors argued that the reduced visibility in the attenuation contrast is
+due to the stronger X-ray hardening effect than that of phase contrast. This
+cannot be correctly evaluated by the referees and readers without knowing
+the size (along to the beam direction) of the structure of the chip,
+including the solders and resistors, and the absolute gray scale of those
+images. Without giving detailed analysis of the contrast on a set of poor
+quality images, and perhaps compare them with lower, say \SI{80}{\kilo\eV} photons, it
+is not convincing that the work does indeed improve the imaging quality of
+visibility for their targeted applications.
+\end{reviewerquote}
+
+It is true that the current data are not sufficient to claim an improvement
+on imaging quality or sensitivity on details in
+general, which is why we do not draw such conclusions in the paper, as the
+reviewer points out. However, we can already point out that the only
+previously published system running on an X-ray tube~\cite{:/content/aip/journal/rsi/80/5/10.1063/1.3127712}, also
+cited in the manuscript, reported a
+visibility of only~\SI{3}{\percent}, hence our system is already performing
+much better than that. We also note once more that comparisons with
+synchrotron sources are completely out of the question since the
+monochromaticity, brilliance and coherence of third generation synchrotrons
+have a great influence on image quality but are impossible to match on a
+laboratory source, and cannot obviously be deployed on a large scale.
+
+\begin{reviewerquote}
+There are also other flaws of this presentation, which were not
+pointed out in the first round reviewer's report. First of all, there is no
+mention about the exact photon energy or range actually used. Referring to
+manufactures data and provide a few more words than "designed energy of 100
+keV" would be more quantitative. The accelerating energy and photon energy
+are used in a confusion fashion of kV, kVp and keV for non-specialists. If
+the average photon energy is~\SI{100}{\kilo\eV} then the author must demonstrate
+significant difference in terms of the image quality between previous
+reports of 82keV and~\SI{60}{\kilo\eV} using synchrotron and Talbot-Lau methods. If
+photon energy is one of the major claim of advantage of this paper, the
+authors cannot escape this comparison by just saying they are done with
+synchrotron or by other type of grating arrangements.
 \end{reviewerquote}
@@
 current have been added to the manuscript. The energy range is not changed
-afterwards by any means, so this is indeed the full
+afterwards by any means, so this is indeed the full                                                   e
 information needed to reproduce the experiment on any similar generator.
@@
 precise statement.
-
-The units for the energy of the
-photons were checked once more, and the authors could not find any
-occurrence where they are confused or incorrectly used, as suggested by the
-reviewer.
+Concerning the comparison with synchrotron experiments, we think
+that at this stage of the development, it should be sufficient to show that
+we can generate phase contrast images at~\SI{100}{\kilo\eV} on a conventional source
+and to provide the discussion the way and extent we did. Again, the differences
+between a synchrotron and a tube-based experiment are so big that the fact
+already that we were able to obtain phase image should be considered as a
+success and worth to be
+published. Again, to now, nobody was able to achieve this.
+The authors do not agree that this is ``just another type of grating
+arrangement'': the traditional method used up to now in grating
+interferometers (face-on illumination) simply makes fabricating the aspect
+ratios needed for high energies impossible. Moreover, it seems unlikely that
+the electroplating techniques can improve by one order of magnitude in the
+near future.
+Hence, the suggested arrangement this might be the \emph{only} arrangement
+that allows grating interferometry on this energy range.
 
 \begin{reviewerquote}
-    how can an improvement from 5\% (device reported here) to 14\% (current best technology) reaching one order of magnitude, "easily"?
+The claim of potential having an order of magnitude decrease in
+the scanning time is not supported by their own argument. If it is indeed
+limited by the visibility of the grating, how can an improvement from 5\%
+(device reported here) to 14\% (current best technology) reaching one order
+of magnitude, "easily”? 
 \end{reviewerquote}
 
-This is because, as explained in the methods section and reference 33, some smaller section
-of our current gratings already have a visibility of \SI{14}{\percent}. This
-means it is almost three times as good as the average, and since the
+This is because, as explained in the methods section, some
+smaller section of our current gratings already have a visibility
+of~\SI{14}{\percent}. 
+This means it is almost three times as good as the average, and since the
 signal-to-noise ratio drops with the square root of the exposure time, but
@@
 a factor of three allows us to shorten the exposure time by a factor of
-nine.
+nine~\cite{Raupach2011}.
+Note that this is not the current best technology
+available in theory, but what we already have in the first generation of
+gratings.
 
 \begin{reviewerquote}
-    The fabrication of the grating is not described specifically, other than
-    saying ``Grating design and fabrication is nonstandard and involves a
-    complex mask design'' with a reference to a fabrication company.
+Even with one order of magnitude improvement, could they obtain
+an image with scanning at a speed fast enough to match the desired
+motion-free imaging?
 \end{reviewerquote}
 
-The fabrication through lithography and electroplating is not the main topic
-of this manuscript, hence it is only cited in 22, 23, 24. The mask design
-was carried out by MicroWorks GmbH, but it is a very technical detail that
-we think bears no impact on the reproducibility of the experiment: any
-design that reliably builds the described circularly arranged pattern will
-produce usable gratings.
+The reviewer should agree that if we were already able to do
+this, the focus and the cut of our publication would be completely
+different. Namely, we would be already where we are aiming at:
+phase-contrast imaging at high energy, on compact systems, fast and,
+ideally, with the 
+same or lower dose. We can only hypothesize that, with the suggested grating
+design, there are no indications against reaching the theoretical maximal
+visibility one might expect at~\SI{100}{\kilo\eV}. This would be physically the best
+result achievable. If, in that case, the hardware around the gratings will
+be carefully selected, we do not see why we should not be able to acquire
+tomographic slices with the same speed as present, absorption-based systems.
 
 \begin{reviewerquote}
-    The SEM image on a selected portion of a grating already shows a rather
-    poor quality placement of \SI{}{\micro\meter} size structures, no mention about
-    how the precision of these structure could affect the imaging or the
-    phase retrieval.
+The authors argued (in their reply) that they can increase the
+acquisition efficiency by stacking the grating. In this case, there will be
+200 such devices needed to be stacked to cover a 2 cm wide area, which they
+have to consider the curvature in this direction as well. At the same time
+they argued that scanning a small beam (a line illumination in this case) is
+better than full field imaging. They quote a commercial system claiming
+reduction of dose which is likely, as pointed out by the author, due to the
+strongly collimation, therefore, is irrelevant to the comparison.
 \end{reviewerquote}
 
-We mention in the manuscript that these irregularities are responsible for the limited
-visibility of the interferometer, and the connection of this value to the signal-to-noise
-ratio in the images.
+The dose argument between scanning, highly collimated systems
+(Philips MicroDose) versus others, based on full-area imaging, is not
+irrelevant, as this is one of the major selling arguments for the low-dose
+Philips systems. Therefore, if we combine a series of collimated, fan beams
+with our gratings geometry and scan them to cover a larger area, we will
+indeed have less dose delivered to the specimen/patient compared to a
+cone-beam approach, requiring a full illumination of the sample. Covering a
+\SI{2}{\centi\meter} wide area in one direction would indeed be a challenge, we agree. The
+question is whether we would need to really cover a \SI{2}{\centi\meter} wide area or if we
+could obtain acceptable results with less (while scanning longer). We also
+have to consider the size of the pixel we are aiming for, which might be
+larger than \SI{100}{\micro\meter}, at least for a human CT system.
 
-\bibliography{library}
-\bibliographystyle{plain}
+\begin{reviewerquote}
+The fabrication of the grating is not described specifically,
+other than saying "Grating design and fabrication is nonstandard and
+involves a complex mask design" with a reference to a fabrication company.
+It is not likely one can follow the actual process with just these
+information. 
+\end{reviewerquote}
+
+The fabrication through lithography and electroplating is not
+the main topic of this manuscript, hence it is only cited in 22, 23, 24. The
+mask design was indeed carried out by MicroWorks GmbH, but it is a very technical
+detail that we think bears no impact on the reproducibility of the
+experiment: any design that reliably builds the described circularly
+arranged pattern will produce usable gratings.
+
+\begin{reviewerquote}
+The SEM image on a selected portion of a grating already shows a
+rather poor quality placement of um size structures, no mention about how
+the precision of these structure could affect the imaging or the phase
+retrieval.
+\end{reviewerquote}
+
+We mention in the manuscript that these irregularities are
+responsible for the limited visibility of the interferometer, and the
+connection of this value to the signal-to-noise ratio in the
+images~\cite{Raupach2011}.
+
+\begin{reviewerquote}
+In terms of the innovation in the arrangement the grating in the
+"edge-on" fashion, Ref. 25 indeed reported a similar arrangement to overcome
+the aspect ratio limitation. As to the adoption of a curved structures, it
+was also proposed in the fabrication of multilayer Laue lens to deal with
+the similar problem by tilting, wedging or curving the nanostructures.
+Therefore, the work indeed puts these ingredients together to realize the
+device, but does not reach high innovation level by applying it to a device
+at different, actually easier, length scale
+\end{reviewerquote}
+
+We do not claim that the
+suggested grating arrangement is completely unheard of, since we even
+provide specific references to previous similar ideas. But we present  phase
+contrast images at~\SI{100}{\kilo\eV}
+on a compact system. To the best of our knowledge this is novel and, as
+we tried to explain, could have a big impact.
+
+\begin{reviewerquote}
+With these observations, this referee argues that this paper
+does not meet the high scientific or innovation value of Scientific Reports.
+The presentation of the results is not rigorous which is not likely be
+corrected without much more investigation to build a better publishable
+case. The rebuttal did not address the main concern of the last review,
+therefore, this referee does not consider this work after revision
+publishable for Scientific Reports.
+\end{reviewerquote}
+
+We hope to have addressed in our present reply the
+concerns of the reviewer. We tried to clarify where we see our work to be
+novel and where we discuss the potential benefits of our approach. While
+lower energy phase-contrast systems are now entering hospitals, the
+generation of a phase-contrast image at~\SI{100}{\kilo\eV} using a conventional X-ray
+tube in a compact setup is something which was never done before and that
+intrinsically carries a high potential for medical applications and beyond.
+This is our message and we are convinced of its relevance and impact which
+seems to be well matched to the requests of Scientific Reports: a journal
+which, to the best of our knowledge, has no absolute novelty criterion as a
+prerequisite for a manuscript to be eligible for publication.
 \end{document}

### 2014-04-14 point_by_point_response.tex
rearranged the arguments and fixed references

@@
 Apparently, we have misinterpreted the message of reviewer \#3
-and we thank him or her for the effort in clarifying the comments. In the
-first part of the argumentations, reviewer \#3 questions whether our
-contribution is ``important of significant''. This is a remark which in
-principle can be made to any scientific contribution, independently to its
-degree of novelty, difficulty or outreach. It has a strong subjective
-component, as demonstrated by the fact that two others reviewers found our
-work more than worth to be published in Scientific Reports while reviewer \#3 still has
-several concerns. Therefore, we would like to reiterate here that our work
-is a step towards the implementation of phase contrast imaging on clinical
-systems which we believe might contribute to improve image contrast while
-keeping the dose under reasonable control. Those systems are compact and are
-operated at high energies, or at least at energies much higher than those
-that have been used for any phase-contrast experiment so far to the best of
-our knowledge. We are not claiming that we found the ultimate solution to
-it, but we present an experimental that addresses to address two major concerns
-(high energy and compactness) which are presently limiting the broad
-application of phase contrast imaging outside the synchrotron community.
+and we thank him or her for the effort in clarifying the comments.
 
@@
 This is why we think that, besides reduction of dose and exposure times for
-existing setups, the exploration of a new energy range is a fundamental
+existing setups, which was very successful in the last years, the
+exploration of a new energy range is also a fundamental
 research topic. Indeed, up to now, no system in the world was able to
@@
 elements, which we could overcome.
+
+In the first part of the argumentations, reviewer \#3 questions whether our
+contribution is ``important of significant''. This is a remark which in
+principle can be made to any scientific contribution, independently to its
+degree of novelty, difficulty or outreach. It has a strong subjective
+component, as demonstrated by the fact that two others reviewers found our
+work more than worth to be published in Scientific Reports while reviewer \#3 still has
+several concerns. Therefore, we would like to reiterate here that our work
+is a step towards the implementation of phase contrast imaging on clinical
+systems which we believe might contribute to improve image contrast while
+keeping the dose under reasonable control. Those systems are compact and are
+operated at high energies, or at least at energies much higher than those
+that have been used for any phase-contrast experiment so far to the best of
+our knowledge. We are not claiming that we found the ultimate solution to
+it, but we present an experimental that addresses to address two major concerns
+(high energy and compactness) which are presently limiting the broad
+application of phase contrast imaging outside the synchrotron community.
 
@@
 and we addressed this in several works, specifically on mammography,
-published elsewhere (InvRad 1, InvRad 2, NatComm). We are very well aware
+published elsewhere~\cite{Stampanoni2011,Donath2010a,Wang2014}. We are very well aware
 about the importance of assessing the advantages of phase contrast imaging
@@
 requirements are secondary problems. As mentioned before, the penetration
-power of the probing radiation is rather a primary issue as we need
+power of the probing radiation is rather a primary issue since we need
 sufficient photon statistics to be generated after penetrating a whole human
-body in order to measure a signal, whether we
-perform absorption or phase-contrast imaging. The comments on whether the phase
+body, whether we
+perform absorption or phase-contrast imaging. Moreover, some clinical
+applications are not only promised, but are actually coming true as shown
+above.
+
+The comments on whether the phase
 retrieval procedure is innovative or not could actually be extended to the
@@
 general, which is why we do not draw such conclusions in the paper, as the
-reviewer points out. However, we can already point out that the only
-previously published system running on an X-ray tube~\cite{:/content/aip/journal/rsi/80/5/10.1063/1.3127712}, also
+reviewer points out. However, we can already claim that the only
+previously published similar system running on an X-ray tube
+at a design energy of~\SI{60}{\kilo\eV}~\cite{:/content/aip/journal/rsi/80/5/10.1063/1.3127712}, also
 cited in the manuscript, reported a
 visibility of only~\SI{3}{\percent}, hence our system is already performing
-much better than that. We also note once more that comparisons with
+much better. We also note once more that comparisons with
 synchrotron sources are completely out of the question since the
@@
 current have been added to the manuscript. The energy range is not changed
-afterwards by any means, so this is indeed the full                                                   e
+afterwards by any means, so this is indeed the full
 information needed to reproduce the experiment on any similar generator.
@@
 precise statement.
+
+The units for the energy of the
+photons and the voltage of the source were checked once more, and the authors could not find any
+occurrence where they are confused or incorrectly used, as suggested by the
+reviewer. We would of course welcome a more detailed reference to such a mistake, just
+to make sure there are no trivial inconsistencies.
+
 Concerning the comparison with synchrotron experiments, we think
@@
 success and worth to be
-published. Again, to now, nobody was able to achieve this.
+published: up to now, nobody was able to achieve this.
 The authors do not agree that this is ``just another type of grating
@@
 this, the focus and the cut of our publication would be completely
-different. Namely, we would be already where we are aiming at:
-phase-contrast imaging at high energy, on compact systems, fast and,
+different. Namely, we would already be where we are aiming at:
+phase-contrast imaging at high energies, on compact systems, fast and,
 ideally, with the 
@@
 
-The dose argument between scanning, highly collimated systems
-(Philips MicroDose) versus others, based on full-area imaging, is not
-irrelevant, as this is one of the major selling arguments for the low-dose
-Philips systems. Therefore, if we combine a series of collimated, fan beams
-with our gratings geometry and scan them to cover a larger area, we will
-indeed have less dose delivered to the specimen/patient compared to a
-cone-beam approach, requiring a full illumination of the sample. Covering a
-\SI{2}{\centi\meter} wide area in one direction would indeed be a challenge, we agree. The
-question is whether we would need to really cover a \SI{2}{\centi\meter} wide area or if we
-could obtain acceptable results with less (while scanning longer). We also
-have to consider the size of the pixel we are aiming for, which might be
-larger than \SI{100}{\micro\meter}, at least for a human CT system.
+The authors think their argument has been slightly misunderstood in the
+above argument: we suggest that stacking several collimated interferometers
+may be possible,
+while still keeping a scanning procedure, exactly like in the Philips
+MicroDose system.
+This does not imply covering a \SI{2}{\centi\meter} wide area in one direction,
+which we agree would be a challenge. We would rather
+have fewer lines and scan longer.
 
@@
 We do not claim that the
-suggested grating arrangement is completely unheard of, since we even
-provide specific references to previous similar ideas. But we present  phase
-contrast images at~\SI{100}{\kilo\eV}
+suggested grating arrangement is completely unheard of, and we
+provide specific references to similar ideas. The goal is to present
+phase-contrast images at~\SI{100}{\kilo\eV}
 on a compact system. To the best of our knowledge this is novel and, as
@@
 prerequisite for a manuscript to be eligible for publication.
+
+\bibliography{library}
+\bibliographystyle{plain}
 \end{document}

### 2014-04-14 point_by_point_response.tex
marcos minor edits

@@
 However, the reviewer is right when he points out that the work presented in
-the manuscript is still far from applications. At the same time, I think he
+the manuscript is still far from applications. At the same time, we think he
 or she can agree on the fact that sources
@@
 our knowledge. We are not claiming that we found the ultimate solution to
-it, but we present an experimental that addresses to address two major concerns
+it, but we present an experimental solution to address two major concerns
 (high energy and compactness) which are presently limiting the broad

### 2014-04-14 figures/plot_images.py

@@ -1,0 +1,99 @@
+#!/usr/bin/env python
+# encoding: utf-8
+
+"""Nice plot of the three DPC images"""
+
+import os
+import h5py
+from scipy import stats
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+
+
+def draw(input_file_name, height,
+         absorption_image,
+         differential_phase_image,
+         dark_field_image,
+         language="it"):
+    """Display the calculated images with matplotlib."""
+    if language == "it":
+        absorption_image_title = "assorbimento"
+        differential_phase_image_title = "fase differenziale"
+        dark_field_image_title = "riduzione di visibilit\\`a"
+    else:
+        absorption_image_title = "absorption"
+        differential_phase_image_title = "differential phase"
+        dark_field_image_title = "dark field"
+    _, ((abs1_plot, abs2_plot),
+        (phase1_plot, phase2_plot),
+        (df1_plot, df2_plot)) = plt.subplots(
+        3, 2, sharex=True, figsize=(4.6, height), dpi=300)
+    min_x = 500
+    max_x = 700
+    min_y = 50
+    max_y = 150
+    abs1 = abs1_plot.imshow(absorption_image,
+                            cmap=plt.cm.Greys, aspect='auto')
+    limits = stats.mstats.mquantiles(absorption_image,
+                                     prob=[0.02, 0.98])
+    abs2 = abs2_plot.imshow(
+        absorption_image[min_x:max_x, min_y:max_y],
+        cmap=plt.cm.Greys, aspect='auto')
+    abs1.set_clim(*limits)
+    abs1_plot.axis("off")
+    abs1_plot.set_title(absorption_image_title, size="medium")
+    phase1 = phase1_plot.imshow(differential_phase_image)
+    phase2 = phase2_plot.imshow(
+        differential_phase_image[min_x:max_x, min_y:max_y])
+    limits = stats.mstats.mquantiles(differential_phase_image,
+                                     prob=[0.02, 0.98])
+    #limits = (-3, 3)
+    phase1.set_clim(*limits)
+    phase1_plot.axis("off")
+    phase1_plot.set_title(differential_phase_image_title, size="medium")
+    df1 = df1_plot.imshow(dark_field_image)
+    df2 = df2_plot.imshow(
+        dark_field_image[min_x:max_x, min_y:max_y])
+    df1_plot.set_title(dark_field_image_title, size="medium")
+    df1_plot.axis("off")
[…]

### 2014-04-14 figures/plot_images.py
plot images now plots the chip img from the data

@@ -5,9 +5,29 @@
 
 import os
 import h5py
+import numpy as np
 from scipy import stats
 import matplotlib as mpl
 import matplotlib.pyplot as plt
+
+
+pgf_with_rc_fonts = {
+    "image.origin": "lower",
+    "font.family": "serif",
+    "pgf.rcfonts": False,
+    "ytick.major.pad": 5,
+    "xtick.major.pad": 5,
+    "font.size": 11,
+    "linewidth": 1,
+    "legend.fontsize": "medium",
+    "axes.labelsize": "medium",
+    "axes.titlesize": "medium",
+    "ytick.labelsize": "medium",
+    "xtick.labelsize": "medium",
+    "axes.linewidth": 1,
+}
+
+mpl.rcParams.update(pgf_with_rc_fonts)
 
 
 def draw(input_file_name, height,
@@ -27,41 +47,105 @@ def draw(input_file_name, height,
     _, ((abs1_plot, abs2_plot),
         (phase1_plot, phase2_plot),
         (df1_plot, df2_plot)) = plt.subplots(
-        3, 2, sharex=True, figsize=(4.6, height), dpi=300)
-    min_x = 500
-    max_x = 700
-    min_y = 50
-    max_y = 150
+        3, 2, figsize=(6, height), dpi=300)
+    plt.subplots_adjust(
+        wspace=0.02,
+        hspace=0.02)
+    min_x = 300
+    max_x = 550
+    min_y = 60
+    max_y = 130
     abs1 = abs1_plot.imshow(absorption_image,
-                            cmap=plt.cm.Greys, aspect='auto')
+                            cmap=plt.cm.Greys,
+                            aspect='auto')
+    abs1_plot.add_patch(mpl.patches.Rectangle(
+        (min_x, min_y),
+        max_x - min_x,
+        max_y - min_y,
+        fill=False,
+        edgecolor="r"))
+    diff_image = np.diff(absorption_image[min_y:max_y, min_x:max_x])
+    abs2 = abs2_plot.imshow(
+        diff_image,
+        cmap=plt.cm.Greys, aspect='auto')
+    abs1_plot.set_ylabel(absorption_image_title + "\n(differential)",
+                         size="large")
+    abs1_plot.set_frame_on(False)
+    abs1_plot.axes.yaxis.set_ticks([])
+    abs1_plot.axes.xaxis.set_ticks([])
+    abs2_plot.axes.yaxis.set_ticks([])
+    abs2_plot.axes.xaxis.set_ticks([])
[…]

### 2014-04-15 hedpc.tex
new figure included in text
cover letter from marco

@@
 shift. The interaction contributing to phase shifts is coherent (Rayleigh)
-scattering~\cite[extras={, p.~280}]{Als-Nielsen2011}.
+scattering~\cite{Als-Nielsen2011}.
 
@@
 complementary source of contrast with respect to absorption by providing
-direct access to the electron density~\cite[extras{, p.71}]{Als-Nielsen2011}. Moreover, the
+direct access to the electron density~\cite{Als-Nielsen2011}. Moreover, the
 combination with attenuation enables the determination of the effective
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
+    \includegraphics[width=.5\textwidth]{figures/images_S00075_S00071.eps}
     \caption{Radiographic scan of an electronic chip. The image was acquired

### 2014-04-15 hedpc.tex
spell check

@@
         \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
-        aspect ratio is defined by the ratio of the travelling distance along the
-        grating lines and the period and can be arbitrarily long. In order to maximise
+        aspect ratio is defined by the ratio of the traveling distance along the
+        grating lines and the period and can be arbitrarily long. In order to maximize
         the field of view, the grating structures are aligned on an
-        arc. A \SI{100}{\kilo\eV} setup was realised where the distance
+        arc. A \SI{100}{\kilo\eV} setup was realized where the distance
         between the source and the source grating is \SI{23}{\centi\metre}
@@
 Fast acquisitions are therefore required, in order to keep the images sharp
-and artefact free. As a consequence, compact, efficient imaging systems need
+and artifact free. As a consequence, compact, efficient imaging systems need
 to be developed to provide imaging capabilities at sufficient speed. Our
